### 2019-11-15 index.Rmd
initial repo setup

---
title: "SI: Analysis Scripts Index"
author: "ADD IN AUTHORS"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    css: stylesheet.css
    fig_caption: yes
    number_sections: no
    toc: no
editor_options:
  chunk_output_type: inline
---

<a href="https://github.com/ORGANIZATION/REPOSITORY/"><img style="position: absolute; top: 0; right: 0; border: 0;" src="https://camo.githubusercontent.com/38ef81f8aca64bb9a64448d0d70f1308ef5341ab/68747470733a2f2f73332e616d617a6f6e6177732e636f6d2f6769746875622f726962626f6e732f666f726b6d655f72696768745f6461726b626c75655f3132313632312e706e67" alt="Fork me on GitHub" data-canonical-src="https://s3.amazonaws.com/github/ribbons/forkme_right_darkblue_121621.png"></a>

# - [analysis 1](analysis1.html)

# - [analysis 2](analysis2.html)

# - [analysis 3](analysis3.html)

### 2019-11-15 libs/functions.R

@@ -1,0 +1,80 @@
+# Plotting helper functions -------
+
+#' Figure Theme
+#' 
+#' Theme for figures with frequently used formatting instructions.
+#' @param legend whether to show the legend
+#' @param grid whether to show the grid
+#' @param plot_margin margins for c(top, right, bottom, left) in mm
+#' @param text_size font size for all text on plot 
+#' @param axis_text_size font size for the axes' text (define only if different from text_size)
+#' @param axis_x_rotated whether to rotate the x axis labels
+theme_figure <- function(legend = TRUE, grid = TRUE, plot_margin = c(1, 1, 1, 1), 
+                         text_size = 20, axis_text_size = NULL, axis_x_rotate = 0) {
+  the_theme <- theme_bw() + 
+    theme(text = element_text(size = text_size),
+          plot.background = element_blank(), panel.background = element_blank(),
+          panel.border = element_rect(color="black", size=1), 
+          strip.background = element_rect(color="black", linetype = 1),
+          plot.margin = unit(plot_margin, "mm")
+    )
+  # adjust grid
+  if(!grid)
+    the_theme <- the_theme + theme(panel.grid = element_blank())
+  else
+    the_theme <- the_theme + theme(panel.grid.minor = element_blank())
+  # adjust legend
+  if (!legend)
+    the_theme <- the_theme + theme(legend.position = "none")
+  # overwrite axis text size if provided
+  if (!is.null(axis_text_size))
+    the_theme <- the_theme + 
+      theme(axis.text = element_text(size = axis_text_size)) 
+  # axis rotation
+  if (axis_x_rotate != 0) {
+    the_theme <- the_theme + 
+      theme(axis.text.x = element_text(angle = axis_x_rotate, vjust = 0.5, hjust = 1))
+  }
+  return(the_theme)
+}
+
+#' Latex labeller
+#' 
+#' Latex labeller for ggplot that will interpret latex equations correctly (i.e. anything between $$). 
+#' Works for both the \code{labels} parameter of discrete ggplot2 scales as well as the \code{labeller} of facets.
+latex_labeller <- function(labels, ...) {
+  
+  require("dplyr")
+  require("tidyr")
+  require("purrr")
+  require("latex2exp")
+  
+  # figure out if we're in a scale or facet labeller
+  facet_labels <- is(labels, "data.frame")
[…]

### 2019-11-20 isotope_data_reduction.rmd
data and inital data reduction pipeline

---
title: "Isotope data reduction"
date: "`r Sys.Date()`"
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# global knitting options for code rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Load packages

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
```

This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.

All code chunks that contain a critical step towards the final data (i.e. do more than visualization or a data summary) are marked with `(*)` in the header to make it easier to follow all key steps during interactive use.

# Load data

## Read raw data files (*)

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files, using example data set here
# (this is a reduced data set of mostly standards with just a few example samples)
data_path <- file.path("data", "201911_isotope_data.cf.rds")

# read files
iso_files_raw <- 
  # path to data files
  data_path %>% 
  # read data files in parallel for fast read
  iso_read_continuous_flow(parallel = TRUE) %>%
  # filter out files with read errors (e.g. from aborted analysis)
  iso_filter_files_with_problems()
```

### 2019-11-20 isotope_data_reduction_TEMPLATE.Rmd
data and inital data reduction pipeline

---
title: "Isotope data reduction"
date: "`r Sys.Date()`"
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# global knitting options for code rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Load packages

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
```

This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.

For use as a data processing template, please follow the `Source` link above, download the raw file and adapt as needed. Knitting for stand-alone data analysis works best to `HTML` rather than the in-package default `html_vignette`.

All code chunks that contain a critical step towards the final data (i.e. do more than visualization or a data summary) are marked with `(*)` in the header to make it easier to follow all key steps during interactive use.

# Load data

## Read raw data files (*)

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files, using example data set here
# (this is a reduced data set of mostly standards with just a few example samples)
data_path <- iso_get_processor_example("gc_irms_example_carbon.cf.rds")

# read files
iso_files_raw <- 
  # path to data files
  data_path %>% 
  # read data files in parallel for fast read
  iso_read_continuous_flow(parallel = TRUE) %>%
  # filter out files with read errors (e.g. from aborted analysis)
  iso_filter_files_with_problems()
```

## Process file info & peak table (*)

```{r}
# process file information
iso_files <- iso_files_raw %>% 
  # rename key file info columns
  iso_rename_file_info(id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
  # parse text info into numbers
  iso_parse_file_info(number = Analysis) %>% 
  # process other file information that is specific to the naming conventions
  # of this particular sequence
  iso_mutate_file_info(
    # what is the type of each analysis?
    type = case_when(
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "[Ll]inearity") ~ "lin",
      str_detect(id1, "A5")           ~ "std",
      TRUE                            ~ "sample"
    ),
    # was there seed oxidation?
    seed_oxidation = ifelse(`Seed Oxidation` == "1", "yes", "no"),
    # what was the injection volume based on the AS method name?
    injection_volume = str_extract(`AS Method`, "AS PTV [0-9.]+") %>% 
      parse_number() %>% iso_double_with_units("uL"),
    # what was the concentration? (assuming Preparation = concentration or volume)
    concentration = str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
      parse_number() %>% iso_double_with_units("ng/uL"),
    # or the volume?
    volume = str_extract(Preparation, "[0-9.]+ ?uL") %>% 
      parse_number() %>% iso_double_with_units("uL"),
    # what folder are the data files in? (assuming folder = sequence)
    folder = basename(dirname(file_path))
  ) %>% 
  # add in additional sample metadata (could be any info)
  # note: this would typically be stored in / read from a csv or excel file
  iso_add_file_info(
    tibble::tribble(
      # column names
      ~id1,                           ~sample,          ~fraction,
      # metadata (row-by-row)
      "OG268_CZO-SJER_F1",            "SJER",           "F1",
      "OG271_CZO-CTNA_F1",            "CTNA",           "F1",
      "OG281_CZO-Niwot_Tundra2_F1",   "Niwot_Tundra2",  "F1",
      "OG282_CZO-Niwot_Tundra1_F1",   "Niwot_Tundra1",  "F1"
    ),
    join_by = "id1"
  ) %>% 
  # focus only on the relevant file info, discarding the rest
  iso_select_file_info(
    folder, Analysis, file_datetime, id1, id2, type, sample, 
    seed_oxidation, injection_volume, concentration, volume
  )

# set peak table from vendor data table with default isodat template
iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)
```

## Show file information

```{r}
# display file information
iso_files %>% 
  iso_get_file_info() %>% select(-file_id, -folder) %>% 
  iso_make_units_explicit() %>% knitr::kable()
```

## Example chromatograms

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # select a few analyses (these #s must exist!)
  iso_filter_files(iso_files, Analysis %in% c(2046, 2106, 2107)),
  # select data and aesthetics
  data = c(44), color = id1, panel = Analysis,
  # zoom in on time interval
  time_interval = c(1000, 3200),
  # peak labels for all peaks > 2V
  peak_label = iso_format(rt, d13C, signif = 3),
  peak_label_size = 3,
  peak_label_filter = amp44 > 2000
) +
  # customize resulting ggplot
  theme(legend.position = "bottom")
```

# ON/OFFs

```{r "on_off_chromatograms", fig.width=8, fig.height=4}
# find files with zero in the Identifier 1 field
on_offs <- iso_files %>% iso_filter_files(type == "on_off")

# visualize the on/offs  
iso_plot_continuous_flow_data(on_offs, data = 44, color = id2)
```

## Summary

```{r "on_off_summary", fig.width=6, fig.height=4}
# calculate on/off summary
on_off_summary <- 
  on_offs %>% 
  # retrieve peak table
  iso_get_peak_table(
    select = c(amp44, area44, d13C),
    include_file_info = c(file_datetime, id2)
  ) %>% 
  # summarize information
  group_by(file_datetime, id2) %>% 
  iso_summarize_data_table()

# table
on_off_summary %>% iso_make_units_explicit() %>% knitr::kable(digits = 3)

# plot
on_off_summary %>% 
  # use generic data plot function
  iso_plot_data(
    x = file_datetime, y = `d13C sd`,
    size = `amp44 mean`, color = id2,
    points = TRUE,
    date_labels = "%b %d - %H:%M"
  ) + 
  # customize resulting ggplot
  expand_limits(y = 0) 
```

# Linearity

```{r "linearity_chromatograms", fig.width=8, fig.height=4}
# find files with linearity in the Identifier 1 field
lins <- iso_files %>% iso_filter_files(type == "lin")

# visualize the linearity runs
iso_plot_continuous_flow_data(lins, data = 44, color = format(file_datetime))
```

## Summary

```{r "linearity_summary", fig.width=7, fig.height=5}
# calculate linearity summary
linearity_summary <- 
  lins %>% 
  # retrieve data table
  iso_get_peak_table(
    select = c(amp44, area44, d13C),
    include_file_info = c(file_datetime)
  ) %>% 
  # calculate linearity regression lines
  nest(data = -file_datetime) %>% 
  mutate(
    fit = map(data, ~lm(d13C ~ amp44, data = iso_strip_units(.x))),
    coefs = map(fit, broom::tidy)
  )

# table
linearity_summary %>%
  unnest(coefs) %>%
  select(file_datetime, term, estimate, std.error) %>%
  filter(term == "amp44") %>%
  mutate(
    term = "linearity [permil/V]",
    estimate = signif(estimate, 2),
    std.error = signif(std.error, 1)
  ) %>% 
  knitr::kable(digits = 4)

# plot
linearity_summary %>% 
  unnest(data) %>% 
  # use generic data plot function
  iso_plot_data(
    x = amp44, y = d13C,
    color = format(file_datetime),
    points = TRUE,
    panel = file_datetime,
    geom_smooth(method = "lm")
  )
```

# Samples and Standards

## Load peak maps

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
peak_maps <- 
  tibble::tribble(
    # column names -> defining 2 peak maps, 'std' and 'sample' here
    # but could define an unlimited number of different maps
    ~compound, ~ref_nr, ~`rt:std`,  ~`rt:sample`,
    # peak map data (row-by-row)
    "CO2",			1,		  79,				  79,
    "CO2",			2,	  	178,				178,
    "CO2",			3,	  	278,				278,
    "CO2",			4,	  	377,				377,
    "CO2",			5,	  	477,				477,
    "CO2",			6,	  	576,				576,
    "CO2",			7,	  	676,				676,
    "CO2",			8,	  	775,				775,
    "CO2",			9,	  	875,				875,
    "nC16",			NA,	    1156,				1156,
    "nC17",			NA,    	1280,				1280,
    "nC18",			NA,    	1409,				1409,
    "nC19",			NA,    	1540,				1540,
    "nC20",			NA,    	1670,				1670,
    "nC21",			NA,	    1797,				1797,
    "nC22",			NA,	    1921,				1921,
    "nC23",			NA,	    2040,				2040,
    "nC24",			NA,	    2156,				2156,
    "nC25",			NA,	    2267,				2267,
    "nC26",			NA,	    2375,				2375,
    "nC27",			NA,	    2479,				2479,
    "nC28",			NA,	    2580,				2580,
    "nC29",			NA,	    2674,				2678,
    "nC30",			NA,	    2770,				2773,
    "nC31",			NA,	    NA,				  2863,
    "CO2",			10,	  	3552,				3552,
    "CO2",			11,	  	3592,				3592
  )
peak_maps %>% knitr::kable(digits = 0)
```

## Fetch peak table (*)

```{r}
# identify peaks
peak_table_w_ids <- iso_files %>% 
  # focus on standards and samples only
  iso_filter_files(type %in% c("std", "sample")) %>% 
  # filter out analyses that
  ## a) did not inject
  iso_filter_files(!Analysis %in% c(2031, 2040, 2069, 2098, 2116, 2138)) %>%
  ## b) had double or rogue peaks from mis-injection
  iso_filter_files(!Analysis %in% c(2044, 2132, 2134)) %>% 
  # map peaks
  iso_map_peaks(peak_maps, map_id = type) %>% 
  # peak table
  iso_get_peak_table(include_file_info = everything())
```

## Inspect peak mappings

```{r "example_chromatograms_with_peaks", fig.width = 8, fig.height = 8}
# use same plotting as earlier, except now with peak features added in
iso_files %>% 
  iso_filter_files(Analysis %in% c(2046, 2106, 2107)) %>% 
  iso_plot_continuous_flow_data(
    # select data and aesthetics
    data = 44, color = id1, panel = Analysis,
    # zoom in on time interval
    time_interval = c(1000, 3200),
    # provide our peak table with ids
    peak_table = peak_table_w_ids, 
    # define peak labels, this can be any valid expression
    peak_label = iso_format(id = peak_info, d13C), 
    # specify which labels to show (removing the !is_identified or putting a 
    # restriction by retention time can help a lot with busy chromatograms)
    peak_label_filter = is_identified | !is_identified | is_missing
  )  +
  # customize resulting ggplot
  theme(legend.position = "bottom")
```

## Overview of unclear peak mappings

```{r, eval = FALSE}
# look at missing and unidentified peaks summary (not run during knitting)
# -> check if any of the missing peaks are unexpected (should be there but aren't)
# -> check if any unidentified peaks should be added to the peak maps
# -> check if any ambiguous peaks need clearer peak map retention times
# when in doubt, look at the chromatograms of the problematic files!
# as needed: iterate on peak map update, then peak mapping inspection
peak_table_w_ids %>% 
  iso_get_problematic_peak_mappings() %>% 
  iso_summarize_peak_mappings()
```

# Reference peaks

```{r "ref_peak_variation", fig.width=10, fig.height=4}
# examine variation in the reference peaks
peak_table_w_ids %>% 
  # focus on reference peaks only
  filter(!is.na(ref_nr)) %>% 
  # mark ref peak used for raw delta values (assuming the same in all anlysis)
  mutate(
    ref_info = paste0(ref_nr, ifelse(is_ref == 1, "*", "")) %>% factor() %>% fct_inorder()
  ) %>% 
  # visualize
  iso_plot_ref_peaks(
    # specify the ratios to visualize
    x = Analysis, ratio = `r45/44`, fill = ref_info,
    panel_scales = "fixed"
  ) +
  labs(x = "Analysis", fill = "Reference\npeak")
```

# Analyte peaks

## Select analyte peaks (*)

```{r}
# focus on analyte peaks and calculate useful summary statistics
peak_table_analytes <- peak_table_w_ids %>% 
  # omit reference peaks for further processing (i.e. analyte peaks only)
  filter(is.na(ref_nr)) %>% 
  # for each analysis, calculate a few useful summary statistics
  iso_mutate_peak_table(
    group_by = file_id,
    rel_area = area44 / sum(area44, na.rm = TRUE),
    # calculate mean area for all peaks
    mean_area = mean(area44, na.rm = TRUE),
    # calculate mean area and amplitude for identified peaks
    mean_area_identified = mean(area44[!is.na(compound)], na.rm = TRUE),
    mean_amp_identified = mean(amp44[!is.na(compound)], na.rm = TRUE)
  )
```

## First look

```{r "first_look_sample_and_standard_peaks", fig.width=7, fig.height=6}
peak_table_analytes %>% 
  # focus on identified peaks (comment out this line to see ALL peaks)
  filter(!is.na(compound)) %>% 
  # visualize with convenience function iso_plot_data
  iso_plot_data(
    # choose x and y (multiple y possible)
    x = area44, y = c(amp44, d13C),
    # choose aesthetics
    color = compound, shape = type, label = compound, size = 3,
    # decide what geoms to include
    points = TRUE
  ) +
  # further customize ggplot with a log scale x axis
  scale_x_log10()
```

## Optionally - use interactive plot

```{r, eval=FALSE, fig.width=7, fig.height=6}
# optinally, use an interactive plot to explore your data
# - make sure you install the plotly library --> install.packages("plotly")
# - switch to eval=TRUE in the options of this chunk to include in knit
# - this should work for all plots in this example processing file
library(plotly)
ggplotly(dynamicTicks = TRUE)
```

## Evaluate signal yield

```{r "yield", fig.width=7, fig.height=6}
# evaluate yield
# (only makes sense if both injection volume and concentration are available)
peak_table_analytes %>% 
  # focus on standards
  filter(type == "std") %>% 
  # calculate injection amount
  mutate(injection = iso_double_with_units(
    as.numeric(injection_volume) * as.numeric(concentration), units = "ng")) %>% 
  # visualize
  iso_plot_data(
    # x and y
    x = injection, y = c(mean_area_identified, mean_amp_identified),
    # aesthetics
    color = factor(injection_volume), shape = factor(concentration), 
    size = file_datetime,
    points = TRUE
  ) +
  # modify plot with trendline and axis limits
  geom_smooth(method = "lm", mapping = aes(color = NULL, shape = NULL)) +
  expand_limits(y = 0, x = 0)
```

# Isotope standard values

## Load isotope standards

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
standards <- 
  tibble::tribble(
    ~compound,   ~true_d13C,
    "nC16",			-26.15,
    "nC17",			-31.88,
    "nC18",			-32.70,
    "nC19",			-31.99,
    "nC20",			-33.97,
    "nC21",			-28.83,
    "nC22",			-33.77,
    "nC23",			-33.37,
    "nC24",			-32.13,
    "nC25",			-28.46,
    "nC26",			-32.94,
    "nC27",			-30.49,
    "nC28",			-33.20,
    "nC29",			-29.10,
    "nC30",			-29.84
  ) %>% 
  mutate(
    type = "std", 
    true_d13C = iso_double_with_units(true_d13C, "permil")
  )
standards %>% knitr::kable(digits = 2)
```

## Add isotope standards (*)

```{r}
peak_table_w_stds <- 
  peak_table_analytes %>% 
  iso_add_standards(stds = standards, match_by = c("type", "compound")) 
```

# Calibration

## Single analysis calibration (for QA)

### Generate calibrations

Determine calibrations fits for all individual standard analyses.

```{r}
stds_w_calibs <- peak_table_w_stds %>%
  # focus on standards
  filter(type == "std") %>% 
  # remove unassigned peaks
  iso_remove_problematic_peak_mappings() %>% 
  # prepare for calibration by defining the grouping column(s) 
  iso_prepare_for_calibration(group_by = Analysis) %>% 
  # run calibration
  iso_generate_calibration(model = lm(d13C ~ true_d13C)) %>% 
  # unnest some useful file information for visualization
  iso_get_calibration_data(
    select = c(file_datetime, injection_volume, seed_oxidation, mean_area_identified))

# check for problematic calibrations
stds_w_calibs %>% iso_get_problematic_calibrations() -> problematic.calibs
# View(problematic.calibs)

# move forward only with good calibrations
stds_w_calibs <- stds_w_calibs %>% iso_remove_problematic_calibrations()
```

### Coefficients

```{r "single_analysis_calibration_coefficients", fig.width=7, fig.height=8}
# look at coefficients and summary
stds_w_calibs %>% 
  # unnest calibration parameters
  iso_get_calibration_parameters(
    select_from_coefs = 
      c(term, estimate, SE = std.error, signif),
    select_from_summary = 
      c(fit_R2 = adj.r.squared, fit_RMSD = deviance, residual_df = df.residual)) %>%
  arrange(term) %>% 
  knitr::kable(digits = 4)

# visualize the calibration coefficients
stds_w_calibs %>% 
  # plot calibration parameters
  iso_plot_calibration_parameters(
    # x-axis, could also be e.g. Analysis or file_datetime (also use date_breaks!)
    x = mean_area_identified,
    # aesthetics
    color = seed_oxidation, size = mean_area_identified,
    # highlight RSD threshold
    geom_hline(data = tibble(term = factor("RSD"), threshold = 0.5),
               mapping = aes(yintercept = threshold), linetype = 2)
  ) 
```

### Residuals

```{r "single_analysis_residuals", fig.width=7, fig.height=6}
stds_w_calibs %>% 
  # pull out all peak data to including residuals
  iso_get_calibration_data() %>% 
  # focus on standard peaks
  filter(is_std_peak) %>% 
  # calculate parameters to visualize
  iso_mutate_peak_table(
    group_by = Analysis,
     `Var: residual` = resid,
    `Var: area diff from mean` = 
      iso_double_with_units((area44/mean(area44) - 1) * 100, "%")
  ) %>% 
  # visualize
  iso_plot_data(
    # x and y 
    x = compound, y = starts_with("Var"),
    # grouping and aesthetics
    group = paste(Analysis, calib), color = seed_oxidation, linetype = calib,
    # geoms
    lines = TRUE
  )
```

## Global Calibration with all standards

### Generate calibrations (*)

```{r}
# define a global calibration across all standards
global_calibs <- 
  peak_table_w_stds %>%
  # remove (most) problematic peaks to speed up calibration calculations
  # note: could additionally remove unidentified peaks if they are of no interest
  iso_remove_problematic_peak_mappings(remove_unidentified = FALSE) %>% 
  # prepare for calibration (no grouping to go across all analyses)
  iso_prepare_for_calibration() %>% 
  # run different calibrations
  iso_generate_calibration(
    model = c(
      linear = lm(d13C ~ true_d13C),
      with_area = lm(d13C ~ true_d13C + area44),
      with_area_cross = lm(d13C ~ true_d13C * area44)
    ),
    # specify which peaks to include in the calibration, here:
    # - all std_peaks (this filter should always be included!)
    # - standard peaks between 5 and 100 Vs
    # - only analyses with seed oxidation (same as all the samples)
    use_in_calib = is_std_peak & area44 > iso_double_with_units(5, "Vs") & 
      area44 < iso_double_with_units(100, "Vs") & seed_oxidation == "yes"
  ) %>% 
  iso_remove_problematic_calibrations()
```

### Coefficients

```{r "global_calibration_coefficients", fig.width=7, fig.height=12}
# look at coefficients and summary
global_calibs %>% 
  # unnest calibration parameters
  iso_get_calibration_parameters(
    select_from_coefs = 
      c(term, estimate, SE = std.error, signif),
    select_from_summary = 
      c(fit_R2 = adj.r.squared, fit_RMSD = deviance, residual_df = df.residual)) %>%
  arrange(term) %>% 
  knitr::kable(digits = 4)

# visualize coefficients for the different global calibrations
global_calibs %>% iso_plot_calibration_parameters()
```

### Residuals

```{r "global_calibration_residuals", fig.width=8, fig.height=4}
global_calibs %>% 
  iso_plot_residuals(
    x = compound, group = paste(Analysis, calib), 
    points = FALSE, lines = TRUE,
    trendlines = FALSE, value_ranges = FALSE
  ) 
```

### Apply global calibration (*)

```{r, cache=TRUE}
# note that depending on the number of data points, this may take a while
# for faster calculations, chose calculate_error = FALSE
global_calibs_applied <- 
  global_calibs %>% 
  # which calibration to use? can include multiple if desired to see the result
  # in this case, the area conscious calibrations are not necessary
  filter(calib == "linear") %>% 
  # apply calibration indication what should be calcculated
  iso_apply_calibration(true_d13C, calculate_error = TRUE)

# calibration ranges
global_calibs_with_ranges <-
  global_calibs_applied %>% 
  # evaluate calibration range for the measured area.Vs and predicted d13C
  iso_evaluate_calibration_range(area44, true_d13C_pred)

# show calibration ranges
global_calibs_with_ranges %>% 
  iso_get_calibration_range() %>% 
  iso_remove_list_columns() %>% 
  knitr::kable(d = 2)

# create calibrated peak table
peak_table_calibrated <- global_calibs_with_ranges %>% 
  iso_get_calibration_data()
```

# Evaluation

## Overview

```{r "data_overview", fig.width=7, fig.height=9}
# replicate earlier overview plot but now with the calibrated delta values
# and with a higlight of the calibration ranges and which points are in range
peak_table_calibrated %>% 
  # focus on identified peaks (comment out this line to see ALL peaks)
  filter(!is.na(compound)) %>% 
  # visualize with convenience function iso_plot_data
  iso_plot_data(
    # choose x and y (multiple y possible)
    x = area44, y = true_d13C_pred,
    # choose aesthetics
    color = in_range, shape = type, label = compound, size = 3,
    # decide what geoms to include
    points = TRUE
  ) %>% 
  # highlight calibration range
  iso_mark_calibration_range() +
  # further customize ggplot with a log scale x axis
  scale_x_log10() +
  # legend
  theme(legend.position = "bottom", legend.direction = "vertical")
```

## Standards

```{r "standards", fig.width=7, fig.height=6}
# visualize how standard line up after calibration
peak_table_calibrated %>% 
  # focus on peaks in calibration
  filter(in_calib) %>% 
  # visualize
  iso_plot_data(
    # x and y
    x = true_d13C, y = true_d13C_pred, y_error = true_d13C_pred_se,
    # aesthetics
    color = compound, size = area44,
    # geoms
    points = TRUE,
    # add 1:1 trendline
    geom_abline(slope = 1, intercept = 0)
  ) 
```

## Data

### Isotopic values

```{r "samples", fig.width = 10, fig.height = 7}
# Warning: data outside the calibration range MUST be taken with a
# grain of salt, especially at the low signal area/amplitude end
peak_table_calibrated %>% 
  # focus on samples
  filter(type == "sample") %>% 
  # focus on identified peaks (comment out this line to see ALL peaks)
  # if there's a lot of data, might need to hone in on a few at a time
  filter(!is.na(compound)) %>% 
  # visualize
  iso_plot_data(
    # x and y
    x = sample, y = true_d13C_pred, y_error = true_d13C_pred_se,
    # aesthetics
    color = in_range, size = rel_area, 
    # paneling
    panel = compound, panel_scales = "fixed",
    # geoms
    points = TRUE
  ) %>% 
  # mark calibration range (include optionally)
  iso_mark_calibration_range() +
  # color palette (here example of manual: www.google.com/search?q=color+picker)
  scale_color_manual(
    values = c("#984EA3", "#E41A1C", "#E41A1C", "#377EB8", "#4DAF4A")
  ) +
  # clarify size scale
  scale_size_continuous(breaks = c(0.01, 0.05, 0.1, 0.2, 0.3), 
                        labels = function(x) paste0(100*x, "%")) +
  # plot labels
  labs(x = NULL)
```

### Relative abundances

```{r "abundances", fig.width = 7, fig.height = 6, warning=FALSE}
# visualize relative abundances
peak_table_calibrated %>% 
  # focus on samples
  filter(type == "sample") %>% 
  # focus on identified peaks (comment out this line to see ALL peaks)
  #filter(!is.na(compound)) %>% 
  # visualize
  iso_plot_data(
    # x and y
    x = sample, y = rel_area,
    # aesthetics
    fill = compound,
    # barchart
    geom_bar(stat = "identity")
  ) +
  # scales
  scale_y_continuous(labels = function(x) paste0(100*x, "%"), expand = c(0, 0)) +
  # plot labels
  labs(x = NULL, y = "Relative abundance (by area)")
```

### Summary

```{r}
# generate data summary
peak_data <- 
  peak_table_calibrated %>% 
  # focus on identified peaks in the samples
  filter(type == "sample", !is.na(compound)) %>% 
  select(sample, compound, Analysis, 
         area44, true_d13C_pred, true_d13C_pred_se, in_range) %>% 
  arrange(sample, compound, Analysis)

# summarize replicates
# this example data set does not contain any replicates but typically all
# analyses should in which case a statistical data summary can be useful
peak_data_summary <- 
  peak_data %>% 
  # here: only peaks within the area calibration range are included
  # you have to explicitly decide which peaks you trust if they are out of range
  filter(
    in_range %in% c("in range", "<'true_d13C_pred' range", ">'true_d13C_pred' range")
  ) %>% 
  # summarize for each sample and compound
  group_by(sample, compound) %>% 
  iso_summarize_data_table(area44, true_d13C_pred)

peak_data_summary %>% iso_make_units_explicit() %>% knitr::kable(d = 2)
```

# Final

Final data processing and visualization usually depends on the type of data and the metadata available for contextualization (e.g. core depth, source organism, age, etc.). The relevant metadata can be added easily with `iso_add_file_info()` during the initial data load / file info procesing. Alternatively, just call `iso_add_file_info()` again at this later point or use dplyr's `left_join` directly.

```{r "final_data", fig.width = 7, fig.height = 6}
# @user: add final data processing and plot(s)
```

# Export

```{r}
# export the global calibration with all its information and data to Excel
peak_table_calibrated %>% 
  iso_export_calibration_to_excel(
    filepath = format(Sys.Date(), "%Y%m%d_gc_irms_example_carbon_export.xlsx"),
    # include data summary as an additional useful tab
    `data summary` = peak_data_summary
  )
```

### 2019-12-01 isotope_data_reduction.rmd
first_plot

@@
   # read data files in parallel for fast read
-  iso_read_continuous_flow(parallel = TRUE) %>%
+  iso_read_continuous_flow() %>%
   # filter out files with read errors (e.g. from aborted analysis)
@@
 ```
+
+## Process file info & peak table (*)
+
+```{r}
+# process file information
+iso_files <- iso_files_raw %>% 
+  # rename key file info columns
+  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
+  # parse text info into numbers
+  iso_parse_file_info(number = analysis) %>% 
+  # process other file information that is specific to the naming conventions
+  # of this particular sequence
+  iso_mutate_file_info(
+    # what is the type of each analysis?
+    type = case_when(
+      str_detect(id1, "[Zz]ero")      ~ "on_off",
+      str_detect(id1, "H3")           ~ "H3_factor",
+      str_detect(id1, "F8")           ~ "std",
+      TRUE                            ~ "sample"
+    ),
+    # what was the concentration? (assuming Preparation = concentration or volume)
+    concentration = 
+      ifelse(type == "std",  
+             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
+               parse_number() %>% iso_double_with_units("ng/uL"),
+             NA),
+    # what folder are the data files in? (assuming folder = sequence)
+    folder = basename(dirname(file_path))
+  ) %>% 
+  # focus only on the relevant file info, discarding the rest
+  iso_select_file_info(
+    folder, analysis, file_datetime, id1, type, concentration
+  ) %>% 
+  # add in additional sample metadata (could be any info)
+  # note: this would typically be stored in / read from a csv or excel file
+  iso_add_file_info(
+    readxl::read_excel(file.path("data", "isotopes_metadata.xlsx")),
+    join_by = "id1"
+  )
+
+# set peak table from vendor data table with default isodat template
+iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
+  # convert units from mV to V for amplitudes and area
+  iso_convert_peak_table_units(V = mV, Vs = mVs)
+
+# focus on sample files
+sample_files <- iso_filter_files(iso_files, type == "sample" & analysis > 5651)
+```
+
+## Show file information
+
+```{r}
+# display file information
+iso_files %>% 
+  iso_get_file_info() %>% select(-file_id, -folder) %>% 
+  iso_make_units_explicit() %>% knitr::kable()
+```
+
+## Example chromatograms
+
+```{r "example_chromatograms", fig.width=8, fig.height=8}
+# plot the chromatograms
+iso_plot_continuous_flow_data(
+  # all sample files
+  sample_files,
+  # select data and aesthetics
+  data = c(2), color = id1, panel = analysis,
+  # zoom in on time interval
+  time_interval = c(1000, 3000),
+  # peak labels for all peaks > 2V
+  peak_bounds = TRUE,
+  peak_marker = FALSE,
+  peak_label = iso_format(rt),
+  #peak_label_size = 3,
+  peak_label_filter = analysis == 5685 & amp2 > 1
+) 
+```
+
+# Peak Mapping
+
+```{r}
+# this information is often maintained in a csv or Excel file instead
+# but generated here from scratch for demonstration purposes
+peak_maps <- 
+  readxl::read_excel(file.path("data","isotopes_peak_maps.xlsx"))
+peak_maps %>% knitr::kable(digits = 0)
+
+# identify peaks
+sample_files_w_ids <- sample_files  %>% 
+  # map peaks
+  iso_map_peaks(peak_maps, map_id = type)
+```
+
+## Chromatograms
+
+```{r "sample_chromatograms", fig.width=8, fig.height=8}
+# plot the chromatograms
+iso_plot_continuous_flow_data(
+  # all sample files
+  sample_files_w_ids,
+  # select data and aesthetics
+  data = c(2), color = id1, panel = analysis,
+  # zoom in on time interval
+  time_interval = c(1000, 3000),
+  # peak labels for all peaks > 2V
+  peak_bounds = TRUE,
+  peak_marker = FALSE,
+  peak_label = iso_format(compound, d2H),
+  #peak_label_size = 3,
+  peak_label_filter = compound != "unknown"
+) 
+```
+
+## Data
+
+```{r}
+sample_files_w_ids %>% 
+  iso_get_peak_table(include_file_info = everything()) %>% 
+  filter(compound != "unknown") %>% 
+  mutate(sample_label = iso_format(control, inc_time, with_glu)) %>% 
+  iso_plot_data(
+    x = compound, y = c(area2, d2H), color = sample_label,
+    points = TRUE
+  )
+```

### 2019-12-02 abundance.Rmd
secondcommit

---
title: "Analysis: NAME"
subtitle: "SUBTITLE"
author: "AUTHORS"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    css: stylesheet.css
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(latex2exp)
library(readxl)
library(isoreader)

# source functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))

# set global chunk options for figure output
figure_prefix <- "PREFIX-"
knitr::opts_chunk$set(
  dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path=file.path("figures", figure_prefix))
```

# Load data

```{r}
root <- "data"
all_data <-
  tibble(
    sample = c("a", "b"),
    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

## Show injection details

```{r}
all_data %>% select(-integration_results) %>% unnest(injection_details) %>% 
  knitr::kable()
```

# Analyze data

```{r}
results <- all_data %>% select(-injection_details) %>% unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0)

results %>% 
  filter(!str_detect(`Peak Name`, fixed("?"))) %>% 
  ggplot() +
  aes(`Peak Name`, `Relative Area`) +
  geom_bar(stat = "identity") +
  theme_figure(axis_x_rotate = 90) +
  scale_y_continuous(expand = c(0,0)) +
  facet_wrap(~sample)
```

```{r}
results %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
  geom_bar(stat = "identity")
```

```{r}
results %>% 
  left_join(
    tibble(
      `Peak Name` = c("19:0", "23:0"), 
      group = c("19", "23")
    ), by = "Peak Name"
  ) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = group, label = `Peak Name`) +
  geom_bar(stat = "identity") +
  facet_grid(sample ~ .) +
  theme_figure() +
  scale_y_continuous(expand = c(0, 0))
```

```{r}
library(plotly)
ggplotly(ggplot2::last_plot(), dynamicTicks = TRUE)
```

### 2019-12-07 tsq_data.Rmd
initial commit

--- 2019-12-02 abundance.Rmd
@@
 ```{r}
-results <- all_data %>% select(-injection_details) %>% unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0)
+results <- all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # major compound groups
+  mutate(
+    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
+  )
 
@@
 results %>% 
-  left_join(
-    tibble(
-      `Peak Name` = c("19:0", "23:0"), 
-      group = c("19", "23")
-    ), by = "Peak Name"
-  ) %>% 
   ggplot() +
@@
   facet_grid(sample ~ .) +
-  theme_figure() +
+  theme_figure(legend = TRUE) +
   scale_y_continuous(expand = c(0, 0))
@@
 ```
+
+# export data
+
+```{r}
+results %>% 
+  filter(sample == "a") %>% 
+  mutate(rt = `Retention Time` * 60) %>% 
+  select(group, `Peak Name`, rt, rel_height = `Relative Height`) %>% 
+  mutate(rt = round(rt, 1), rel_height = round(rel_height, 2)) %>%
+  filter(rel_height > 1) %>% 
+  openxlsx::write.xlsx(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
+```

### 2019-12-07 example_R/gc_irms_example.Rmd

---
title: "gc_irms_example"
output: html_document
---

# Set Up, Load packages
```{r}
# restart your R session (this command only works in RStudio)
.rs.restartR()

# installs the development tools package if not yet installed
if(!requireNamespace("devtools", quietly = TRUE)) install.packages("devtools")

# installs the newest version of isoreader and isoprocessor
devtools::install_github("isoverse/isoreader")
devtools::install_github("isoverse/isoprocessor")
```

```{r}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
```

# Load Data
```{r}
# Set file paths to data files, folders or rds collections
# Can be multiple folders or mix of folders/files
# this is reduced data, mostly standards, just a few samples
data_path <- iso_get_processor_example("gc_irms_example_carbon.cf.rds")
```

# Read files, create "raw" iso files
Here we read the continuous flow files in parallel (improves speed) and remove files with problems, such as aborted runs.
```{r}
iso_files_raw <-
  data_path %>% # path to data files
  iso_read_continuous_flow(parallel = TRUE) %>% # read data files in parallel for fast read
  iso_filter_files_with_problems() # filter out files with read errors, such as from aborted analysis

```

# Process File Info and Peak Table
```{r}
# process file information
iso_files <- iso_files_raw %>% 
  # rename key file info columns
  iso_rename_file_info(id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
  # parse text info into numbers
  iso_parse_file_info(number = Analysis) %>% 
  # process other file information that is specific to the naming conventions
  # of this particular sequence
  iso_mutate_file_info(
    # what is the type of each analysis?
    type = case_when(
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "[Ll]inearity") ~ "lin",
      str_detect(id1, "A5")           ~ "std",
      TRUE                            ~ "sample"
    ),
    # was there seed oxidation?
    seed_oxidation = ifelse(`Seed Oxidation` == "1", "yes", "no"),
    # what was the injection volume based on the AS method name?
    injection_volume = str_extract(`AS Method`, "AS PTV [0-9.]+") %>% 
      parse_number() %>% iso_double_with_units("uL"),
    # what was the concentration? (assuming Preparation = concentration or volume)
    concentration = str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
      parse_number() %>% iso_double_with_units("ng/uL"),
    # or the volume?
    volume = str_extract(Preparation, "[0-9.]+ ?uL") %>% 
      parse_number() %>% iso_double_with_units("uL"),
    # what folder are the data files in? (assuming folder = sequence)
    folder = basename(dirname(file_path))
  ) %>% 
  # add in additional sample metadata (could be any info)
  # note: this would typically be stored in / read from a csv or excel file
  iso_add_file_info(
    tibble::tribble(
      # column names
      ~id1,                           ~sample,          ~fraction,
      # metadata (row-by-row)
      "OG268_CZO-SJER_F1",            "SJER",           "F1",
      "OG271_CZO-CTNA_F1",            "CTNA",           "F1",
      "OG281_CZO-Niwot_Tundra2_F1",   "Niwot_Tundra2",  "F1",
      "OG282_CZO-Niwot_Tundra1_F1",   "Niwot_Tundra1",  "F1"
    ),
    join_by = "id1"
  ) %>% 
  # focus only on the relevant file info, discarding the rest
  iso_select_file_info(
    folder, Analysis, file_datetime, id1, id2, type, sample, 
    seed_oxidation, injection_volume, concentration, volume
  )
#> Info: renaming 2 file info column(s) wherever they exist across 45 isofile(s):
#>  - for 44 file(s): 'Identifier 1'->'id1', 'Identifier 2'->'id2'
#>  - for 1 file(s): 'Identifier 1'->'id1'
#> Info: parsing 1 file info columns for 45 data file(s):
#>  - to number: 'Analysis'
#> Info: mutating file info for 45 data file(s)
#> Info: adding new file information ('sample', 'fraction') to 45 data file(s), joining by 'id1'...
#>  - 'id1' join: 4/4 new info rows matched 4/45 data files
#> Info: keeping 12 file info column(s) wherever they exist across 45 isofile(s):
#>  - for 45 file(s): 'file_id', 'folder', 'Analysis', 'file_datetime', 'id1', 'id2', 'type', 'sample', 'seed_oxidation', 'injection_volume', 'concentration', 'volume'

# set peak table from vendor data table with default isodat template
iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)
#> Info: setting peak table from vendor data table with the following renames:
#> - for 45 file(s): 'Nr.'->'peak_nr', 'Is Ref.?'->'is_ref', 'Start'->'rt_start', 'Rt'->'rt', 'End'->'rt_end', 'Ampl 44'->'amp44', 'Ampl 45'->'amp45', 'Ampl 46'->'amp46', 'BGD 44'->'bgrd44_start', 'BGD 45'->'bgrd45_start', 'BGD 46'->'bgrd46_start', 'BGD 44'->'bgrd44_end', 'BGD 45'->'bgrd45_end', 'BGD 46'->'bgrd46_end', 'rIntensity 44'->'area44', 'rIntensity 45'->'area45', 'rIntensity 46'->'area46', 'rR 45CO2/44CO2'->'r45/44', 'rR 46CO2/44CO2'->'r46/44', 'rd 45CO2/44CO2'->'rd45/44', 'rd 46CO2/44CO2'->'rd46/44', 'd 45CO2/44CO2'->'d45/44', 'd 46CO2/44CO2'->'d46/44', 'd 13C/12C'->'d13C', 'd 18O/16O'->'d18O', 'd 17O/16O'->'d17O', 'AT% 13C/12C'->'at13C', 'AT% 18O/16O'->'at18O'
#> Info: converting peak table column units where applicable from 'mV'->'V' and 'mVs'->'Vs' for columns matching 'everything()'

```

# Display file info
```{r}
# display file information
iso_files %>% 
  iso_get_file_info() %>% select(-file_id, -folder) %>% 
  iso_make_units_explicit() %>% knitr::kable()
#> Info: aggregating file info from 45 data file(s)
```

# Chromatograms
```{r}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # select a few analyses (these #s must exist!)
  iso_filter_files(iso_files, Analysis %in% c(2046, 2106, 2107)),
  # select data and aesthetics
  data = c(44), color = id1, panel = Analysis,
  # zoom in on time interval
  time_interval = c(1000, 3200),
  # peak labels for all peaks > 2V
  peak_label = iso_format(rt, d13C, signif = 3),
  peak_label_size = 3,
  peak_label_filter = amp44 > 2000
) +
  # customize resulting ggplot
  theme(legend.position = "bottom")
#> Info: applying file filter, keeping 3 of 45 files
```

```{r}
# find files with zero in the Identifier 1 field
on_offs <- iso_files %>% iso_filter_files(type == "on_off") 
#> Info: applying file filter, keeping 4 of 45 files

# visualize the on/offs  
iso_plot_continuous_flow_data(on_offs, data = 44, color = id2)
```

```{r}
# calculate on/off summary
on_off_summary <- 
  on_offs %>% 
  # retrieve peak table
  iso_get_peak_table(
    select = c(amp44, area44, d13C),
    include_file_info = c(file_datetime, id2)
  ) %>% 
  # summarize information
  group_by(file_datetime, id2) %>% 
  iso_summarize_data_table() 
#> Info: aggregating peak table from 4 data file(s), including file info 'c(file_datetime, id2)'

# table
on_off_summary %>% iso_make_units_explicit() %>% knitr::kable(digits = 3)
```

```{r}
# plot
on_off_summary %>% 
  # use generic data plot function
  iso_plot_data(
    x = file_datetime, y = `d13C sd`,
    size = `amp44 mean`, color = id2,
    points = TRUE,
    date_labels = "%b %d - %H:%M"
  ) + 
  # customize resulting ggplot
  expand_limits(y = 0) 
```

```{r}
# find files with linearity in the Identifier 1 field
lins <- iso_files %>% iso_filter_files(type == "lin") 
#> Info: applying file filter, keeping 1 of 45 files

# visualize the linearity runs
iso_plot_continuous_flow_data(lins, data = 44, color = format(file_datetime))
```

```{r}
# calculate linearity summary
linearity_summary <- 
  lins %>% 
  # retrieve data table
  iso_get_peak_table(
    select = c(amp44, area44, d13C),
    include_file_info = c(file_datetime)
  ) %>% 
  # calculate linearity regression lines
  nest(data = -file_datetime) %>% 
  mutate(
    fit = map(data, ~lm(d13C ~ amp44, data = iso_strip_units(.x))),
    coefs = map(fit, broom::tidy)
  )
#> Info: aggregating peak table from 1 data file(s), including file info 'c(file_datetime)'

# table
linearity_summary %>%
  unnest(coefs) %>%
  select(file_datetime, term, estimate, std.error) %>%
  filter(term == "amp44") %>%
  mutate(
    term = "linearity [permil/V]",
    estimate = signif(estimate, 2),
    std.error = signif(std.error, 1)
  ) %>% 
  knitr::kable(digits = 4)
```

```{r}
# plot
linearity_summary %>% 
  unnest(data) %>% 
  # use generic data plot function
  iso_plot_data(
    x = amp44, y = d13C,
    color = format(file_datetime),
    points = TRUE,
    panel = file_datetime,
    geom_smooth(method = "lm")
  )
```

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
peak_maps <- 
  tibble::tribble(
    # column names -> defining 2 peak maps, 'std' and 'sample' here
    # but could define an unlimited number of different maps
    ~compound, ~ref_nr, ~`rt:std`,  ~`rt:sample`,
    # peak map data (row-by-row)
    "CO2",          1,        79,                 79,
    "CO2",          2,      178,                178,
    "CO2",          3,      278,                278,
    "CO2",          4,      377,                377,
    "CO2",          5,      477,                477,
    "CO2",          6,      576,                576,
    "CO2",          7,      676,                676,
    "CO2",          8,      775,                775,
    "CO2",          9,      875,                875,
    "nC16",         NA,     1156,               1156,
    "nC17",         NA,     1280,               1280,
    "nC18",         NA,     1409,               1409,
    "nC19",         NA,     1540,               1540,
    "nC20",         NA,     1670,               1670,
    "nC21",         NA,     1797,               1797,
    "nC22",         NA,     1921,               1921,
    "nC23",         NA,     2040,               2040,
    "nC24",         NA,     2156,               2156,
    "nC25",         NA,     2267,               2267,
    "nC26",         NA,     2375,               2375,
    "nC27",         NA,     2479,               2479,
    "nC28",         NA,     2580,               2580,
    "nC29",         NA,     2674,               2678,
    "nC30",         NA,     2770,               2773,
    "nC31",         NA,     NA,               2863,
    "CO2",          10,     3552,               3552,
    "CO2",          11,     3592,               3592
  )
peak_maps %>% knitr::kable(digits = 0)
```

```{r}
# identify peaks
peak_table_w_ids <- iso_files %>% 
  # focus on standards and samples only
  iso_filter_files(type %in% c("std", "sample")) %>% 
  # filter out analyses that
  ## a) did not inject
  iso_filter_files(!Analysis %in% c(2031, 2040, 2069, 2098, 2116, 2138)) %>%
  ## b) had double or rogue peaks from mis-injection
  iso_filter_files(!Analysis %in% c(2044, 2132, 2134)) %>% 
  # map peaks
  iso_map_peaks(peak_maps, map_id = type) %>% 
  # peak table
  iso_get_peak_table(include_file_info = everything())
```

```{r}
# use same plotting as earlier, except now with peak features added in
iso_files %>% 
  iso_filter_files(Analysis %in% c(2046, 2106, 2107)) %>% 
  iso_plot_continuous_flow_data(
    # select data and aesthetics
    data = 44, color = id1, panel = Analysis,
    # zoom in on time interval
    time_interval = c(1000, 3200),
    # provide our peak table with ids
    peak_table = peak_table_w_ids, 
    # define peak labels, this can be any valid expression
    peak_label = iso_format(id = peak_info, d13C), 
    # specify which labels to show (removing the !is_identified or putting a 
    # restriction by retention time can help a lot with busy chromatograms)
    peak_label_filter = is_identified | !is_identified | is_missing
  )  +
  # customize resulting ggplot
  theme(legend.position = "bottom")
#> Info: applying file filter, keeping 3 of 45 files
```

```{r}
# look at missing and unidentified peaks summary (not run during knitting)
# -> check if any of the missing peaks are unexpected (should be there but aren't)
# -> check if any unidentified peaks should be added to the peak maps
# -> check if any ambiguous peaks need clearer peak map retention times
# when in doubt, look at the chromatograms of the problematic files!
# as needed: iterate on peak map update, then peak mapping inspection
peak_table_w_ids %>% 
  iso_get_problematic_peak_mappings() %>% 
  iso_summarize_peak_mappings()
```

```{r}
# examine variation in the reference peaks
peak_table_w_ids %>% 
  # focus on reference peaks only
  filter(!is.na(ref_nr)) %>% 
  # mark ref peak used for raw delta values (assuming the same in all anlysis)
  mutate(
    ref_info = paste0(ref_nr, ifelse(is_ref == 1, "*", "")) %>% factor() %>% fct_inorder()
  ) %>% 
  # visualize
  iso_plot_ref_peaks(
    # specify the ratios to visualize
    x = Analysis, ratio = `r45/44`, fill = ref_info,
    panel_scales = "fixed"
  ) +
  labs(x = "Analysis", fill = "Reference\npeak")
```

# Analyte Peaks
```{r}
# focus on analyte peaks and calculate useful summary statistics
peak_table_analytes <- peak_table_w_ids %>% 
  # omit reference peaks for further processing (i.e. analyte peaks only)
  filter(is.na(ref_nr)) %>% 
  # for each analysis, calculate a few useful summary statistics
  iso_mutate_peak_table(
    group_by = file_id,
    rel_area = area44 / sum(area44, na.rm = TRUE),
    # calculate mean area for all peaks
    mean_area = mean(area44, na.rm = TRUE),
    # calculate mean area and amplitude for identified peaks
    mean_area_identified = mean(area44[!is.na(compound)], na.rm = TRUE),
    mean_amp_identified = mean(amp44[!is.na(compound)], na.rm = TRUE)
  )
```

```{r}
peak_table_analytes %>% 
  # focus on identified peaks (comment out this line to see ALL peaks)
  filter(!is.na(compound)) %>% 
  # visualize with convenience function iso_plot_data
  iso_plot_data(
    # choose x and y (multiple y possible)
    x = area44, y = c(amp44, d13C),
    # choose aesthetics
    color = compound, shape = type, label = compound, size = 3,
    # decide what geoms to include
    points = TRUE
  ) +
  # further customize ggplot with a log scale x axis
  scale_x_log10()
```

### 2019-12-07 isotope_data_reduction.rmd
added new plots and map peaks

@@
 ```{r}
+real_data <- 
   sample_files_w_ids %>% 
   iso_get_peak_table(include_file_info = everything()) %>% 
-  filter(compound != "unknown") %>% 
+  filter(compound != "H2") %>% 
+  group_by(file_id) %>% 
+  mutate(rel_amount = area2 / sum(area2[compound != "IS"])) %>% 
+  ungroup() %>% 
+  filter(compound != "unknown") 
+```
+
+```{r}
+real_data %>% 
   mutate(sample_label = iso_format(control, inc_time, with_glu)) %>% 
   iso_plot_data(
-    x = compound, y = c(area2, d2H), color = sample_label,
-    points = TRUE
+    x = inc_time, y = d2H, color = compound, shape = with_glu, size = rel_amount,
+    points = TRUE,
+    lines = TRUE,
+    panel = with_glu ~ .
+    #panel_scales = "fixed"
   )
 ```
+
+# FOR PROCESSING ONLY
+
+# Export data
+
+```{r}
+irms_example_data <- 
+  sample_files_w_ids %>%
+  iso_filter_files(analysis == 5689) %>% 
+  iso_get_peak_table() %>% 
+  filter(compound != "H2") %>% 
+  select(rt, rt_start, rt_end, amp2, area2) %>% 
+  mutate(rel_height = amp2/sum(amp2) * 100) %>% 
+  filter(rel_height > 1)
+
+irms_example_data %>% 
+  openxlsx::write.xlsx(file.path("tables", "gc_irms_single_sample_peak_table.xlsx"))
+```
+
+# Peak Mapping help
+
+```{r}
+tsq_example_data <- read_excel(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
+```
+
+```{r}
+bind_rows(
+  irms_example_data %>% mutate(type = "irms") %>% iso_strip_units(),
+  tsq_example_data %>% mutate(type = "tsq")
+) %>% 
+  ggplot() +
+  aes(rt, rel_height, label = paste0(`Peak Name`, "\n", round(rt))) +
+  geom_bar(stat = "identity")+
+  ggrepel::geom_text_repel(color = "red", alpha = 0.5, min.segment.length = 0)+
+  facet_grid(type ~ .)
+ggsave(file.path("figures", "irms_tsq_comparison.pdf"), width = 12, height = 8)
+```
+
+##
+```{r}
+# examine variation in the reference peaks
+sample_files_w_ids %>% 
+  # focus on reference peaks only
+  filter(!is.na(ref_nr)) %>% 
+  # mark ref peak used for raw delta values (assuming the same in all anlysis)
+  mutate(
+    ref_info = paste0(ref_nr, ifelse(is_ref == 1, "*", "")) %>% factor() %>% fct_inorder()
+  ) %>% 
+  # visualize
+  iso_plot_ref_peaks(
+    # specify the ratios to visualize
+    x = Analysis, ratio = `r45/44`, fill = ref_info,
+    panel_scales = "fixed"
+  ) +
+  labs(x = "Analysis", fill = "Reference\npeak")
+```
+
+##
+```{r}
+# focus on analyte peaks and calculate useful summary statistics
+peak_table_analytes <- sample_files_w_ids %>% 
+  # omit reference peaks for further processing (i.e. analyte peaks only)
+  filter(is.na(ref_nr)) %>% 
+  # for each analysis, calculate a few useful summary statistics
+  iso_mutate_peak_table(
+    group_by = file_id,
+    rel_area = area44 / sum(area44, na.rm = TRUE),
+    # calculate mean area for all peaks
+    mean_area = mean(area44, na.rm = TRUE),
+    # calculate mean area and amplitude for identified peaks
+    mean_area_identified = mean(area44[!is.na(compound)], na.rm = TRUE),
+    mean_amp_identified = mean(amp44[!is.na(compound)], na.rm = TRUE)
+  )
+```
+
+##
+```{r}
+# find files with linearity in the Identifier 1 field
+lins <- iso_files %>% iso_filter_files(type == "lin") 
+#> Info: applying file filter, keeping 1 of 45 files
+
+# visualize the linearity runs
+iso_plot_continuous_flow_data(lins, data = 44, color = format(file_datetime))
+
+```
+
+##
+```{r}
+# calculate on/off summary
+on_off_summary <- 
+  on_offs %>% 
+  # retrieve peak table
+  iso_get_peak_table(
+    select = c(amp44, area44, d13C),
+    include_file_info = c(file_datetime, id2)
+  ) %>% 
+  # summarize information
+  group_by(file_datetime, id2) %>% 
+  iso_summarize_data_table() 
+#> Info: aggregating peak table from 4 data file(s), including file info 'c(file_datetime, id2)'
+
+# table
+on_off_summary %>% iso_make_units_explicit() %>% knitr::kable(digits = 3)
+```

### 2019-12-28 abundance.Rmd
commit as of 12/28/2019

@@
 ```{r}
-root <- "data"
+root <- "data/tsq_reports"
 all_data <-
@@
     sample = c("a", "b"),
-    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
+    file = c("TSQ5934_mAx_TAC_2ml.xls", "TSQ5934_mAx_TAC_2ml.xls"),
     data = map(file.path(root, file), read_chromeleon_export),

### 2019-12-28 labeling_calculations.Rmd
commit as of 12/28/2019

---
title: "Labeling Calculations"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    toc: yes
    toc_float: true
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# libraries
library(tidyverse)
library(lubridate)
library(latex2exp)
library(isotopia) # install.packages("devtools"); devtools::install_github("sebkopf/isotopia")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Theory

Isotopic enrichment resulting from unbiased clonal growth in the presence of an isotopic label is described by the folowing equation:

$$
F(t) = a \cdot F_L \left(1-e^{-\mu\cdot t}\right) + F_{0} \cdot e^{-\mu \cdot t}
$$
where $F_L$ is the isotopic composition (in atom % of the rare isotope) of the isotope label, $a$ is the assimilation efficiency of the tracer (from 0 to 1), $F_0$ is the isotopic composition of native biomass, $\mu$ is specific growth rate and $t$ is time. Substituting the growth rate for the expected generation time ($µ=\ln(2)/T$), one can readily calculate the required labeling time to reach a target isotopic composition $F_t$:

$$
t = \frac{T}{\ln(2)} \cdot \ln \left(\frac{a\cdot F_L - F_0}{a\cdot F_L - F_t}\right)
$$
Likewise, one can calculate the required strength of the isotope label based on expected generation time, target isotopic composition and intended incubation length:

$$
F_L = \frac{F_t - F_{0} \cdot e^{-\mu \cdot t}}{a \left(1-e^{-\mu\cdot t}\right)}
$$

# Heavy water labeling

```{r, echo=FALSE}
# parameters
dD_nat <- -200
dD_enrich_min <- +50
dD_enrich_avg <- +500
dD_enrich_max <- +5000
F_0.percent <- delta(dD_nat, ref_ratio = get_standard("2H")) %>% to_ab() %>% get_value("percent")
F_t.percent <- delta(dD_nat + dD_enrich_avg, ref_ratio = get_standard("2H")) %>% to_ab() %>% get_value("percent")
F_min.percent <- delta(dD_nat + dD_enrich_min, ref_ratio = get_standard("2H")) %>% to_ab() %>% get_value("percent")
F_max.percent <- delta(dD_nat + dD_enrich_max, ref_ratio = get_standard("2H")) %>% to_ab() %>% get_value("percent")
a <- 0.5
```

Assuming that heterotrophs incorporate the tracer from water into lipids with about a 50% efficiency (taking into consideration the combination of water hydrogen assimilation and net isotope fractionation) and that native lipids will have an isotopic composition of about $`r dD_nat`$‰, we have $a=`r a`$ and $F_0 = `r F_0.percent`$ atom %.

For precise quantification, an ideal target labeling enriches by at least $`r dD_enrich_min`$‰, at most $`r dD_enrich_max`$‰, and on average about $`r dD_enrich_avg`$‰ above the original lipids, i.e. a target of $`r dD_nat + dD_enrich_avg`$‰, or $F_t = `r F_t.percent`$ atom %. This results in the following labeling space.

## Isotope tracer strength by incubation time

```{r "tracer_strength", fig.width = 8 , fig.height = 6, warning=FALSE, message=FALSE}
# generation times of interest
gen_times <- tribble(
  ~value, ~units,
  20, "minutes",
  90,  "minutes",
  6,  "hours",
  1,  "day",
  1,  "week",
  1,  "month",
  3,  "months", 
  1,  "year",
  3,  "years"
) %>% mutate(
  label = paste(value, units) %>% factor() %>% fct_inorder(),
  gen_time.s = map2_dbl(value, units, ~duration(.x, .y)),
  gen_time.log10 = log10(gen_time.s),
  mu.1_s = log(2) / gen_time.s
)
gen_times

# incubation times
inc_time.s <- duration(c(1, 10, 50), "hours")

# labeling space
label_strengths <- 
  # generation time space (log linear to acccount for large range in gen. times)
  tibble(
    gen_time.log10 = gen_times %>% 
      with(seq(from = min(gen_time.log10), to = max(gen_time.log10), length.out = 100))
  ) %>% 
  # all combinations with incubation time
  crossing(inc_time.s) %>% 
  # min avg max quantification limits
  crossing(
    tibble(
      F_t_type = c("average", "min", "max"),
      F_t.percent = c(F_t.percent, F_min.percent, F_max.percent)
    )
  ) %>% 
  mutate(
    gen_time.s = 10^gen_time.log10,
    mu.1_s = log(2) / gen_time.s,
    F_L.percent = (F_t.percent - F_0.percent * exp(-mu.1_s * inc_time.s)) / (a * (1 - exp(-mu.1_s * inc_time.s)))
  )

# plot
label_strengths %>% 
  # spread the different F_t_type values
  select(-F_t.percent) %>%  spread(F_t_type, F_L.percent) %>% 
  # color factor
  mutate(incubation_time = sprintf("%.0f hours", inc_time.s/3600) %>% factor() %>% fct_inorder()) %>% 
  # send to plot
  ggplot() +
  aes(gen_time.log10, color = incubation_time, fill = incubation_time) + 
  geom_hline(yintercept = c(0.5, 1.0)) +
  geom_ribbon(mapping = aes(ymin = min, ymax = max, color = NULL), alpha = 0.1) +
  geom_line(mapping = aes(y = average), size = 2) +  
  labs(title = 
         sprintf("Tracer strength to reach enrichment between\n%.0f\u2030 and %.0f\u2030 (line = %.0f\u2030)", 
                 dD_enrich_min, dD_enrich_max, dD_enrich_avg)) + 
  scale_x_continuous(
    "generation time", 
    breaks = gen_times$gen_time.log10,
    labels = function(x) gen_times$label,
    expand = c(0, 0)
  ) +
  scale_y_continuous(TeX("isotope tracer strength ($F_L$)"), labels = function(x) sprintf("%.2f at%%", x)) +
  scale_color_brewer("after\nincubation\ntime", palette = "Set1") +
  scale_fill_brewer("after\nincubation\ntime", palette = "Set1") +
  coord_cartesian(ylim = c(0, 1)) +
  #facet_wrap(~incubation_time, nrow = 1) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        panel.grid.minor = element_blank()) 
```

## Incubation time by tracer strength

```{r "req_incubation_time", fig.width = 8 , fig.height = 6, warning=FALSE, message=FALSE}
# labeling strengths
F_L.percent <- c(0.5)

# incubation times
inc_times <- 
  # generation time space (log linear to acccount for large range in gen. times)
  tibble(
    gen_time.log10 = gen_times %>% 
      with(seq(from = min(gen_time.log10), to = max(gen_time.log10), length.out = 100)) %>% 
      union(gen_times$gen_time.log10)
  ) %>% 
  # all combinations with tracer strength
  crossing(F_L.percent) %>% 
  # min avg max quantification limits
  crossing(
    tibble(
      F_t_type = c("average", "min", "max"),
      F_t.percent = c(F_t.percent, F_min.percent, F_max.percent)
    )
  ) %>% 
  mutate(
    gen_time.s = 10^gen_time.log10,
    inc_time.s = gen_time.s / log(2) * log( (a * F_L.percent - F_0.percent) / (a * F_L.percent - F_t.percent) ),
    inc_time.log10 = log10(inc_time.s)
  )

# y breaks
y_breaks <- inc_times %>% 
  filter(F_t_type == "average") %>% 
  semi_join(gen_times, by = "gen_time.log10") %>% 
  mutate(
    # clean up lubridate time estimates
    label = duration(inc_time.s) %>% as.character() %>% 
      str_extract("(\\~\\d+\\.?\\d*\\s\\w+|.*s$)") %>% 
      str_replace("\\.\\d+s", " seconds")
  )

# plot
inc_times %>% 
  # spread the different F_t_type values
  select(-F_t.percent, -inc_time.s) %>%  spread(F_t_type, inc_time.log10) %>% 
  # color factor
  mutate(label_strength = paste("F_L =", F_L.percent, "at%") %>% factor() %>% fct_inorder()) %>% 
  # send to plot
  ggplot() +
  aes(gen_time.log10, color = label_strength, fill = label_strength) + 
  geom_hline(
    data = tibble(inc_time.s = as.numeric(inc_time.s), inc_time.log10 = log10(inc_time.s)),
    mapping = aes(yintercept = inc_time.log10, linetype = paste(inc_time.s/3600, "hours"))
  ) +
  geom_ribbon(mapping = aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(mapping = aes(y = average), size = 2) +  
  labs(title =
         sprintf("Required incubation times to reach enrichment\nbetween %.0f\u2030 and %.0f\u2030 (thick line = %.0f\u2030)",
                 dD_enrich_min, dD_enrich_max, dD_enrich_avg),
       linetype = "target incubation times") +
  scale_x_continuous(
    "generation time", 
    breaks = gen_times$gen_time.log10,
    labels = function(x) gen_times$label,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    "required incubation time", 
    breaks = y_breaks$inc_time.log10,
    labels = function(x) y_breaks$label,
    expand = c(0, 0)
  ) +
  scale_color_brewer("tracer strength", palette = "Set1") +
  scale_fill_brewer("tracer strength", palette = "Set1") +
  coord_cartesian(ylim = range(y_breaks$inc_time.log10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        panel.grid.minor = element_blank())
```

## Enrichment curves by generation time

```{r "enrichment_curves", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
# labeling strengths
F_L.percent <- c(0.5, 1)

# labeling curves
labeling_curves <- 
  # extend to twice max incubation time
  tibble(inc_time.s = seq(from = 0, to = 2 * max(inc_time.s), length.out = 100)) %>%   
  crossing(gen_times[-1, ]) %>% 
  crossing(F_L.percent) %>% 
  mutate(
    F_t.percent = a * F_L.percent * (1 - exp(-mu.1_s  * inc_time.s)) + F_0.percent * exp(-mu.1_s * inc_time.s),
    inc_time.h = inc_time.s/3600,
    grid_y = paste("F_L =", F_L.percent, "at%")
  )

# plot
p1 <- labeling_curves %>% 
  # panel for time zoom
  mutate(grid_x = ifelse(inc_time.h <= 5.1, "1", "2")) %>% 
  # make sure time transition at panel edge is smooth
  { bind_rows(., filter(., grid_x == "1") %>% filter(inc_time.h == max(inc_time.h)) %>% mutate(grid_x = "2")) } %>% 
  # send to plot
  ggplot() + 
  aes(inc_time.h, F_t.percent, color = label) +
  # highlight area of quantification
  geom_rect(xmin = -Inf, xmax = Inf, ymin = F_min.percent, ymax = F_max.percent, 
            color = "gray", fill = "gray", alpha = 0.25, show.legend = FALSE) + 
  geom_hline(yintercept = F_0.percent, linetype = 2) +
  geom_hline(yintercept = F_t.percent) +
  #geom_vline(xintercept = as.numeric(inc_time.s, "hours")) +
  geom_line() + 
  labs(title = "Isotopic composition/enrichment after incubation time\n(gray box = quantification range)") + 
  scale_x_continuous("Incubation time [hours]", expand = c(0, 0)) +
  scale_y_continuous(
    TeX("estimated isotopic composition ($F_t$)"), labels = function(x) sprintf("%.2f at%%", x),
    sec.axis = sec_axis(
      trans = function(x) { 
        ab(x, notation = "percent") %>% 
          to_ratio() %>% to_delta(ref_ratio = get_standard("2H")) %>% 
          get_value("permil") - 
        ab(F_0.percent, notation = "percent") %>% 
          to_ratio() %>% to_delta(ref_ratio = get_standard("2H")) %>% 
          get_value("permil")
      }, 
      labels = function(x) sprintf("%+.0f\u2030", x), 
      name = TeX("estimated enrichmen ($\\delta{}D$)")),
    expand = c(0, 0)
  ) +
  scale_color_brewer("generation time", palette = "Set1") +
  facet_grid(grid_y ~ grid_x, scales = "free_x") +
  theme_bw() +
  theme(strip.background.x = element_blank(), strip.text.x = element_blank(),
        panel.spacing.x = unit(0, "mm"))

p1 + geom_hline(
  mapping = aes(yintercept = 0.325, linetype = "approx upper\nlimit for IRMS")
) + scale_linetype_manual(values = 2)
```

### Zoom in on quantification range

```{r "enrichment_curves_zoomed1", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
p1 + coord_cartesian(ylim = c(0, 0.12))
```

### Zoom in on low enrichment

```{r "enrichment_curves_zoomed2", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
p1 + coord_cartesian(ylim = c(0.01, 0.025))
```

### 2019-12-28 isotope_data_reduction.rmd

--- 2019-12-01 isotope_data_reduction.rmd
@@
 library(isoprocessor) # processing the data
+library(readxl)
 ```
@@
 
-## Data
+## Data *
 
 ```{r}
+real_data <- 
   sample_files_w_ids %>% 
   iso_get_peak_table(include_file_info = everything()) %>% 
-  filter(compound != "unknown") %>% 
+  filter(compound != "H2") %>% 
+  group_by(file_id) %>% 
+  mutate(rel_amount = area2 / sum(area2[compound != "IS"])) %>% 
+  ungroup() %>% 
+  filter(compound != "unknown") 
+```
+
+```{r}
+# Unaltered data plot
+real_data %>% 
   mutate(sample_label = iso_format(control, inc_time, with_glu)) %>% 
+  mutate(inc_time = ifelse(control == TRUE, 0, inc_time)) %>% 
   iso_plot_data(
-    x = compound, y = c(area2, d2H), color = sample_label,
-    points = TRUE
+    x = inc_time, y = d2H, color = compound, shape = with_glu, size = rel_amount,
+    points = TRUE,
+    lines = TRUE,
+    panel = with_glu ~ .
+    #panel_scales = "fixed"
+  ) +
+  geom_hline(yintercept = -200) +
+  geom_hline(yintercept = -180)
+ggsave(file.path("figures", "d2H_all_compounds_2.pdf"), width = 12, height = 8)
+
+```
+
+```{r}
+real_data_normalized <- real_data
+real_data_normalized <- real_data_normalized %>%
+  mutate(sample_label = iso_format(control, inc_time, with_glu)) %>%
+  select(id1, control, inc_time, with_glu, compound, d2H, rel_amount)
+
+real_data_normalized2 <- read_csv(file.path("data", "real_data_normalized.csv"))
+
+real_data_normalized2 %>% filter(control != TRUE) %>%
+  iso_plot_data(
+    x = inc_time, y = d2H_normal, color = compound, shape = with_glu,
+    points = TRUE,
+    lines = TRUE,
+    panel = with_glu ~ .,
+    panel_scales = "fixed") #+ geom_smooth(method = "lm", alpha = .15, aes(fill = with_glu))
+ggsave(file.path("figures", "d2H_comp_normalized_zoomed.png"), width = 12, height = 8)
+```
+
+```{r}
+# Mean Across Compounds
+real_data_abbreviated <- real_data
+real_data_abbreviated <- real_data_abbreviated %>%
+  mutate(sample_label = iso_format(control, inc_time, with_glu)) %>%
+  select(id1, control, inc_time, with_glu, compound, d2H, rel_amount)
+
+real_data_abbreviated <- real_data_abbreviated %>%
+  group_by(inc_time, with_glu) %>%
+  summarise(mean_d2H = mean(d2H),
+            sdev = sd(d2H))
+
+real_data_abbreviated %>%
+  iso_plot_data(
+    x = inc_time, y = mean_d2H, color = with_glu, shape = with_glu,
+    points = TRUE,
+    lines = TRUE
+    #panel = with_glu ~ .
+    #panel_scales = "fixed"
+  ) + geom_smooth(method = "lm", alpha = .15, aes(fill = with_glu))
+ggsave(file.path("figures", "d2H_averaged_comp.pdf"), width = 12, height = 8)
+```
+
+## Labeling Calculations
+For example:
+FL = 0.005 # tracer strength = 0.5%
+a = 0.5 # incorporation efficiency of 50%
+FT = 0.02 # resultant isotopic enrichment
+F0 = 0.0124 # beginning isotopic enrichment
+
+```{r}
+
+gencalc <- function(a, FT, F0, FL, t) {
+  case_when(
+    t == 0 ~ NA_real_,
+    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
   )
+}
+
+'
+FL = 0.005 # tracer strength = 0.5% --> 
+a = 0.5 # incorporation efficiency of 50%
+FT = 0.02 # resultant isotopic enrichment
+F0 = 0.0124 # beginning isotopic enrichment
+'
+
+calc_data <- real_data_normalized2
+ref_ratio <- get_standard("2H") %>% as.numeric()
+# Calculate the starting iso enrichment NOTE: using 1hr as a standin for 0hr until that data is acquired
+
+calc_data <- calc_data %>%
+  # only focus on fatty acids
+  filter(!compound %in% c("alkane", "C23:0 (IS)")) %>% 
+  mutate(
+    R = (d2H/1000 +1) * ref_ratio,
+    t = inc_time,
+    FT = R / (1 + R)
+  ) %>% 
+  # for each compound in each time series
+  group_by(with_glu, compound) %>%
+  mutate(
+    # use negative controls as reference
+    t0 = 0,
+    n_t0 = sum(control),
+    F0 = mean(FT[control]),
+    t = ifelse(control, 0, t)
+    # use first time point as reference
+    #t0 = min(t),
+    #n_t0 = sum(t == t0),
+    #F0 = mean(FT[t == t0])
+  ) %>% 
+  ungroup() %>% 
+  #mutate(u = NA) %>%
+  # calculate growth rate mu
+  mutate(
+    d_FT = FT - F0,
+    d_t = t - t0,
+    u.1_hr = gencalc(a = a, FT = d_FT, F0 = 0, FL = fl, t = d_t),
+    u.1_d = u.1_hr * 24,
+    u.1_mon = u.1_d * 30,
+    gen.d = log(2) / u.1_d
+  ) %>% 
+  # calculate relative amounts for shared peaks
+  group_by(control, with_glu, inc_time) %>% 
+  mutate(rel_amount_present = rel_amount / sum(rel_amount)) %>% 
+  ungroup() %>% 
+  # general info
+  mutate(
+    panel = ifelse(with_glu, "with glucose", "no glucose"),
+    compound = factor(compound) %>% fct_inorder()
+  ) %>% 
+  identity()
+
 ```
+
+# all growth data
+
+```{r}
+calc_data %>% 
+  filter(
+    !is.na(u.1_hr), 
+    u.1_hr > 0
+  ) %>% 
+  mutate(
+    `var µ [1/day]` = u.1_d,
+    `var T [days]` = gen.d,
+    `var Amt [%]` = 100 * rel_amount_present
+  ) %>% 
+  gather(key = "variable", value = "value", starts_with("var")) %>% 
+  mutate(variable = str_remove(variable, "^var ") %>% factor() %>% fct_inorder()) %>% 
+  ggplot() +
+    aes(compound, y = value, fill = factor(inc_time)) +
+    geom_bar(stat = "identity", position = "dodge") +
+    facet_grid(variable ~ panel, scales = "free_y", switch = "y") +
+    labs(x = NULL, y = NULL) + 
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
+#  coord_cartesian(y = c(0, 1000))
+```
+
+```{r}
+calc_data %>% 
+  filter(
+    !is.na(u.1_hr), 
+    u.1_hr > 0
+  ) %>% 
+  mutate(
+    `var µ [1/day]` = u.1_d
+  ) %>% 
+  gather(key = "variable", value = "value", starts_with("var")) %>% 
+  mutate(variable = str_remove(variable, "^var ") %>% factor() %>% fct_inorder()) %>% 
+  ggplot() +
+  aes(compound, y = value, fill = factor(inc_time)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_grid(variable ~ panel, scales = "free_y", switch = "y") +
+  labs(x = NULL, y = NULL) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
+#  coord_cartesian(y = c(0, 1000))
+```
+
+# weighted growth data
+
+```{r}
+spread_data <- calc_data %>% 
+  filter(!control) %>%  
+  {
+    full_join(
+      filter(., with_glu) %>% select(inc_time, compound, with_glu_rel_amount = rel_amount_present, with_glu_u.1_mon = u.1_mon),
+      filter(., !with_glu) %>% select(inc_time, compound, no_glu_rel_amount = rel_amount_present, no_glu_u.1_mon = u.1_mon),
+      by = c("inc_time", "compound")
+    ) %>% 
+      mutate(mean_rel_amount = 0.5 * with_glu_rel_amount + 0.5 * no_glu_rel_amount)
+  }
+spread_data_sum <- spread_data %>% 
+  group_by(inc_time) %>% 
+  summarise(
+    with_glu_u.1_mon = sum(with_glu_rel_amount * with_glu_u.1_mon) / sum(with_glu_rel_amount),
+    no_glu_u.1_mon = sum(no_glu_rel_amount * no_glu_u.1_mon) / sum(no_glu_rel_amount),
+    mean_rel_amount = 1
+    # what is a good weighted measure of the mu distribution spread??
+  ) 
+spread_data_sum
+```
+
+```{r}
+ggplot() +
+  aes(no_glu_u.1_mon, with_glu_u.1_mon, shape = paste(inc_time, "hours")) +
+  geom_abline(slope = 1, intercept = 0, color = 'orange') +
+  xlab('Cell Turnover per Month: No Glucose') +
+  ylab('Cell Turnover per Month: With Glucose') +
+  # individual compounds
+  #geom_path(data = spread_data, mapping = aes(color = compound, shape = NULL), alpha = 0.5) +
+  #geom_point(data = spread_data, mapping = aes(color = compound, size = 100 * mean_rel_amount), alpha = 0.5) +
+  # weighted means
+  geom_path(data = spread_data_sum, mapping = aes(shape = NULL)) +
+  geom_point(data = spread_data_sum, mapping = aes(size = 100 * mean_rel_amount)) +
+  #coord_fixed(x = c(0, 15), y = c(0, 15))
+  coord_fixed(x = c(0, 4), y = c(0, 4))
+
+```
+
+```{r}
+
+mean_u <- read_csv(file.path("data", "weighted_mean_u.csv"))
+mean_u %>%
+ggplot() +
+  aes(x = factor(inc_time), y = u.1_mon, fill = with_glu) +
+  geom_bar(stat = 'identity', position = 'dodge') +
+  theme_bw() +
+  xlab('Incuation Time') +
+  ylab('Generations per Month')
+ggsave(file.path("figures", "weighted_mean_u_bar.png"), width = 8, height = 8)
+```
+
+# control - look good
+
+```{r}
+calc_data %>% 
+  filter(control) %>% 
+  ggplot() +
+  aes(compound, d2H, color = panel) +
+  geom_point() +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
+```
+
+# FOR PROCESSING ONLY
+
+# Export data
+
+```{r}
+irms_example_data <- 
+  sample_files_w_ids %>%
+  iso_filter_files(analysis == 5689) %>% 
+  iso_get_peak_table() %>% 
+  filter(compound != "H2") %>% 
+  select(rt, rt_start, rt_end, amp2, area2) %>% 
+  mutate(rel_height = amp2/sum(amp2) * 100) %>% 
+  filter(rel_height > 1)
+
+irms_example_data %>% 
+  openxlsx::write.xlsx(file.path("tables", "gc_irms_single_sample_peak_table.xlsx"))
+```
+
+# Peak Mapping help
+
+```{r}
+tsq_example_data <- read_excel(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
+```
+
+```{r}
+bind_rows(
+  irms_example_data %>% mutate(type = "irms") %>% iso_strip_units(),
+  tsq_example_data %>% mutate(type = "tsq")
+) %>% 
+  ggplot() +
+  aes(rt, rel_height, label = paste0(`Peak Name`, "\n", round(rt))) +
+  geom_bar(stat = "identity")+
+  ggrepel::geom_text_repel(color = "red", alpha = 0.5, min.segment.length = 0)+
+  facet_grid(type ~ .)
+ggsave(file.path("figures", "irms_tsq_comparison2.pdf"), width = 12, height = 8)
+```

### 2020-12-10 isotope_data_reduction.rmd
no update

@@
 library(isoprocessor) # processing the data
+library(isotopia)
 library(readxl)

### 2020-12-10 silver_ion_chroma.Rmd
initial commit

---
title: "Silver Ion Chroma"
author: "Tristan Caro"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-12-10 silver_ion_chroma.Rmd
plots added

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+A BAMES standard was run through two silver ion (Ag) columns to test the efficacy/cleanliness of the columns.
+A **Supelco Ag-Ion Discovery** column "Disc" and a homemade **Silver Nitrate** "Nitr" column were both tested (protocol courtesy of Nicolo Ardenghi).
+
+- Instrument method: `OG_DB-1_F9_longMethod_fullscan_300Csource_cyclohexane_FAMES`
+- Processing Method: `BAMES STANDARD`
+
+# Protocol
+TC-BAME2 was taken from OGL Center Mini -20˚C. 245µg of total lipid BAME was suspended in 245µL of hex.
+10µL (10µg) was removed and combined with 250µL hexane. The entirey of this stock (10µg) was applied to the Ag column.
+
+0. Set up Ag-Ion columns over waste colleciton vials.
+1. Condition SPE with 4mL acetone
+2. Equilibrate cartridge with 4mL hexane. 
+3. Load FAMEs in hexane derived from sample extraction at a flow rate of 2-3 drops/second. Remove waste collection vials and replace with fraction 1 (F1) collection vials (40mL glass vials).
+4. Elute F1 with 6mL hexane:acetone 96:4
+*Fraction 1 targets saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids*
+5. Elute F2 with 4mL hexane:acetone 90:10
+*Fraction 2 will target: cis monoenes, trans/trans dienes, CLAs*
+6. Elute F3 with 4mL acetone
+*Fraction 3 targets cis/cis dienes, other dienes, trienes.*
+7. Evaporate all fractions at 40˚C under N2, sparge.
+8. Reconstituted in three 100µL hexane washes, added to a GC vial with insert.
+8. Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.
+
+# Data
+
+```{r, include = FALSE}
+# Libraries
+library(tidyverse)
+library(plotly)
+
+# Source
+source(file.path("libs", "visualization.R"))
+source(file.path("libs", "chromleon.R"))
 ```
 
-## R Markdown
+## Data Import
+```{r}
+# Define the root directory and the path names for each file
+root <- "data"
+path_names = c("2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7517_TCBAMES_2_5ug_ul.xls",
+          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7518_BAMES_F1_Disc.xls",
+          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7519_BAMES_F2_Disc.xls",
+          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7520_BAMES_F3_Disc.xls",
+          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7521_BAMES_F1_Nitr.xls",
+          "2020.12.09_TC_BAMES_Agion/2020.12.09_TC_BAMES_Agion_DB1/TSQ7522_BAMES_F2_Nitr.xls")
+# Define the sample names
+sample_names = c("tc_bames2", "bames_disc_f1", "bames_disc_f2", "bames_disc_f3", "bames_nitr_f1", "bames_nitr_f2")
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# read_chromeleon_export is a sourced R function. See above.
+all_data <-
+  tibble(
+    sample = sample_names,
+    file = path_names,
+    data = map(file.path(root, file), read_chromeleon_export),
+    injection_details = map(data, "injection_details"),
+    integration_results = map(data, "integration_results")
+  ) %>% select(-data)
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+## Data Cleanup
+``` {r}
+results <- all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # major compound groups
+  mutate(
+    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
+  ) 
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Plot
+```{r}
+p_tc_bames2 <- results %>%
+  filter(sample == c("tc_bames2")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  ggtitle("BAMES Standard 10µg/µL") +
+  theme_bw()
+
+p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
+```
+```{r}
+p_bames_disc_f1 <- results %>%
+  filter(sample == c("bames_disc_f1")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  labs(title = "BAMES Discovery Ag-Ion F1", subtitle = "saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids") +
+  theme_bw()
+
+p_bames_disc_f1 %>% ggplotly(dynamicTicks = TRUE)
+```
+```{r}
+p_bames_disc_f2 <- results %>%
+  filter(sample == c("bames_disc_f2")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  labs(title = "BAMES Discovery Ag-Ion F2", subtitle = "cis monoenes, trans/trans dienes, CLAs") +
+  theme_bw()
+
+p_bames_disc_f2 %>% ggplotly(dynamicTicks = TRUE)
+```
+
+```{r}
+p_bames_disc_f3 <- results %>%
+  filter(sample == c("bames_disc_f3")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  labs(title = "BAMES Discovery Ag-Ion F3", subtitle = "cis/cis dienes, other dienes, trienes.") +
+  theme_bw()
+
+p_bames_disc_f3 %>% ggplotly(dynamicTicks = TRUE)
+```
+```{r}
+p_bames_nitr_f1 <- results %>%
+  filter(sample == c("bames_nitr_f1")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  labs(title = "BAMES Ag - Nitrate F1") +
+  theme_bw()
+
+p_bames_nitr_f1 %>% ggplotly(dynamicTicks = TRUE)
+```
+
+```{r}
+p_bames_nitr_f2 <- results %>%
+  filter(sample == c("bames_nitr_f2")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  scale_fill_viridis_d() +
+  labs(title = "BAMES Ag - Nitrate F2") +
+  theme_bw()
+
+p_bames_nitr_f2 %>% ggplotly(dynamicTicks = TRUE)
+```
+#### Issue with R plotting
+Facet wrapping results in incomplete plotting - data points in tc_bames2 are not plotted.
+```{r}
+p_tc_bames2 <- results %>%
+  filter(sample == c("tc_bames2", "bames_disc_f1", "bames_nitr_f1")) %>% 
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  facet_wrap(~sample, nrow = 1, scales = "free_y") +
+  scale_fill_viridis_d() +
+  ggtitle("BAMES Standard 10µg/µL") +
+  theme_bw()
+
+p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
+
+```

### 2020-12-10 tsq_data.Rmd
reviewed for syntax

@@
     sample = c("a", "b"),
-    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
+    file = c("tsq_reports/TSQ5934_mAx_TAC_2ml.xls", "tsq_reports/TSQ5934_mAx_TAC_2ml.xls"),
     data = map(file.path(root, file), read_chromeleon_export),

### 2020-12-10 silver_ion_chroma.Rmd
added summary

@@
 date: "12/10/2020"
-output: html_document
+output:
+  html_document:
+    toc: true
+    toc_float: true
 ---
 
+# Summary
+For those compounds observed in F1, the silver ion column resulted in an order-of-magnitude decrease in TIC. F1 was greatly depleted in hydroxy-bearing FAMES.
+
+No compounds eluted in F2, which targets cis monoenes, trans/trans dienes, and CLAs. All monoenes eluted in F1.
+
+None of the compounds expected in F3 eluted (dienes). Oddly, one compound eluted in F3 of the discovery column, FAME C16:0, which would be expected to elute in F1.
+
+Silocone signal was observed across all samples.
+Silicone peaks coeluted with FAMEs 3-OH 14:0 (28 minutes) 17:0 (31 minutes), and 20:0 (36 minutes).
+My guess is that this is a product of the column production/cleaning.
+
+```{r, echo = FALSE}
+knitr::include_graphics('images/silocone_ms.png')
+```
+
+# Protocol
 A BAMES standard was run through two silver ion (Ag) columns to test the efficacy/cleanliness of the columns.
@@
 
-- Instrument method: `OG_DB-1_F9_longMethod_fullscan_300Csource_cyclohexane_FAMES`
-- Processing Method: `BAMES STANDARD`
+`TC-BAME2` was taken from OGL Center Mini -20˚C. 245µg of total lipid BAME was suspended in 245µL of hex.
+10µL (10µg) was removed and combined with 250µL hexane. The entirey of this stock **(10µg)** was applied to the Ag column.
 
-# Protocol
-TC-BAME2 was taken from OGL Center Mini -20˚C. 245µg of total lipid BAME was suspended in 245µL of hex.
-10µL (10µg) was removed and combined with 250µL hexane. The entirey of this stock (10µg) was applied to the Ag column.
-
+### Discovery Ag-Ion Column Chromatography
 0. Set up Ag-Ion columns over waste colleciton vials.
@@
 8. Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.
+
+**GC-MS**
+
+- Instrument method: `OG_DB-1_F9_longMethod_fullscan_300Csource_cyclohexane_FAMES`
+- Processing Method: `BAMES STANDARD`
+
+```
+Autosampler Position: Sample
+37: Cyclohex Blank
+38: TC-BAMES-2
+39: BAMES F1 Disc
+40: BAMES F2 Disc
+41: BAMES F3 Disc
+42: BAMES F1 Nitr
+43: BAMES F2 Nitr
+37: Cyclohex Blank
+```
+
+NOTE: F3 of Ag-Nitrate was disqualified due to the presence of Ag-nitrate powder in the sample collection vial.
 
@@
 ## Plot
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_tc_bames2 <- results %>%
@@
 ```
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_bames_disc_f1 <- results %>%
@@
 ```
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_bames_disc_f2 <- results %>%
@@
 
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_bames_disc_f3 <- results %>%
@@
 ```
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_bames_nitr_f1 <- results %>%
@@
 
-```{r}
+```{r, echo = FALSE, warning=FALSE}
 p_bames_nitr_f2 <- results %>%
@@
 ```
-#### Issue with R plotting
+
+### Issue with R plotting
 Facet wrapping results in incomplete plotting - data points in tc_bames2 are not plotted.

### 2020-12-14 silver_ion_chroma.Rmd
fixed facet wrap

@@
     toc_float: true
+    toc_depth: 3
 ---
@@
 
-## Plot
+#Plots
+Plots generated using `ggplot2` and `plotly`.
+
+## Overview Plot
+```{r, echo = FALSE, warning=FALSE}
+factored_samples <- c('tc_bames2','bames_disc_f1','bames_disc_f2','bames_disc_f3', 'bames_nitr_f1', 'bames_nitr_f2', 'bames_nitr_f3')
+results$sample_f = factor(results$sample, levels=factored_samples)
+
+plot_results <- results %>% 
+  filter(sample %in% c('tc_bames2', 'bames_disc_f1', 'bames_disc_f3', 'bames_nitr_f1'))
+
+p_tc_bames2 <- plot_results %>%
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  facet_wrap(~sample_f, ncol = 1, scales = "free_y") +
+  scale_fill_viridis_d() +
+  ggtitle("BAMES Standard 10µg/µL") +
+  theme_bw()
+
+p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
+
+```
+
+## Individual Plots
+
 ```{r, echo = FALSE, warning=FALSE}
@@
 ```
-
-### Issue with R plotting
-Facet wrapping results in incomplete plotting - data points in tc_bames2 are not plotted.
-```{r}
-p_tc_bames2 <- results %>%
-  filter(sample == c("tc_bames2", "bames_disc_f1", "bames_nitr_f1")) %>% 
-  ggplot() +
-  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
-  geom_bar(stat = 'identity', width = 0.1)+
-  facet_wrap(~sample, nrow = 1, scales = "free_y") +
-  scale_fill_viridis_d() +
-  ggtitle("BAMES Standard 10µg/µL") +
-  theme_bw()
-
-p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE)
-
-```

### 2020-12-16 silver_ion_chroma.Rmd
fixed typo

@@
 # Summary
+
 For those compounds observed in F1, the silver ion column resulted in an order-of-magnitude decrease in TIC. F1 was greatly depleted in hydroxy-bearing FAMES.
@@
 # Protocol
+
 A BAMES standard was run through two silver ion (Ag) columns to test the efficacy/cleanliness of the columns.
@@
 
-`TC-BAME2` was taken from OGL Center Mini -20˚C. 245µg of total lipid BAME was suspended in 245µL of hex.
-10µL (10µg) was removed and combined with 250µL hexane. The entirey of this stock **(10µg)** was applied to the Ag column.
+`TC-BAME2` was taken from OGL Center Mini -20˚C.
+245µg of total lipid BAME was suspended in 245µL of hex.
+10µL (10µg) was removed and combined with 250µL hexane.
+The entirey of this stock **(10µg)** was applied to the Ag column.
 
 ### Discovery Ag-Ion Column Chromatography
-0. Set up Ag-Ion columns over waste colleciton vials.
+
+0.  Set up Ag-Ion columns over waste collection vials.
 1.  Condition SPE with 4mL acetone
@@
 3.  Load FAMEs in hexane derived from sample extraction at a flow rate of 2-3 drops/second. Remove waste collection vials and replace with fraction 1 (F1) collection vials (40mL glass vials).
-4. Elute F1 with 6mL hexane:acetone 96:4
-*Fraction 1 targets saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids*
-5. Elute F2 with 4mL hexane:acetone 90:10
-*Fraction 2 will target: cis monoenes, trans/trans dienes, CLAs*
-6. Elute F3 with 4mL acetone
-*Fraction 3 targets cis/cis dienes, other dienes, trienes.*
+4.  Elute F1 with 6mL hexane:acetone 96:4 *Fraction 1 targets saturated FAs, trans monoenes, cis/cis and trans/trans conjugated linoleic acids*
+5.  Elute F2 with 4mL hexane:acetone 90:10 *Fraction 2 will target: cis monoenes, trans/trans dienes, CLAs*
+6.  Elute F3 with 4mL acetone *Fraction 3 targets cis/cis dienes, other dienes, trienes.*
 7.  Evaporate all fractions at 40˚C under N2, sparge.
 8.  Reconstituted in three 100µL hexane washes, added to a GC vial with insert.
-8. Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.
+9.  Evaporated at 40˚C under N2, reconstituted in 50µL cyclohexane for GC analysis.
 
@@
 
+```{=html}
+<!-- -->
 ```
@@
     37: Cyclohex Blank
-```
 
@@
 ## Data Import
+
 ```{r}
@@
 ## Data Cleanup
-``` {r}
+
+```{r}
 results <- all_data %>% 
@@
 
-#Plots
-Plots generated using `ggplot2` and `plotly`.
+\#Plots Plots generated using `ggplot2` and `plotly`.
 
 ## Overview Plot
+
 ```{r, echo = FALSE, warning=FALSE}
@@
 ```
+
 ```{r, echo = FALSE, warning=FALSE}

### 2020-12-16 modified_silver_ion_chroma.Rmd
second agion attempt

---
title: "Modified Silver Ion Chroma"
author: "Tristan Caro"
date: "12/16/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

# Silver Ion Chroma (12/15/2020)

## Summary

## Protocol

Derived from ["Supelco Discovery Ag-Ion SPE"](https://www.sigmaaldrich.com/catalog/product/supelco/54225u?lang=en&region=US) and comments from Seb & Jamie. This protocol provides a wider range of liquid phases with which to elute FAMEs.

1.  Set up Ag-Ion columns (SPE) over waste collection (40mL) vials.

2.  Condition SPE with 4mL acetone.

3.  Equilibrate with 4mL hexane.

4.  Load FAMES in 100µL hexane derived from sample extraction at a flow rate of 2-3 drops per second. Remove waste collection vials and replace with Fraction 1 (F1) collection vials.

5.  Elute **F1** with 4mL hexane.
    *F1 should rule out solvent carry-through.*

6.  Elute **F2** with 4mL hexane:acetone 99:1.

7.  Elute **F3** with 4mL hexane:acetone 96:4.

8.  Elute **F4** with 4mL hexane:acetone 90:10.

9.  Elute **F5** with 4mL acetone.

10. Evaporate all fractions at 40˚C under N2.

11. Reconstitute in 100µL cyclohexane prior to GC analysis.

**BAME Standard and Sample**

1.  Use TC-BAME3 (50µg BAME in 200µL: 0.25µg/µL or 10ng/µL per compound)

2.  Divide in half:
    Use 100µL as a **standard**.
    Use 100µL as a **sample.**
    *The column sees 100µL \* 10ng/µL = 1000ng (1µg) per compound).*

3.  **After** SPE, add PAIBE to each fraction (to conc of 10ng/µL), including BAME standard.

    -   From `100ng/1µL PAIBE`, add 10µL to each fraction (1000ng; 1µg) for a total volume of 100µL. (1000ng / 100µL = 10ng/µL)

**PAIBE**

1.  PAIBE donated from JM as 1mg/1mL (1µg/1µL) in cyclohexane.

2.  Remove 2mL of 1µg/1µL (2µg). Add to GC vial. Label `PAIBE 1µg/1µL`.

3.  Remove 100µL of 1µg/1µL (100ng). Add to GC vial. Dilute with 900µL cyclohexane for a total volume of 1mL. Label `PAIBE 100ng/1µL`.

## Results

```{r, include = FALSE}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)

# Source
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
```

### Data Import

```{r}
# Define path names and sample names
root <- "data/2020.12.15_TC_BAMES_AgionMod_DB1"
path_names <- list.files("data/2020.12.15_TC_BAMES_AgionMod_DB1")
sample_names <- path_names %>% 
  str_sub(start = 9, end = -5) %>% 
  str_replace("_100ul", "")
sample_names

# read_chromeleon_export is a sourced R function. See above.
all_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)

```

### Data Cleanup

```{r, warning = FALSE}
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
  )

results <- results %>% 
  mutate(saturation = case_when(
    str_detect(`Peak Name`, "OH") ~ "n0 hydroxy",
    str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
    str_detect(`Peak Name`, ":0") ~ "n0",
    str_detect(`Peak Name`, ":2") ~ "n2 cis",
    str_detect(`Peak Name`, "cis") ~ "n1 cis",
    str_detect(`Peak Name`, "trans") ~ "n1 trans",
    str_detect(`Peak Name`, "PAIBE") ~ "PAIBE"
    )
  )
```

### Overview Plot

```{r, echo = FALSE, warning=FALSE, fig.width=7, fig.height = 10}
plot_results <- results %>% 
  filter(!sample %in% c('cyclohex_blank1', 'cyclohex_blank2', 'cyclohex_blank3', 'cyclohex_blank4'))

factored_samples <- c('tcbames3','BAME_modagion_F1','BAME_modagion_F2','BAME_modagion_F3', 'BAME_modagion_F4', 'BAME_modagion_F5')

plot_results$sample_f = factor(plot_results$sample, levels=factored_samples)

p_tc_bames2 <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = saturation, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~sample_f, ncol = 1, scales = "free_y") +
  ggtitle("BAMES Standard 10µg/µL") +
  theme_bw()

p_tc_bames2 %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))
```

### Quantification

PAIBE was used as a quantification standard at 10ng/µL. This was meant to be comparable to the concentration of individual BAME compounds run through the column (10ng/µL per BAME, 250ng/µL total BAME).

```{results <- results %>%}
  group_by(sample) %>% 
  mutate(
    PAIBE_height = # PAIBE relative height value for given `sample`,
    rel_to_PAIBE = `Relative Height` * / PAIBE_height
    conc_ng_ul = rel_to_PAIBE * 10
  )

```

###

### 2020-12-16 silver_ion_chroma.Rmd
fixed typo

@@
 author: "Tristan Caro"
-date: "12/10/2020"
+date: "12/16/2020"
 output:
@@
 
-# Summary
+# Silver Ion Chroma (12/10/2020)
+
+## Summary
+
+> NOTE: BAME concentrations were not correct. See \`modified_silver_ion_chroma.Rmd\`
 
@@
 
-# Protocol
+### Protocol
 
@@
 
-### Discovery Ag-Ion Column Chromatography
+#### Discovery Ag-Ion Column Chromatography
 
@@
 
-```{=html}
 <!-- -->
-```
+
     Autosampler Position: Sample
@@
 
-# Data
+## Data
 
@@
 
-## Data Import
+### Data Import
 
@@
 
-## Data Cleanup
+### Data Cleanup
 
@@
 
-## Overview Plot
+### Overview Plot
 
@@
 
-## Individual Plots
+### Individual Plots
 

### 2021-01-18 modified_silver_ion_chroma_2.Rmd
methods, data import

---
title: "Modified Silver Ion Chroma"
author: "Tristan Caro"
date: "1/18/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

# Modified Silver Ion Chroma (1/15/21)

Following the success of [1️⃣**Modified Ag-ion SPE 1**](https://www.notion.so/Modified-Ag-ion-SPE-1-846ff2a886094428bd8effbb9f86e8b6), and comments from Seb and Jamie, we have further refined the ideal silver ion separation for FAMEs. Now, we are testing separation of FAMEs derived from free fatty acids ("F4s") donated by Jamie. The free FAs were derivatized to FAMEs using the BF3/MeOH method. In short:

1.  100µL of BF3/MeOH mixed with free FAs in 2ml DCM.
2.  Heated at 70˚C for 10 minutes (temp checked with digital heat block, let temp equilibrate for 5 minutes).
3.  Add 2mL H2O and 3mL hexane for liquid liquid extraction. Repeat hexane extraction 2x for a total of 9ml organic phase removed.
4.  Dry down under N2.

Samples were then fractioned by silver ion chromatography as described below.

## Modified Ag-Ion SPE Protocol 2

1.  Set up Ag-Ion columns (SPE) over waste collection (40mL) vials.
2.  Condition SPE with 4mL acetone.
3.  Equilibrate with 4mL hexane.
4.  Load FAMES in 100µL hexane derived from sample extraction at a flow rate of 2-3 drops per second. Remove waste collection vials and replace with Fraction 1 (F1) collection vials.
5.  Elute **F1** with 5mL 99:1 hex:ac (saturated and cyclo FAMEs)
6.  Elute **F2** with 5mL hex:ac 99:2 (additional saturated FAMEs)
7.  Elute **F3** with 5mL 90:10 hex:ac (trans, cis monoenes)
8.  Elute **F4** with 5mL acetone (dienes)
9.  Elute **F5** with 5mL 94:6 acetone:acetonitrile (trienes and tetraenes).
10. Evaporate all fractions at 40˚C under N2.
11. Reconstitute in 100µL cyclohexane prior to GC analysis.

Before GCMS analysis, 1µg of PAIBE quantification standard was added as 10µL of 100ng/µL. This was added to all fractions but *not* BAME standard.

BAME standard used is TC-BAME3.

## Results

```{r, include = FALSE}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)

# Source
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
```

```{r}
# Define path names and sample names
root <- "data/2021.01.15_TC_SFAMES_AgIon_DB1"
path_names <- list.files("data/2021.01.15_TC_SFAMES_AgIon_DB1")
path_names <- path_names %>% 
  str_subset("blank", negate = TRUE) %>% 
  str_subset("Blank", negate = TRUE) %>% 
  str_subset("GCMS-STD", negate = TRUE)
sample_names <- path_names %>% 
  str_replace("TSQ.....", "") %>% 
  str_replace(".xls", "")

# read_chromeleon_export is a sourced R function. See above.
all_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

### 2021-01-19 modified_silver_ion_chroma_2.Rmd
added plotly and knitted

@@
     toc_depth: 3
+    code_folding: hide
 ---
@@
 
-Following the success of [1️⃣**Modified Ag-ion SPE 1**](https://www.notion.so/Modified-Ag-ion-SPE-1-846ff2a886094428bd8effbb9f86e8b6), and comments from Seb and Jamie, we have further refined the ideal silver ion separation for FAMEs.
+Following the tentative success of [1️⃣**Modified Ag-ion SPE 1**](https://www.notion.so/Modified-Ag-ion-SPE-1-846ff2a886094428bd8effbb9f86e8b6), and comments from Seb and Jamie, we have further refined the ideal silver ion separation for FAMEs.
 Now, we are testing separation of FAMEs derived from free fatty acids ("F4s") donated by Jamie.
@@
 
-## Results
+## Data Proc and Cleanup
 
-```{r, include = FALSE}
+```{r}
 # Libraries
@@
 ```
+
+```{r, warning = FALSE}
+# Data cleanup
+results <- all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # major compound groups
+  mutate(
+    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
+  )
+
+results <- results %>% 
+  mutate(saturation = case_when(
+    str_detect(`Peak Name`, "OH") ~ "n0 hydroxy",
+    str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
+    str_detect(`Peak Name`, ":0") ~ "n0",
+    str_detect(`Peak Name`, ":2") ~ "n2 cis",
+    str_detect(`Peak Name`, "cis") ~ "n1 cis",
+    str_detect(`Peak Name`, "trans") ~ "n1 trans",
+    str_detect(`Peak Name`, "PAIBE") ~ "PAIBE"
+    )
+  )
+```
+
+## Overview Plot
+
+Most compounds derivatized from the free fatty acid fraction (F4) of Jamie's Boulder soil sample are saturated FAMEs or not readily identifiable by mass spec.
+For clarity, sterols, alkanes, and ethers were excluded from the chromeleon data export.
+FAMEs are saturated unless noted otherwise.
+
+```{r, fig.width=8, fig.height=10, warning=FALSE}
+# Any necessary limitations to plotted results would go here
+plot_results <- results
+
+# Factor the samples to desired order
+factored_samples <- c('TC_BAMES_3','SFAMES','SFAMES_F1','SFAMES_F2', 'SFAMES_F3', 'SFAMES_F4', "SFAMES_F5")
+
+plot_results$sample_f = factor(plot_results$sample, levels=factored_samples)
+
+plot_results <- plot_results %>% 
+  mutate(fraction_eluent = case_when(
+    sample == "TC_BAMES_3" ~ "BAME",
+    sample == "SFAMES" ~ "Total Fraction",
+    sample == "SFAMES_F1" ~ "F1: 99:1 Hex:Ac (Saturated/Cyclo FAMES)",
+    sample == "SFAMES_F2" ~ "F2: 99:2 Hex:Ac (Addl Saturated FAMES)",
+    sample == "SFAMES_F3" ~ "F3: 90:10 Hex:Ac (trans, cis monoenes)",
+    sample == "SFAMES_F4" ~ "F4: Acetone (dienes)",
+    sample == "SFAMES_F5" ~ "F5: 94:6 Acetone:acetonitrile (poly-enes)"
+     )
+  )
+
+factored_eluents <- c('BAME', "Total Fraction", "F1: 99:1 Hex:Ac (Saturated/Cyclo FAMES)","F2: 99:2 Hex:Ac (Addl Saturated FAMES)","F3: 90:10 Hex:Ac (trans, cis monoenes)", "F4: Acetone (dienes)", "F5: 94:6 Acetone:acetonitrile (poly-enes)")
+
+plot_results$fraction_eluent_f = factor(plot_results$fraction_eluent, levels=factored_eluents)
+
+p_sfames <- plot_results %>%
+  ggplot() +
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
+  geom_bar(stat = 'identity', width = 0.1)+
+  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
+  ggtitle("Boulder Soil Free FA as FAMES") +
+  theme_bw() +
+  theme(legend.position = "none")
+
+p_sfames %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))
+```

### 2021-01-21 modified_silver_ion_chroma_2.Rmd
updated plots

@@
   mutate(saturation = case_when(
-    str_detect(`Peak Name`, "OH") ~ "n0 hydroxy",
+    str_detect(`Peak Name`, "C19 monoene") ~ "C19:1",
     str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
@@
   ggtitle("Boulder Soil Free FA as FAMES") +
-  theme_bw() +
-  theme(legend.position = "none")
+  theme_bw()
 

### 2021-02-17 libs/chromeleon_peaks.R
added new library for peak resolution

@@ -2,10 +2,10 @@
 #' read a chromleon export file
 #' @param file_path path to the excel file to be read
 #' @return a list with two data frames for injection_details and integration_results
-read_chromeleon_export <- function(file_path) {
+read_chromeleon_export_peaks <- function(file_path) {
   
   # read raw data
-  raw_data <- suppressMessages(readxl::read_excel(file_path, sheet = "Integration"))
+  raw_data <- suppressMessages(readxl::read_excel(file_path, sheet = "Peak Analysis"))
   names(raw_data) <- paste0("x", 1:ncol(raw_data))
   
   
@@ -19,11 +19,11 @@ read_chromeleon_export <- function(file_path) {
   injection_details %>% knitr::kable()
   
   all_results <- raw_data %>% 
-    filter(row_number() > which(x1 == "Integration Results")[1]) 
+    filter(row_number() > which(x1 == "Peak Analysis")[1]) 
   
   integration_results <- 
     setNames(all_results[-c(1:3),], t(all_results[1,])[,1]) %>%
     mutate_at(vars(-`Peak Name`), function(x) suppressWarnings(as.numeric(x)))
   
-  list(injection_details = injection_details, integration_results = integration_results)
+  list(injection_details = injection_details, peak_analysis = peak_analysis)
 }

### 2021-02-17 gc_column_comparison.Rmd
added comparison of gc column elution quality

---
title: "Column Comparison"
author: "Tristan Caro"
date: "2/16/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

```{r}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)

# Source
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
source(file.path("libs", "chromeleon_peaks.R"))
```

```{r}
# Define path and sample names
root <- "data/2021.02.04_TC_FAMES_Test_DB1"
path_names <- list.files(root)
path_names <- path_names %>% 
  str_subset("blank", negate = TRUE) %>% 
  str_subset("Blank", negate = TRUE) %>% 
  str_subset("GCMS-STD", negate = TRUE)
sample_names <- path_names %>% 
  str_replace("TSQ.....", "") %>% 
  str_replace(".xls", "")

# Create a tibble of integration data
# read_chromeleon_export is a sourced function. See above.
all_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)

# Create a tibble of peak analysis data
peak_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export_peaks),
    injection_details = map(data, "injection_details"),
    peak_analysis = map(data, "peak_analysis")
  ) %>% select(-data)
```

```{r, warning = FALSE}
# Data cleanup
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor(),
    saturation = case_when(
      str_detect(`Peak Name`, ":0") ~ "n0",
      str_detect(`Peak Name`, ":1") ~ "n1",
      str_detect(`Peak Name`, "cis") ~ "n1 cis",
      str_detect(`Peak Name`, "trans") ~ "n2 trans",
      str_detect(`Peak Name`, ":2") ~ "n2",
      str_detect(`Peak Name`, ":3") ~ "n3",
      str_detect(`Peak Name`, ":4") ~ "n4",
      str_detect(`Peak Name`, ":5") ~ "n5",
      str_detect(`Peak Name`, ":6") ~ "n6",
      str_detect(`Peak Name`, ":7") ~ "n7",
    ),
    is_standard = case_when(
      str_detect(`Peak Name`, "STD") ~ TRUE,
      str_detect(`Peak Name`, "STD", negate = TRUE) ~ FALSE,
    )
  )
```

```{r, fig.width=8, fig.height=13, warning=FALSE}
# Overview Plot
p_fames_db1 <- results %>%
  ggplot() +
  aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1) +
  facet_wrap(~sample, ncol = 1, scales = "free_y") +
  ggtitle("Soil FAMEs on DB1 Overview") +
  geom_label_repel(aes(vjust =-7, box.padding = 0.5),
                   show.legend = FALSE,
                   size = 2,
                   segment.alpha = 0.5) +
  theme_bw() +
  theme(legend.position = "bottom")
p_fames_db1
```

### 2021-03-08 gc_column_comparison.Rmd
conflict

@@
 ```
+
+# Load Data
 
@@
     injection_details = map(data, "injection_details"),
-    peak_analysis = map(data, "peak_analysis")
+    integration_results = map(data, "integration_results")
   ) %>% select(-data)

### 2021-03-08 libs/chromeleon_peaks.R
peak analysis library

@@ -1,7 +1,7 @@
 
 #' read a chromleon export file
 #' @param file_path path to the excel file to be read
-#' @return a list with two data frames for injection_details and integration_results
+#' @return a list with two data frames for injection_details and peak analysis
 read_chromeleon_export_peaks <- function(file_path) {
   
   # read raw data
@@ -19,11 +19,11 @@ read_chromeleon_export_peaks <- function(file_path) {
   injection_details %>% knitr::kable()
   
   all_results <- raw_data %>% 
-    filter(row_number() > which(x1 == "Peak Analysis")[1]) 
+    filter(row_number() > which(x1 == "Peak Results")[1]) 
   
   integration_results <- 
     setNames(all_results[-c(1:3),], t(all_results[1,])[,1]) %>%
     mutate_at(vars(-`Peak Name`), function(x) suppressWarnings(as.numeric(x)))
   
-  list(injection_details = injection_details, peak_analysis = peak_analysis)
+  list(injection_details = injection_details, integration_results = integration_results)
 }

### 2021-03-08 gc_column_comparison_2.Rmd
image

---
title: "Column Comparison"
author: "Tristan Caro"
date: "2/16/2021"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
---

# Relevant Equations
## Plates (EP)

$$
N = 5.54\cdot(\frac{R_t}{W})^2
$$
Where N is the plate count (theoretical plates), Rt is retention time, W is peak width at 50% peak height (FWHM).

## Asymmetry (EP)
$$
A_s = \frac{w_{0.05}}{2d}
$$
Where $A_s$ is symmetry factor, $w_{0.05}$ is peak width at one-twentieth of peak height, d is distance between perpendicular dropped from the peak max and the leading edge of the peak at one-twentieth peak height.

## Resolution
Chromeleon uses the European Pharmacopeia (EP) resolution equation.

$$
R = \frac{1.18(Rt_2 - Rt_1)}{(W_2 + W_1)}
$$

Where R is resolution, $Rt$ is retention time, and W is the peak width at 50% peak height (FWHM).

# Libraries

```{r}
# Libraries
library(tidyverse)
library(plotly)
library(ggrepel)
library(ggsci)

# Source
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
source(file.path("libs", "chromeleon_peaks.R"))
```

# Load Data

```{r}
# Define path and sample names
root <- "column_testing/run_data"
path_names <- list.files(root)
path_names <- path_names %>% 
  str_subset("blank", negate = TRUE) %>% 
  str_subset("Blank", negate = TRUE) %>% 
  str_subset("GCMS-STD", negate = TRUE)
sample_names <- path_names %>% 
  str_replace("TSQ.....", "") %>% 
  str_replace(".xls", "")

# Create a tibble of integration data
# read_chromeleon_export is a sourced function. See above.
all_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)

# Create a tibble of peak analysis data
peak_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export_peaks),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

```{r, warning = FALSE}
# Data cleanup

results <- all_data %>%
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor(),
    saturation = case_when(
      str_detect(`Peak Name`, ":0") ~ "n0",
      str_detect(`Peak Name`, "PAIBE") ~ "n0",
      str_detect(`Peak Name`, ":1") ~ "n1",
      str_detect(`Peak Name`, ":2") ~ "n2",
      str_detect(`Peak Name`, ":3") ~ "n3",
      str_detect(`Peak Name`, ":4") ~ "n4",
      str_detect(`Peak Name`, ":5") ~ "n5",
      str_detect(`Peak Name`, ":6") ~ "n6",
      str_detect(`Peak Name`, ":7") ~ "n7",
    ),
    is_standard = case_when(
      str_detect(`Peak Name`, "STD") ~ TRUE,
      str_detect(`Peak Name`, "STD", negate = TRUE) ~ FALSE,
    ),
    column_type = case_when(
      str_detect(`sample`, "DB1") ~ "DB1",
      str_detect(`sample`, "DB5") ~ "DB5",
      str_detect(`sample`, "ZBFAMES") ~ "ZBFAMES",
    ),
    standard_ID = case_when(
      str_detect(`sample`, "BAME") ~ "BAME",
      str_detect(`sample`, "FAMES37") ~ "37FAME",
    )
  )

# Turn Column type into a factor
results$column_type <- factor(results$column_type, levels = c("DB1", "DB5", "ZBFAMES"))

```

```{r, fig.width=10, fig.height=10, warning=FALSE}
# Overview Plot
p_fames_db1 <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_grid(rows = vars(column_type), cols = vars(standard_ID), scales = "free_y") +
    ggtitle("FAME Standards Overview") +
    #geom_label_repel(aes(vjust =-7, box.padding = 0.5),
                     #show.legend = FALSE,
                     #size = 2,
                     #segment.alpha = 0.5) +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames_db1
```

### 2021-03-08 gc_column_comparison_2.Rmd
new plotting with facet_grid

@@
     ggtitle("FAME Standards Overview") +
-    #geom_label_repel(aes(vjust =-7, box.padding = 0.5),
-                     #show.legend = FALSE,
-                     #size = 2,
-                     #segment.alpha = 0.5) +
     theme_bw() +

### 2021-03-08 gc_column_comparison_2.Rmd
Update gc_column_comparison_2.Rmd

@@
 library(ggsci)
+library(ggsignif)
 
@@
 
+# Data cleanup
+
 ```{r, warning = FALSE}
 # Data cleanup
-
 results <- all_data %>%
@@
 
-```{r, fig.width=10, fig.height=10, warning=FALSE}
+# Overview Plot
+```{r, fig.width=10, fig.height=6, warning=FALSE}
 # Overview Plot
@@
 ```
+
+```{r}
+peak_analysis <- peak_data %>%
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # major compound groups
+  mutate(
+    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor(),
+    saturation = case_when(
+      str_detect(`Peak Name`, ":0") ~ "n0",
+      str_detect(`Peak Name`, "PAIBE") ~ "n0",
+      str_detect(`Peak Name`, ":1") ~ "n1",
+      str_detect(`Peak Name`, ":2") ~ "n2",
+      str_detect(`Peak Name`, ":3") ~ "n3",
+      str_detect(`Peak Name`, ":4") ~ "n4",
+      str_detect(`Peak Name`, ":5") ~ "n5",
+      str_detect(`Peak Name`, ":6") ~ "n6",
+      str_detect(`Peak Name`, ":7") ~ "n7",
+    ),
+    is_standard = case_when(
+      str_detect(`Peak Name`, "STD") ~ TRUE,
+      str_detect(`Peak Name`, "STD", negate = TRUE) ~ FALSE,
+    ),
+    column_type = case_when(
+      str_detect(`sample`, "DB1") ~ "DB1",
+      str_detect(`sample`, "DB5") ~ "DB5",
+      str_detect(`sample`, "ZBFAMES") ~ "ZBFAMES",
+    ),
+    standard_ID = case_when(
+      str_detect(`sample`, "BAME") ~ "BAME",
+      str_detect(`sample`, "FAMES37") ~ "37FAME",
+    )
+  )
+
+# Turn Column type into a factor
+results$column_type <- factor(results$column_type, levels = c("DB1", "DB5", "ZBFAMES"))
+```
+# Resolution Plot
+Significance testing via Wilcox Test
+
+```{r}
+p_resolution <- peak_analysis %>% ggplot(aes(x = column_type, y = `Resolution (EP)`, fill = column_type)) +
+  geom_boxplot() +
+  facet_wrap(~standard_ID)+
+  scale_fill_npg() +
+  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
+              textsize = 2) +
+  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
+              y_position = 40,
+              textsize = 2) +
+  xlab("Column Type") +
+  ggtitle("FAME Peak Resolution") +
+  theme_classic() +
+  theme(legend.title = element_blank())
+p_resolution
+```
+
+# Symmetry Plot
+Significance testing via Wilcox Test
+
+```{r}
+p_symmetry <- peak_analysis %>% ggplot(aes(x = column_type, y = `Asymmetry (EP)`, color = saturation)) +
+  geom_point() +
+  geom_jitter(width = 0.2, height = 0) +
+  facet_wrap(~standard_ID)+
+  scale_color_npg() +
+  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
+  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
+              y_position = 4.1,
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
+  xlab("Column Type") +
+  ggtitle("FAME Peak Asymmetry") +
+  theme_classic() +
+  theme(legend.title = element_blank())
+p_symmetry
+```
+
+# Plates Plot
+Significance testing via Wilcox Test
+
+```{r}
+p_plates <- peak_analysis %>% ggplot(aes(x = column_type, y = `Plates (EP)`, color = saturation)) +
+  geom_point() +
+  geom_jitter(width = 0.2, height = 0) +
+  facet_wrap(~standard_ID)+
+  scale_color_npg() +
+  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
+  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
+              textsize = 2,
+              map_signif_level = TRUE,
+              y_position = 6e6,
+              color = "black") +
+  xlab("Column Type") +
+  ggtitle("FAME Plates") +
+  theme_classic() +
+  theme(legend.title = element_blank())
+p_plates
+```
+
+# Retention Time Plot
+
+```{r}
+p_retention <- peak_analysis %>% ggplot(aes(x = column_type, y = `Retention Time`, color = saturation)) +
+  geom_point() +
+  geom_jitter(width = 0.2, height = 0) +
+  facet_wrap(~standard_ID)+
+  scale_color_npg() +
+  geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
+  geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black",
+              y_position = 41) +
+  xlab("Column Type") +
+  ylab("Retention Time (Minutes") +
+  ggtitle("FAME Retention Times") +
+  theme_classic() +
+  theme(legend.title = element_blank())
+p_retention
+```

### 2021-03-09 gc_column_comparison_2.Rmd
additional plots

@@
 # Overview Plot
-p_fames_db1 <- results %>%
+p_fames_overview <- results %>%
   ggplot() +
@@
     theme(legend.position = "bottom")
-p_fames_db1
+p_fames_overview
 ```
@@
 ```{r}
-p_resolution <- peak_analysis %>% ggplot(aes(x = column_type, y = `Resolution (EP)`, fill = column_type)) +
+p_resolution <- peak_analysis %>% ggplot(aes(x = column_type, y = `Resolution (EP)`, color = saturation)) +
   geom_boxplot() +
   facet_wrap(~standard_ID)+
-  scale_fill_npg() +
+  scale_color_npg() +
   geom_signif(comparisons = list(c("DB1", "DB5"), c("DB5", "ZBFAMES")),
-              textsize = 2) +
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
   geom_signif(comparisons = list(c("DB1", "ZBFAMES")),
               y_position = 40,
-              textsize = 2) +
+              textsize = 2,
+              map_signif_level = TRUE,
+              color = "black") +
   xlab("Column Type") +
@@
 
+Peak resolution distributions are more or less conserved across all column types.
+
 # Symmetry Plot
@@
 ```{r}
-p_symmetry <- peak_analysis %>% ggplot(aes(x = column_type, y = `Asymmetry (EP)`, color = saturation)) +
-  geom_point() +
-  geom_jitter(width = 0.2, height = 0) +
+p_symmetry <- peak_analysis %>% ggplot(aes(x = column_type, y = `Asymmetry (EP)`)) +
+  geom_boxplot() +
   facet_wrap(~standard_ID)+
@@
 
+Not sure what to make of peak asymmetry metric. Most of the data hovers around 1, which I assume is a good sign that peaks do not have much tailing.
+
 # Plates Plot
-Significance testing via Wilcox Test
+Significance testing via Wilcox Test.
 
@@
 p_plates <- peak_analysis %>% ggplot(aes(x = column_type, y = `Plates (EP)`, color = saturation)) +
-  geom_point() +
-  geom_jitter(width = 0.2, height = 0) +
+  geom_boxplot() +
   facet_wrap(~standard_ID)+
@@
 
+DB1 has the highest theoretical plate count.
+This is not surprising since it is a 60m column and plates are proportional to column.
+Both DB5 and ZBFAMES are 30m column, and DB5 has significantly higher theoretical plate count.
+
 # Retention Time Plot
@@
 p_retention <- peak_analysis %>% ggplot(aes(x = column_type, y = `Retention Time`, color = saturation)) +
-  geom_point() +
-  geom_jitter(width = 0.2, height = 0) +
+  geom_jitter(width = 0.1, height = 0) +
   facet_wrap(~standard_ID)+
@@
 ```
+Retention times for DB1 are much longer. DB5 and ZBFAMES are roughly similar.
+
+# Average Peak Distancing
+
+```{r}
+# Mutate to give spacing based on previous peak RT
+peak_analysis <- peak_analysis %>%
+  group_by(sample) %>% 
+  mutate(
+  peak_spacing = `Retention Time` - lag(`Retention Time`))
+peak_analysis_avg <- peak_analysis %>%
+  group_by(sample) %>% 
+  summarise(avg_peak_spacing = mean(peak_spacing, na.rm = TRUE))
+
+# Plot
+p_peak_spacing <- peak_analysis_avg %>%
+  ggplot(aes(x = sample, y = avg_peak_spacing)) +
+  geom_bar(stat = 'identity') +
+  theme(axis.text.x = element_text(angle = 90))
+p_peak_spacing
+```
+This plot isn't telling me too much.
+
+# Saturated Compound Elution
+
+```{r, fig.width=10, fig.height=6, warning=FALSE}
+
+c18points <- results$`Peak Name` %>% 
+  str_subset("18")
+
+p_fames37 <- results %>%
+  filter(column_type %in% c("DB5", "ZBFAMES")) %>% 
+  filter(standard_ID == "37FAME") %>% 
+  ggplot() +
+    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
+    geom_bar(stat = 'identity', width = 0.1) +
+    facet_wrap(~column_type, ncol = 1) +
+    ggtitle("37FAME DB5/ZBFAMES") +
+    # Subset labels
+    geom_label_repel(data = . %>% 
+                       mutate(label = ifelse(`Peak Name` %in% c18points, `Peak Name`, "")),
+                     aes(label = label),
+                     show.legend = FALSE,
+                     size = 2,
+                     nudge_y = 7,
+                     box.padding = 1) +
+    coord_cartesian(ylim = c(0,11)) +
+    theme_bw() +
+    scale_fill_npg() +
+    theme(legend.position = "bottom")
+p_fames37
+
+```

### 2021-03-09 gc_column_comparison_2.Rmd
Update gc_column_comparison_2.Rmd
fixed plot labels

@@
 # Relevant Equations
+
 ## Plates (EP)
+Chromeleon uses the European Pharmacopeia (EP) theoretical plate calculation.
 
@@
 
-```{r}
+```{r, include=FALSE}
 # Libraries
@@
 
-c18points <- results$`Peak Name` %>% 
-  str_subset("18")
+desired_points <- results$`Peak Name` %>% 
+  str_subset(":0|18:")
 
@@
     geom_label_repel(data = . %>% 
-                       mutate(label = ifelse(`Peak Name` %in% c18points, `Peak Name`, "")),
+                       mutate(label = ifelse(`Peak Name` %in% desired_points, `Peak Name`, "")),
                      aes(label = label),
@@
                      size = 2,
-                     nudge_y = 7,
-                     box.padding = 1) +
+                     nudge_y = 2,
+                     box.padding = .5,
+                     label.r = 0) +
     coord_cartesian(ylim = c(0,11)) +
@@
 ```
+
+Here we see that ZBFAMES elution schedule is reversed for multi-saturated compounds.

### 2021-03-11 gc_column_comparison_2.Rmd
added new figure for bame standards

@@
 Here we see that ZBFAMES elution schedule is reversed for multi-saturated compounds.
+
+```{r, fig.width=10, fig.height=6, warning=FALSE}
+desired_points <- results$`Peak Name` %>% 
+  str_subset(":0|18:")
+
+p_bamesdb5zbfames <- results %>%
+  filter(column_type %in% c("DB5", "ZBFAMES")) %>% 
+  filter(standard_ID == "BAME") %>% 
+  ggplot() +
+    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
+    geom_bar(stat = 'identity', width = 0.1) +
+    facet_wrap(~column_type, ncol = 1) +
+    ggtitle("BAME DB5/ZBFAMES") +
+    # Subset labels
+    geom_label_repel(data = . %>% 
+                       mutate(label = ifelse(`Peak Name` %in% desired_points, `Peak Name`, "")),
+                     aes(label = label),
+                     show.legend = FALSE,
+                     size = 2,
+                     nudge_y = 2,
+                     box.padding = .5,
+                     label.r = 0) +
+    coord_cartesian(ylim = c(0,11)) +
+    theme_bw() +
+    scale_fill_npg() +
+    theme(legend.position = "bottom")
+p_bamesdb5zbfames
+
+```

### 2021-07-20 gc_column_comparison_2.Rmd
final commit

--- 2021-03-09 gc_column_comparison_2.Rmd
@@
 # Overview Plot
-```{r, fig.width=10, fig.height=6, warning=FALSE}
+```{r, fig.width=8, fig.height=4, warning=FALSE}
 # Overview Plot

### 2021-07-20 soil_report.Rmd
Soil analysis Rmd

---
title: "Soil Quality"
author: "Tristan Caro"
date: "7/20/2021"
output: html_document
---

# Soil Quality Report
Soils were submitted to CSU Soil Testing Lab on 6/10/2021. Data was reported on 6/30/2021.
The lab tests for pH, salts, excess lime, texture, organic matter, as well as N, P, K, Zn, Fe, Mn, Cu, and S.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggsci)
```

```{r, message=FALSE}
soil_data <- read_csv("soil_report_06302021.csv")

soil_qualities <- soil_data %>% 
  select(c(`Sample ID`, `Excess Lime`, `Texture Estimate`))

soil_values <- soil_data %>% 
  select(!c(`Excess Lime`, `Texture Estimate`))

soil_values_long <- soil_values %>% 
  select(!`Sample Depth (cm)`) %>% 
  pivot_longer(!`Sample ID`, names_to = "Measurement", values_to = "Value")

```

```{r}
p_soil_values_long <- soil_values_long %>% 
  ggplot(aes(x = `Sample ID`, y = `Value`, fill = `Sample ID`)) +
  geom_col() +
  facet_wrap(~`Measurement`, scales = "free_y") +
  scale_fill_aaas() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave("soil_report_plot.png", plot = p_soil_values_long, height = 10, width = 15)
```

### 2021-07-21 tsq_data.Rmd
added gcfid data and plotted it

--- 2019-12-07 tsq_data.Rmd
@@
 ```{r}
-root <- "data"
+root <- "data/gc_fid_data_2020/"
+file_list = list.files(path = root)
 all_data <-
   tibble(
-    sample = c("a", "b"),
-    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
+    sample = file_list,
+    file = file_list,
     data = map(file.path(root, file), read_chromeleon_export),

### 2021-07-21 Sequencing/tables and code/caro_16S.R
initial commit

@@ -1,0 +1,337 @@
+library(mctoolsr)
+
+tax_table_fp = 'seqtab_wTax_mctoolsr_16s_caro.txt'
+map_fp = 'caro_16s_mapping.txt' 
+input = load_taxa_table(tax_table_fp, map_fp)
+
+# Remove mitochondrial and chloroplast sequences, Remove reads assigned as eukaryotes
+input_filt <- filter_taxa_from_input(input, taxa_to_remove = c("Chloroplast","Mitochondria", "Eukaryota"))
+# Remove reads that are unassigned at domain level
+input_filt <- filter_taxa_from_input(input_filt, at_spec_level = 2, taxa_to_remove = "NA")
+
+# Normalize or rarefy your ASV table
+#input_filt <- single_rarefy(input = input_filt, depth = 5000) # CHANGE ME to desired depth.
+
+#### Now following Cliff's R Tutorial for Alpha & Beta Diversity and other Visualization Techniques
+library(plyr) # For hulls
+library(tidyverse) # For data manipulation and plotting
+library(RColorBrewer) # For color palettes
+library(vegan) # For alpha and beta diversity analyses
+library(indicspecies) # For indicator species
+library(car) # For Levene Test and anova
+library(PMCMR) # For Nemenyi posthoc test
+
+
+# We now have an object called input. It contains 3 files - a sequence table, a mapping file, and a taxonomic file.
+head(input$data_loaded) # Rows are OTUs, columns are samples
+head(input$taxonomy_loaded) # Rows are OTUs (now ASVs), columns are different taxonomic levels
+head(input$map_loaded) # Rows are samples, columns are variables
+
+# Initial data examination, rarefying, filtering
+# One of the first things we want to do is see how many sequences per sample there are
+# This is done by getting the column sums of the sequence table, and we'll sort it too.
+sort(colSums(input$data_loaded))
+# We could also save this as an object and plot it
+seqcounts <- as.data.frame(sort(colSums(input$data_loaded)))
+# This puts the sample names as row names and the sequence counts column is titled "sort(colSums(input$data_loaded)))
+# We'll use the pipeline %>% which is very useful for dataframe management with the dplyr package
+# We'll rename the column and make a new column all at once
+seqcounts <- as.data.frame(sort(colSums(input$data_loaded))) %>%
+  rename("seqs" = "sort(colSums(input$data_loaded))") %>%
+  rownames_to_column(var = "sampleID")
[…]

### 2021-07-21 gc_fid_data.Rmd
initial commit

--- 2019-12-07 tsq_data.Rmd
@@
 library(isoreader)
+library(ggrepel)
+library(ggsci)
 
@@
 ```{r}
-root <- "data"
+root <- "data/gc_fid_data_2020/"
+file_list = list.files(path = root)
+file_list <- file_list %>% 
+  str_subset("blank", negate = TRUE) %>% 
+  str_subset("Blank", negate = TRUE) %>% 
+  str_subset("GCMS-STD", negate = TRUE) %>% 
+  str_subset("BLK", negate = TRUE) # remove procedural blanks
+sample_names <- file_list %>% 
+  str_replace("FID.....", "") %>% 
+  str_replace("_100ul-nhex.xls", "") %>% 
+  str_replace("_100ul.xls",)
+
 all_data <-
   tibble(
-    sample = c("a", "b"),
-    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
+    sample = sample_names,
+    file = file_list,
     data = map(file.path(root, file), read_chromeleon_export),
@@
 
-results %>% 
-  filter(!str_detect(`Peak Name`, fixed("?"))) %>% 
-  ggplot() +
-  aes(`Peak Name`, `Relative Area`) +
-  geom_bar(stat = "identity") +
-  theme_figure(axis_x_rotate = 90) +
-  scale_y_continuous(expand = c(0,0)) +
-  facet_wrap(~sample)
+# Combine triplicate samples into one
+results_trip <- results %>% 
+  # Remove standards and fractions for this
+  filter(sample != "FAME37.1") %>% 
+  filter(sample != "TCBAME-2") %>% 
+  filter(!str_detect(sample, "F1")) %>% 
+  filter(!str_detect(sample, "F2")) %>% 
+  filter(!str_detect(sample, "F3")) %>% 
+  filter(!str_detect(sample, "cr")) %>% 
+  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
+  group_by(sample_rep, `Peak Name`) %>% 
+  summarize(rel_area_max = max(`Relative Area`),
+            rel_area_min = min(`Relative Area`),
+            rel_height_max = max(`Relative Height`),
+            rel_height_min = min(`Relative Height`),
+            `Retention Time` = mean(`Retention Time`),
+            `Relative Area` = mean(`Relative Area`),
+            `Relative Height` = mean(`Relative Height`)) %>% 
+  # Add some basic metadata
+  mutate(inc_time_0 = case_when(
+    str_detect(sample_rep, "0") ~ 0,
+    str_detect(sample_rep, "3") ~ 3,
+    str_detect(sample_rep, "7") ~ 7),
+    site = case_when(
+      str_detect(sample_rep, "c") ~ "GG Conifer",
+      str_detect(sample_rep, "t") ~ "NWT Tundra",
+      str_detect(sample_rep, "g") ~ "MM Grassland",
+      str_detect(sample_rep, "m") ~ "GG Meadow")
+  )
+
+results_trip %>% ggplot(aes(x = `Retention Time`, y = `Relative Area`, color = sample_rep, fill = sample_rep)) +
+  geom_col() +
+  geom_errorbar(aes(ymin=rel_area_min, ymax = rel_area_max), color = "black") +
+  theme_classic()
+
+######### PICK UP WITH THIS GGPLOT!
 ```

### 2021-07-26 gc_fid_data.Rmd
attempting to collapse Fx

--- 2021-07-21 tsq_data.Rmd
@@
   fig.keep="all", fig.path=file.path("figures", figure_prefix))
+
+# Define a way to negate  %in%
+`%nin%` = Negate(`%in%`)
 ```
@@
 file_list = list.files(path = root)
+file_list <- file_list %>% 
+  str_subset("blank", negate = TRUE) %>% 
+  str_subset("Blank", negate = TRUE) %>% 
+  str_subset("GCMS-STD", negate = TRUE) %>% 
+  str_subset("BLK", negate = TRUE) # remove procedural blanks
+sample_names <- file_list %>% 
+  str_replace("FID.....", "") %>% 
+  str_replace("_100ul-nhex.xls", "") %>% 
+  str_replace("_100ul.xls", "")
+
 all_data <-
   tibble(
-    sample = file_list,
+    sample = sample_names,
     file = file_list,
@@
 
-# Analyze data
+# Tidy Data
+
+## Unnest integrationd etails
 
@@
 
-results %>% 
-  filter(!str_detect(`Peak Name`, fixed("?"))) %>% 
-  ggplot() +
-  aes(`Peak Name`, `Relative Area`) +
-  geom_bar(stat = "identity") +
-  theme_figure(axis_x_rotate = 90) +
-  scale_y_continuous(expand = c(0,0)) +
-  facet_wrap(~sample)
+```
+
+## Recombine Fractions for m0f0 + m0f3 samples
+See `https://docs.google.com/document/d/1kBNM27kpLauVsBvefoXglYV64GAE0KPrE9SXfRSTvno/edit?usp=sharing` entry `6/8/2021` for more details.
+
+```{r}
+# Recombine Fractions for m0f0 + m0f3 samples
+results_m0f0_m0f3 <- results %>% 
+  filter(str_detect(sample, "_F")) %>% 
+  mutate(frac = case_when(
+    str_detect(sample, "F1") ~ "F1",
+    str_detect(sample, "F2") ~ "F2",
+    str_detect(sample, "F3") ~ "F3")) %>% 
+  mutate(
+    sample = str_remove(sample, "_F.")) %>% 
+  mutate(
+    sample = str_remove(sample, "_"))
+
 ```
@@
 ```{r}
-results %>% 
-  ggplot() +
-  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`) +
-  geom_bar(stat = "identity")
+# Combine triplicate samples into one
+results_trip <- results %>% 
+  # Remove standards and fractions for this
+  filter(sample != "FAME37.1") %>% 
+  filter(sample != "TCBAME-2") %>% 
+  filter(!str_detect(sample, "F1")) %>% 
+  filter(!str_detect(sample, "F2")) %>% 
+  filter(!str_detect(sample, "F3")) %>% 
+  filter(!str_detect(sample, "cr")) %>%
+  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
+  group_by(sample_rep, `Peak Name`) %>%
+  # Replace NA Height and Area values with Zero in order to do summarizing operations
+  mutate(`Relative Height` = replace(`Relative Height`, is.na(`Relative Height`), 0)) %>%
+  mutate(`Relative Area` = replace(`Relative Area`, is.na(`Relative Area`), 0)) %>% 
+  # Generate summary stats
+  summarize(rel_area_max = max(`Relative Area`),
+            rel_area_min = min(`Relative Area`),
+            rel_height_max = max(`Relative Height`),
+            rel_height_min = min(`Relative Height`),
+            `Retention Time` = mean(`Retention Time`),
+            `Relative Area` = mean(`Relative Area`),
+            `Relative Height` = mean(`Relative Height`)) %>% 
+  # Add some basic metadata
+  mutate(inc_time = case_when(
+    str_detect(sample_rep, "...0") ~ 0,
+    str_detect(sample_rep, "...3") ~ 3,
+    str_detect(sample_rep, "...7") ~ 7),
+    site = case_when(
+      str_detect(sample_rep, "c") ~ "GG Conifer",
+      str_detect(sample_rep, "t") ~ "NWT Tundra",
+      str_detect(sample_rep, "g") ~ "MM Grassland",
+      str_detect(sample_rep, "m") ~ "GG Meadow")
+  )
+```
+
+# Summary Plots
+```{r}
+p_0hr_FAs <- results_trip %>% filter(inc_time == "0") %>% 
+  # Remove Standard Peaks
+  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
+  ggplot(aes(x = `Retention Time`, 
+             y = `Relative Area`, 
+             color = sample_rep, 
+             fill = sample_rep, 
+             label = `Peak Name`)) +
+  geom_col(width = 0.08) +
+  geom_errorbar(aes(ymin=rel_area_min, 
+                    ymax = rel_area_max), 
+                color = "black", 
+                width = 0.05) +
+  facet_wrap(~sample_rep, 
+             ncol = 1, 
+             scales = "free_y") +
+  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
+  ggtitle("PLFA Profile: 0hr") +
+  theme_bw() +
+  scale_color_jama() +
+  scale_fill_jama()
+
+p_72hr_FAs <- results_trip %>% filter(inc_time == "3") %>% 
+  # Remove Standard Peaks
+  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
+  ggplot(aes(x = `Retention Time`, 
+             y = `Relative Area`, 
+             color = sample_rep, 
+             fill = sample_rep, 
+             label = `Peak Name`)) +
+  geom_col(width = 0.08) +
+  geom_errorbar(aes(ymin=rel_area_min, 
+                    ymax = rel_area_max), 
+                color = "black", 
+                width = 0.05) +
+  facet_wrap(~sample_rep, 
+             ncol = 1, 
+             scales = "free_y") +
+  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
+  ggtitle("PLFA Profile: 72hr") +
+  theme_bw() +
+  scale_color_jama() +
+  scale_fill_jama()
+
+p_168hr_FAs <- results_trip %>% filter(inc_time == "7") %>% 
+  # Remove Standard Peaks
+  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
+  ggplot(aes(x = `Retention Time`, 
+             y = `Relative Area`, 
+             color = sample_rep, 
+             fill = sample_rep, 
+             label = `Peak Name`)) +
+  geom_col(width = 0.08) +
+  geom_errorbar(aes(ymin=rel_area_min, 
+                    ymax = rel_area_max), 
+                color = "black", 
+                width = 0.05) +
+  facet_wrap(~sample_rep, 
+             ncol = 1, 
+             scales = "free_y") +
+  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 3, nudge_y = 2, segment.color = "black") +
+  ggtitle("PLFA Profile: 168hr") +
+  theme_bw() +
+  scale_color_jama() +
+  scale_fill_jama()
+p_168hr_FAs
+
+```
+
+## Biocrust Plots
+```{r}
+# Subsetting Intact Biocrust Experiment
+results_cr <- results %>% filter(sample %in% c("cri0", "cri3", "cri5", "cri7"))
+results_cr <- as.data.frame(results_cr)
+
+results_cr <- results_cr %>% 
+  # Add some basic metadata
+  mutate(inc_time = case_when(
+    str_detect(sample, "...0") ~ 0,
+    str_detect(sample, "...3") ~ 3,
+    str_detect(sample, "...5") ~ 5,
+    str_detect(sample, "...7") ~ 7),
+    site = "intact biocrust")
+write.csv(file = "data/intact_biocrust_PLFAs.csv", results_cr)
 ```
@@
 ```{r}
-results %>% 
-  ggplot() +
-  aes(`Retention Time`, `Relative Height`, fill = group, label = `Peak Name`) +
-  geom_bar(stat = "identity") +
-  facet_grid(sample ~ .) +
-  theme_figure(legend = TRUE) +
-  scale_y_continuous(expand = c(0, 0))
-```
+# Plot the intact biocrust PLFA profiles
+p_cri_FAs <- results_cr %>% 
+  # Remove Standard Peaks
+  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
+  ggplot(aes(x = `Retention Time`, 
+             y = `Relative Area`, 
+             color = sample, 
+             fill = sample, 
+             label = `Peak Name`)) +
+  geom_col(width = 0.08) +
+  facet_wrap(~sample, 
+             ncol = 1, 
+             scales = "free_y") +
+  geom_label_repel(fill = "black", color = "white", alpha = 0.7, size = 2.5, nudge_y = 2, segment.color = "black") +
+  theme_bw() +
+  scale_color_jama() +
+  scale_fill_jama()
+p_cri_FAs
 
-```{r}
-library(plotly)
-ggplotly(ggplot2::last_plot(), dynamicTicks = TRUE)
 ```
@@
   filter(rel_height > 1) %>% 
-  openxlsx::write.xlsx(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
+  openxlsx::write.xlsx(file.path("tables", "fid_single_sample_peak_table.xlsx"))
 ```

### 2021-07-27 gc_fid_data.Rmd
combine Fractions computationally

@@
   mutate(
-    sample = str_remove(sample, "_"))
+    sample = str_remove(sample, "_")) %>% 
+  # Generate summary statistics with summarize()
+  group_by(sample, `Peak Name`) %>% 
+  summarize(
+    `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
+    Area = mean(Area, na.rm=TRUE),
+    Height = mean(Height, na.rm=TRUE),
+    `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
+    `Relative Height` = mean(`Relative Height`, na.rm=TRUE)
+  )
 
+# Remove Fraction Data from `results` tbl
+results <- results %>% 
+  filter(!str_detect(sample, "_F")) %>% 
+  bind_rows(results_m0f0_m0f3)
 ```
@@
   group_by(sample_rep, `Peak Name`) %>%
-  # Replace NA Height and Area values with Zero in order to do summarizing operations
-  mutate(`Relative Height` = replace(`Relative Height`, is.na(`Relative Height`), 0)) %>%
-  mutate(`Relative Area` = replace(`Relative Area`, is.na(`Relative Area`), 0)) %>% 
   # Generate summary stats
-  summarize(rel_area_max = max(`Relative Area`),
-            rel_area_min = min(`Relative Area`),
-            rel_height_max = max(`Relative Height`),
-            rel_height_min = min(`Relative Height`),
-            `Retention Time` = mean(`Retention Time`),
-            `Relative Area` = mean(`Relative Area`),
-            `Relative Height` = mean(`Relative Height`)) %>% 
+  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
+            rel_area_min = min(`Relative Area`, na.rm=TRUE),
+            rel_height_max = max(`Relative Height`, na.rm=TRUE),
+            rel_height_min = min(`Relative Height`, na.rm=TRUE),
+            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
+            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
+            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
   # Add some basic metadata

### 2021-08-11 gc_ramp_comparison.Rmd
tidy data and overview plot

---
title: "R Notebook"
output: html_notebook
---

```{r, include=FALSE}
# Libraries
library(tidyverse) # What are we without the tidyverse? c:
library(plotly)
library(ggrepel)
library(ggsci)
library(ggsignif)

# Source
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
source(file.path("libs", "chromeleon_peaks.R"))
```

# Relevant Equations

## Plates (EP)
Chromeleon uses the European Pharmacopeia (EP) theoretical plate calculation.

$$
N = 5.54\cdot(\frac{R_t}{W})^2
$$
Where N is the plate count (theoretical plates), Rt is retention time, W is peak width at 50% peak height (FWHM).

## Asymmetry (EP)
$$
A_s = \frac{w_{0.05}}{2d}
$$
Where $A_s$ is symmetry factor, $w_{0.05}$ is peak width at one-twentieth of peak height, d is distance between perpendicular dropped from the peak max and the leading edge of the peak at one-twentieth peak height.

## Resolution
Chromeleon uses the European Pharmacopeia (EP) resolution equation.

$$
R = \frac{1.18(Rt_2 - Rt_1)}{(W_2 + W_1)}
$$

Where R is resolution, $Rt$ is retention time, and W is the peak width at 50% peak height (FWHM).

# Load Data
```{r}
root <- "data/2021-08-10_TAC_BAME_Ramp_Tests/"
# Generate a list of files in the directory
file_list = list.files(path = root)
# Subset this list for the samples we want
file_list <- file_list %>% 
  str_subset("blank", negate = TRUE) %>% # remove blanks!
  str_subset("Blank", negate = TRUE) %>% # remove more blanks!
  str_subset("GCMS-STD", negate = TRUE) %>% # remove GCMS Standards!
  str_subset("BLK", negate = TRUE) # remove even more blanks! ^_^
# Make a list of sample names without all the mumbo jumbo in the exact filename
sample_names <- file_list %>% 
  str_replace("FID.....", "") %>% # remove FID header
  str_replace("_100ul-nhex.xls", "") %>% # remove volume and type of solvent
  str_replace("_100ul.xls", "") %>% 
  str_replace(".xls", "") %>% 
  str_replace("TCBAME6_", "")

# Make a big tibble containing all of our data
# With Injection Details and Integration Results nested inside
all_data <-
  tibble(
    sample = sample_names,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)

# Create a tibble of peak analysis data
peak_data <-
  tibble(
    sample = sample_names,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export_peaks),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)

# Make a tibble containing all of the integration data
peak_analysis <- peak_data %>%
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0)

results <- all_data %>%
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  filter(sample != "TCBAME-2") %>% # Don't need this sample
  # Add ramp information
  mutate(ramp = str_extract(sample, "\\d"))
```

# Overview Plot
```{r, fig.width=8, fig.height=4, warning=FALSE}
# Overview Plot
p_bame_overview <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = ramp) +
    geom_col(width = 0.1) +
    facet_wrap(.~ramp, ncol = 1) +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_bame_overview
```

### 2021-08-11 gc_ramp_comparison.Rmd
resolution plates and asymmetry

@@
 library(ggsignif)
+library(ggdist)
 
@@
   unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0)
+  filter(nchar(`Peak Name`) > 0) %>% 
+  filter(sample != "TCBAME-2") %>% # Don't need this sample
+  # Add ramp information
+  mutate(ramp = str_extract(sample, "\\d"))
 
@@
 ```
+
+```{r}
+p_bame_resolution <- peak_analysis %>% 
+  filter(!is.na(`Resolution (EP)`)) %>% 
+  ggplot() +
+  aes(x = `Resolution (EP)`, y = ramp) +
+  stat_slab(aes(color = ramp,
+                fill = ramp), 
+            height = 0.5) +
+   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
+             size = 2, 
+             alpha = 0.3) +
+  stat_pointinterval() +
+  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
+  xlab("Resolution (EP)") +
+  ylab("Ramp Rate (C per min)") +
+  scale_color_npg() +
+  scale_fill_npg() +
+  theme_minimal()
+p_bame_resolution
+```
+
+```{r}
+p_bame_plates <- peak_analysis %>% 
+  filter(!is.na(`Plates (EP)`)) %>% 
+  ggplot() +
+  aes(x = `Plates (EP)`, y = ramp) +
+  stat_slab(aes(color = ramp,
+                fill = ramp), 
+            height = 0.5) +
+   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
+             size = 2, 
+             alpha = 0.3) +
+  stat_pointinterval() +
+  ggtitle("DB5-HT 30m Plates Versus Ramp Rate") +
+  xlab("Plates (EP)") +
+  ylab("Ramp Rate (C per min)") +
+  scale_color_npg() +
+  scale_fill_npg() +
+  theme_minimal()
+p_bame_plates
+```
+
+```{r}
+p_bame_asymmetry <- peak_analysis %>% 
+  filter(!is.na(`Asymmetry (EP)`)) %>% 
+  ggplot() +
+  aes(x = `Asymmetry (EP)`, y = ramp) +
+  stat_slab(aes(color = ramp,
+                fill = ramp), 
+            height = 0.5) +
+   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
+             size = 2, 
+             alpha = 0.3) +
+  stat_pointinterval() +
+  ggtitle("DB5-HT 30m Asymmetry Versus Ramp Rate") +
+  xlab("Asymmetry (EP)") +
+  ylab("Ramp Rate (C per min)") +
+  scale_color_npg() +
+  scale_fill_npg() +
+  theme_minimal()
+p_bame_asymmetry
+```
+
+## Save Images
+```{r}
+ggsave("fig_output/p_bame_overview.png", p_bame_overview)
+```

### 2021-08-11 gc_ramp_comparison.Rmd
new resolution plot

@@
 title: "R Notebook"
-output: html_notebook
+output: html_document
 ---
@@
 library(ggdist)
+library(ggborderline)
 
@@
 ```
-
-# Relevant Equations
-
-## Plates (EP)
-Chromeleon uses the European Pharmacopeia (EP) theoretical plate calculation.
-
-$$
-N = 5.54\cdot(\frac{R_t}{W})^2
-$$
-Where N is the plate count (theoretical plates), Rt is retention time, W is peak width at 50% peak height (FWHM).
-
-## Asymmetry (EP)
-$$
-A_s = \frac{w_{0.05}}{2d}
-$$
-Where $A_s$ is symmetry factor, $w_{0.05}$ is peak width at one-twentieth of peak height, d is distance between perpendicular dropped from the peak max and the leading edge of the peak at one-twentieth peak height.
-
-## Resolution
-Chromeleon uses the European Pharmacopeia (EP) resolution equation.
-
-$$
-R = \frac{1.18(Rt_2 - Rt_1)}{(W_2 + W_1)}
-$$
-
-Where R is resolution, $Rt$ is retention time, and W is the peak width at 50% peak height (FWHM).
 
@@
 # Overview Plot
+Here we see the retention times of BAME standard compounds across 5 GC ramps ranging from 1 to 5 C per minute.
 ```{r, fig.width=8, fig.height=4, warning=FALSE}
@@
 p_bame_resolution
+```
+```{r}
+p_bame_resolution2 <- peak_analysis %>% 
+  filter(!is.na(`Resolution (EP)`)) %>% 
+  ggplot() +
+  aes(y = `Resolution (EP)`, x = `ramp`, color = `Peak Name`, group = `Peak Name`) + 
+  geom_point() +
+  geom_path() +
+  scale_color_viridis_d() +
+  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
+  ylab("Resolution (EP)") +
+  xlab("Ramp Rate (C per min)") +
+  theme_minimal()
+p_bame_resolution2
 ```
@@
 ```{r}
-ggsave("fig_output/p_bame_overview.png", p_bame_overview)
+ggsave("fig_output/p_bame_overview.png", p_bame_overview, height = 7, width = 11, dpi = 300)
+ggsave("fig_output/p_bame_resolution.png", p_bame_resolution)
+ggsave("fig_output/p_bame_resolution2.png", p_bame_resolution2)
 ```
+
+# Relevant Equations
+
+## Plates (EP)
+Chromeleon uses the European Pharmacopeia (EP) theoretical plate calculation.
+
+$$
+N = 5.54\cdot(\frac{R_t}{W})^2
+$$
+Where N is the plate count (theoretical plates), Rt is retention time, W is peak width at 50% peak height (FWHM).
+
+## Asymmetry (EP)
+$$
+A_s = \frac{w_{0.05}}{2d}
+$$
+Where $A_s$ is symmetry factor, $w_{0.05}$ is peak width at one-twentieth of peak height, d is distance between perpendicular dropped from the peak max and the leading edge of the peak at one-twentieth peak height.
+
+## Resolution
+Chromeleon uses the European Pharmacopeia (EP) resolution equation.
+
+$$
+R = \frac{1.18(Rt_2 - Rt_1)}{(W_2 + W_1)}
+$$
+
+Where R is resolution, $Rt$ is retention time, and W is the peak width at 50% peak height (FWHM).

### 2021-08-17 gc_ramp_comparison.Rmd
plot final

--- 2021-08-11 gc_ramp_comparison.Rmd
@@
 
-```{r}
+```{r, dpi=300}
 p_bame_asymmetry <- peak_analysis %>% 

### 2021-09-01 irms_ramp_testing/irms_ramp_testing.Rmd
irms_ramp_testing

---
title: "IRMS Ramp Tests"
author: "Tristan Caro"
date: "8/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(ggdist)
```

# Read in the data
```{r}
file_list <- list.files("data/", pattern='*.xls')
ramp_data <- do.call(rbind, lapply(paste0("data/", file_list), read_excel))

res_calc <- function(rt2, rt1, w2, w1) {
  res = (rt2 - rt1) / (1/2)*(w1 + w2)
  return(res)
}

# Clean up some <chr>
ramp_data$`Area 2 (Vs)` <- as.numeric(ramp_data$`Area 2 (Vs)`)
ramp_data$`Ampl  2 (mV)` <- as.numeric(ramp_data$`Ampl  2 (mV)`)

# Make Peak Numbers Numeric and filter out gas calibration peaks
ramp_data <- ramp_data %>%
  mutate(`Peak Nr` = parse_number(`Peak Nr`)) %>% 
  group_by(Filename) %>% 
  # Remove first 10 peaks and last 5 that correspond to gas calibration
  filter(`Peak Nr` > 10, `Peak Nr` < max(`Peak Nr`) - 5)

```

Calculate resolution using the following:

$$
R = \frac{t_{R2} - t_{R1}}{\frac{1}{2}(W_1 + W_2)}
$$

# BAMES
```{r}
bames <- ramp_data %>% 
  filter(str_detect(Filename, "BAMES")) %>% 
  mutate(ramp_cpm = case_when(
    # Not the best way to assign ramp temp .. brain dead.
    str_detect(Filename, "5_0Cpm") ~ "5",
    str_detect(Filename, "2_0Cpm") ~ "2.0",
    str_detect(Filename, "1_5Cprm") ~ "1.5",
    str_detect(Filename, "1_0Cpm") ~ "1.0")
  ) %>% 
  group_by(Filename) %>% 
  mutate(rt2 = as.numeric(`Rt (s)`), # later peak
         rt1 = as.numeric(lag(`Rt (s)`, n = 1)), # earlier peak
         w2 = as.numeric(`Width (s)`), # later peak
         w1 = as.numeric(lag(`Width (s)`, n = 1)), # earlier peak
         resolution = res_calc(rt2 = rt2, rt1 = rt1, w2 = w2, w1 = w1))
```

```{r}
bames %>% ggplot(aes(x = `Filename`, y = resolution, color = ramp_cpm)) +
  stat_pointinterval(color = "black") +
  geom_jitter(width = 0.2, alpha = 0.3) +
  theme_classic() +
  ggtitle("BAMES Resolution vs. Ramp") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```

```{r}
bames %>%
  ggplot(aes(x = `Area 2 (Vs)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm") +
  facet_wrap(~ramp_cpm) +
  theme_classic()
```

```{r}
bames %>%
  ggplot(aes(x = `Ampl  2 (mV)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm") +
  facet_wrap(~ramp_cpm) +
  theme_classic()
```

# Soil FAME sample t0f0x

```{r}
sfames <- ramp_data %>% 
  filter(str_detect(Filename, "t0f0x")) %>% 
  mutate(ramp_cpm = case_when(
    # Not the best way to assign ramp temp .. brain dead.
    str_detect(Filename, "5_0Cpm") ~ "5",
    str_detect(Filename, "2_0Cpm") ~ "2.0",
    str_detect(Filename, "1_5Cpm") ~ "1.5",
    str_detect(Filename, "1_0Cpm") ~ "1.0")
  ) %>% 
  group_by(Filename) %>% 
  mutate(rt2 = as.numeric(`Rt (s)`), # later peak
         rt1 = as.numeric(lag(`Rt (s)`, n = 1)), # earlier peak
         w2 = as.numeric(`Width (s)`), # later peak
         w1 = as.numeric(lag(`Width (s)`, n = 1)), # earlier peak
         resolution = res_calc(rt2 = rt2, rt1 = rt1, w2 = w2, w1 = w1))
```

```{r}
sfames %>% 
  ggplot(aes(x = `Filename`, y = resolution, color = ramp_cpm)) +
  stat_pointinterval(color = "black") +
  geom_jitter(width = 0.2, alpha = 0.3) +
  coord_cartesian(ylim = c(0, 100000)) +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```

```{r}
sfames %>%
  ggplot(aes(x = `Area 2 (Vs)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  theme_classic()
```

```{r}
sfames %>%
  ggplot(aes(x = `Ampl  2 (mV)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  theme_classic()
```

```{r}
sfames %>%
  ggplot(aes(x = `Ampl  2 (mV)`, y = resolution, color = ramp_cpm)) +
  geom_point() +
  facet_wrap(~ramp_cpm, scales = "free") +
  theme_classic()
```

### 2021-09-03 irms_ramp_testing/irms_ramp_testing.Rmd
ramp testing

@@
 author: "Tristan Caro"
-date: "8/31/2021"
-output: html_document
+date: "Last knitted `r format(Sys.Date(), '%d %b %Y')`"
+output:
+  html_document: 
+    df_print: paged
+    number_sections: yes
+    toc: yes
+    toc_float: true
+    toc_depth: 3
+    code_folding: show
+editor_options:
+  chunk_output_type: console
 ---
@@
 ```
+
+```{r}
+sfames %>%
+  ggplot(aes(x = `Area 2 (Vs)`, y = resolution, color = ramp_cpm)) +
+  geom_point() +
+  geom_smooth(se = FALSE,
+              method = "lm") +
+  facet_wrap(~ramp_cpm) +
+  theme_classic()
+```

### 2021-09-05 qSIP_calculations.Rmd
generation time calculations

---
title: "2H qSIP Calculations"
author: "Tristan Caro"
date: "`r Sys.Date()`"
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# global knitting options for code rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Load packages

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel)
```

This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.

# Load data

## Read raw data files

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files, using example data set here
data_path <- file.path("data", "IRMS", "2021-09-02_H_FAMES_TC")
ref_ratio <- get_standard("2H") %>% as.numeric()

# read files
iso_files_raw <- 
  # path to data files
  data_path %>% 
  # read data files in parallel for fast read
  iso_read_continuous_flow() %>%
  # filter out files with read errors (e.g. from aborted analysis)
  iso_filter_files_with_problems()
```

## Process file info & peak table

```{r}
# process file information
iso_files <- iso_files_raw %>% 
  # rename key file info columns
  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
  # parse text info into numbers
  iso_parse_file_info(number = analysis) %>% 
  # process other file information that is specific to the naming conventions
  # of this particular sequence
  iso_mutate_file_info(
    # what is the type of each analysis?
    type = case_when(
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "H3")           ~ "H3_factor",
      str_detect(id1, "F8")           ~ "F8_std",
      str_detect(id1, "F9")           ~ "F9_std",
      TRUE                            ~ "sample"
    ),
    # what was the concentration? (assuming Preparation = concentration or volume)
    concentration = 
      ifelse(type == "std",  
             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
               parse_number() %>% iso_double_with_units("ng/uL"),
             NA),
    # what folder are the data files in? (assuming folder = sequence)
    folder = basename(dirname(file_path))
  ) %>% 
  # focus only on the relevant file info, discarding the rest
  iso_select_file_info(
    folder, analysis, file_datetime, id1, type, concentration
  ) %>% 
  # add in additional sample metadata (could be any info)
  # note: this would typically be stored in / read from a csv or excel file
  iso_add_file_info(
    read_csv(file.path("data", "sample_metadata_2021.csv")),
    join_by = "id1"
  )

# set peak table from vendor data table with default isodat template
iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)

# focus on sample files
sample_files <- iso_filter_files(iso_files, type == "sample")

# focus on not CRC samples
sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))
```

## Show file information

```{r}
# display file information
iso_files %>% 
  iso_get_file_info() %>% select(-file_id, -folder) %>% 
  iso_make_units_explicit() %>% knitr::kable()
```

## Example chromatograms

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # all sample files
  sample_files,
  # select data and aesthetics
  data = c(2), color = id1, panel = id1,
  # zoom in on time interval
  time_interval = c(750, 4000),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = FALSE,
  peak_label = iso_format(rt),
  #peak_label_size = 3,
  peak_label_filter = analysis == 5685 & amp2 > 1
) + scale_color_npg() + 
  theme_classic() +
  theme(strip.background = element_blank())
```

# Peak Mapping

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
peak_map <- 
  readxl::read_excel(file.path("data","IRMS", "peak_map_manual.xlsx"))
peak_map

peak_table <- sample_files %>%
  iso_set_peak_table_from_isodat_vendor_data_table() %>%
  iso_get_peak_table() %>% 
  mutate(Analysis = substr(file_id, 1, 7),
         sample_id = substr(file_id, 10,14))
```

```{r}
peaks_mapped <- peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound))
```

## Generation Time Calculations

```{r}
# FL = 0.005 # tracer strength = 0.5%
# a = 0.5 # incorporation efficiency of 50%
# FT = 0.02 # resulting isotopic enrichment
# F0 = 0.0124 # beginning isotopic enrichment

gencalc <- function(a, FT, F0, FL, t) {
  case_when(
    t == 0 ~ NA_real_,
    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
  )
}

# Add Some Metadata

peaks_mapped <- peaks_mapped %>% 
  group_by(sample_id) %>% 
  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
         f_label = 0.005)

inc_time_zero <- peaks_mapped %>% 
  filter(inc_time_d == 0)

peaks_mapped <- peaks_mapped %>%
  group_by(sample_id) %>% 
  mutate(f_start = case_when(
           inc_time_d == 0 ~ at2H,
           inc_time_d != 0 ~ inc_time_zero$at2H
           ),
         terrain = case_when(
           substr(sample_id, 1, 1) == "t" ~ "Tundra",
           substr(sample_id, 1 ,1) == "c" ~ "Alpine Conifer Forest",
           substr(sample_id, 1 ,1) == "m" ~ "Alpine Meadow",
           substr(sample_id, 1 ,1) == "g" ~ "Grassland"))

peaks_mapped_active <- peaks_mapped %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

```{r}
gen_calc_data <- peaks_mapped_active %>% 
  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, terrain, f_start)) %>% 
  mutate(at2H_label = 0.005) %>% 
  mutate(f_label = 0.005, # label is 0.5 at%
         a = 0.5,
         #R = (d2H/1000 +1) * ref_ratio,
         t = inc_time_d,
         #f_t = R / (1 + R) %>%  # 2F at time t where t = inc_time_d
         f_t = at2H) %>% 
  group_by(compound) %>% 
  mutate(
    t0 = 0,
    d_ft = as.numeric(f_t - f_start), # change in isotopic enrichment from start to time t
    d_t = t - t0, # change in time from start to time t (days)
    u_d = gencalc(a = a, FT = f_t, F0 = f_start, FL = f_label, t = d_t) # turnover (µ) in days^-1
  )

gen_calc_data
```

```{r}
peaks_mapped_active %>% ggplot(
  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
  geom_point() +
  geom_borderline() +
  scale_color_viridis_d() +
  theme_minimal()
```

```{r "shaded chromatogram", fig.width=8, fig.height=8}
peaks_mapped_active %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c() +
  facet_wrap(~sample_id, ncol = 1) +
  geom_label_repel(size = 2, box.padding = 1) +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = "2F",
         x = "Retention Time (s)",
         y = "Amplitude (mV)")
```

### 2021-09-06 qSIP_calculations.Rmd
gencalc fixed to use at%

@@
 library(ggrepel)
+library(latex2exp)
+library(ggdist)
 ```
@@
   mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
+         inc_time_d_str = paste(inc_time_d, "Days"),
          f_label = 0.005)
@@
 
+```
+
+## Remove standards from gencalcs
+```{r}
 peaks_mapped_active <- peaks_mapped %>% 
@@
 gen_calc_data <- peaks_mapped_active %>% 
-  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, terrain, f_start)) %>% 
-  mutate(at2H_label = 0.005) %>% 
-  mutate(f_label = 0.005, # label is 0.5 at%
-         a = 0.5,
-         #R = (d2H/1000 +1) * ref_ratio,
-         t = inc_time_d,
-         #f_t = R / (1 + R) %>%  # 2F at time t where t = inc_time_d
-         f_t = at2H) %>% 
-  group_by(compound) %>% 
+  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, inc_time_d_str, terrain, f_start)) %>% 
   mutate(
-    t0 = 0,
-    d_ft = as.numeric(f_t - f_start), # change in isotopic enrichment from start to time t
-    d_t = t - t0, # change in time from start to time t (days)
-    u_d = gencalc(a = a, FT = f_t, F0 = f_start, FL = f_label, t = d_t) # turnover (µ) in days^-1
+    at2H_label = 0.005,
+    f_label = 0.5, # label is 0.5 at%
+    a = 0.5, # assimilation efficiency
+    t0 = 0, # start time
+    d_t = inc_time_d - t0, # change in time
+    f_t = at2H, # restate 2F at time t
+    u_d = gencalc(a = 0.5, # Assimilation efficiency
+                  FT = f_t, # 2F at time t (at%)
+                  F0 = f_start, # 2F at t0 (at%)
+                  FL = f_label, # 2F of label (at%)
+                  t = d_t), # change in time
+         # Returns turnover (µ) in days^-1
+         gen_d = log(2) / u_d # calculate generation time
   )
-
-gen_calc_data
 ```
@@
 
+## Chromatogram scaled by 2F
 ```{r "shaded chromatogram", fig.width=8, fig.height=8}
@@
   geom_col(aes(width = rt_end - rt_start)) +
-  scale_fill_viridis_c() +
-  facet_wrap(~sample_id, ncol = 1) +
-  geom_label_repel(size = 2, box.padding = 1) +
+  scale_fill_viridis_c(option = "magma") +
+  facet_wrap(~inc_time_d_str, ncol = 1) +
+  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
+  theme_classic() +
   coord_cartesian(ylim = c(0, 1300)) +
-  labs(fill = "2F",
+  labs(fill = TeX("$^2F$"),
          x = "Retention Time (s)",
-         y = "Amplitude (mV)")
+         y = "Amplitude (mV)") +
+  theme(strip.background = element_blank())
 ```
+
+```{r}
+gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = gen_d, 
+      y = inc_time_d_str, 
+      color = inc_time_d_str, 
+      fill = inc_time_d_str)) +
+  stat_slab(height = 0.3) +
+  geom_point(
+    shape = 124,
+    size = 5,
+    alpha = 0.5,
+    position = position_nudge(y = -.07)) +
+  stat_pointinterval(color = "black") +
+  scale_x_log10() +
+  annotation_logticks(sides = "b") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Generation time (days)",
+       y = "Incubation time") +
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+```

### 2021-09-06 qSIP_calculations.Rmd
u_d versus rel_amount plot

--- 2021-09-05 qSIP_calculations.Rmd
@@
 library(ggrepel)
+library(latex2exp)
+library(ggdist)
+
+source(file.path("libs", "visualization.R"))
+source(file.path("libs", "chromleon.R"))
+`%nin%` = Negate(`%in%`)
 ```
@@
 
-## Generation Time Calculations
+# Generation Time Calculations
 
@@
 
+peaks_mapped <- peaks_mapped %>% 
+  mutate(rel_amount = area2 / sum(area2[compound != "IS"]))
+```
+
+## Remove standards from gencalcs
+```{r}
 peaks_mapped_active <- peaks_mapped %>% 
@@
 gen_calc_data <- peaks_mapped_active %>% 
-  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, terrain, f_start)) %>% 
-  mutate(at2H_label = 0.005) %>% 
-  mutate(f_label = 0.005, # label is 0.5 at%
-         a = 0.5,
-         #R = (d2H/1000 +1) * ref_ratio,
-         t = inc_time_d,
-         #f_t = R / (1 + R) %>%  # 2F at time t where t = inc_time_d
-         f_t = at2H) %>% 
-  group_by(compound) %>% 
+  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, inc_time_d_str, terrain, f_start, rel_amount)) %>% 
   mutate(
-    t0 = 0,
-    d_ft = as.numeric(f_t - f_start), # change in isotopic enrichment from start to time t
-    d_t = t - t0, # change in time from start to time t (days)
-    u_d = gencalc(a = a, FT = f_t, F0 = f_start, FL = f_label, t = d_t) # turnover (µ) in days^-1
+    at2H_label = 0.005,
+    f_label = 0.5, # label is 0.5 at%
+    a = 0.5, # assimilation efficiency
+    t0 = 0, # start time
+    d_t = inc_time_d - t0, # change in time
+    f_t = at2H, # restate 2F at time t
+    u_d = gencalc(a = 0.5, # Assimilation efficiency
+                  FT = f_t, # 2F at time t (at%)
+                  F0 = f_start, # 2F at t0 (at%)
+                  FL = f_label, # 2F of label (at%)
+                  t = d_t), # change in time
+         # Returns turnover (µ) in days^-1
+         gen_d = log(2) / u_d # calculate generation time
   )
-
-gen_calc_data
 ```
@@
 
+## Chromatogram scaled by 2F
+
 ```{r "shaded chromatogram", fig.width=8, fig.height=8}
@@
   geom_col(aes(width = rt_end - rt_start)) +
-  scale_fill_viridis_c() +
-  facet_wrap(~sample_id, ncol = 1) +
-  geom_label_repel(size = 2, box.padding = 1) +
+  scale_fill_viridis_c(option = "magma") +
+  facet_wrap(~inc_time_d_str, ncol = 1) +
+  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
+  theme_classic() +
   coord_cartesian(ylim = c(0, 1300)) +
-  labs(fill = "2F",
+  labs(fill = TeX("$^2F$"),
          x = "Retention Time (s)",
-         y = "Amplitude (mV)")
+         y = "Amplitude (mV)") +
+  theme(strip.background = element_blank())
 ```
+
+```{r}
+gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = gen_d, 
+      y = inc_time_d_str, 
+      color = inc_time_d_str, 
+      fill = inc_time_d_str)) +
+  stat_slab(height = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  geom_point(
+    color = "black",
+    shape = 124,
+    size = 3,
+    alpha = 1,
+    position = position_nudge(y = .03)) +
+  geom_text_repel(aes(label = compound), 
+                  color = "black", 
+                  nudge_y = -0.3, 
+                  size = 3) +
+  scale_x_log10() +
+  annotation_logticks(sides = "b") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Generation time (days)",
+       y = "Incubation time",
+       title = "Generation times of soil bacteria",
+       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
+       caption = "Soils collected from Niwot Ridge LTER") +
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+```
+
+# GC-FID Data
+
+## Import GC-FID Data
+```{r}
+root <- file.path("data", "gc_fid_data_2020")
+file_list = list.files(path = root)
+file_list <- file_list %>% 
+  str_subset("blank", negate = TRUE) %>% 
+  str_subset("Blank", negate = TRUE) %>% 
+  str_subset("GCMS-STD", negate = TRUE) %>% 
+  str_subset("BLK", negate = TRUE) # remove procedural blanks
+sample_names <- file_list %>% 
+  str_replace("FID.....", "") %>% 
+  str_replace("_100ul-nhex.xls", "") %>% 
+  str_replace("_100ul.xls", "")
+
+all_data <-
+  tibble(
+    sample = sample_names,
+    file = file_list,
+    data = map(file.path(root, file), read_chromeleon_export),
+    injection_details = map(data, "injection_details"),
+    integration_results = map(data, "integration_results")
+  ) %>% select(-data)
+```
+
+## Unnest integration details
+
+```{r}
+results <- all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # major compound groups
+  mutate(
+    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
+  )
+```
+
+```{r}
+# Combine triplicate samples into one
+results_trip <- results %>% 
+  # Remove standards and fractions
+  filter(sample != "FAME37.1") %>% 
+  filter(sample != "TCBAME-2") %>% 
+  filter(!str_detect(sample, "F1")) %>% 
+  filter(!str_detect(sample, "F2")) %>% 
+  filter(!str_detect(sample, "F3")) %>% 
+  filter(!str_detect(sample, "cr")) %>%
+  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
+  group_by(sample_rep, `Peak Name`) %>%
+  # Generate summary stats
+  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
+            rel_area_min = min(`Relative Area`, na.rm=TRUE),
+            rel_height_max = max(`Relative Height`, na.rm=TRUE),
+            rel_height_min = min(`Relative Height`, na.rm=TRUE),
+            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
+            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
+            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
+  # Add some basic metadata
+  mutate(inc_time = case_when(
+    str_detect(sample_rep, "...0") ~ 0,
+    str_detect(sample_rep, "...3") ~ 3,
+    str_detect(sample_rep, "...7") ~ 7),
+    site = case_when(
+      str_detect(sample_rep, "c") ~ "Conifer",
+      str_detect(sample_rep, "t") ~ "Tundra",
+      str_detect(sample_rep, "g") ~ "Grassland",
+      str_detect(sample_rep, "m") ~ "Meadow")
+  )
+```
+
+## PLFA Summary Plot
+```{r}
+p_72hr_FAs <- results_trip %>% filter(inc_time == "3") %>% 
+  # Remove Standard Peaks
+  #filter(str_detect(`Peak Name`, c("PAIBE", "21:0 (STD)", "23:0 (STD)"), negate = TRUE)) %>% 
+  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
+  ggplot(aes(x = `Retention Time`, 
+             y = `Relative Area`, 
+             color = sample_rep, 
+             fill = sample_rep, 
+             label = `Peak Name`)) +
+  geom_col(width = 0.08) +
+  geom_errorbar(aes(ymin=rel_area_min, 
+                    ymax = rel_area_max), 
+                color = "black", 
+                width = 0.05) +
+  facet_wrap(~sample_rep, 
+             ncol = 1, 
+             scales = "free_y") +
+  geom_label_repel(fill = "black", 
+                   color = "white", 
+                   alpha = 0.7, 
+                   size = 3, 
+                   nudge_y = 2, 
+                   segment.color = "black") +
+  ggtitle("PLFA Profile: 72hr") +
+  theme_bw() +
+  scale_color_jama() +
+  scale_fill_jama()
+p_72hr_FAs
+```
+
+### IRMS relabund
+```{r}
+peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, color = inc_time_d_str)) +
+  geom_col() +
+  facet_wrap(~inc_time_d_str, ncol = 1)
+```
+
+### Relabund vs. activity
+```{r}
+gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = rel_amount, y = u_d, color = inc_time_d_str, label = compound)) +
+  geom_point() +
+  geom_smooth(method = "lm",
+              se = FALSE) +
+  geom_text_repel(size = 3) +
+  scale_color_npg()
+```
+
+## Merge IRMS and FID data
+
+### PICK UP HERE: how do we match GC-FID compound data with IRMS compound data?
+
+```{r}
+results_trip_matched <- results_trip %>% 
+  filter(`Peak Name` %in% gen_calc_data$compound)
+
+matched_idx <- match(gen_calc_data$compound, results_trip_matched$`Peak Name`)
+results_trip_matched$`Peak Name`[matched_idx]
+
+combined_irms_fid <- gen_calc_data %>%
+  group_by(terrain) %>% 
+  mutate(relative_area = results_trip$`Relative Area`[""])
+```

### 2021-09-07 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

@@
 ```{r "shaded chromatogram", fig.width=8, fig.height=8}
-peaks_mapped_active %>% ggplot(
+p_peaks_mapped_active <- peaks_mapped_active %>% ggplot(
   aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
@@
   theme(strip.background = element_blank())
+
 ```
@@
 ```{r}
-gen_calc_data %>% filter(inc_time_d != 0) %>% 
+p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
   ggplot(
@@
         axis.ticks.y = element_blank())
+
+ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
 ```

### 2021-09-09 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

@@
 date: "`r Sys.Date()`"
+output:
     html_document:
@@
         axis.ticks.y = element_blank())
+p_gen_time_dist
 
-ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
+#ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
 ```
@@
 ```{r}
-peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, color = inc_time_d_str)) +
+peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, fill = inc_time_d_str, color = inc_time_d_str)) +
   geom_col() +
@@
 ```{r}
-gen_calc_data %>% filter(inc_time_d != 0) %>% 
+gen_calc_data %>%
+  filter(inc_time_d != 0) %>% 
   ggplot(
-  aes(x = rel_amount, y = u_d, color = inc_time_d_str, label = compound)) +
+  aes(x = rel_amount, 
+      y = u_d, 
+      color = inc_time_d_str, 
+      label = compound)) +
   geom_point() +
   geom_smooth(method = "lm",
-              se = FALSE) +
+              se = FALSE,
+              formula = "y~x") +
+  geom_line(aes(group = compound), 
+            color = "black", 
+            alpha = 0.3) +
   geom_text_repel(size = 3) +
-  scale_color_npg()
+  theme_classic() +
+  scale_color_npg() +
+  labs(x = "Relative Amount",
+       y = "Turnover (d^-1)",
+       color = "Incubation Time") +
+  theme(legend.position = "top")
+```
+
+### Relabund vs. activity colored by 2F
+
+```{r}
+gen_calc_data %>%
+  filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = rel_amount, 
+      y = u_d, 
+      color = as.numeric(f_t), 
+      label = compound)) +
+  geom_point(aes(shape = inc_time_d_str)) +
+  geom_smooth(method = "lm",
+              se = FALSE,
+              formula = "y~x") +
+  geom_line(aes(group = compound), 
+            color = "black", 
+            alpha = 0.3) +
+  geom_text_repel(color = "black", 
+                  size = 3) +
+  scale_color_viridis_c(option = "magma") +
+  theme_classic() +
+  labs(x = "Relative Amount",
+       y = "Turnover (d^-1)",
+       shape = "Incubation Time",
+       color = "2F") +
+  theme(legend.position = "bottom")
 ```

### 2021-10-18 qSIP_calculations.Rmd
updated file path to include all new IRMS runs

@@
 # set file path(s) to data files, folders or rds collections 
-# can be multiple folders or mix of folders and files, using example data set here
-data_path <- file.path("data", "IRMS", "2021-09-02_H_FAMES_TC")
+# can be multiple folders or mix of folders and files
+# setting the month of analysis folder - Isoverse will iteratively search subfolders. Huzzah! ^_^
+data_path <- file.path("data", "IRMS", "2021-09")
 ref_ratio <- get_standard("2H") %>% as.numeric()

### 2021-10-18 qSIP_calculations.Rmd
whole-analysis peak table

@@
 
-# focus on not CRC samples
+# EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
 sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))
+
+sample_files <- iso_filter_files(sample_files, str_detect(id1, "cr0", negate = TRUE))
+
+# EXCLUDE C26 ALKANE STANDARD
+sample_files <- iso_filter_files(sample_files, str_detect(id1, "C26", negate = TRUE))
 ```
@@
 ```{r "example_chromatograms", fig.width=8, fig.height=8}
-# plot the chromatograms
+# plot an example chromatogram
+
+sample_files[10] %>% # choosing arbitrary file to plot
 iso_plot_continuous_flow_data(
-  # all sample files
-  sample_files,
   # select data and aesthetics
@@
 ```{r}
-# this information is often maintained in a csv or Excel file instead
-# but generated here from scratch for demonstration purposes
+# this information is often maintained in a csv or Excel file
 peak_map <- 
-  readxl::read_excel(file.path("data","IRMS", "peak_map_manual.xlsx"))
+  readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
 peak_map
@@
 ```{r}
+# Generate an isoverse peak map
 peaks_mapped <- peak_table %>%
@@
 ```{r}
+# Define a function to calculate turnover and generation time
+# ARGUMENTS:
 # FL = 0.005 # tracer strength = 0.5%
 # a = 0.5 # incorporation efficiency of 50%
-# FT = 0.02 # resulting isotopic enrichment
-# F0 = 0.0124 # beginning isotopic enrichment
+# FT = numeric # resulting isotopic enrichment
+# F0 = numeric # beginning isotopic enrichment
 
@@
 
+```
+
+```{r}
+
 # Add Some Metadata
+
+mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
+sample_names <- mtda$id1
+
+peaks_mapped <- peaks_mapped %>% 
+  filter(sample_id %in% sample_names)
 
@@
          terrain = case_when(
-           substr(sample_id, 1, 1) == "t" ~ "Tundra",
-           substr(sample_id, 1 ,1) == "c" ~ "Alpine Conifer Forest",
-           substr(sample_id, 1 ,1) == "m" ~ "Alpine Meadow",
-           substr(sample_id, 1 ,1) == "g" ~ "Grassland"))
+           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
+           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
+           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
+           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))
 
@@
 ```{r}
+# Don't want our standard compounds to be used for generation time calculations! x_x
 peaks_mapped_active <- peaks_mapped %>% 
@@
 ```
+
+Generation time is related to the turnover rate as below:
+$$
+g = \frac{ln(2)}{\mu}
+$$
 

### 2021-10-19 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

@@
          inc_time_d_str = paste(inc_time_d, "Days"),
-         f_label = 0.005)
+         f_label = 0.005,
+         t_series_id = paste0(substr(sample_id, 1,1), 
+                              substr(sample_id, 5,5)))
 
 inc_time_zero <- peaks_mapped %>% 
-  filter(inc_time_d == 0)
+  filter(inc_time_d == 0) %>% 
+  select(sample_id, compound, at2H) %>% 
+  mutate(f_start = at2H)
+         # extract first and lass code of sample_id
 
+```
+
+```{r}
 peaks_mapped <- peaks_mapped %>%

### 2021-10-19 qSIP_calculations.Rmd
add zero time points, resolve ambiguous peaks

@@
 
+# Turnover Calculation Function
+
+```{r}
+# Define a function to calculate turnover and generation time
+# ARGUMENTS:
+# FL = 0.005 # tracer strength = 0.5%
+# a = 0.5 # incorporation efficiency of 50%
+# FT = numeric # resulting isotopic enrichment
+# F0 = numeric # beginning isotopic enrichment
+
+gencalc <- function(a, FT, F0, FL, t) {
+  case_when(
+    t == 0 ~ NA_real_,
+    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
+  )
+}
+
+```
+
 # Load data
+
+## Load Metadata and Problematic Run Data
+
+```{r}
+mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
+sample_names <- mtda$id1
+
+problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
+```
 
@@
 
+## Generate Isoverse Peak Map
 ```{r}
@@
   filter(!is.na(compound))
+
 ```
 
-# Generation Time Calculations
+## Remove readychecks, blanks, etc. from analysis
+```{r}
+# Filter based on what is in the sample_names metadata
+peaks_mapped <- peaks_mapped %>% 
+  filter(sample_id %in% sample_names)
 
+# Filter out runs that are on our problematic_runs list
+peaks_mapped <- peaks_mapped %>% 
+  filter(Analysis %nin% problematic_runs)
+```
+
+## Check problematic peak assignments
 ```{r}
-# Define a function to calculate turnover and generation time
-# ARGUMENTS:
-# FL = 0.005 # tracer strength = 0.5%
-# a = 0.5 # incorporation efficiency of 50%
-# FT = numeric # resulting isotopic enrichment
-# F0 = numeric # beginning isotopic enrichment
-
-gencalc <- function(a, FT, F0, FL, t) {
-  case_when(
-    t == 0 ~ NA_real_,
-    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
-  )
-}
-
+problem_peaks <- iso_get_problematic_peak_mappings(peaks_mapped)
 ```
@@
 # Add Some Metadata
-
-mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
-sample_names <- mtda$id1
-
-peaks_mapped <- peaks_mapped %>% 
-  filter(sample_id %in% sample_names)
 
@@
   filter(inc_time_d == 0) %>% 
-  select(sample_id, compound, at2H) %>% 
-  mutate(f_start = at2H)
-         # extract first and lass code of sample_id
+  select(sample_id, compound, at2H, t_series_id) %>% 
+  mutate(f_start = at2H) %>% 
+  select(-at2H)
 
+## Trying a simpler example
+c_inc_time_zero <- inc_time_zero %>% 
+  filter(str_detect(t_series_id, "c"))
+
+c_peaks_mapped <- peaks_mapped %>% 
+  filter(str_detect(t_series_id, "c")) %>% 
+  full_join(c_inc_time_zero, by = c("t_series_id", "compound"))
+
+```
+
+```{r}
+zero_peaks <- peaks_mapped %>%
+  filter(inc_time_d_str == "0 Days") %>%
+  group_by(t_series_id, compound) %>%
+  mutate(n_analyical_reps = n()) %>%
+  ungroup() %>%
+  # exclude ambiguous peaks and those with multiple data points
+  # this needs to be fixed
+  filter(!is_ambiguous, n_analyical_reps == 1)
+
+peaks_mapped_with_zeros <- 
+  peaks_mapped %>%
+  left_join(
+    zero_peaks %>%
+      select(
+        compound, t_series_id, zero_sample_id = sample_id, area2_zero = area2, d2H_zero = d2H
+      ),
+    by = c("t_series_id", "compound")
+  ) 
+stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))
+
+# no zero samples
+peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
+```
+
+```{r}
+#peak maps
+peaks_mapped %>%
+  ungroup() %>%
+  select(Analysis, compound, rt) %>%
+  mutate(rt = round(rt, digits=0)) %>%
+  pivot_wider(
+    names_from = Analysis, 
+    names_prefix = "rt:",
+    values_from = rt, 
+    id_cols = compound, 
+    values_fn = function(x) paste(x, collapse = "; ")
+  ) %>%
+  openxlsx::write.xlsx(file.path("data", "IRMS", "peak_maps_resolve.xlsx"))
 ```

### 2021-10-20 qSIP_calculations.Rmd
new peak table

@@
 problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
+problematic_analyses <- problematic_runs$Analysis
+problematic_analyses_num <- parse_number(problematic_analyses)
+```
+
+## Load Peak Map
+
+```{r}
+# this information is often maintained in a csv or Excel file
+peak_map <- 
+  # initial peak map:
+  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
+  # corrected peak map
+  readxl::read_excel(file.path("data", "IRMS", "peak_maps_resolved.xlsx"))
+peak_map
 ```
@@
 
+# # EXCLUDE C26 ALKANE STANDARD
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "C26", negate = TRUE))
+# 
+# # EXCLUDE SQUALANE STANDARD
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "squalane", negate = TRUE))
+# 
+# # EXCLUDE BLANKS AND TESTS
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "blank", negate = TRUE))
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "BLANK", negate = TRUE))
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "H2", negate = TRUE))
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "nhex", negate = TRUE))
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "cleaning", negate = TRUE))
+# 
+# # EXCLUDE BAME STANDARD
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "BAME", negate = TRUE))
+# 
+# # EXCLUDE F HEAVY
+# sample_files <- iso_filter_files(sample_files, str_detect(id1, "F_HEAVY", negate = TRUE))
+#
+
+# Include only sample files
+ sample_files <- iso_filter_files(sample_files, id1 %in% sample_names)
+
 # EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
@@
 
-# EXCLUDE C26 ALKANE STANDARD
-sample_files <- iso_filter_files(sample_files, str_detect(id1, "C26", negate = TRUE))
+# EXCLUDE RUN WE'VE DEEMED PROBLEMATIC
+sample_files <- iso_filter_files(sample_files, analysis %nin% problematic_analyses_num)
+
 ```
@@
 
-sample_files[10] %>% # choosing arbitrary file to plot
-iso_plot_continuous_flow_data(
-  # select data and aesthetics
-  data = c(2), color = id1, panel = id1,
-  # zoom in on time interval
-  time_interval = c(750, 4000),
-  # peak labels for all peaks > 2V
-  peak_bounds = TRUE,
-  peak_marker = FALSE,
-  peak_label = iso_format(rt),
-  #peak_label_size = 3,
-  peak_label_filter = analysis == 5685 & amp2 > 1
-) + scale_color_npg() + 
-  theme_classic() +
-  theme(strip.background = element_blank())
+# sample_files[10] %>% # choosing arbitrary file to plot
+# iso_plot_continuous_flow_data(
+#   # select data and aesthetics
+#   data = c(2), color = id1, panel = id1,
+#   # zoom in on time interval
+#   time_interval = c(750, 4000),
+#   # peak labels for all peaks > 2V
+#   peak_bounds = TRUE,
+#   peak_marker = FALSE,
+#   peak_label = iso_format(rt),
+#   #peak_label_size = 3,
+#   peak_label_filter = analysis == 5685 & amp2 > 1
+# ) + scale_color_npg() + 
+#   theme_classic() +
+#   theme(strip.background = element_blank())
 ```
@@
 ```{r}
-# this information is often maintained in a csv or Excel file
-peak_map <- 
-  readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
-peak_map
-
-peak_table <- sample_files %>%
+sample_peak_table <- sample_files %>%
   iso_set_peak_table_from_isodat_vendor_data_table() %>%
@@
 # Generate an isoverse peak map
-peaks_mapped <- peak_table %>%
+peaks_mapped <- sample_peak_table %>%
   iso_map_peaks(peak_map, map_id = Analysis) %>%

### 2021-10-21 qSIP_calculations.Rmd
full data pipeline, plots

@@
 library(ggdist)
+library(ggsignif)
 
@@
   filter(!is.na(compound))
-
 ```
@@
 
+## Export summary of unresolved peaks
 ```{r}
-
-# Add Some Metadata
-
-peaks_mapped <- peaks_mapped %>% 
-  group_by(sample_id) %>% 
-  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
-         inc_time_d_str = paste(inc_time_d, "Days"),
-         f_label = 0.005,
-         t_series_id = paste0(substr(sample_id, 1,1), 
-                              substr(sample_id, 5,5)))
-
-inc_time_zero <- peaks_mapped %>% 
-  filter(inc_time_d == 0) %>% 
-  select(sample_id, compound, at2H, t_series_id) %>% 
-  mutate(f_start = at2H) %>% 
-  select(-at2H)
-
-## Trying a simpler example
-c_inc_time_zero <- inc_time_zero %>% 
-  filter(str_detect(t_series_id, "c"))
-
-c_peaks_mapped <- peaks_mapped %>% 
-  filter(str_detect(t_series_id, "c")) %>% 
-  full_join(c_inc_time_zero, by = c("t_series_id", "compound"))
-
-```
-
-```{r}
-zero_peaks <- peaks_mapped %>%
-  filter(inc_time_d_str == "0 Days") %>%
-  group_by(t_series_id, compound) %>%
-  mutate(n_analyical_reps = n()) %>%
-  ungroup() %>%
-  # exclude ambiguous peaks and those with multiple data points
-  # this needs to be fixed
-  filter(!is_ambiguous, n_analyical_reps == 1)
-
-peaks_mapped_with_zeros <- 
-  peaks_mapped %>%
-  left_join(
-    zero_peaks %>%
-      select(
-        compound, t_series_id, zero_sample_id = sample_id, area2_zero = area2, d2H_zero = d2H
-      ),
-    by = c("t_series_id", "compound")
-  ) 
-stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))
-
-# no zero samples
-peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
-```
-
-```{r}
-#peak maps
+# Spit out peaks that need to be resolved
 peaks_mapped %>%
@@
 
+## Assign incubation params
 ```{r}
+
+# Add Some Parameters
 peaks_mapped <- peaks_mapped %>% 
   group_by(sample_id) %>% 
-  mutate(f_start = case_when(
-           inc_time_d == 0 ~ at2H,
-           inc_time_d != 0 ~ inc_time_zero$at2H
-           ),
+  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
+         inc_time_d_str = paste(inc_time_d, "Days"),
+         f_label = 0.005,
+         t_series_id = paste0(substr(sample_id, 1,1), 
+                              substr(sample_id, 5,5)),
+         soil_id = substr(t_series_id, 1,1),
+         replicate_id = substr(t_series_id, 2,2),
          terrain = case_when(
@@
            substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))
+# 
+# inc_time_zero <- peaks_mapped %>% 
+#   filter(inc_time_d == 0) %>% 
+#   select(sample_id, compound, at2H, t_series_id) %>% 
+#   mutate(f_start = at2H) %>% 
+#   select(-at2H)
+# 
+#
 
-peaks_mapped <- peaks_mapped %>% 
-  mutate(rel_amount = area2 / sum(area2[compound != "IS"]))
+```
+
+## Extract zero timepoint values
+```{r}
+zero_peaks <- peaks_mapped %>%
+  filter(inc_time_d_str == "0 Days") %>%
+  group_by(t_series_id, compound) %>%
+  mutate(n_analyical_reps = n()) %>%
+  ungroup() %>%
+  # exclude ambiguous peaks and those with multiple data points
+  # this needs to be fixed
+  filter(!is_ambiguous, n_analyical_reps == 1)
+
+zero_peaks_averaged <- zero_peaks %>% 
+  group_by(soil_id, compound) %>% 
+  summarise(at2H_mn_zero = mean(at2H),
+            d2H_mn_zero = mean(d2H),
+            area2_mn_zero = mean(area2))
+
+zero_peaks_averaged %>% 
+  openxlsx::write.xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"),
+                       overwrite = TRUE)
+
+# This is the dataset we will use for generation time calculations
+peaks_mapped_with_zeros <- 
+  peaks_mapped %>%
+  left_join(
+    zero_peaks_averaged,
+    by = c("soil_id", "compound")
+  ) 
+stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))
+
+# no zero samples
+peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
 ```
@@
 # Don't want our standard compounds to be used for generation time calculations! x_x
-peaks_mapped_active <- peaks_mapped %>% 
+peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros %>% 
   filter(str_detect(compound, "STD", negate = TRUE))
@@
 ```{r}
-gen_calc_data <- peaks_mapped_active %>% 
-  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, inc_time_d_str, terrain, f_start, rel_amount)) %>% 
+gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
   mutate(
-    at2H_label = 0.005,
     f_label = 0.5, # label is 0.5 at%
@@
     t0 = 0, # start time
+    f_start = at2H_mn_zero,
     d_t = inc_time_d - t0, # change in time
@@
   )
+
+gen_calc_data_abbr <- gen_calc_data %>% 
+  select(Analysis, sample_id, soil_id, terrain, replicate_id, compound, peak_nr, area2, 
+         at2H, at2H_mn_zero,u_d, gen_d)
 ```
@@
 ```{r}
-peaks_mapped_active %>% ggplot(
+peaks_mapped_with_zeros_analytes %>% ggplot(
   aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
   geom_point() +
-  geom_borderline() +
+  #geom_borderline() +
   scale_color_viridis_d() +
@@
 ```{r "shaded chromatogram", fig.width=8, fig.height=8}
-p_peaks_mapped_active <- peaks_mapped_active %>% ggplot(
+p_peaks_mapped_active <- peaks_mapped_with_zeros_analytes %>% ggplot(
   aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
@@
   scale_fill_viridis_c(option = "magma") +
-  facet_wrap(~inc_time_d_str, ncol = 1) +
+  facet_wrap(~sample_id, ncol = 1) +
   geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
@@
 
+# Plots
+
+## Generation Time of All Points
+
 ```{r}
@@
   stat_slab(height = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
+  # stat_pointinterval(color = "black") +
+  geom_boxplot(fill = "white",
+               color = "black",
+               width = 0.1,
+               outlier.shape = NA) +
   geom_point(
     color = "black",
-    shape = 124,
-    size = 3,
-    alpha = 1,
-    position = position_nudge(y = .03)) +
-  geom_text_repel(aes(label = compound), 
-                  color = "black", 
-                  nudge_y = -0.3, 
-                  size = 3) +
+    #shape = 124,
+    #size = 3,
+    alpha = 0.5,
+    position = position_nudge(y = -.03)) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
   scale_x_log10() +
@@
        subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
-       caption = "Soils collected from Niwot Ridge LTER") +
+       caption = "Soils collected from Colorado") +
   theme(legend.position = "none",
@@
 ```
+
+## Generation Time, Broken by Terrain
+
+```{r}
+p_gen_time_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = gen_d, 
+      y = terrain, 
+      color = terrain, 
+      fill = terrain)) +
+  stat_slab(height = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  geom_point(
+    color = "black",
+    shape = 124,
+    size = 3,
+    alpha = 0.5,
+    position = position_nudge(y = -.03)) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  scale_x_log10() +
+  annotation_logticks(sides = "b") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Generation time (days)",
+       y = "Terrain",
+       title = "Generation times of soil bacteria across terrain")
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+p_gen_time_terrain
+```
+
+## Turnover time by compound
+
+```{r}
+gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(aes(x = compound, y = u_d, color = terrain)) +
+  facet_wrap(vars(terrain, inc_time_d_str)) +
+  geom_point() +
+  theme_bw() +
+  labs(x = "Compound",
+       y = "Turnover time (d^-1)",
+       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
+  theme(
+    axis.text.x = element_text(angle = 90)
+  )
+```
+
+## Generation Time, Broken by Terrain and Incubation Time
+
+```{r}
+p_gen_time_terrain_inc <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = gen_d, 
+      y = inc_time_d_str, 
+      color = soil_id, 
+      fill = soil_id)) +
+  stat_slab(height = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  geom_point(
+    color = "black",
+    shape = 124,
+    size = 3,
+    alpha = 0.5,
+    position = position_nudge(y = -.03)) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  facet_wrap(~soil_id, ncol = 1) +
+  scale_x_log10() +
+  annotation_logticks(sides = "b") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Generation time (days)",
+       y = "Terrain",
+       title = "Generation times of soil bacteria across terrain")
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+p_gen_time_terrain_inc
+```
+
+## Turnover Time, Broken By Terrain
+
+```{r}
+p_turnover_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = inc_time_d_str, 
+      y = u_d, 
+      color = terrain, 
+      fill = terrain)) +
+  #stat_slab(height = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  geom_point(
+    color = "black",
+    #shape = 124,
+    size = 1,
+    alpha = 0.5,
+    position = position_nudge(x = -.03)) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  facet_wrap(~terrain, nrow = 1) +
+  scale_y_log10() +
+  annotation_logticks(sides = "a") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_bw() +
+  labs(x = "Generation time (days)",
+       y = "Terrain",
+       title = "Generation times of soil bacteria across terrain")
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+p_turnover_terrain
+```
+
+## 7 Day Turnover Times By Terrain
+
+```{r}
+p_turnover_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
+  ggplot(
+  aes(x = terrain, 
+      y = u_d)) +
+  #stat_slab(height = 0.3, alpha = 0.7) +
+  #stat_pointinterval(color = "black") +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(
+    color = "black",
+    #shape = 124,
+    size = 1,
+    alpha = 0.5) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  scale_y_log10() +
+  annotation_logticks(sides = "a") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_bw() +
+  labs(x = "Terrain",
+       y = "Turnover time (d^-1)",
+       title = "Generation times of soil bacteria across terrain") +
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+p_turnover_terrain_7d
+```
+
+## 7 Day Generation Times across terrain
+
+```{r}
+p_gen_time_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
+  ggplot(
+  aes(x = terrain, 
+      y = gen_d)) +
+  #stat_slab(height = 0.3, alpha = 0.7) +
+  #stat_pointinterval(color = "black") +
+  geom_boxplot(outlier.shape = NA) +
+  geom_point(
+    color = "black",
+    #shape = 124,
+    size = 1,
+    alpha = 0.5) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  scale_y_log10() +
+  annotation_logticks(sides = "a") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_bw() +
+  labs(x = "Terrain",
+       y = "Turnover time (d^-1)",
+       title = "Generation times of soil bacteria across terrain") +
+  theme(legend.position = "none",
+        axis.ticks.y = element_blank())
+p_gen_time_terrain_7d
+```
+
+## Literature Rates of Cell Turnover
 

### 2021-10-22 qSIP_calculations.Rmd
many more plot types, FID data now integrated

@@
 
-## Read raw data files
+## Import GC-FID Data
+```{r}
+root <- file.path("data", "gc_fid_data_2020")
+file_list = list.files(path = root)
+file_list <- file_list %>% 
+  str_subset("blank", negate = TRUE) %>% 
+  str_subset("Blank", negate = TRUE) %>% 
+  str_subset("GCMS-STD", negate = TRUE) %>% 
+  str_subset("BLK", negate = TRUE) # remove procedural blanks
+sample_names <- file_list %>% 
+  str_replace("FID.....", "") %>% 
+  str_replace("_100ul-nhex.xls", "") %>% 
+  str_replace("_100ul.xls", "")
+
+FID_all_data <-
+  tibble(
+    sample = sample_names,
+    file = file_list,
+    data = map(file.path(root, file), read_chromeleon_export),
+    injection_details = map(data, "injection_details"),
+    integration_results = map(data, "integration_results")
+  ) %>% select(-data)
+```
+
+### Unnest integration details
+
+```{r}
+FID_results <- FID_all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # Specify chain length
+  mutate(
+    chain = `Peak Name` %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs() %>% 
+      {paste0("C", .)} %>% 
+      factor()
+      ) %>% 
+  # Rename these columns so we can join the IRMS and FID data
+  # Important to specify what data comes from FID!
+  rename("sample_id" = sample,
+         "compound" = `Peak Name`,
+         "rt_FID" = `Retention Time`,
+         "area_FID" = `Area`,
+         "height_FID" = `Height`,
+         "rel_area_FID" = `Relative Area`,
+         "rel_height_FID" = `Relative Height`,
+         "amount_FID" = `Amount`
+         )
+```
+
+## Read raw IRMS data files
 
@@
 peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
+
+peaks_mapped_with_zeros <- peaks_mapped_with_zeros %>% 
+  mutate(
+    sample_id = substr(file_id, 10,14)
+    )
+```
+
+## Join IRMS and GC-FID Data
+
+```{r}
+peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
+  left_join(FID_results, by = c("sample_id", "compound"))
+```
+
+```{r}
+# Combine triplicate samples into one
+FID_results_trip <- FID_results %>% 
+  # Remove standards and fractions
+  filter(sample != "FAME37.1") %>% 
+  filter(sample != "TCBAME-2") %>% 
+  filter(!str_detect(sample, "F1")) %>% 
+  filter(!str_detect(sample, "F2")) %>% 
+  filter(!str_detect(sample, "F3")) %>% 
+  filter(!str_detect(sample, "cr")) %>%
+  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
+  group_by(sample_rep, `Peak Name`) %>%
+  # Generate summary stats
+  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
+            rel_area_min = min(`Relative Area`, na.rm=TRUE),
+            rel_height_max = max(`Relative Height`, na.rm=TRUE),
+            rel_height_min = min(`Relative Height`, na.rm=TRUE),
+            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
+            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
+            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
+  # Add some basic metadata
+  mutate(inc_time = case_when(
+    str_detect(sample_rep, "...0") ~ 0,
+    str_detect(sample_rep, "...3") ~ 3,
+    str_detect(sample_rep, "...7") ~ 7),
+    site = case_when(
+      str_detect(sample_rep, "c") ~ "Conifer",
+      str_detect(sample_rep, "t") ~ "Tundra",
+      str_detect(sample_rep, "g") ~ "Grassland",
+      str_detect(sample_rep, "m") ~ "Meadow")
+  )
 ```
@@
        title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
+       subtitle = "Lipid-specific generation times of bacteria",
        caption = "Soils collected from Colorado") +
@@
 #ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
+```
+
+## Generation Time, all points, not separated by inc_time
+
+```{r}
+p_gen_time_dist_all <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(
+  aes(x = gen_d, 
+      y = 1)) +
+  stat_halfeye(height = 0.1, 
+            alpha = 0.7,
+            color = "black") +
+  geom_jitter(aes(y = 0.9, 
+                 color = inc_time_d_str),
+             alpha = 0.5,
+             height = 0.03,
+             size = 1) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  scale_x_log10() +
+  coord_cartesian(ylim = c(0.5, 1.25)) +
+  annotation_logticks(sides = "b") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Generation time (days)",
+       title = "Generation times of soil bacteria",
+       subtitle = "Lipid-specific generation times of bacteria",
+       caption = "Soils collected from Colorado",
+       color = "Incubation Time") +
+  theme(legend.position = "bottom",
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank())
+p_gen_time_dist_all
+```
+
+## Generation time of all points, not log scale
+
+```{r}
+p_gen_time_dist_all_lin <- gen_calc_data %>% 
+  filter(inc_time_d != 0,
+         gen_d >= 0) %>% 
+  ggplot(
+  aes(x = u_d, 
+      y = 1)) +
+  stat_halfeye(height = 0.25, 
+            alpha = 0.7,
+            color = "black") +
+  geom_jitter(aes(y = 0.9, 
+                 color = inc_time_d_str),
+             alpha = 0.5,
+             height = 0.03,
+             size = 1) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  coord_cartesian(ylim = c(0.8, 1.25)) +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(x = "Turnover Time (d^-1)",
+       title = "Turnover Times",
+       subtitle = "Lipid-specific turnover times of bacteria",
+       caption = "Soils collected from Colorado",
+       color = "Incubation Time") +
+  theme(legend.position = "bottom",
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank())
+p_gen_time_dist_all_lin
 ```
@@
 
-# GC-FID Data
-
-## Import GC-FID Data
 ```{r}
-root <- file.path("data", "gc_fid_data_2020")
-file_list = list.files(path = root)
-file_list <- file_list %>% 
-  str_subset("blank", negate = TRUE) %>% 
-  str_subset("Blank", negate = TRUE) %>% 
-  str_subset("GCMS-STD", negate = TRUE) %>% 
-  str_subset("BLK", negate = TRUE) # remove procedural blanks
-sample_names <- file_list %>% 
-  str_replace("FID.....", "") %>% 
-  str_replace("_100ul-nhex.xls", "") %>% 
-  str_replace("_100ul.xls", "")
-
-all_data <-
-  tibble(
-    sample = sample_names,
-    file = file_list,
-    data = map(file.path(root, file), read_chromeleon_export),
-    injection_details = map(data, "injection_details"),
-    integration_results = map(data, "integration_results")
-  ) %>% select(-data)
+# coming soon!
 ```
 
-## Unnest integration details
-
+## Compound Abundance Versus Turnover Time
 ```{r}
-results <- all_data %>% 
-  select(-injection_details) %>% 
-  unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0) %>% 
-  # major compound groups
-  mutate(
-    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
-  )
+# coming soon!
 ```
-
-```{r}
-# Combine triplicate samples into one
-results_trip <- results %>% 
-  # Remove standards and fractions
-  filter(sample != "FAME37.1") %>% 
-  filter(sample != "TCBAME-2") %>% 
-  filter(!str_detect(sample, "F1")) %>% 
-  filter(!str_detect(sample, "F2")) %>% 
-  filter(!str_detect(sample, "F3")) %>% 
-  filter(!str_detect(sample, "cr")) %>%
-  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
-  group_by(sample_rep, `Peak Name`) %>%
-  # Generate summary stats
-  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
-            rel_area_min = min(`Relative Area`, na.rm=TRUE),
-            rel_height_max = max(`Relative Height`, na.rm=TRUE),
-            rel_height_min = min(`Relative Height`, na.rm=TRUE),
-            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
-            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
-            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
-  # Add some basic metadata
-  mutate(inc_time = case_when(
-    str_detect(sample_rep, "...0") ~ 0,
-    str_detect(sample_rep, "...3") ~ 3,
-    str_detect(sample_rep, "...7") ~ 7),
-    site = case_when(
-      str_detect(sample_rep, "c") ~ "Conifer",
-      str_detect(sample_rep, "t") ~ "Tundra",
-      str_detect(sample_rep, "g") ~ "Grassland",
-      str_detect(sample_rep, "m") ~ "Meadow")
-  )
-```
-
-## PLFA Summary Plot
-```{r}
-p_72hr_FAs <- results_trip %>% filter(inc_time == "3") %>% 
-  # Remove Standard Peaks
-  #filter(str_detect(`Peak Name`, c("PAIBE", "21:0 (STD)", "23:0 (STD)"), negate = TRUE)) %>% 
-  filter(`Peak Name` %nin% c("PAIBE", "21:0 (STD)", "23:0 (STD)")) %>% 
-  ggplot(aes(x = `Retention Time`, 
-             y = `Relative Area`, 
-             color = sample_rep, 
-             fill = sample_rep, 
-             label = `Peak Name`)) +
-  geom_col(width = 0.08) +
-  geom_errorbar(aes(ymin=rel_area_min, 
-                    ymax = rel_area_max), 
-                color = "black", 
-                width = 0.05) +
-  facet_wrap(~sample_rep, 
-             ncol = 1, 
-             scales = "free_y") +
-  geom_label_repel(fill = "black", 
-                   color = "white", 
-                   alpha = 0.7, 
-                   size = 3, 
-                   nudge_y = 2, 
-                   segment.color = "black") +
-  ggtitle("PLFA Profile: 72hr") +
-  theme_bw() +
-  scale_color_jama() +
-  scale_fill_jama()
-p_72hr_FAs
-```
-
-### IRMS relabund
-```{r}
-peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, fill = inc_time_d_str, color = inc_time_d_str)) +
-  geom_col() +
-  facet_wrap(~inc_time_d_str, ncol = 1)
-```
-
-### Relabund vs. activity
-```{r}
-gen_calc_data %>%
-  filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(x = rel_amount, 
-      y = u_d, 
-      color = inc_time_d_str, 
-      label = compound)) +
-  geom_point() +
-  geom_smooth(method = "lm",
-              se = FALSE,
-              formula = "y~x") +
-  geom_line(aes(group = compound), 
-            color = "black", 
-            alpha = 0.3) +
-  geom_text_repel(size = 3) +
-  theme_classic() +
-  scale_color_npg() +
-  labs(x = "Relative Amount",
-       y = "Turnover (d^-1)",
-       color = "Incubation Time") +
-  theme(legend.position = "top")
-```
-
-### Relabund vs. activity colored by 2F
-
-```{r}
-gen_calc_data %>%
-  filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(x = rel_amount, 
-      y = u_d, 
-      color = as.numeric(f_t), 
-      label = compound)) +
-  geom_point(aes(shape = inc_time_d_str)) +
-  geom_smooth(method = "lm",
-              se = FALSE,
-              formula = "y~x") +
-  geom_line(aes(group = compound), 
-            color = "black", 
-            alpha = 0.3) +
-  geom_text_repel(color = "black", 
-                  size = 3) +
-  scale_color_viridis_c(option = "magma") +
-  theme_classic() +
-  labs(x = "Relative Amount",
-       y = "Turnover (d^-1)",
-       shape = "Incubation Time",
-       color = "2F") +
-  theme(legend.position = "bottom")
-```
-
-## Merge IRMS and FID data
-
-### PICK UP HERE: how do we match GC-FID compound data with IRMS compound data?
-
-```{r}
-results_trip_matched <- results_trip %>% 
-  filter(`Peak Name` %in% gen_calc_data$compound)
-
-matched_idx <- match(gen_calc_data$compound, results_trip_matched$`Peak Name`)
-results_trip_matched$`Peak Name`[matched_idx]
-
-combined_irms_fid <- gen_calc_data %>%
-  group_by(terrain) %>% 
-  mutate(relative_area = results_trip$`Relative Area`[""])
-```

### 2021-10-27 qSIP_calculations.Rmd
LOTS O' PLOTS

@@
 ```{r, message=FALSE, warning=FALSE}
+# Libraries
 library(tidyverse) # general data wrangling and plotting
+library(forcats) # handling factors
 library(isoreader) # reading the raw data files
@@
 library(ggborderline) # nice looking ggplot lines
-library(ggrepel)
-library(latex2exp)
-library(ggdist)
-library(ggsignif)
+library(ggrepel) # nice looking ggplot labels
+library(latex2exp) # latex parsing
+library(ggdist) # ggplot distribution geoms
+library(ggsignif) # ggplot significance markers
+library(ggridges) # ggplot ridgeline geoms
 
+# Sourced Functions
 source(file.path("libs", "visualization.R"))
@@
 
-## Load Metadata and Problematic Run Data
+## Load IRMS Data
+
+### Load Metadata and Problematic Run Data
 
@@
 
-## Load Peak Map
+### Load Peak Map
 
@@
 
-## Import GC-FID Data
-```{r}
-root <- file.path("data", "gc_fid_data_2020")
-file_list = list.files(path = root)
-file_list <- file_list %>% 
-  str_subset("blank", negate = TRUE) %>% 
-  str_subset("Blank", negate = TRUE) %>% 
-  str_subset("GCMS-STD", negate = TRUE) %>% 
-  str_subset("BLK", negate = TRUE) # remove procedural blanks
-sample_names <- file_list %>% 
-  str_replace("FID.....", "") %>% 
-  str_replace("_100ul-nhex.xls", "") %>% 
-  str_replace("_100ul.xls", "")
-
-FID_all_data <-
-  tibble(
-    sample = sample_names,
-    file = file_list,
-    data = map(file.path(root, file), read_chromeleon_export),
-    injection_details = map(data, "injection_details"),
-    integration_results = map(data, "integration_results")
-  ) %>% select(-data)
-```
-
-### Unnest integration details
-
-```{r}
-FID_results <- FID_all_data %>% 
-  select(-injection_details) %>% 
-  unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0) %>% 
-  # Specify chain length
-  mutate(
-    chain = `Peak Name` %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs() %>% 
-      {paste0("C", .)} %>% 
-      factor()
-      ) %>% 
-  # Rename these columns so we can join the IRMS and FID data
-  # Important to specify what data comes from FID!
-  rename("sample_id" = sample,
-         "compound" = `Peak Name`,
-         "rt_FID" = `Retention Time`,
-         "area_FID" = `Area`,
-         "height_FID" = `Height`,
-         "rel_area_FID" = `Relative Area`,
-         "rel_height_FID" = `Relative Height`,
-         "amount_FID" = `Amount`
-         )
-```
-
-## Read raw IRMS data files
+### Read raw IRMS data files
 
 ```{r, warning=FALSE}
-# set file path(s) to data files, folders or rds collections 
+# Set file path(s) to data files, folders or rds collections 
 # can be multiple folders or mix of folders and files
-# setting the month of analysis folder - Isoverse will iteratively search subfolders. Huzzah! ^_^
-data_path <- file.path("data", "IRMS", "2021-09")
+# Isoverse will iteratively search subfolders. Huzzah! ^_^
+data_path <- file.path("data", "IRMS", "raw_data")
 ref_ratio <- get_standard("2H") %>% as.numeric()
@@
 
-## Process file info & peak table
+### Process file info & peak table
 
@@
 
-## Show file information
+### Show file information
 
@@
 
-## Example chromatograms
+### Example chromatograms
 
@@
 #   theme(strip.background = element_blank())
+```
+
+## Import GC-FID Data
+```{r}
+root <- file.path("data", "gc_fid_data_2020")
+file_list = list.files(path = root)
+file_list <- file_list %>% 
+  str_subset("blank", negate = TRUE) %>% 
+  str_subset("Blank", negate = TRUE) %>% 
+  str_subset("GCMS-STD", negate = TRUE) %>% 
+  str_subset("BLK", negate = TRUE) # remove procedural blanks
+sample_names <- file_list %>% 
+  str_replace("FID.....", "") %>% 
+  str_replace("_100ul-nhex.xls", "") %>% 
+  str_replace("_100ul.xls", "")
+
+FID_all_data <-
+  tibble(
+    sample = sample_names,
+    file = file_list,
+    data = map(file.path(root, file), read_chromeleon_export),
+    injection_details = map(data, "injection_details"),
+    integration_results = map(data, "integration_results")
+  ) %>% select(-data)
+```
+
+### Unnest FID integration details
+
+```{r}
+FID_results <- FID_all_data %>% 
+  select(-injection_details) %>% 
+  unnest(integration_results) %>% 
+  filter(nchar(`Peak Name`) > 0) %>% 
+  # Specify chain length
+  mutate(
+    chain = `Peak Name` %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs() %>% 
+      {paste0("C", .)} %>% 
+      factor()
+      ) %>% 
+  # Rename these columns so we can join the IRMS and FID data
+  # Important to specify what data comes from FID!
+  rename("sample_id" = sample,
+         "compound" = `Peak Name`,
+         "rt_FID" = `Retention Time`,
+         "area_FID" = `Area`,
+         "height_FID" = `Height`,
+         "rel_area_FID" = `Relative Area`,
+         "rel_height_FID" = `Relative Height`,
+         "amount_FID" = `Amount`
+         )
 ```
@@
   ungroup() %>%
-  # exclude ambiguous peaks and those with multiple data points
-  # this needs to be fixed
-  filter(!is_ambiguous, n_analyical_reps == 1)
+  # exclude ambiguous peaks
+  filter(!is_ambiguous)
 
@@
   # Remove standards and fractions
-  filter(sample != "FAME37.1") %>% 
-  filter(sample != "TCBAME-2") %>% 
-  filter(!str_detect(sample, "F1")) %>% 
-  filter(!str_detect(sample, "F2")) %>% 
-  filter(!str_detect(sample, "F3")) %>% 
-  filter(!str_detect(sample, "cr")) %>%
-  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
-  group_by(sample_rep, `Peak Name`) %>%
+  filter(sample_id != "FAME37.1") %>% 
+  filter(sample_id != "TCBAME-2") %>% 
+  filter(!str_detect(sample_id, "F1")) %>% 
+  filter(!str_detect(sample_id, "F2")) %>% 
+  filter(!str_detect(sample_id, "F3")) %>% 
+  filter(!str_detect(sample_id, "cr")) %>%
+  mutate(sample_rep = str_remove(sample_id, "[xyz]")) %>% 
+  group_by(sample_rep, compound) %>%
   # Generate summary stats
-  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
-            rel_area_min = min(`Relative Area`, na.rm=TRUE),
-            rel_height_max = max(`Relative Height`, na.rm=TRUE),
-            rel_height_min = min(`Relative Height`, na.rm=TRUE),
-            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
-            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
-            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
+  summarize(rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
+            rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
+            rel_height_FID_max = max(rel_height_FID, na.rm=TRUE),
+            rel_height_FID_min = min(rel_height_FID, na.rm=TRUE),
+            rt_FID = mean(rt_FID, na.rm=TRUE),
+            rel_area_FID = mean(rel_area_FID, na.rm=TRUE),
+            rel_height_FID = mean(rel_height_FID, na.rm=TRUE)) %>% 
   # Add some basic metadata
@@
 # Don't want our standard compounds to be used for generation time calculations! x_x
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros %>% 
+peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
   filter(str_detect(compound, "STD", negate = TRUE))
+```
+
+## Summarize Analytical and Experimental Replicates
+
+```{r}
+peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
+  group_by(terrain, inc_time_d, compound) %>% 
+  summarize_if(is.numeric, mean, na.rm = TRUE)
+```
+
+## Calculate turnover time
+Turnover is calculated as below:
+
+$$
+\mu = - \frac{1}{t} \cdot (ln (\frac{F_T - a \cdot F_L}{F_0 - a \cdot F_L})
+$$
+
+```
+# R code:
+gencalc <- function(a, FT, F0, FL, t) {
+  case_when(
+    t == 0 ~ NA_real_,
+    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
+  )
+}
+
 ```
@@
                   t = d_t), # change in time
-         # Returns turnover (µ) in days^-1
-         gen_d = log(2) / u_d # calculate generation time
+    # "negative" turnovers are artifacts of noise and should be zero
+    u_d = if_else(u_d < 0, 0, u_d),
+    # calculate generation time, converting negatives to zero
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+  ) %>%
+  mutate(
+    chain_fctr = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs() %>% 
+      {paste0("C", .)} %>% 
+      factor()
+      ) %>% 
+  mutate(
+    chain_num = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs()
+  )
+
+gen_calc_data_summarized <- peaks_mapped_summarized %>% 
+  mutate(
+    f_label = 0.5, # label is 0.5 at%
+    a = 0.5, # assimilation efficiency
+    t0 = 0, # start time
+    f_start = at2H_mn_zero,
+    d_t = inc_time_d - t0, # change in time
+    f_t = at2H, # restate 2F at time t
+    u_d = gencalc(a = 0.5, # Assimilation efficiency
+                  FT = f_t, # 2F at time t (at%)
+                  F0 = f_start, # 2F at t0 (at%)
+                  FL = f_label, # 2F of label (at%)
+                  t = d_t), # change in time
+    # "negative" turnovers are artifacts of noise and should be zero
+    u_d = if_else(u_d < 0, 0, u_d),
+    # calculate generation time, converting negatives to zero
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+  ) %>%
+  mutate(
+    chain_fctr = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs() %>% 
+      {paste0("C", .)} %>% 
+      factor()
+      ) %>% 
+  mutate(
+    chain_num = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs()
   )
@@
 
+# Plots
+
+## Peak Tracer Incorporation
 ```{r}
@@
   geom_point() +
+  geom_smooth(se = FALSE,
+              method = "loess") +
   #geom_borderline() +
@@
 
-# Plots
+## Compound enrichment over time
+
+```{r}
+gen_calc_data_summarized %>% 
+  mutate(compound = fct_reorder(compound, rt)) %>% 
+  ggplot(aes(x = inc_time_d,
+             y = at2H,
+             color = compound)) +
+  geom_borderline() +
+  geom_point() +
+  facet_wrap(vars(terrain)) +
+  scale_x_continuous(breaks = c(0, 3, 7)) +
+  scale_color_viridis_d() +
+  theme_bw() +
+  labs(x = "Incubation Time (Days)",
+       y = "Mean %D")
+```
+
+## Compound enrichment over time with label strength
+
+```{r}
+gen_calc_data_summarized %>% 
+  filter(compound != "i-16:0") %>% 
+  mutate(compound = fct_reorder(compound, rt)) %>% 
+  ggplot(aes(x = inc_time_d,
+             y = at2H,
+             color = compound)) +
+  geom_point() +
+  geom_borderline() +
+  geom_hline(yintercept = 0.5,
+             color = "red") +
+  facet_wrap(vars(terrain)) +
+  scale_x_continuous(breaks = c(0, 3, 7)) +
+  scale_color_viridis_d() +
+  labs(x = "Incubation Time (Days)",
+       y = "Mean %D") +
+  theme_bw()
+```
 
@@
 ```{r}
-p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+p_gen_time_dist <- gen_calc_data %>% 
+  filter(inc_time_d != 0) %>% 
   ggplot(
-  aes(x = gen_d, 
-      y = inc_time_d_str, 
+  aes(y = gen_d, 
+      x = inc_time_d_str, 
       color = inc_time_d_str, 
       fill = inc_time_d_str)) +
-  stat_slab(height = 0.3, alpha = 0.7) +
-  # stat_pointinterval(color = "black") +
-  geom_boxplot(fill = "white",
-               color = "black",
-               width = 0.1,
-               outlier.shape = NA) +
+  stat_slab(width = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  # geom_boxplot(fill = "white",
+  #              color = "black",
+  #              width = 0.1,
+  #              outlier.shape = NA) +
   geom_point(
     color = "black",
-    #shape = 124,
-    #size = 3,
+    shape = 95,
+    size = 3,
     alpha = 0.5,
-    position = position_nudge(y = -.03)) +
+    position = position_nudge(x = -.03)) +
   # geom_text_repel(aes(label = compound), 
@@
   #                 size = 3) +
-  scale_x_log10() +
-  annotation_logticks(sides = "b") +
+  scale_y_log10() +
+  annotation_logticks(sides = "l") +
   scale_fill_npg() +
@@
   theme_classic() +
-  labs(x = "Generation time (days)",
-       y = "Incubation time",
+  labs(y = "Generation time (days)",
+       x = "Incubation time",
        title = "Generation times of soil bacteria",
@@
   ggplot(
-  aes(x = gen_d, 
-      y = 1)) +
-  stat_halfeye(height = 0.1, 
-            alpha = 0.7,
-            color = "black") +
-  geom_jitter(aes(y = 0.9, 
-                 color = inc_time_d_str),
+  aes(y = gen_d, 
+      x = 1)) +
+  stat_slab(width = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  # geom_boxplot(fill = "white",
+  #              color = "black",
+  #              width = 0.1,
+  #              outlier.shape = NA) +
+  geom_point(
+    color = "black",
+    shape = 95,
+    size = 3,
     alpha = 0.5,
-             height = 0.03,
-             size = 1) +
+    position = position_nudge(x = -.03)) +
   # geom_text_repel(aes(label = compound), 
@@
   #                 size = 3) +
-  scale_x_log10() +
-  coord_cartesian(ylim = c(0.5, 1.25)) +
-  annotation_logticks(sides = "b") +
+  scale_y_log10() +
+  annotation_logticks(sides = "l") +
   scale_fill_npg() +
@@
   theme_classic() +
-  labs(x = "Generation time (days)",
+  labs(y = "Generation time (days)",
        title = "Generation times of soil bacteria",
        subtitle = "Lipid-specific generation times of bacteria",
-       caption = "Soils collected from Colorado",
-       color = "Incubation Time") +
-  theme(legend.position = "bottom",
-        axis.ticks.y = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank())
+       caption = "Soils collected from Colorado") +
+  theme(legend.position = "none",
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank())
 p_gen_time_dist_all
+```
+
+## Generation Time, all points, not separated, > C19 removed
+
+```{r}
+p_gen_time_dist_all_no19 <- gen_calc_data %>% 
+  filter(inc_time_d != 0,
+         chain_num < 19) %>% 
+  ggplot(
+  aes(y = gen_d, 
+      x = 1)) +
+  stat_slab(width = 0.3, alpha = 0.7) +
+  stat_pointinterval(color = "black") +
+  # geom_boxplot(fill = "white",
+  #              color = "black",
+  #              width = 0.1,
+  #              outlier.shape = NA) +
+  geom_point(
+    color = "black",
+    shape = 95,
+    size = 3,
+    alpha = 0.5,
+    position = position_nudge(x = -.03)) +
+  # geom_text_repel(aes(label = compound), 
+  #                 color = "black", 
+  #                 nudge_y = -0.3, 
+  #                 size = 3) +
+  scale_y_log10() +
+  annotation_logticks(sides = "l") +
+  scale_fill_npg() +
+  scale_color_npg() +
+  theme_classic() +
+  labs(y = "Generation time (days)",
+       title = "Generation times of soil bacteria",
+       subtitle = "Lipid-specific generation times of bacteria \nC20+ removed",
+       caption = "Soils collected from Colorado") +
+  theme(legend.position = "none",
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank())
+p_gen_time_dist_all_no19
 ```
@@
   filter(inc_time_d != 0,
-         gen_d >= 0) %>% 
+         gen_d >= 0,
+         chain_num < 19) %>% 
   ggplot(
-  aes(x = u_d, 
-      y = 1)) +
-  stat_halfeye(height = 0.25, 
+  aes(y = gen_d, 
+      x = 1)) +
+  stat_slab(width = 0.25, 
             alpha = 0.7,
             color = "black") +
-  geom_jitter(aes(y = 0.9, 
-                 color = inc_time_d_str),
+  stat_pointinterval(color = "black") +
+  # geom_boxplot(fill = "white",
+  #              color = "black",
+  #              width = 0.1,
+  #              outlier.shape = NA) +
+  geom_point(
+    color = "black",
+    shape = 95,
+    size = 3,
     alpha = 0.5,
-             height = 0.03,
-             size = 1) +
+    position = position_nudge(x = -.03)) +
   # geom_text_repel(aes(label = compound), 
@@
   #                 size = 3) +
-  coord_cartesian(ylim = c(0.8, 1.25)) +
   scale_fill_npg() +
@@
   theme_classic() +
-  labs(x = "Turnover Time (d^-1)",
-       title = "Turnover Times",
-       subtitle = "Lipid-specific turnover times of bacteria",
-       caption = "Soils collected from Colorado",
-       color = "Incubation Time") +
-  theme(legend.position = "bottom",
-        axis.ticks.y = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank())
+  labs(y = "Generation time (days)",
+       title = "Generation times of soil bacteria",
+       subtitle = "Lipid-specific generation times of bacteria",
+       caption = "Soils collected from Colorado") +
+  theme(legend.position = "none",
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title.x = element_blank())
 p_gen_time_dist_all_lin
@@
 ```{r}
-p_gen_time_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
+signif_comparisons <- gen_calc_data %>% pull(terrain) %>% unique()
+
+p_gen_time_terrain <- gen_calc_data %>% 
+  filter(inc_time_d != 0,
+         chain_num < 19) %>% 
   ggplot(
-  aes(x = gen_d, 
-      y = terrain, 
+  aes(y = gen_d, 
+      x = terrain,
       color = terrain,
       fill = terrain)) +
-  stat_slab(height = 0.3, alpha = 0.7) +
+  stat_slab(width = 0.25, 
+            alpha = 0.7,
+            color = "black") +
   stat_pointinterval(color = "black") +
+  # geom_boxplot(fill = "white",
+  #              color = "black",
+  #              width = 0.1,
+  #              outlier.shape = NA) +
   geom_point(
     color = "black",
-    shape = 124,
+    shape = 95,
     size = 3,
     alpha = 0.5,
-    position = position_nudge(y = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_x_log10() +
-  annotation_logticks(sides = "b") +
+    position = position_nudge(x = -.07)) +
+  geom_signif(comparisons = list(signif_comparisons),
+              map_signif_level = TRUE) +
+  scale_y_log10(breaks = c(1, 10, 100)) +
+  annotation_logticks(sides = "l") +
   scale_fill_npg() +
@@
   theme_classic() +
-  labs(x = "Generation time (days)",
-       y = "Terrain",
-       title = "Generation times of soil bacteria across terrain")
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
+  labs(y = "Generation time (days)",
+       title = "Generation times of soil bacteria",
+       subtitle = "Lipid-specific generation times of bacteria \nC20+ omitted") +
+  theme(axis.ticks.y = element_blank(),
+        axis.text.x = element_text(angle = 45, hjust = 1))
 p_gen_time_terrain
@@
 gen_calc_data %>% filter(inc_time_d != 0) %>% 
-  ggplot(aes(x = compound, y = u_d, color = terrain)) +
-  facet_wrap(vars(terrain, inc_time_d_str)) +
+  mutate(compound = fct_reorder(compound, rt)) %>% 
+  ggplot(aes(x = compound,
+             y = u_d, 
+             color = terrain, 
+             fill = terrain)) +
+  facet_wrap(vars(terrain, inc_time_d_str),
+             ncol = 2) +
+  geom_segment(aes(xend = compound,
+                   yend = 0),
+               color = "black") +
   geom_point() +
-  theme_bw() +
+  scale_color_npg() +
   labs(x = "Compound",
        y = "Turnover time (d^-1)",
-       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
+       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids",
+       color = "Terrain",
+       fill = "Terrain") +
+  theme_bw() +
   theme(
-    axis.text.x = element_text(angle = 90)
+    axis.text.x = element_text(angle = 90, 
+                               hjust = 1)
   )
-```
-
-## Generation Time, Broken by Terrain and Incubation Time
-
-```{r}
-p_gen_time_terrain_inc <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(x = gen_d, 
-      y = inc_time_d_str, 
-      color = soil_id, 
-      fill = soil_id)) +
-  stat_slab(height = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
-  geom_point(
-    color = "black",
-    shape = 124,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(y = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  facet_wrap(~soil_id, ncol = 1) +
-  scale_x_log10() +
-  annotation_logticks(sides = "b") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(x = "Generation time (days)",
-       y = "Terrain",
-       title = "Generation times of soil bacteria across terrain")
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
-p_gen_time_terrain_inc
 ```
@@
   stat_pointinterval(color = "black") +
-  geom_point(
-    color = "black",
-    #shape = 124,
-    size = 1,
-    alpha = 0.5,
-    position = position_nudge(x = -.03)) +
+  # geom_point(
+  #   color = "black",
+  #   #shape = 124,
+  #   size = 1,
+  #   alpha = 0.5,
+  #   position = position_nudge(x = -.05)) +
   # geom_text_repel(aes(label = compound), 
@@
   theme_bw() +
-  labs(x = "Generation time (days)",
-       y = "Terrain",
+  labs(x = "Incubation Time",
+       y = "Turnover Time (d^-1)",
        title = "Generation times of soil bacteria across terrain")
@@
     alpha = 0.5) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
+  geom_signif(comparisons = list(signif_comparisons),
+              map_signif_level = TRUE) +
   scale_y_log10() +
@@
 
+## Turnover time versus lipid relative abundance
+
+```{r}
+
+gen_calc_data %>% filter(inc_time_d != 0) %>% 
+  ggplot(aes(x = rel_area_FID,
+             y = u_d,
+             color = chain_fctr)) +
+  geom_point() +
+  scale_color_viridis_d() +
+  facet_wrap(~terrain) +
+  labs(x = "Relative Area (GC-FID)",
+       y = "Turnover (d^-1)",
+       color = "Compound class") +
+  theme_bw()
+
+```
+
+## Compound-Specific Enrichment
+
+```{r}
+gen_calc_data %>% 
+  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
+  ggplot(aes(x = at2H,
+             y = compound,
+             fill = stat(x))) +
+  geom_density_ridges_gradient(scale = 3) +
+  # Vline showing enrichment strength
+  # geom_vline(xintercept = 0.5,
+  #            color = "red") +
+  facet_wrap(vars(inc_time_d_str), ncol = 1) +
+  scale_fill_viridis_c(option = "C") +
+  labs(fill = "% D",
+       x = "% D",
+       y = "Compound") +
+  theme_ridges() +
+  theme(axis.text.y = element_text(size = 5),
+        legend.position = "right",
+        legend.key.width = unit(0.2, "line"),
+        legend.text = element_text(size = 10))
+```
+
+## Compound specific turnover
+```{r}
+gen_calc_data %>% 
+  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
+  ggplot(aes(x = u_d,
+             y = compound,
+             fill = stat(x))) +
+  geom_density_ridges_gradient() +
+  # Vline showing enrichment strength
+  facet_wrap(vars(inc_time_d_str), ncol = 1) +
+  scale_fill_viridis_c(option = "C") +
+  labs(fill = "µ (d^-1)",
+       x = "µ (d^-1)",
+       y = "Compound") +
+  theme_minimal()
+```
+
+## Mean Turnover by Terrain
+
+```{r}
+gen_calc_data_summarized %>% 
+  group_by(inc_time_d, terrain) %>% 
+  summarize(u_d_mn = mean(u_d),
+            u_d_max = max(u_d),
+            u_d_min = min(u_d),
+            gen_d_mn = mean(gen_d),
+            gen_d_max = max(gen_d),
+            gen_d_min = min(gen_d)) %>% 
+  ggplot(aes(x = terrain, 
+             y = u_d_mn,
+             color = as.character(inc_time_d))) +
+  geom_path(color = "black") +
+  geom_point() +
+  coord_cartesian(ylim = c(0, 0.05)) +
+  labs(x = "Terrain",
+       y = "Mean Turnover (d^-1)",
+       color = "Incubation Time") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
+
+## Mean Turnover Aggregated
+
+```{r}
+gen_calc_data_summarized %>% 
+  # Calculate means, by terrain
+  group_by(inc_time_d, terrain) %>% 
+  summarize(u_d_mn = mean(u_d),
+            u_d_max = max(u_d),
+            u_d_min = min(u_d),
+            gen_d_mn = mean(gen_d),
+            gen_d_max = max(gen_d),
+            gen_d_min = min(gen_d)) %>% 
+  # Calculate mean of means
+  group_by(inc_time_d) %>% 
+  summarize(u_d_mn_ag = mean(u_d_mn),
+            u_d_max_ag = max(u_d_mn),
+            u_d_min_ag = min(u_d_mn),
+            gen_d_mn_ag = mean(gen_d_mn),
+            gen_d_max_ag = max(gen_d_mn),
+            gen_d_min_ag = min(gen_d_mn)) %>% 
+  ggplot(aes(x = 1, 
+             y = u_d_mn_ag,
+             color = as.character(inc_time_d))) +
+  geom_path(color = "black") +
+  geom_point() +
+  coord_cartesian(ylim = c(0, 0.05)) +
+  labs(x = "Terrain",
+       y = "Mean Turnover (d^-1)",
+       color = "Incubation Time") +
+  theme_minimal() +
+  theme(axis.text.x = element_blank(),
+        axis.title.x = element_blank())
+
+```
+
 ## Literature Rates of Cell Turnover
@@
 ```{r}
-# coming soon!
+# Import lit search data
+lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))
+
+lit_turnover <- lit_turnover %>% 
+  # Arrange by turnover time
+  arrange(u_d_mn) %>% 
+  # Reassign n values
+  mutate(n = seq(from = 1, to = nrow(lit_turnover)))
+
+# Our summarized data
+gen_calc_mini <- gen_calc_data_summarized %>% 
+  # Calculate mean per terrain per inc time
+  group_by(inc_time_d, terrain) %>% 
+  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
+            u_d_max = max(u_d),
+            u_d_min = min(u_d)) %>%
+  # Calculate mean of means (combine inc_times)
+  group_by(terrain) %>% 
+  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
+            u_d_max = max(u_d_mn, na.rm = TRUE),
+            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
+  # Rename to match `lit_turnover` tibble
+  rename(soil_type = terrain) %>% 
+  arrange(u_d_mn) %>% 
+  mutate(method = "2H Lipid SIP",
+         n = c(17, 18, 19),
+    soil_type = case_when(
+      soil_type == "Niwot Ridge Tundra" ~ "tundra",
+      soil_type == "Gordon Gulch Conifer Forest" ~ "conifer forest",
+      soil_type == "Marshall Mesa Grassland" ~ "grassland")
+  )
+
+# Add in our data! ^_^
+lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)
+
+lit_turnover_w_ours <- lit_turnover_w_ours %>% 
+  mutate(
+    source = case_when(
+      method == "2H Lipid SIP" ~ "This study",
+      TRUE ~ "Literature values"
+  ))
+
+# By terrain
+
+lit_turnover_w_ours %>%
+  # order by mean turnover rate
+  ggplot(aes(x = n, 
+             y = u_d_mn,
+             color = soil_type)) +
+  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
+               color = "black") +
+  geom_point(size = 3) +
+  scale_color_npg() +
+  geom_label(label = "This study",
+            x = 18,
+            y = 0.13,
+            color = "black") +
+  geom_label(label = "Literature values",
+            x = 9,
+            y = 0.6,
+            color = "black") +
+  #scale_y_log10() +
+  #annotation_logticks(sides = "l") +
+  coord_cartesian(
+    xlim = c(0, 20),
+    ylim = c(0, 0.80), 
+    expand = FALSE) +
+  labs(y = "Mean Turnover Time (d^-1)",
+       color = "Soil Source") +
+  theme_classic() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = "bottom")
+
+## With log scale
+
+lit_turnover_w_ours %>%
+  # order by mean turnover rate
+  ggplot(aes(x = n, 
+             y = u_d_mn,
+             color = soil_type)) +
+  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
+               color = "black") +
+  geom_point(size = 3) +
+  scale_color_npg() +
+  geom_label(label = "This study",
+            x = 18,
+            y = 0.10,
+            color = "black") +
+  geom_label(label = "Literature values",
+            x = 9,
+            y = 0.35,
+            color = "black") +
+  scale_y_log10() +
+  annotation_logticks(sides = "l") +
+  labs(y = "Mean Turnover Time (d^-1)",
+       color = "Soil Source") +
+  theme_classic() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = "bottom")
+
 ```
 
-## Compound Abundance Versus Turnover Time
+## Literature Rates of Cell Turnover by Method
 ```{r}
-# coming soon!
+lit_turnover_w_ours %>%
+  # order by mean turnover rate
+  ggplot(aes(x = n, 
+             y = u_d_mn,
+             color = method)) +
+  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
+               color = "black") +
+  geom_point(size = 3) +
+  geom_text_repel(aes(label = method),
+                  color = "black",
+                  size = 2,
+                  segment.color = "red",
+                  nudge_y = 0.2,
+                  segment.curvature = -0.1,
+                  segment.angle = -20,
+                  segment.ncp = 3,
+                  segment.size = 0.1) +
+  scale_color_viridis_d() +
+  scale_y_log10(breaks = c(0.01, 0.05, 0.1, 0.5)) +
+  annotation_logticks(sides = "l") +
+  labs(y = "Mean Turnover Time (d^-1)",
+       color = "Soil Source") +
+  theme_classic() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title.x = element_blank(),
+        )
 ```

### 2021-10-27 qSIP_calculations.Rmd
fixed issue where at2H was parsed as chr

@@
 
+# zero_peaks_averaged <- read_xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"))
+
 # This is the dataset we will use for generation time calculations
@@
 # no zero samples
-peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
+# peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
 
@@
   )
+```
+
+```{r}
 
@@
 
-gen_calc_data_abbr <- gen_calc_data %>% 
-  select(Analysis, sample_id, soil_id, terrain, replicate_id, compound, peak_nr, area2, 
-         at2H, at2H_mn_zero,u_d, gen_d)
+# gen_calc_data_summarized %>% openxlsx::write.xlsx(file.path("data", "gen_calc_data_summarized.xlsx"))
 ```
@@
 ```{r}
-gen_calc_data %>% filter(inc_time_d != 0) %>% 
-  mutate(compound = fct_reorder(compound, rt)) %>% 
+gen_calc_data_summarized %>% 
+  filter(inc_time_d != 0, compound != "i-16:0") %>%
+  group_by(compound) %>% 
+  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
+  mutate(compound = fct_reorder(compound, u_d)) %>% 
   ggplot(aes(x = compound,
              y = u_d,
-             color = terrain, 
-             fill = terrain)) +
-  facet_wrap(vars(terrain, inc_time_d_str),
-             ncol = 2) +
-  geom_segment(aes(xend = compound,
-                   yend = 0),
-               color = "black") +
-  geom_point() +
-  scale_color_npg() +
+             fill = u_d)) +
+  geom_col(position = "dodge") +
+  scale_fill_viridis_c(option = "plasma") +
   labs(x = "Compound",
-       y = "Turnover time (d^-1)",
-       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids",
-       color = "Terrain",
-       fill = "Terrain") +
+       y = "Mean Turnover time (d^-1)",
+       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
   theme_bw() +
@@
 
-gen_calc_data %>% filter(inc_time_d != 0) %>% 
+gen_calc_data %>% 
+  filter(inc_time_d != 0) %>% 
   ggplot(aes(x = rel_area_FID,
-             y = u_d,
-             color = chain_fctr)) +
-  geom_point() +
+             y = u_d)) +
+  geom_point(aes(color = chain_fctr)) +
+  geom_smooth(method = "lm",
+              se = FALSE) +
   scale_color_viridis_d() +

### 2021-10-27 qSIP_taxonomy.Rmd
initial commit

---
title: "2H SIP Taxonomy"
author: "Tristan Caro"
date: "10/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages
```{r}
library(tidyverse)
library(ggsci)
library(ggbiplot)
library(readxl)
library(ggrepel)
```

# Load Data
```{r}
# Generation time data from `qSIP_calculations.Rmd`
gen_calc_data_summarized <- read_xlsx(file.path("data", "gen_calc_data_summarized.xlsx"))

# BacDive data from `fatty_acids_from_BacDive.Rmd`
fatty_acids_with_tax <- read_xlsx(file.path("data", "fatty_acids_with_tax.xlsx"))

fatty_acids_wide_with_tax <- read_xlsx(file.path("data", "fatty_acids_wide_with_tax.xlsx"))
```

# Join dataframes

```{r}
fatty_acids_with_tax <- fatty_acids_with_tax %>% 
  mutate(
    FA = case_when(
      FA == "a15:0" ~ "a-15:0",
      FA == "i15:0" ~ "i-15:0",
      FA == "a17:0" ~ "a-17:0",
      FA == "i17:0" ~ "i-17:0",
      TRUE ~ FA
    ))

sixteen_ones <- c("16:1 trans 9", "16:1 cis 9")
eighteen_ones <- c("18:1 cis 9", "18:1 trans 9", "18:1")

gen_calc_taxa <- gen_calc_data_summarized %>% 
  select(terrain, inc_time_d, compound, at2H, at2H_mn_zero, rel_area_FID, u_d, gen_d, chain_fctr, chain_num) %>% 
  mutate(
    FA = case_when(
      compound %in% sixteen_ones ~ "16:1",
      compound == "16:0" ~ "16:0",
      compound == "18:0" ~ "18:0",
      compound %in% eighteen_ones ~ "18:1",
      compound == "18:2 trans 9, 12" ~ "18:2",
      compound == "17:0 cyclo" ~ "cyc 17:0",
      TRUE ~ compound
  ))

## Making the choice to select 3 day turnover rates, averaged across environments
gen_calc_taxa_3d_agg <- gen_calc_taxa %>% 
  filter(inc_time_d == 3) %>% 
  group_by(FA) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)

FA_w_turnover <- left_join(fatty_acids_with_tax, gen_calc_taxa_3d_agg, by = "FA")
```

# Plot Averages

```{r}
fatty_acids_wide_with_tax %>% 
  group_by(phylum) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
  ggplot(aes(x = FA, 
             y = `Relative Abundance`,
             color = phylum,
             fill = phylum)) +
  geom_col() +
  facet_wrap(vars(phylum)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")
```

## Acidobacteria

```{r}
fatty_acids_wide_with_tax %>% 
  group_by(phylum) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
  filter(phylum == "Acidobacteria") %>% 
  ggplot(aes(x = FA, 
             y = `Relative Abundance`,
             color = phylum,
             fill = phylum)) +
  geom_col() +
  facet_wrap(vars(phylum)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")
```

## Proteobacteria

```{r}
FA_w_turnover %>% 
  filter(phylum == "Proteobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Proteobacteria") +
  theme_bw()
```

## Actinobacteria
```{r}
FA_w_turnover %>% 
  filter(phylum == "Actinobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Actinobacteria") +
  theme_bw()
```

## Acidobacteria

```{r}
FA_w_turnover %>% 
  filter(phylum == "Acidobacteria") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Acidobacteria") +
  theme_bw()
```

```{r}
FA_w_turnover %>% 
  filter(phylum == "Firmicutes") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Firmicutes") +
  theme_bw()
```

```{r}
FA_w_turnover %>% 
  filter(phylum == "Bacteroidetes") %>% 
  ggplot(aes(y = u_d, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Bacteroidetes") +
  theme_bw()

```

```{r}
FA_w_turnover %>% 
  filter(phylum == "Actinobacteria") %>% 
  ggplot(aes(y = rel_area_FID, 
             x = `Relative Abundance`,
             fill = u_d,
             color = u_d)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm",
              size = 0.5) +
  geom_label_repel(aes(label = FA),
                   color = "black",
                   fill = "white") +
  labs(title = "Actinobacteria") +
  theme_bw()
```

### 2021-10-28 scripts/plotting_functions.R
initial data analysis

@@ -1,0 +1,80 @@
+# Plotting helper functions -------
+
+#' Figure Theme
+#' 
+#' Theme for figures with frequently used formatting instructions.
+#' @param legend whether to show the legend
+#' @param grid whether to show the grid
+#' @param plot_margin margins for c(top, right, bottom, left) in mm
+#' @param text_size font size for all text on plot 
+#' @param axis_text_size font size for the axes' text (define only if different from text_size)
+#' @param axis_x_rotated whether to rotate the x axis labels
+theme_figure <- function(legend = TRUE, grid = TRUE, plot_margin = c(1, 1, 1, 1), 
+                         text_size = 20, axis_text_size = NULL, axis_x_rotate = 0) {
+  the_theme <- theme_bw() + 
+    theme(text = element_text(size = text_size),
+          plot.background = element_blank(), panel.background = element_blank(),
+          panel.border = element_rect(color="black", size=1), 
+          strip.background = element_rect(color="black", linetype = 1),
+          plot.margin = unit(plot_margin, "mm")
+    )
+  # adjust grid
+  if(!grid)
+    the_theme <- the_theme + theme(panel.grid = element_blank())
+  else
+    the_theme <- the_theme + theme(panel.grid.minor = element_blank())
+  # adjust legend
+  if (!legend)
+    the_theme <- the_theme + theme(legend.position = "none")
+  # overwrite axis text size if provided
+  if (!is.null(axis_text_size))
+    the_theme <- the_theme + 
+      theme(axis.text = element_text(size = axis_text_size)) 
+  # axis rotation
+  if (axis_x_rotate != 0) {
+    the_theme <- the_theme + 
+      theme(axis.text.x = element_text(angle = axis_x_rotate, vjust = 0.5, hjust = 1))
+  }
+  return(the_theme)
+}
+
+#' Latex labeller
+#' 
+#' Latex labeller for ggplot that will interpret latex equations correctly (i.e. anything between $$). 
+#' Works for both the \code{labels} parameter of discrete ggplot2 scales as well as the \code{labeller} of facets.
+latex_labeller <- function(labels, ...) {
+  
+  require("dplyr")
+  require("tidyr")
+  require("purrr")
+  require("latex2exp")
+  
+  # figure out if we're in a scale or facet labeller
+  facet_labels <- is(labels, "data.frame")
[…]

### 2021-11-03 qSIP_calculations.Rmd
added save workspace image
added package info

@@
 # Libraries
-library(tidyverse) # general data wrangling and plotting
-library(forcats) # handling factors
-library(isoreader) # reading the raw data files
-library(isoprocessor) # processing the data
-library(isotopia) # isotope utilities
-library(readxl) # reading excel docs
-library(ggsci) # some nice color palettes
-library(ggborderline) # nice looking ggplot lines
-library(ggrepel) # nice looking ggplot labels
-library(latex2exp) # latex parsing
-library(ggdist) # ggplot distribution geoms
-library(ggsignif) # ggplot significance markers
-library(ggridges) # ggplot ridgeline geoms
+library(tidyverse)    # CRAN v1.3.1
+library(forcats)      # CRAN v0.5.1 
+library(isoreader)    # [::NA/NA] v1.3.0 # CRAN v1.3.0
+library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7
+library(isotopia)     # [github::isoverse/isotopia] v0.5.8 
+library(readxl)       # CRAN v1.3.1 
+library(ggsci)        # CRAN v2.9 
+library(ggborderline) # [github::wurli/ggborderline] v0.1.0
+library(ggrepel)      # CRAN v0.9.1 
+library(latex2exp)    # CRAN v0.5.0
+library(ggdist)       # CRAN v3.0.0 
+library(ggsignif)     # CRAN v0.6.2
+library(ggridges)     # CRAN v0.5.3
+library(cowplot)      # CRAN v1.1.1
 
@@
 
+## Weighted turnover over time course
+
+```{r}
+# Take peaks_mapped_summarized (which is the dataframe of IRMS values averaged across
+# experimental and analytical replicates).
+# Determine the weighted at2H, which is the sum of at2H values times relative area 
+# divided by total area.
+
+weighted_time_course <- peaks_mapped_summarized %>% 
+  group_by(terrain, inc_time_d) %>%
+  summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
+
+peaks_mapped_summarized <- left_join(peaks_mapped_summarized, 
+                                     weighted_time_course,
+                                     by = c("terrain", "inc_time_d"))
+
+```
+
 ## Calculate turnover time
@@
 
-# Plots
+# Save Workspace Image
+Handoff to paper plotting script
+
+```{r}
+# This will take a minute. 
+# Uncomment below to save the workspace image.
+# save.image(file = "cache/qSIP_calculations.RData")
+```
+
+# Practice Plotting
 
@@
   geom_smooth(se = FALSE,
-              method = "loess") +
+              method = "lm") +
   #geom_borderline() +
@@
 ```{r}
-gen_calc_data_summarized %>% 
-  mutate(compound = fct_reorder(compound, rt)) %>% 
+peaks_mapped_summarized %>% 
+  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
   ggplot(aes(x = inc_time_d,
              y = at2H,
-             color = compound)) +
-  geom_borderline() +
+             group = compound)) +
+  geom_borderline(color = "gray") +
   geom_point() +
-  facet_wrap(vars(terrain)) +
+  geom_line(aes(x = inc_time_d,
+                y = at2H_weighted,
+                color = terrain),
+            size = .8) +
+  geom_point(aes(x = inc_time_d,
+                y = at2H_weighted, 
+                color = terrain),
+             shape = 18,
+             size = 3) +
+  geom_label_repel(data = peaks_mapped_summarized %>% filter(inc_time_d == 7),
+                   nudge_x = 2,
+                   nudge_y = 0.005,
+                   size = 2.5,
+                   aes(label = compound)) +
+  geom_label_repel(data = weighted_time_course %>% filter(inc_time_d == 3),
+                   aes(x = inc_time_d,
+                       y = at2H_weighted,
+                       group = terrain,
+                       color = terrain),
+                   label = "Weighted Mean",
+                   nudge_y = -.01,
+                   nudge_x = 1,
+                   size = 2.5) +
+  facet_wrap(vars(terrain), nrow = 1) +
   scale_x_continuous(breaks = c(0, 3, 7)) +
-  scale_color_viridis_d() +
-  theme_bw() +
+  scale_color_npg() +
+  coord_cartesian(xlim = c(0, 10), clip = FALSE) +
   labs(x = "Incubation Time (Days)",
-       y = "Mean %D")
+       y = TeX("% $^2H$"),
+       color = "Soil Type") +
+  theme_classic() +
+  theme(legend.position = "none",
+        strip.background = element_blank())
+
 ```

### 2021-11-08 qSIP_calculations.Rmd
added weighted turnover calculation

@@
                   FL = f_label, # 2F of label (at%)
-                  t = d_t), # change in time
+                  t = d_t), # change in time (d)
     # "negative" turnovers are artifacts of noise and should be zero
@@
     # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
+    # calculate weighted turnover rates
+    u_d_weighted = gencalc(a = 0.5, # Assimilation efficiency
+                           FT = at2H_weighted, # weighted 2F (at%)
+                           F0 = f_start, # 2F at t0 (at%)
+                           FL = f_label, # 2F of label (at%)
+                           t = d_t # change in time (d)
+                           ),
+    # "negative" turnovers are artifacts of noise and should be zero
+     u_d_weighted = if_else(u_d_weighted < 0, 0, u_d_weighted),
+    # calculate generation time, converting negatives to zero
+     gen_d_weighted = if_else(u_d_weighted < 0, 0, log(2) / u_d_weighted),
   ) %>%
@@
 # Uncomment below to save the workspace image.
-# save.image(file = "cache/qSIP_calculations.RData")
+save.image(file = "cache/qSIP_calculations.RData")
 ```

### 2021-11-08 qSIP_calculations.Rmd
added weighted turnover

--- 2021-11-03 qSIP_calculations.Rmd
@@
 
-# Load packages
+# Load packages and functions
 
@@
 
-# Turnover Calculation Function
+## Turnover Calculation Function
 
@@
     # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
   ) %>%
@@
 
+weighted_turnover_summarized <- gen_calc_data_summarized %>% 
+  group_by(terrain, inc_time_d) %>%
+  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
+
+gen_calc_data_summarized <- left_join(gen_calc_data_summarized, 
+                                     weighted_turnover_summarized,
+                                     by = c("terrain", "inc_time_d"))
+
 # gen_calc_data_summarized %>% openxlsx::write.xlsx(file.path("data", "gen_calc_data_summarized.xlsx"))

### 2021-11-09 qSIP_calculations.Rmd
filtered long chain fatty acids out of weighted mean calculations

@@
   group_by(terrain, inc_time_d, compound) %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
   summarize_if(is.numeric, mean, na.rm = TRUE)
@@
   group_by(terrain, inc_time_d) %>%
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
   summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
@@
 gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
   mutate(
@@
 gen_calc_data_summarized <- peaks_mapped_summarized %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
   mutate(
@@
   group_by(terrain, inc_time_d) %>%
-  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
+  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE),
+            gen_d_weighted = sum(gen_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
 

### 2021-11-15 qSIP_calculations.Rmd
removed practice plots moved to figure script

@@
 
-gen_calc_data_summarized <- left_join(gen_calc_data_summarized, 
+```
+
+```{r join weighted gen calc}
+gen_calc_data_summarized_weighted <- left_join(gen_calc_data_summarized, 
                                      weighted_turnover_summarized,
@@
 
-# gen_calc_data_summarized %>% openxlsx::write.xlsx(file.path("data", "gen_calc_data_summarized.xlsx"))
 ```
@@
 ```
-
-# Practice Plotting
-
-## Peak Tracer Incorporation
-```{r}
-peaks_mapped_with_zeros_analytes %>% ggplot(
-  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm") +
-  #geom_borderline() +
-  scale_color_viridis_d() +
-  theme_minimal()
-```
-
-## Chromatogram scaled by 2F
-
-```{r "shaded chromatogram", fig.width=8, fig.height=8}
-p_peaks_mapped_active <- peaks_mapped_with_zeros_analytes %>% ggplot(
-  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
-  geom_col(aes(width = rt_end - rt_start)) +
-  scale_fill_viridis_c(option = "magma") +
-  facet_wrap(~sample_id, ncol = 1) +
-  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
-  theme_classic() +
-  coord_cartesian(ylim = c(0, 1300)) +
-  labs(fill = TeX("$^2F$"),
-         x = "Retention Time (s)",
-         y = "Amplitude (mV)") +
-  theme(strip.background = element_blank())
-
-```
-
-## Compound enrichment over time
-
-```{r}
-peaks_mapped_summarized %>% 
-  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H,
-             group = compound)) +
-  geom_borderline(color = "gray") +
-  geom_point() +
-  geom_line(aes(x = inc_time_d,
-                y = at2H_weighted,
-                color = terrain),
-            size = .8) +
-  geom_point(aes(x = inc_time_d,
-                y = at2H_weighted, 
-                color = terrain),
-             shape = 18,
-             size = 3) +
-  geom_label_repel(data = peaks_mapped_summarized %>% filter(inc_time_d == 7),
-                   nudge_x = 2,
-                   nudge_y = 0.005,
-                   size = 2.5,
-                   aes(label = compound)) +
-  geom_label_repel(data = weighted_time_course %>% filter(inc_time_d == 3),
-                   aes(x = inc_time_d,
-                       y = at2H_weighted,
-                       group = terrain,
-                       color = terrain),
-                   label = "Weighted Mean",
-                   nudge_y = -.01,
-                   nudge_x = 1,
-                   size = 2.5) +
-  facet_wrap(vars(terrain), nrow = 1) +
-  scale_x_continuous(breaks = c(0, 3, 7)) +
-  scale_color_npg() +
-  coord_cartesian(xlim = c(0, 10), clip = FALSE) +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("% $^2H$"),
-       color = "Soil Type") +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank())
-
-```
-
-## Compound enrichment over time with label strength
-
-```{r}
-gen_calc_data_summarized %>% 
-  filter(compound != "i-16:0") %>% 
-  mutate(compound = fct_reorder(compound, rt)) %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H,
-             color = compound)) +
-  geom_point() +
-  geom_borderline() +
-  geom_hline(yintercept = 0.5,
-             color = "red") +
-  facet_wrap(vars(terrain)) +
-  scale_x_continuous(breaks = c(0, 3, 7)) +
-  scale_color_viridis_d() +
-  labs(x = "Incubation Time (Days)",
-       y = "Mean %D") +
-  theme_bw()
-```
-
-## Generation Time of All Points
-
-```{r}
-p_gen_time_dist <- gen_calc_data %>% 
-  filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(y = gen_d, 
-      x = inc_time_d_str, 
-      color = inc_time_d_str, 
-      fill = inc_time_d_str)) +
-  stat_slab(width = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
-  # geom_boxplot(fill = "white",
-  #              color = "black",
-  #              width = 0.1,
-  #              outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    shape = 95,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(x = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(y = "Generation time (days)",
-       x = "Incubation time",
-       title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria",
-       caption = "Soils collected from Colorado") +
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
-p_gen_time_dist
-
-#ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
-```
-
-## Generation Time, all points, not separated by inc_time
-
-```{r}
-p_gen_time_dist_all <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(y = gen_d, 
-      x = 1)) +
-  stat_slab(width = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
-  # geom_boxplot(fill = "white",
-  #              color = "black",
-  #              width = 0.1,
-  #              outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    shape = 95,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(x = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(y = "Generation time (days)",
-       title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria",
-       caption = "Soils collected from Colorado") +
-  theme(legend.position = "none",
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.x = element_blank())
-p_gen_time_dist_all
-```
-
-## Generation Time, all points, not separated, > C19 removed
-
-```{r}
-p_gen_time_dist_all_no19 <- gen_calc_data %>% 
-  filter(inc_time_d != 0,
-         chain_num < 19) %>% 
-  ggplot(
-  aes(y = gen_d, 
-      x = 1)) +
-  stat_slab(width = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
-  # geom_boxplot(fill = "white",
-  #              color = "black",
-  #              width = 0.1,
-  #              outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    shape = 95,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(x = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(y = "Generation time (days)",
-       title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria \nC20+ removed",
-       caption = "Soils collected from Colorado") +
-  theme(legend.position = "none",
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.x = element_blank())
-p_gen_time_dist_all_no19
-```
-
-## Generation time of all points, not log scale
-
-```{r}
-p_gen_time_dist_all_lin <- gen_calc_data %>% 
-  filter(inc_time_d != 0,
-         gen_d >= 0,
-         chain_num < 19) %>% 
-  ggplot(
-  aes(y = gen_d, 
-      x = 1)) +
-  stat_slab(width = 0.25, 
-            alpha = 0.7,
-            color = "black") +
-  stat_pointinterval(color = "black") +
-  # geom_boxplot(fill = "white",
-  #              color = "black",
-  #              width = 0.1,
-  #              outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    shape = 95,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(x = -.03)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(y = "Generation time (days)",
-       title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria",
-       caption = "Soils collected from Colorado") +
-  theme(legend.position = "none",
-        axis.ticks.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.title.x = element_blank())
-p_gen_time_dist_all_lin
-```
-
-## Generation Time, Broken by Terrain
-
-```{r}
-signif_comparisons <- gen_calc_data %>% pull(terrain) %>% unique()
-
-p_gen_time_terrain <- gen_calc_data %>% 
-  filter(inc_time_d != 0,
-         chain_num < 19) %>% 
-  ggplot(
-  aes(y = gen_d, 
-      x = terrain,
-      color = terrain,
-      fill = terrain)) +
-  stat_slab(width = 0.25, 
-            alpha = 0.7,
-            color = "black") +
-  stat_pointinterval(color = "black") +
-  # geom_boxplot(fill = "white",
-  #              color = "black",
-  #              width = 0.1,
-  #              outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    shape = 95,
-    size = 3,
-    alpha = 0.5,
-    position = position_nudge(x = -.07)) +
-  geom_signif(comparisons = list(signif_comparisons),
-              map_signif_level = TRUE) +
-  scale_y_log10(breaks = c(1, 10, 100)) +
-  annotation_logticks(sides = "l") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_classic() +
-  labs(y = "Generation time (days)",
-       title = "Generation times of soil bacteria",
-       subtitle = "Lipid-specific generation times of bacteria \nC20+ omitted") +
-  theme(axis.ticks.y = element_blank(),
-        axis.text.x = element_text(angle = 45, hjust = 1))
-p_gen_time_terrain
-```
-
-## Turnover time by compound
-
-```{r}
-gen_calc_data_summarized %>% 
-  filter(inc_time_d != 0, compound != "i-16:0") %>%
-  group_by(compound) %>% 
-  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
-  mutate(compound = fct_reorder(compound, u_d)) %>% 
-  ggplot(aes(x = compound,
-             y = u_d,
-             fill = u_d)) +
-  geom_col(position = "dodge") +
-  scale_fill_viridis_c(option = "plasma") +
-  labs(x = "Compound",
-       y = "Mean Turnover time (d^-1)",
-       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
-  theme_bw() +
-  theme(
-    axis.text.x = element_text(angle = 90, 
-                               hjust = 1)
-  )
-```
-
-## Turnover Time, Broken By Terrain
-
-```{r}
-p_turnover_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
-  ggplot(
-  aes(x = inc_time_d_str, 
-      y = u_d, 
-      color = terrain, 
-      fill = terrain)) +
-  #stat_slab(height = 0.3, alpha = 0.7) +
-  stat_pointinterval(color = "black") +
-  # geom_point(
-  #   color = "black",
-  #   #shape = 124,
-  #   size = 1,
-  #   alpha = 0.5,
-  #   position = position_nudge(x = -.05)) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  facet_wrap(~terrain, nrow = 1) +
-  scale_y_log10() +
-  annotation_logticks(sides = "a") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_bw() +
-  labs(x = "Incubation Time",
-       y = "Turnover Time (d^-1)",
-       title = "Generation times of soil bacteria across terrain")
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
-p_turnover_terrain
-```
-
-## 7 Day Turnover Times By Terrain
-
-```{r}
-p_turnover_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
-  ggplot(
-  aes(x = terrain, 
-      y = u_d)) +
-  #stat_slab(height = 0.3, alpha = 0.7) +
-  #stat_pointinterval(color = "black") +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    #shape = 124,
-    size = 1,
-    alpha = 0.5) +
-  geom_signif(comparisons = list(signif_comparisons),
-              map_signif_level = TRUE) +
-  scale_y_log10() +
-  annotation_logticks(sides = "a") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_bw() +
-  labs(x = "Terrain",
-       y = "Turnover time (d^-1)",
-       title = "Generation times of soil bacteria across terrain") +
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
-p_turnover_terrain_7d
-```
-
-## 7 Day Generation Times across terrain
-
-```{r}
-p_gen_time_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
-  ggplot(
-  aes(x = terrain, 
-      y = gen_d)) +
-  #stat_slab(height = 0.3, alpha = 0.7) +
-  #stat_pointinterval(color = "black") +
-  geom_boxplot(outlier.shape = NA) +
-  geom_point(
-    color = "black",
-    #shape = 124,
-    size = 1,
-    alpha = 0.5) +
-  # geom_text_repel(aes(label = compound), 
-  #                 color = "black", 
-  #                 nudge_y = -0.3, 
-  #                 size = 3) +
-  scale_y_log10() +
-  annotation_logticks(sides = "a") +
-  scale_fill_npg() +
-  scale_color_npg() +
-  theme_bw() +
-  labs(x = "Terrain",
-       y = "Turnover time (d^-1)",
-       title = "Generation times of soil bacteria across terrain") +
-  theme(legend.position = "none",
-        axis.ticks.y = element_blank())
-p_gen_time_terrain_7d
-```
-
-## Turnover time versus lipid relative abundance
-
-```{r}
-
-gen_calc_data %>% 
-  filter(inc_time_d != 0) %>% 
-  ggplot(aes(x = rel_area_FID,
-             y = u_d)) +
-  geom_point(aes(color = chain_fctr)) +
-  geom_smooth(method = "lm",
-              se = FALSE) +
-  scale_color_viridis_d() +
-  facet_wrap(~terrain) +
-  labs(x = "Relative Area (GC-FID)",
-       y = "Turnover (d^-1)",
-       color = "Compound class") +
-  theme_bw()
-
-```
-
-## Compound-Specific Enrichment
-
-```{r}
-gen_calc_data %>% 
-  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
-  ggplot(aes(x = at2H,
-             y = compound,
-             fill = stat(x))) +
-  geom_density_ridges_gradient(scale = 3) +
-  # Vline showing enrichment strength
-  # geom_vline(xintercept = 0.5,
-  #            color = "red") +
-  facet_wrap(vars(inc_time_d_str), ncol = 1) +
-  scale_fill_viridis_c(option = "C") +
-  labs(fill = "% D",
-       x = "% D",
-       y = "Compound") +
-  theme_ridges() +
-  theme(axis.text.y = element_text(size = 5),
-        legend.position = "right",
-        legend.key.width = unit(0.2, "line"),
-        legend.text = element_text(size = 10))
-```
-
-## Compound specific turnover
-```{r}
-gen_calc_data %>% 
-  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
-  ggplot(aes(x = u_d,
-             y = compound,
-             fill = stat(x))) +
-  geom_density_ridges_gradient() +
-  # Vline showing enrichment strength
-  facet_wrap(vars(inc_time_d_str), ncol = 1) +
-  scale_fill_viridis_c(option = "C") +
-  labs(fill = "µ (d^-1)",
-       x = "µ (d^-1)",
-       y = "Compound") +
-  theme_minimal()
-```
-
-## Mean Turnover by Terrain
-
-```{r}
-gen_calc_data_summarized %>% 
-  group_by(inc_time_d, terrain) %>% 
-  summarize(u_d_mn = mean(u_d),
-            u_d_max = max(u_d),
-            u_d_min = min(u_d),
-            gen_d_mn = mean(gen_d),
-            gen_d_max = max(gen_d),
-            gen_d_min = min(gen_d)) %>% 
-  ggplot(aes(x = terrain, 
-             y = u_d_mn,
-             color = as.character(inc_time_d))) +
-  geom_path(color = "black") +
-  geom_point() +
-  coord_cartesian(ylim = c(0, 0.05)) +
-  labs(x = "Terrain",
-       y = "Mean Turnover (d^-1)",
-       color = "Incubation Time") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-```
-
-## Mean Turnover Aggregated
-
-```{r}
-gen_calc_data_summarized %>% 
-  # Calculate means, by terrain
-  group_by(inc_time_d, terrain) %>% 
-  summarize(u_d_mn = mean(u_d),
-            u_d_max = max(u_d),
-            u_d_min = min(u_d),
-            gen_d_mn = mean(gen_d),
-            gen_d_max = max(gen_d),
-            gen_d_min = min(gen_d)) %>% 
-  # Calculate mean of means
-  group_by(inc_time_d) %>% 
-  summarize(u_d_mn_ag = mean(u_d_mn),
-            u_d_max_ag = max(u_d_mn),
-            u_d_min_ag = min(u_d_mn),
-            gen_d_mn_ag = mean(gen_d_mn),
-            gen_d_max_ag = max(gen_d_mn),
-            gen_d_min_ag = min(gen_d_mn)) %>% 
-  ggplot(aes(x = 1, 
-             y = u_d_mn_ag,
-             color = as.character(inc_time_d))) +
-  geom_path(color = "black") +
-  geom_point() +
-  coord_cartesian(ylim = c(0, 0.05)) +
-  labs(x = "Terrain",
-       y = "Mean Turnover (d^-1)",
-       color = "Incubation Time") +
-  theme_minimal() +
-  theme(axis.text.x = element_blank(),
-        axis.title.x = element_blank())
-
-```
-
-## Literature Rates of Cell Turnover
-
-```{r}
-# Import lit search data
-lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))
-
-lit_turnover <- lit_turnover %>% 
-  # Arrange by turnover time
-  arrange(u_d_mn) %>% 
-  # Reassign n values
-  mutate(n = seq(from = 1, to = nrow(lit_turnover)))
-
-# Our summarized data
-gen_calc_mini <- gen_calc_data_summarized %>% 
-  # Calculate mean per terrain per inc time
-  group_by(inc_time_d, terrain) %>% 
-  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
-            u_d_max = max(u_d),
-            u_d_min = min(u_d)) %>%
-  # Calculate mean of means (combine inc_times)
-  group_by(terrain) %>% 
-  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
-            u_d_max = max(u_d_mn, na.rm = TRUE),
-            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
-  # Rename to match `lit_turnover` tibble
-  rename(soil_type = terrain) %>% 
-  arrange(u_d_mn) %>% 
-  mutate(method = "2H Lipid SIP",
-         n = c(17, 18, 19),
-    soil_type = case_when(
-      soil_type == "Niwot Ridge Tundra" ~ "tundra",
-      soil_type == "Gordon Gulch Conifer Forest" ~ "conifer forest",
-      soil_type == "Marshall Mesa Grassland" ~ "grassland")
-  )
-
-# Add in our data! ^_^
-lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)
-
-lit_turnover_w_ours <- lit_turnover_w_ours %>% 
-  mutate(
-    source = case_when(
-      method == "2H Lipid SIP" ~ "This study",
-      TRUE ~ "Literature values"
-  ))
-
-# By terrain
-
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = soil_type)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  scale_color_npg() +
-  geom_label(label = "This study",
-            x = 18,
-            y = 0.13,
-            color = "black") +
-  geom_label(label = "Literature values",
-            x = 9,
-            y = 0.6,
-            color = "black") +
-  #scale_y_log10() +
-  #annotation_logticks(sides = "l") +
-  coord_cartesian(
-    xlim = c(0, 20),
-    ylim = c(0, 0.80), 
-    expand = FALSE) +
-  labs(y = "Mean Turnover Time (d^-1)",
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        legend.position = "bottom")
-
-## With log scale
-
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = soil_type)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  scale_color_npg() +
-  geom_label(label = "This study",
-            x = 18,
-            y = 0.10,
-            color = "black") +
-  geom_label(label = "Literature values",
-            x = 9,
-            y = 0.35,
-            color = "black") +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  labs(y = "Mean Turnover Time (d^-1)",
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        legend.position = "bottom")
-
-```
-
-## Literature Rates of Cell Turnover by Method
-```{r}
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = method)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  geom_text_repel(aes(label = method),
-                  color = "black",
-                  size = 2,
-                  segment.color = "red",
-                  nudge_y = 0.2,
-                  segment.curvature = -0.1,
-                  segment.angle = -20,
-                  segment.ncp = 3,
-                  segment.size = 0.1) +
-  scale_color_viridis_d() +
-  scale_y_log10(breaks = c(0.01, 0.05, 0.1, 0.5)) +
-  annotation_logticks(sides = "l") +
-  labs(y = "Mean Turnover Time (d^-1)",
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        )
-```

### 2022-01-07 soil_report.Rmd
cleaned up soil report

@@
 ```{r, message=FALSE}
-soil_data <- read_csv("soil_report_06302021.csv")
+soil_data <- read_csv("data/soil_data/soil_report_06302021.csv")
+
+soil_data <- soil_data %>% 
+  mutate(
+    soil_type = case_when(
+      str_detect(`Sample ID`, "grassland") ~ "Grassland",
+      str_detect(`Sample ID`, "tundra") ~ "Tundra",
+      str_detect(`Sample ID`, "confier") ~ "Conifer Forest",
+      str_detect(`Sample ID`, "meadow_0cm") ~ "Meadow 0cm",
+      str_detect(`Sample ID`, "meadow_30cm") ~ "Meadow 30cm"
+    )
+  )
 
@@
 soil_values <- soil_data %>% 
-  select(!c(`Excess Lime`, `Texture Estimate`))
+  select(!c(`Excess Lime`, `Texture Estimate`, `Sample ID`))
 
@@
   select(!`Sample Depth (cm)`) %>% 
-  pivot_longer(!`Sample ID`, names_to = "Measurement", values_to = "Value")
+  pivot_longer(!soil_type, names_to = "Measurement", values_to = "Value")
 
@@
 p_soil_values_long <- soil_values_long %>% 
-  ggplot(aes(x = `Sample ID`, y = `Value`, fill = `Sample ID`)) +
+  filter(soil_type %in% c("Tundra", "Grassland", "Conifer Forest")) %>% 
+  ggplot(aes(x = soil_type, y = `Value`, fill = soil_type)) +
   geom_col() +
   facet_wrap(~`Measurement`, scales = "free_y") +
-  scale_fill_aaas() +
+  scale_fill_futurama() +
   theme_classic() +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+p_soil_values_long
 
-ggsave("soil_report_plot.png", plot = p_soil_values_long, height = 10, width = 15)
+#ggsave("soil_report_plot.png", plot = p_soil_values_long, height = 10, width = 15)
 ```

### 2022-01-08 qSIP_calculations.Rmd
compound abundance

@@
 source(file.path("libs", "chromleon.R"))
-`%nin%` = Negate(`%in%`)
+`%nin%` = Negate(`%in%`) # "Not In" function
+var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
 ```
@@
   # Important to specify what data comes from FID!
-  rename("sample_id" = sample,
+  rename(
+    "sample_id" = sample,
     "compound" = `Peak Name`,
@@
   # Generate summary stats
-  summarize(rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
+  summarize(
+    rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
     rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
@@
   # Add some basic metadata
-  mutate(inc_time = case_when(
+  mutate(
+  inc_time = case_when(
     str_detect(sample_rep, "...0") ~ 0,
@@
 peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
-  group_by(terrain, inc_time_d, compound) %>% 
+  group_by(
+    terrain, 
+    inc_time_d, 
+    compound
+  ) %>% 
   # FILTER OUT NON BACTERIAL COMPOUNDS
   filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
-  summarize_if(is.numeric, mean, na.rm = TRUE)
+  summarize_if(
+    is.numeric, 
+    mean, 
+    na.rm = TRUE
+  )
 ```
@@
 weighted_time_course <- peaks_mapped_summarized %>% 
-  group_by(terrain, inc_time_d) %>%
+  group_by(
+    terrain, 
+    inc_time_d
+  ) %>%
   # FILTER OUT NON BACTERIAL COMPOUNDS
   filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
-  summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
+  summarize(
+    at2H_weighted = 
+      sum(at2H * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE)
+  )
 
@@
 weighted_turnover_summarized <- gen_calc_data_summarized %>% 
-  group_by(terrain, inc_time_d) %>%
-  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE),
-            gen_d_weighted = sum(gen_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
+  group_by(
+    terrain, 
+    inc_time_d
+  ) %>%
+  summarize(
+    u_d_weighted = 
+      sum(u_d * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    gen_d_weighted = 
+      sum(gen_d * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE))
 
@@
 
-```{r join weighted gen calc}
-gen_calc_data_summarized_weighted <- left_join(gen_calc_data_summarized, 
+```{r join_weighted_gen_calc}
+gen_calc_data_summarized_weighted <- left_join(
+  gen_calc_data_summarized, 
   weighted_turnover_summarized,
-                                     by = c("terrain", "inc_time_d"))
+  by = c("terrain", "inc_time_d")
+  )
 
+```
+
+# Compound abundance
+
+```{r compound_abundance}
+# Compute the instrument response for each run:
+# Response = µg per unit area using 10µg of PAIBE as quantification STD
+FID_results_PAIBE_ug <- FID_results %>% 
+  select(
+    sample_id, 
+    file,
+    compound,
+    area_FID, 
+    rel_area_FID) %>% 
+  filter(compound == "PAIBE") %>% 
+  mutate(
+    PAIBE_area = area_FID,
+    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
+    # Find instrument response as PAIBE mass per FID area
+    ug_per_area = PAIBE_ug_inj / PAIBE_area,
+    # Check that the inferred mass is the same as known mass
+    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
+  ) %>%
+  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
+
+```
+
+## Calculate mass of analyte injected into GC-FID
+
+```{r response}
+# Put the response info back into the abundance data frame:
+FID_results_abundance <- 
+  left_join(
+    FID_results, 
+    FID_results_PAIBE_ug, 
+    by = "file"
+    ) %>%
+  # Calculate the quantity of analyte injected based off of area and 
+  # instrument response
+  mutate(
+    compound_ug_inj = area_FID * ug_per_area,
+    inj_vol_ul = 1, # GC-FID injection volume µL
+    susp_vol_ul = 100, # suspension volume µL
+    # The mass of analyte in vial is the concentration of analyte (mass 
+    # seen per unit volume injected) times the suspension volume.
+    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
+  )
+
+```
+
+## Calculate fractional derivatization efficiency (21-PC)
+```{r 21_PC}
+FID_results_abundance_21 <- FID_results_abundance %>% 
+  filter(compound == "21:0 (STD)") %>% 
+  # Derivatization efficiency is the amount of standard observed divided by 
+  # the amount of standard added (21:0 PC = 10µg)
+  mutate(
+    STD21_ug = 10,
+    deriv_efficiency = compound_ug_vial / STD21_ug
+  ) %>% 
+  select(file, STD21_ug, deriv_efficiency)
+
+# Add deriv efficiency back into results data frame
+FID_results_abundance <- 
+  left_join(
+    FID_results_abundance, 
+    FID_results_abundance_21, 
+    by = "file"
+  ) %>% 
+  # Calculate mass of fatty acids in extraction mixture as
+  # compounds present as FAMEs multiplied by derivatization efficiency
+  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
+```
+
+## Calculate extraction efficiency (23-PC)
+
+```{r 23_PC}
+FID_results_abundance_23 <- FID_results_abundance %>% 
+  filter(compound == "23:0 (STD)") %>% 
+  # Lipid Recovery Efficiency is the amount of initial standard 
+  # observed divided by the amount of standard added (23:0 PC = 100ug)
+  mutate(
+    STD23_ug = 100,
+    extr_efficiency = compound_ug_vial / STD23_ug
+  ) %>% 
+  select(file, STD23_ug, extr_efficiency)
+
+# Add extr efficiency back into results data frame
+FID_results_abundance <- 
+  left_join(
+    FID_results_abundance,
+    FID_results_abundance_23,
+    by = "file"
+  ) %>% 
+  mutate(
+    # Calculate amount of analyte in soil sample
+    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
+    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
+    soil_mass_g = 3,
+    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
+  )
+```
+
+## Remove standards from soil abundances
+
+```{r}
+# Remove standards from soil abundances
+
+FID_results_abundance_no_stds <- FID_results_abundance %>% 
+  filter(
+    compound %nin% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
+    str_detect(sample_id, "FAME", negate = TRUE),
+    str_detect(sample_id, "BAME", negate = TRUE)
+  )
+```
+
+## Select only samples that are included in analysis
+
+```{r}
+# Remove meadow samples and Ag-ion fractions
+FID_results_abundance_reported <- FID_results_abundance_no_stds %>% 
+  filter(
+    str_detect(sample_id, "m0", negate = TRUE), # remove meadow samples
+    str_detect(sample_id, "m3", negate = TRUE), # remove meadow 30cm samples
+    str_detect(sample_id, "t0t", negate = TRUE) # remove amended tundra samples
+  )
+
+# Uncomment to view included samples:
+# FID_results_abundance_reported %>% select(sample_id) %>% unique() %>% view()
 ```
@@
 
-```{r}
+```{r save_workspace_image}
 # This will take a minute. 
@@
 ```
+
+# Save output tables
+
+```{r save_output_tables}
+# Save gen_calc_data
+# Uncomment below to save output files
+# write_csv(gen_calc_data, file = "data_output/gen_calc_data.csv")
+# write_csv(gen_calc_data_summarized, file = "data_output/gen_calc_data_summarized.csv")
+# write_csv(gen_calc_data_summarized_weighted, file = "data_output/gen_calc_data_summarized_weighted.csv")
+```

### 2022-01-11 qSIP_calculations.Rmd
join compound abundance with gencalc data

@@
 ```{r}
-root <- file.path("data", "gc_fid_data_2020")
+root <- file.path("data", "gc_fid_data_2021")
 file_list = list.files(path = root)
@@
 
-### Unnest FID integration details
+### Unnest FID integration details and clean
 
@@
     "amount_FID" = `Amount`
+         ) %>% 
+  # Clean up notation discrepencies
+  mutate(
+    compound = 
+      case_when(
+        str_detect(compound, "18:2 trans 9, 12") ~ "18:2 9, 12",
+        str_detect(compound, "18:2 trans 9,12") ~ "18:2 9, 12",
+        str_detect(compound, "18:2 9,12") ~ "18:2 9, 12",
+        str_detect(compound, "16:1 cis-9") ~ "16:1 cis 9",
+        str_detect(compound, "16:1 trans-9") ~ "16:1 trans 9",
+        str_detect(compound, "18:1 cis-9") ~ "18:1 cis 9",
+        str_detect(compound, "18:1 trans-9") ~ "18:1 trans 9",
+        str_detect(compound, "21:0") ~ "21:0 (STD)",
+        str_detect(compound, "23:0") ~ "23:0 (STD)",
+        TRUE ~ compound
+      )
+  )
+```
+
+# Compound abundance
+
+```{r compound_abundance}
+# Compute the instrument response for each run:
+# Response = µg per unit area using 10µg of PAIBE as quantification STD
+FID_results_PAIBE_ug <- FID_results %>% 
+  select(
+    sample_id, 
+    file,
+    compound,
+    area_FID, 
+    rel_area_FID) %>% 
+  filter(compound == "PAIBE") %>% 
+  mutate(
+    PAIBE_area = area_FID,
+    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
+    # Find instrument response as PAIBE mass per FID area
+    ug_per_area = PAIBE_ug_inj / PAIBE_area,
+    # Check that the inferred mass is the same as known mass
+    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
+  ) %>%
+  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
+
+```
+
+## Calculate mass of analyte injected into GC-FID
+
+```{r response}
+# Put the response info back into the abundance data frame:
+FID_results_abundance <- 
+  left_join(
+    FID_results, 
+    FID_results_PAIBE_ug, 
+    by = "file"
+    ) %>%
+  # Calculate the quantity of analyte injected based off of area and 
+  # instrument response
+  mutate(
+    compound_ug_inj = area_FID * ug_per_area,
+    inj_vol_ul = 1, # GC-FID injection volume µL
+    susp_vol_ul = 100, # suspension volume µL
+    # The mass of analyte in vial is the concentration of analyte (mass 
+    # seen per unit volume injected) times the suspension volume.
+    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
+  )
+
+```
+
+## Calculate fractional derivatization efficiency (21-PC)
+```{r 21_PC}
+FID_results_abundance_21 <- FID_results_abundance %>% 
+  filter(compound == "21:0 (STD)") %>% 
+  # Derivatization efficiency is the amount of standard observed divided by 
+  # the amount of standard added (21:0 PC = 10µg)
+  mutate(
+    STD21_ug = 10,
+    deriv_efficiency = compound_ug_vial / STD21_ug
+  ) %>% 
+  select(file, STD21_ug, deriv_efficiency)
+
+# Add deriv efficiency back into results data frame
+FID_results_abundance <- 
+  left_join(
+    FID_results_abundance, 
+    FID_results_abundance_21, 
+    by = "file"
+  ) %>% 
+  # Calculate mass of fatty acids in extraction mixture as
+  # compounds present as FAMEs multiplied by derivatization efficiency
+  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
+```
+
+## Calculate extraction efficiency (23-PC)
+
+```{r 23_PC}
+FID_results_abundance_23 <- FID_results_abundance %>% 
+  filter(compound == "23:0 (STD)") %>% 
+  # Lipid Recovery Efficiency is the amount of initial standard 
+  # observed divided by the amount of standard added (23:0 PC = 100ug)
+  mutate(
+    STD23_ug = 100,
+    extr_efficiency = compound_ug_vial / STD23_ug
+  ) %>% 
+  select(file, STD23_ug, extr_efficiency)
+
+# Add extr efficiency back into results data frame
+FID_results_abundance <- 
+  left_join(
+    FID_results_abundance,
+    FID_results_abundance_23,
+    by = "file"
+  ) %>% 
+  mutate(
+    # Calculate amount of analyte in soil sample
+    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
+    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
+    soil_mass_g = 10, # 10 g of each soil were used for this study
+    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
+  )
+```
+
+## Remove standards from soil abundances
+
+```{r}
+# Remove standards from soil abundances
+
+FID_results_abundance_no_stds <- FID_results_abundance %>% 
+  filter(
+    compound %nin% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
+    str_detect(sample_id, "FAME", negate = TRUE),
+    str_detect(sample_id, "BAME", negate = TRUE)
   )
@@
 ```{r}
+# peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
+#   left_join(FID_results, by = c("sample_id", "compound"))
+
 peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>%
-  left_join(FID_results, by = c("sample_id", "compound"))
+  left_join(
+    FID_results_abundance_no_stds, 
+    by = c("sample_id", "compound")
+  )
 ```
@@
 
-# Compound abundance
-
-```{r compound_abundance}
-# Compute the instrument response for each run:
-# Response = µg per unit area using 10µg of PAIBE as quantification STD
-FID_results_PAIBE_ug <- FID_results %>% 
-  select(
-    sample_id, 
-    file,
-    compound,
-    area_FID, 
-    rel_area_FID) %>% 
-  filter(compound == "PAIBE") %>% 
-  mutate(
-    PAIBE_area = area_FID,
-    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
-    # Find instrument response as PAIBE mass per FID area
-    ug_per_area = PAIBE_ug_inj / PAIBE_area,
-    # Check that the inferred mass is the same as known mass
-    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
-  ) %>%
-  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
-
-```
-
-## Calculate mass of analyte injected into GC-FID
-
-```{r response}
-# Put the response info back into the abundance data frame:
-FID_results_abundance <- 
-  left_join(
-    FID_results, 
-    FID_results_PAIBE_ug, 
-    by = "file"
-    ) %>%
-  # Calculate the quantity of analyte injected based off of area and 
-  # instrument response
-  mutate(
-    compound_ug_inj = area_FID * ug_per_area,
-    inj_vol_ul = 1, # GC-FID injection volume µL
-    susp_vol_ul = 100, # suspension volume µL
-    # The mass of analyte in vial is the concentration of analyte (mass 
-    # seen per unit volume injected) times the suspension volume.
-    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
-  )
-
-```
-
-## Calculate fractional derivatization efficiency (21-PC)
-```{r 21_PC}
-FID_results_abundance_21 <- FID_results_abundance %>% 
-  filter(compound == "21:0 (STD)") %>% 
-  # Derivatization efficiency is the amount of standard observed divided by 
-  # the amount of standard added (21:0 PC = 10µg)
-  mutate(
-    STD21_ug = 10,
-    deriv_efficiency = compound_ug_vial / STD21_ug
-  ) %>% 
-  select(file, STD21_ug, deriv_efficiency)
-
-# Add deriv efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance, 
-    FID_results_abundance_21, 
-    by = "file"
-  ) %>% 
-  # Calculate mass of fatty acids in extraction mixture as
-  # compounds present as FAMEs multiplied by derivatization efficiency
-  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
-```
-
-## Calculate extraction efficiency (23-PC)
-
-```{r 23_PC}
-FID_results_abundance_23 <- FID_results_abundance %>% 
-  filter(compound == "23:0 (STD)") %>% 
-  # Lipid Recovery Efficiency is the amount of initial standard 
-  # observed divided by the amount of standard added (23:0 PC = 100ug)
-  mutate(
-    STD23_ug = 100,
-    extr_efficiency = compound_ug_vial / STD23_ug
-  ) %>% 
-  select(file, STD23_ug, extr_efficiency)
-
-# Add extr efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance,
-    FID_results_abundance_23,
-    by = "file"
-  ) %>% 
-  mutate(
-    # Calculate amount of analyte in soil sample
-    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
-    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
-    soil_mass_g = 3,
-    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
-  )
-```
-
-## Remove standards from soil abundances
-
-```{r}
-# Remove standards from soil abundances
-
-FID_results_abundance_no_stds <- FID_results_abundance %>% 
-  filter(
-    compound %nin% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
-    str_detect(sample_id, "FAME", negate = TRUE),
-    str_detect(sample_id, "BAME", negate = TRUE)
-  )
-```
-
-## Select only samples that are included in analysis
-
-```{r}
-# Remove meadow samples and Ag-ion fractions
-FID_results_abundance_reported <- FID_results_abundance_no_stds %>% 
-  filter(
-    str_detect(sample_id, "m0", negate = TRUE), # remove meadow samples
-    str_detect(sample_id, "m3", negate = TRUE), # remove meadow 30cm samples
-    str_detect(sample_id, "t0t", negate = TRUE) # remove amended tundra samples
-  )
-
-# Uncomment to view included samples:
-# FID_results_abundance_reported %>% select(sample_id) %>% unique() %>% view()
-```
-
 # Save Workspace Image
@@
 # Uncomment below to save the workspace image.
-save.image(file = "cache/qSIP_calculations.RData")
+# save.image(file = "cache/qSIP_calculations.RData")
 ```

### 2022-03-15 qSIP_calculations_error_prop.Rmd
Create qSIP_calculations_error_prop.Rmd

--- 2022-01-11 qSIP_calculations.Rmd
@@
     a = 0.5, # assimilation efficiency
+    #a_se = ???
+    #f_t_se = ???
+    #f_l_se = ???
     t0 = 0, # start time
@@
                   t = d_t), # change in time
+    #u_d_se = # pull from wikipedia equation --> describe
     # "negative" turnovers are artifacts of noise and should be zero
@@
 
+## Error propagation
+
+### Define a function to iterate across assimilation efficiency values
+```{r}
+generate_assim_error_prop <- 
+  function(df_init, a_list = seq(from = 0.35, to = 0.8, by = 0.05)) {
+
+    gen_calc_temp <- df_init
+
+    for (k in a_list) {
+      gen_calc_temp <- gen_calc_temp %>% 
+      mutate(a = k) %>% 
+      bind_rows(gen_calc_temp)
+    }
+
+    return(gen_calc_temp)
+  }
+
+```
+
+```{r}
+
+gen_calc_errorprop <- peaks_mapped_with_zeros_analytes %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
+  mutate(
+    f_label = 0.5, # label is 0.5 at%
+    t0 = 0, # start time
+    f_start = at2H_mn_zero,
+    d_t = inc_time_d - t0, # change in time
+    f_t = at2H, # restate 2F at time t
+  ) %>% 
+  select(file_id,
+         compound,
+         sample_id,
+         inc_time_d_str,
+         f_label,
+         t0,
+         f_start,
+         d_t,
+         f_t,
+         terrain) %>% 
+  generate_assim_error_prop() %>% 
+  mutate(
+    u_d = gencalc(a = 0.5, # Assimilation efficiency
+                    FT = f_t, # 2F at time t (at%)
+                    F0 = f_start, # 2F at t0 (at%)
+                    FL = f_label, # 2F of label (at%)
+                    t = d_t), # change in time (d)
+      # "negative" turnovers are artifacts of noise and should be zero
+      u_d = if_else(u_d < 0, 0, u_d),
+      # calculate generation time, converting negatives to zero
+      gen_d = if_else(u_d < 0, 0, log(2) / u_d),
+    ) %>%
+    mutate(
+      chain_fctr = compound %>% 
+        str_remove("\\d+-OH") %>% 
+        parse_number() %>% 
+        abs() %>% 
+        {paste0("C", .)} %>% 
+        factor()
+        ) %>% 
+    mutate(
+      chain_num = compound %>% 
+        str_remove("\\d+-OH") %>% 
+        parse_number() %>% 
+        abs()
+    )
+
+write_csv(gen_calc_errorprop, file = "data_output/gen_calc_errorprop.csv")
+
+```
+
 # Save Workspace Image

### 2022-03-15 qSIP_calculations.Rmd
Loade F_L 2F data

@@
 # Load data
+
+## Load F_L 2F Data
+
+```{r}
+F_L_2F <- read_csv("data/Label_2H_Data/dD_cleaned.csv") %>% 
+  group_by(soil) %>% 
+  summarize(F_label_ppm_mn = mean(F_label_ppm),
+            F_label_ppm_se = sd(F_label_ppm)) %>% 
+  mutate(terrain = case_when(
+    soil == "Conifer" ~ "Gordon Gulch Conifer Forest",
+    soil == "Tundra" ~ "Niwot Ridge Tundra",
+    soil == "Grassland" ~ "Marshall Mesa Grassland"
+  ))
+```
 
@@
 
+## Correct for PAME
+
 ```{r}
-# Combine triplicate samples into one
-FID_results_trip <- FID_results %>% 
-  # Remove standards and fractions
-  filter(sample_id != "FAME37.1") %>% 
-  filter(sample_id != "TCBAME-2") %>% 
-  filter(!str_detect(sample_id, "F1")) %>% 
-  filter(!str_detect(sample_id, "F2")) %>% 
-  filter(!str_detect(sample_id, "F3")) %>% 
-  filter(!str_detect(sample_id, "cr")) %>%
-  mutate(sample_rep = str_remove(sample_id, "[xyz]")) %>% 
-  group_by(sample_rep, compound) %>%
-  # Generate summary stats
-  summarize(
-    rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
-    rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
-    rel_height_FID_max = max(rel_height_FID, na.rm=TRUE),
-    rel_height_FID_min = min(rel_height_FID, na.rm=TRUE),
-    rt_FID = mean(rt_FID, na.rm=TRUE),
-    rel_area_FID = mean(rel_area_FID, na.rm=TRUE),
-    rel_height_FID = mean(rel_height_FID, na.rm=TRUE)) %>% 
-  # Add some basic metadata
-  mutate(
-  inc_time = case_when(
-    str_detect(sample_rep, "...0") ~ 0,
-    str_detect(sample_rep, "...3") ~ 3,
-    str_detect(sample_rep, "...7") ~ 7),
-  site = case_when(
-    str_detect(sample_rep, "c") ~ "Conifer",
-    str_detect(sample_rep, "t") ~ "Tundra",
-    str_detect(sample_rep, "g") ~ "Grassland",
-    str_detect(sample_rep, "m") ~ "Meadow")
-  )
-```
+## PICK UP HERE
 
-## Remove standards from gencalcs
-```{r}
+peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
   # Don't want our standard compounds to be used for generation time calculations! x_x
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
-  filter(str_detect(compound, "STD", negate = TRUE))
+  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
+  # Determine number of carbons in alkyl chain
+  mutate(n_C = NA)
+
 ```

### 2022-03-15 qSIP_calculations.Rmd
added PAME adjustments

@@
 
-## Load IRMS Data
+## Load Compound nC and nH Data sheet
+
+```{r}
+compound_nC_nH <- read_xlsx("data/compound_nC_nH.xlsx")
+```
+
+## Load Phthalic Acid IRMS Data
+
+```{r}
+# Load PAME Iso Files
+PAME_data_path <- file.path("data", "IRMS", "PAME_data")
+ref_ratio <- get_standard("2H") %>% as.numeric()
+
+# read files
+PAME_iso_files_raw <- 
+  # path to data files
+  PAME_data_path %>% 
+  # read data files in parallel for fast read
+  iso_read_continuous_flow() %>%
+  # filter out files with read errors (e.g. from aborted analysis)
+  iso_filter_files_with_problems()
+
+# Load Peak Map
+
+PAME_peak_map <- 
+  # initial peak map:
+  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
+  # corrected peak map
+  readxl::read_excel(file.path("data", "IRMS", "PAME_peak_map.xlsx"))
+PAME_peak_map
+
+# process file information
+PAME_iso_files <- PAME_iso_files_raw %>% 
+  # rename key file info columns
+  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
+  # parse text info into numbers
+  iso_parse_file_info(number = analysis) %>% 
+  # process other file information that is specific to the naming conventions
+  # of this particular sequence
+  iso_mutate_file_info(
+    # what is the type of each analysis?
+    type = case_when(
+      str_detect(id1, "[Zz]ero")      ~ "on_off",
+      str_detect(id1, "H3")           ~ "H3_factor",
+      str_detect(id1, "F8")           ~ "F8_std",
+      str_detect(id1, "F9")           ~ "F9_std",
+      TRUE                            ~ "sample"
+    ),
+    # what was the concentration? (assuming Preparation = concentration or volume)
+    concentration = 
+      ifelse(type == "std",  
+             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
+               parse_number() %>% iso_double_with_units("ng/uL"),
+             NA),
+    # what folder are the data files in? (assuming folder = sequence)
+    folder = basename(dirname(file_path))
+  ) %>% 
+  # focus only on the relevant file info, discarding the rest
+  iso_select_file_info(
+    folder, analysis, file_datetime, id1, type, concentration
+  )
+
+# Peak Mapping
+# set peak table from vendor data table with default isodat template
+PAME_iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(PAME_iso_files) %>% 
+  # convert units from mV to V for amplitudes and area
+  iso_convert_peak_table_units(V = mV, Vs = mVs)
+
+# Create Peak Table
+PAME_peak_table <- PAME_iso_files %>%
+  iso_filter_files(str_detect(id1, "PAME")) %>% 
+  iso_filter_files(str_detect(file_id, "success")) %>% 
+  iso_set_peak_table_from_isodat_vendor_data_table() %>%
+  iso_get_peak_table() %>% 
+  mutate(Analysis = substr(file_id, 1, 7),
+         sample_id = substr(file_id, 10,14))
+
+PAME_peak_mapped <- PAME_peak_table %>%
+  iso_map_peaks(PAME_peak_map, map_id = Analysis) %>%
+  filter(!is.na(compound))
+```
+
+## Load Analyte IRMS Data
 
@@
 
+peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros_FID %>% 
+  left_join(compound_nC_nH, by = "compound") %>% 
+  mutate(`2F_Me` = NA,
+         `2F_FAME` = at2H,
+         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+
 peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 

### 2022-03-16 qSIP_calculations.Rmd
updated gencalcs to use PAME-corrected values

@@
             F_label_ppm_se = sd(F_label_ppm)) %>% 
+  mutate(F_label_mn = F_label_ppm_mn / 10000,
+         F_label_se = F_label_ppm_se / 10000) %>% 
   mutate(terrain = case_when(
@@
 
-# Create Peak Table
+# Create Peak Table and filter out non-PAME samples
 PAME_peak_table <- PAME_iso_files %>%
   iso_filter_files(str_detect(id1, "PAME")) %>% 
+  # Choose only runs that worked
   iso_filter_files(str_detect(file_id, "success")) %>% 
@@
   filter(!is.na(compound))
+
+# Summarize the mean and standard error
+PAME_summarized <- PAME_peak_mapped %>%
+  summarize(at2H_mn = mean(at2H),
+            at2H_se = sd(at2H)) %>% 
+  mutate(at2H_mn_ppm = at2H_mn * 10000,
+         at2H_se_ppm = at2H_se * 10000)
 ```
@@
 ```{r}
-## PICK UP HERE
 
@@
   left_join(compound_nC_nH, by = "compound") %>% 
-  mutate(`2F_Me` = NA,
+  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
          `2F_FAME` = at2H,
          `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+```
 
+```{r}
 peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
@@
   filter(str_detect(compound, "STD", negate = TRUE)) %>% 
-  # Determine number of carbons in alkyl chain
-  mutate(n_C = NA)
-
+  left_join(F_L_2F, by = "terrain")
 ```
@@
 
-## Calculate turnover time
+## Calculate turnover rate
 Turnover is calculated as below:
@@
   mutate(
-    f_label = 0.5, # label is 0.5 at%
+    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
     a = 0.5, # assimilation efficiency
@@
     d_t = inc_time_d - t0, # change in time
-    f_t = at2H, # restate 2F at time t
+    f_t = `2F_alk`, # use PAME-corrected 2F value
+    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
     u_d = gencalc(a = 0.5, # Assimilation efficiency
@@
                   FL = f_label, # 2F of label (at%)
-                  t = d_t), # change in time
+                  t = d_t # change in time
+                  ),
     # "negative" turnovers are artifacts of noise and should be zero

### 2022-03-16 libs/error_prop.R
uncertainty propagation

@@ -1,0 +1,30 @@
+#' Propagation of uncertainty
+#' @param a assimilation efficiency
+#' @param F_L 2F of label 
+#' @param F_T 2F of biomass at time t
+#' @param F_0 2F of biomass at time 0
+#' @param t incubation time
+#' @param sF_0 uncertainty in F_0
+#' @param sF_L uncertainty in F_L
+#' @param sF_T uncertainty in F_T
+#' @param sa uncertainty in a
+#' @return the uncertainty in µ, turnover rate 'su'
+
+sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
+  
+  # the big equation :)
+  
+  # numerator
+  num = sqrt(
+    ((a*F_L - F_T)^2 * sF_0^2) +
+    ((a*F_L - F_0)^2 * sF_T^2) +
+    (a^2 * (F_0 - F_T)^2 * sF_L^2) +
+    (F_L^2 * (F_0 - F_T)^2 * sa^2)
+  )
+  
+  # denominator
+  denom = t * (a*F_L - F_0) * (a*F_L - F_T)
+  
+  su = num/denom
+  return(su)
+}

### 2022-03-16 qSIP_calculations.Rmd
added F_0 uncertainty

@@
 
+## Separate analytes and standards
+
 ```{r}
+# Analytes
 peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
@@
   left_join(F_L_2F, by = "terrain")
+
+# Standards
+peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID %>% 
+  filter(str_detect(compound, "STD"))
+
+# 23:0 and 21:0 PC standard errors at inc time zero
+# Determines our standard error in FAME measurements at F_0
+sF_0 <- peaks_mapped_with_zeros_standards %>% 
+  # Select only 21 and 23 PC standards at initial time point
+  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
+         inc_time_d == 0) %>%
+  group_by(compound) %>% 
+  summarize(F_0_at2H_mn = mean(at2H),
+            F_0_at2H_se = sd(at2H))
+
 ```

### 2022-03-16 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

@@
             F_0_at2H_se = sd(at2H))
-
 ```

### 2022-03-16 libs/error_prop.R
made function name a verb

@@ -10,7 +10,7 @@
 #' @param sa uncertainty in a
 #' @return the uncertainty in µ, turnover rate 'su'
 
-sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
+calculate_sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
   
   # the big equation :)
   

### 2022-03-16 qSIP_calculations.Rmd
added su_d calculation

--- 2022-03-16 qSIP_calculations.Rmd
@@
 source(file.path("libs", "chromleon.R"))
+source(file.path("libs", "error_prop.R"))
 `%nin%` = Negate(`%in%`) # "Not In" function
@@
 
-## Separate analytes and standards
+## Separate analytes and standards, calculate F_0 se
 
@@
   filter(str_detect(compound, "STD", negate = TRUE)) %>% 
+  # Also don't want our yeast-extract stimulated condition in our analyte pool
+  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
   left_join(F_L_2F, by = "terrain")
@@
          inc_time_d == 0) %>%
-  group_by(compound) %>% 
+  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
+  ungroup() %>% 
   summarize(F_0_at2H_mn = mean(at2H),
@@
 
+# Add sF_0 to analyte data
+
+peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
+  mutate(F_0_at2H_se = 
+           sF_0 %>% pull(F_0_at2H_se)
+         )
 ```
@@
 gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
-  # FILTER OUT NON BACTERIAL COMPOUNDS
-  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
   mutate(
+    # Explicitly define incubation parameters:
     f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
@@
     f_t = `2F_alk`, # use PAME-corrected 2F value
+
     # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
@@
     # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
+
+    # Calculate uncertainty in turnover rate
+    su_d = calculate_sigma_mu(
+      # Mean values:
+      a = a,
+      F_L = f_label,
+      F_T = f_t,
+      F_0 = f_start,
+      t = d_t,
+      # Uncertainties:
+      sF_0 = F_0_at2H_se,
+      sF_L = F_label_se,
+      sF_T = 0,
+      sa = 0,
+    )
+
   ) %>%
@@
 ```
+
+## Combine experimental replicates
 

### 2022-03-16 libs/error_prop.R
Update error_prop.R

@@ -12,13 +12,16 @@
 
 calculate_sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
   
-  # the big equation :)
+  # the big uncertainty propagation equation :)
   
   # numerator
   num = sqrt(
     ((a*F_L - F_T)^2 * sF_0^2) +
+      
     ((a*F_L - F_0)^2 * sF_T^2) +
+      
     (a^2 * (F_0 - F_T)^2 * sF_L^2) +
+      
     (F_L^2 * (F_0 - F_T)^2 * sa^2)
   )
   

### 2022-03-23 00_LH-SIP_Data_Reduction.Rmd
separated data reduction from qSIP script

--- 2022-03-16 qSIP_calculations.Rmd
@@
 ---
-title: "2H qSIP Calculations"
+title: "00_LH-SIP_Data_Reduction"
 author: "Tristan Caro"
@@
 ---
+
+# Setup
 
@@
 
-# Load packages and functions
+## Load packages
 
@@
 library(cowplot)      # CRAN v1.1.1
+```
 
+## Load sourced functions
+These functions are found in the `libs/` directory.
+```{r}
 # Sourced Functions
-source(file.path("libs", "visualization.R"))
-source(file.path("libs", "chromleon.R"))
-source(file.path("libs", "error_prop.R"))
+source(file.path("libs", "visualization.R"))              # Visualization scripts
+source(file.path("libs", "chromeleon.R"))                 # Chromeleon Reader
+source(file.path("libs", "error_prop.R"))                 # Error Propagation
+source(file.path("libs", "calculate_turnover.R"))         # Turnover Calculator
 `%nin%` = Negate(`%in%`)                                  # "Not In" function
 var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
-```
-
-This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.
-
-## Turnover Calculation Function
-
-```{r}
-# Define a function to calculate turnover and generation time
-# ARGUMENTS:
-# FL = 0.005 # tracer strength = 0.5%
-# a = 0.5 # incorporation efficiency of 50%
-# FT = numeric # resulting isotopic enrichment
-# F0 = numeric # beginning isotopic enrichment
-
-gencalc <- function(a, FT, F0, FL, t) {
-  case_when(
-    t == 0 ~ NA_real_,
-    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
-  )
-}
-
 ```
@@
 
-## Load Analyte IRMS Data
+## Load IRMS Data
 
@@
   readxl::read_excel(file.path("data", "IRMS", "peak_maps_resolved.xlsx"))
-peak_map
 ```
@@
 ```{r}
-# process file information
+# process IRMS file information
 iso_files <- iso_files_raw %>% 
@@
 
-# # EXCLUDE C26 ALKANE STANDARD
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "C26", negate = TRUE))
-# 
-# # EXCLUDE SQUALANE STANDARD
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "squalane", negate = TRUE))
-# 
-# # EXCLUDE BLANKS AND TESTS
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "blank", negate = TRUE))
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "BLANK", negate = TRUE))
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "H2", negate = TRUE))
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "nhex", negate = TRUE))
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "cleaning", negate = TRUE))
-# 
-# # EXCLUDE BAME STANDARD
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "BAME", negate = TRUE))
-# 
-# # EXCLUDE F HEAVY
-# sample_files <- iso_filter_files(sample_files, str_detect(id1, "F_HEAVY", negate = TRUE))
-#
-
 # Include only sample files
@@
 
-### Example chromatograms
+### Example chromatogram
 
@@
 
-## Import GC-FID Data
+## Load GC-FID Data
+
 ```{r}
@@
          ) %>% 
-  # Clean up notation discrepencies
+  # Make FID notation match IRMS notation
   mutate(
@@
 # Response = µg per unit area using 10µg of PAIBE as quantification STD
+
 FID_results_PAIBE_ug <- FID_results %>% 
@@
 
-# Peak Mapping
+# IRMS Peak Mapping
 
@@
 ```{r}
-
 # Add Some Parameters
@@
 
+## Extract 3 day timepoint values
+
+```{r}
+three_day_peaks <- peaks_mapped %>%
+  filter(inc_time_d_str == "3 Days") %>%
+  group_by(t_series_id, compound) %>%
+  mutate(n_analyical_reps = n()) %>%
+  ungroup() %>%
+  # exclude ambiguous peaks
+  filter(!is_ambiguous)
+
+three_day_peaks_averaged <- three_day_peaks %>% 
+  group_by(soil_id, compound) %>% 
+  summarise(at2H_mn_three = mean(at2H),
+            d2H_mn_three = mean(d2H),
+            area2_mn_three = mean(area2))
+
+peaks_mapped_with_threes <- 
+  peaks_mapped %>%
+  left_join(
+    three_day_peaks_averaged,
+    by = c("soil_id", "compound")
+  )
+stopifnot(nrow(peaks_mapped_with_threes) == nrow(peaks_mapped))
+
+peaks_mapped_with_threes <- peaks_mapped_with_threes %>% 
+  mutate(
+    sample_id = substr(file_id, 10,14)
+    )
+```
+
 ## Join IRMS and GC-FID Data
@@
   )
+
+peaks_mapped_with_threes_FID <- peaks_mapped_with_threes %>% 
+    left_join(
+    FID_results_abundance_no_stds, 
+    by = c("sample_id", "compound")
+  )
 ```
@@
 
+# For 0 -3, 0-7 timepoints
 peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros_FID %>% 
+  left_join(compound_nC_nH, by = "compound") %>% 
+  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
+         `2F_FAME` = at2H,
+         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+
+# for 3-7 timepoints
+peaks_mapped_with_threes_FID <- peaks_mapped_with_threes_FID %>% 
   left_join(compound_nC_nH, by = "compound") %>% 
@@
 ```{r}
+# For 0-3,0-7 timepoints
 # Analytes
@@
          )
-```
 
-## Summarize Analytical and Experimental Replicates
+# For 3 -7 timepoints
+# Analytes
+peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID %>% 
+  # Don't want our standard compounds to be used for generation time calculations! x_x
+  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
+  # Also don't want our yeast-extract stimulated condition in our analyte pool
+  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
+  left_join(F_L_2F, by = "terrain")
 
-```{r}
-peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
-  group_by(
-    terrain, 
-    inc_time_d, 
-    compound
-  ) %>% 
-  # FILTER OUT NON BACTERIAL COMPOUNDS
-  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
-  summarize_if(
-    is.numeric, 
-    mean, 
-    na.rm = TRUE
-  )
-```
+# Standards
+peaks_mapped_with_threes_standards<- peaks_mapped_with_threes_FID %>% 
+  filter(str_detect(compound, "STD"))
 
-## Weighted turnover over time course
+# 23:0 and 21:0 PC standard errors at inc time zero
+# Determines our standard error in FAME measurements at F_0
+sF_0 <- peaks_mapped_with_threes_standards %>% 
+  # Select only 21 and 23 PC standards at initial time point
+  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
+         inc_time_d == 0) %>%
+  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
+  ungroup() %>% 
+  summarize(F_0_at2H_mn = mean(at2H),
+            F_0_at2H_se = sd(at2H))
 
-```{r}
-# Take peaks_mapped_summarized (which is the dataframe of IRMS values averaged across
-# experimental and analytical replicates).
-# Determine the weighted at2H, which is the sum of at2H values times relative area 
-# divided by total area.
+# Add sF_0 to analyte data
 
-weighted_time_course <- peaks_mapped_summarized %>% 
-  group_by(
-    terrain, 
-    inc_time_d
-  ) %>%
-  # FILTER OUT NON BACTERIAL COMPOUNDS
-  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
-  summarize(
-    at2H_weighted = 
-      sum(at2H * rel_area_FID, na.rm = TRUE) / 
-      sum(rel_area_FID, na.rm = TRUE)
-  )
-
-peaks_mapped_summarized <- left_join(peaks_mapped_summarized, 
-                                     weighted_time_course,
-                                     by = c("terrain", "inc_time_d"))
-
-```
-
-## Calculate turnover rate
-Turnover is calculated as below:
-
-$$
-\mu = - \frac{1}{t} \cdot (ln (\frac{F_T - a \cdot F_L}{F_0 - a \cdot F_L})
-$$
-
-```
-# R code:
-gencalc <- function(a, FT, F0, FL, t) {
-  case_when(
-    t == 0 ~ NA_real_,
-    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
-  )
-}
-
-```
-
-Generation time is related to the turnover rate as below:
-$$
-g = \frac{ln(2)}{\mu}
-$$
-
-```{r}
-gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
-  mutate(
-    # Explicitly define incubation parameters:
-    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
-    a = 0.5, # assimilation efficiency
-    t0 = 0, # start time
-    f_start = at2H_mn_zero,
-    d_t = inc_time_d - t0, # change in time
-    f_t = `2F_alk`, # use PAME-corrected 2F value
-
-    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
-    u_d = gencalc(a = 0.5, # Assimilation efficiency
-                  FT = f_t, # 2F at time t (at%)
-                  F0 = f_start, # 2F at t0 (at%)
-                  FL = f_label, # 2F of label (at%)
-                  t = d_t # change in time
-                  ),
-    # "negative" turnovers are artifacts of noise and should be zero
-    u_d = if_else(u_d < 0, 0, u_d),
-    # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
-
-    # Calculate uncertainty in turnover rate
-    su_d = calculate_sigma_mu(
-      # Mean values:
-      a = a,
-      F_L = f_label,
-      F_T = f_t,
-      F_0 = f_start,
-      t = d_t,
-      # Uncertainties:
-      sF_0 = F_0_at2H_se,
-      sF_L = F_label_se,
-      sF_T = 0,
-      sa = 0,
-    )
-
-  ) %>%
-  mutate(
-    chain_fctr = compound %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs() %>% 
-      {paste0("C", .)} %>% 
-      factor()
-      ) %>% 
-  mutate(
-    chain_num = compound %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs()
-  )
-```
-
-## Combine experimental replicates
-
-```{r}
-
-gen_calc_data_summarized <- peaks_mapped_summarized %>% 
-  # FILTER OUT NON BACTERIAL COMPOUNDS
-  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
-  mutate(
-    f_label = 0.5, # label is 0.5 at%
-    a = 0.5, # assimilation efficiency
-    t0 = 0, # start time
-    f_start = at2H_mn_zero,
-    d_t = inc_time_d - t0, # change in time
-    f_t = at2H, # restate 2F at time t
-    u_d = gencalc(a = 0.5, # Assimilation efficiency
-                  FT = f_t, # 2F at time t (at%)
-                  F0 = f_start, # 2F at t0 (at%)
-                  FL = f_label, # 2F of label (at%)
-                  t = d_t), # change in time (d)
-    # "negative" turnovers are artifacts of noise and should be zero
-    u_d = if_else(u_d < 0, 0, u_d),
-    # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
-  ) %>%
-  mutate(
-    chain_fctr = compound %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs() %>% 
-      {paste0("C", .)} %>% 
-      factor()
-      ) %>% 
-  mutate(
-    chain_num = compound %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs()
-  )
-
-weighted_turnover_summarized <- gen_calc_data_summarized %>% 
-  group_by(
-    terrain, 
-    inc_time_d
-  ) %>%
-  summarize(
-    u_d_weighted = 
-      sum(u_d * rel_area_FID, na.rm = TRUE) / 
-      sum(rel_area_FID, na.rm = TRUE),
-    gen_d_weighted = 
-      sum(gen_d * rel_area_FID, na.rm = TRUE) / 
-      sum(rel_area_FID, na.rm = TRUE))
-
-```
-
-```{r join_weighted_gen_calc}
-gen_calc_data_summarized_weighted <- left_join(
-  gen_calc_data_summarized, 
-  weighted_turnover_summarized,
-  by = c("terrain", "inc_time_d")
+peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_analytes %>% 
+  mutate(F_0_at2H_se = 
+           sF_0 %>% pull(F_0_at2H_se)
          )
@@
 ```
-
-# Save Workspace Image
-Handoff to paper plotting script
-
-```{r save_workspace_image}
-# This will take a minute. 
-# Uncomment below to save the workspace image.
-# save.image(file = "cache/qSIP_calculations.RData")
-```
-
-# Save output tables
-
-```{r save_output_tables}
-# Save gen_calc_data
-# Uncomment below to save output files
-# write_csv(gen_calc_data, file = "data_output/gen_calc_data.csv")
-# write_csv(gen_calc_data_summarized, file = "data_output/gen_calc_data_summarized.csv")
-# write_csv(gen_calc_data_summarized_weighted, file = "data_output/gen_calc_data_summarized_weighted.csv")
-```

### 2022-03-23 libs/calculate_turnover.R
turnover calculator function

@@ -1,0 +1,25 @@
+#' Turnover Rate Calculation
+#' @param a assimilation efficiency
+#' @param FL 2F of label in at%
+#' @param FT 2F of biomass at time t in at%
+#' @param F0 2F of biomass at time 0 in at%
+#' @param t incubation time
+#' @return turnover rate, µ, in units of 't'
+
+
+calculate_turnover <- function(a, FT, F0, FL, t) {
+  
+  # Calculate µ
+  mu <- case_when(
+    t == 0 ~ NA_real_,
+    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
+    )
+  
+  # Return µ if positive
+  return(
+    case_when(
+      mu >= 0 ~ mu,
+      mu < 0, ~ 0
+      )
+  )
+}

### 2022-03-23 libs/error_prop.R
error prop fn

@@ -1,8 +1,8 @@
 #' Propagation of uncertainty
 #' @param a assimilation efficiency
-#' @param F_L 2F of label 
-#' @param F_T 2F of biomass at time t
-#' @param F_0 2F of biomass at time 0
+#' @param F_L 2F of label at%
+#' @param F_T 2F of biomass at time t at%
+#' @param F_0 2F of biomass at time 0 at%
 #' @param t incubation time
 #' @param sF_0 uncertainty in F_0
 #' @param sF_L uncertainty in F_L
@@ -14,6 +14,7 @@ calculate_sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
   
   # the big uncertainty propagation equation :)
   
+ 
   # numerator
   num = sqrt(
     ((a*F_L - F_T)^2 * sF_0^2) +
@@ -24,6 +25,7 @@ calculate_sigma_mu <- function(a, F_L, F_T, F_0, t, sF_0, sF_L, sF_T, sa) {
       
     (F_L^2 * (F_0 - F_T)^2 * sa^2)
   )
+  
   
   # denominator
   denom = t * (a*F_L - F_0) * (a*F_L - F_T)

### 2022-03-23 qSIP_calculations.Rmd
testing for calculate_sigma_mu
Update qSIP_calculations.Rmd

@@
 ---
-title: "2H qSIP Calculations"
+title: "2H LH-SIP Calculations"
 author: "Tristan Caro"
@@
 ---
+
+# Current todos:
+
+> 1. Change script to calculate µ for individual replicates *then* calculate means of µ, not 
+> calculate mean enrichment --> µ. (DONE).
+
+> 2. Get standard error of F_L by taking se of each terrain F_L measurement (DONE).
+--> No error estimate on the measurement itself, took se of measurements across each terrain.
+
+> 3. Get se of F_0 by taking se of 21 and 23 PC standards at timepoint zero. (DONE)
+--> subtract means from both measurements before taking se
+
+4. Add additional calculation of µ between 0 and 3 days (DONE) and 3 and 7 days (in progress).
+
+5. Get standard error of assimilation efficiency (`a`) by using literature epsilon values Seb has collected.
+Question: Unclear how to get `a` from epsilon. (I should know this?)
+
+6. Remake enrichment curves as ∆2F enrichment instead of 2F (in progress)
 
@@
 source(file.path("libs", "visualization.R"))
-source(file.path("libs", "chromleon.R"))
+source(file.path("libs", "chromeleon.R"))
 source(file.path("libs", "error_prop.R"))
+source(file.path("libs", "calculate_turnover.R"))
 `%nin%` = Negate(`%in%`) # "Not In" function
@@
          )
+
+# For 3 -7 timepoints
+# Analytes
+peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID %>% 
+  # Don't want our standard compounds to be used for generation time calculations! x_x
+  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
+  # Also don't want our yeast-extract stimulated condition in our analyte pool
+  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
+  left_join(F_L_2F, by = "terrain")
+
+# Standards
+peaks_mapped_with_threes_standards<- peaks_mapped_with_threes_FID %>% 
+  filter(str_detect(compound, "STD"))
+
+# 23:0 and 21:0 PC standard errors at inc time zero
+# Determines our standard error in FAME measurements at F_0
+sF_0 <- peaks_mapped_with_threes_standards %>% 
+  # Select only 21 and 23 PC standards at initial time point
+  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
+         inc_time_d == 0) %>%
+  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
+  ungroup() %>% 
+  summarize(F_0_at2H_mn = mean(at2H),
+            F_0_at2H_se = sd(at2H))
+
+# Add sF_0 to analyte data
+
+peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_analytes %>% 
+  mutate(F_0_at2H_se = 
+           sF_0 %>% pull(F_0_at2H_se)
+         )
+
 ```
@@
 gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
+  ungroup() %>%
   mutate(
@@
     # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
-    u_d = gencalc(a = 0.5, # Assimilation efficiency
+    u_d = gencalc(a = a, # Assimilation efficiency
                   FT = f_t, # 2F at time t (at%)
@@
       sF_T = 0,
-      sa = 0,
+      sa = 0
     )
+
+  ) %>%
+  mutate(
+    chain_fctr = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs() %>% 
+      {paste0("C", .)} %>% 
+      factor()
+      ) %>% 
+  mutate(
+    chain_num = compound %>% 
+      str_remove("\\d+-OH") %>% 
+      parse_number() %>% 
+      abs()
+  )
+```
+
+```{r}
+gen_calc_data_3_to_7 <- peaks_mapped_with_threes_analytes %>% 
+  mutate(
+    # Explicitly define incubation parameters:
+    f_label = F_label_mn, # label is adjusted for the effective 2F of the label in a specific terrain
+    a = 0.5, # assimilation efficiency
+    t0 = 0, # start time
+    f_start = at2H_mn_three, # use time point three instead of timepoint zero
+    d_t = inc_time_d - t0, # change in time
+    f_t = `2F_alk`, # use PAME-corrected 2F value
+
+    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
+    u_d = gencalc(a = 0.5, # Assimilation efficiency
+                  FT = f_t, # 2F at time t (at%)
+                  F0 = f_start, # 2F at t0 (at%)
+                  FL = f_label, # 2F of label (at%)
+                  t = d_t # change in time
+                  ),
+    # "negative" turnovers are artifacts of noise and should be zero
+    u_d = if_else(u_d < 0, 0, u_d),
+    # calculate generation time, converting negatives to zero
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
+    # 
+    # # Calculate uncertainty in turnover rate
+    # su_d = calculate_sigma_mu(
+    #   # Mean values:
+    #   a = a,
+    #   F_L = f_label,
+    #   F_T = f_t,
+    #   F_0 = f_start,
+    #   t = d_t,
+    #   # Uncertainties:
+    #   sF_0 = F_0_at2H_se,
+    #   sF_L = F_label_se,
+    #   sF_T = 0,
+    #   sa = 0,
+    # )
 
@@
 ```
+
+```{r}
+test_data <- peaks_mapped_with_zeros_analytes[249,]
+test_data <- test_data %>% 
+  mutate(
+    su_d = calculate_sigma_mu(
+      a = 1,
+      F_L = 1,
+      F_T = 1,
+      F_0 = 1,
+      t = 1,
+      sF_0 = 0.1,
+      sF_L = 0.1,
+      sF_T = 0.1,
+      sa = 0.1
+  ))
+```

### 2022-03-24 libs/calculate_turnover.R
fix logical error

@@ -19,7 +19,7 @@ calculate_turnover <- function(a, FT, F0, FL, t) {
   return(
     case_when(
       mu >= 0 ~ mu,
-      mu < 0, ~ 0
+      mu < 0 ~ 0
       )
   )
 }

### 2022-03-24 libs/chromeleon.R
rename chromeleon library

@@ -1,0 +1,29 @@
+
+#' read a chromleon export file
+#' @param file_path path to the excel file to be read
+#' @return a list with two data frames for injection_details and integration_results
+read_chromeleon_export <- function(file_path) {
+  
+  # read raw data
+  raw_data <- suppressMessages(readxl::read_excel(file_path, sheet = "Integration"))
+  names(raw_data) <- paste0("x", 1:ncol(raw_data))
+  
+  
+  injection_details <- raw_data %>% 
+    # remove rows that have no information
+    filter(!is.na(x1)) %>% 
+    # focus on rows between Injection Details and Chromatogram sections
+    filter(row_number() > which(x1 == "Injection Details")[1] & row_number() < which(x1 == "Chromatogram")[1]) %>% 
+    # remove columns that have no information in them at all
+    { .[map_lgl(., ~!all(is.na(.x)))] }
+  injection_details %>% knitr::kable()
+  
+  all_results <- raw_data %>% 
+    filter(row_number() > which(x1 == "Integration Results")[1]) 
+  
+  integration_results <- 
+    setNames(all_results[-c(1:3),], t(all_results[1,])[,1]) %>%
+    mutate_at(vars(-`Peak Name`), function(x) suppressWarnings(as.numeric(x)))
+  
+  list(injection_details = injection_details, integration_results = integration_results)
+}

### 2022-03-24 libs/chromleon.R
rename chromelon library

@@ -1,29 +1,0 @@
-
-#' read a chromleon export file
-#' @param file_path path to the excel file to be read
-#' @return a list with two data frames for injection_details and integration_results
-read_chromeleon_export <- function(file_path) {
-  
-  # read raw data
-  raw_data <- suppressMessages(readxl::read_excel(file_path, sheet = "Integration"))
-  names(raw_data) <- paste0("x", 1:ncol(raw_data))
-  
-  
-  injection_details <- raw_data %>% 
-    # remove rows that have no information
-    filter(!is.na(x1)) %>% 
-    # focus on rows between Injection Details and Chromatogram sections
-    filter(row_number() > which(x1 == "Injection Details")[1] & row_number() < which(x1 == "Chromatogram")[1]) %>% 
-    # remove columns that have no information in them at all
-    { .[map_lgl(., ~!all(is.na(.x)))] }
-  injection_details %>% knitr::kable()
-  
-  all_results <- raw_data %>% 
-    filter(row_number() > which(x1 == "Integration Results")[1]) 
-  
-  integration_results <- 
-    setNames(all_results[-c(1:3),], t(all_results[1,])[,1]) %>%
-    mutate_at(vars(-`Peak Name`), function(x) suppressWarnings(as.numeric(x)))
-  
-  list(injection_details = injection_details, integration_results = integration_results)
-}

### 2022-03-24 00_dD_label_measurements.Rmd
rename

---
title: "dD_label_measurements"
author: "Tristan Caro"
date: "3/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r}
library(tidyverse)
```

```{r}
vsmow <- 0.0001557643
permil_to_F <- function(dD) {
  frac <- (dD/1000 + 1) * vsmow / (1 + (dD/1000 + 1) * vsmow) * 1000000
  return(frac)
}

dD_df <- readxl::read_xlsx("data/Label_2H_Data/CU dD water data_Oct2021.xlsx",
                        sheet = 2,
                        skip = 1) %>% 
  filter(str_detect(`CH Vial Labes`, "CU-")) %>% 
  mutate(`F_label_ppm` = permil_to_F(as.numeric(dD_SMOW_corr))) %>% 
  mutate(inc_time_d = case_when(
    str_detect(Vial_label, "0x") ~ 0,
    str_detect(Vial_label, "0y") ~ 0,
    str_detect(Vial_label, "0z") ~ 0,
    str_detect(Vial_label, "3x") ~ 3,
    str_detect(Vial_label, "3y") ~ 3,
    str_detect(Vial_label, "3z") ~ 3,
    str_detect(Vial_label, "7x") ~ 7,
    str_detect(Vial_label, "7y") ~ 7,
    str_detect(Vial_label, "7z") ~ 7,
  )) %>% 
  mutate(soil = case_when(
    str_detect(Vial_label, "t") ~ "Tundra",
    str_detect(Vial_label, "c0") ~ "Conifer",
    str_detect(Vial_label, "g") ~ "Grassland",
    str_detect(Vial_label, "cr") ~ "Crust",
  ))

# Do we see changes in F_L over the course of the incubation? Over different terrains?
p_dD_df <- dD_df %>% 
  ggplot(aes(x = inc_time_d, y = F_label_ppm, color = soil)) +
  geom_smooth(method = "lm") +
  geom_point()

p_dD_df2 <- dD_df %>% 
  ggplot(aes(x = inc_time_d, y = as.numeric(dD_SMOW_corr), color = soil)) +
  geom_smooth(method = "lm") +
  geom_point()

dD_df %>% 
  group_by(soil) %>% 
  summarize(F_label_ppm_mn = mean(F_label_ppm),
            F_label_ppm_se = sd(F_label_ppm))
```

# Data export 
```{r}
write_csv(dD_df, file = "data/Label_2H_Data/dD_cleaned.csv")
```

### 2022-03-24 00_soil_report.Rmd
rename

--- 2022-01-07 soil_report.Rmd
@@
 
+reported_soil_data <- soil_data %>% 
+  filter(soil_type %in% c("Tundra", "Conifer Forest", "Grassland"))
+
 ```
 
-```{r}
+```{r data_output}
+write_csv(reported_soil_data, file = "data_output/reported_soil_data.csv")
+```
+
+```{r summary_plot}
 p_soil_values_long <- soil_values_long %>% 

### 2022-03-24 01_LH-SIP_Data_Reduction.Rmd
rename

--- 2022-03-23 00_LH-SIP_Data_Reduction.Rmd
@@
   # Select only 21 and 23 PC standards at initial time point
-  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
+  filter(compound %in% c("21:0 (STD)"),
          inc_time_d == 0) %>%
@@
 ```
+
+# Export
+```{r}
+# Reduce the 0d --> 3d --> 7d incubation data
+peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
+  mutate(time_course = "0d -->") %>% 
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         d2H_mn_zero,
+         d2H,
+         at2H_mn_zero,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_zero,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Turn all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+
+peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
+  # Filter out 0d data points from this dataset
+  filter(inc_time_d != 0) %>% 
+  # Add a time course tag
+  mutate(time_course = "3d -->") %>% 
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         d2H_mn_three,
+         d2H,
+         at2H_mn_three,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_three,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Convert all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+
+# Export as RDS
+saveRDS(peaks_mapped_with_zeros_analytes_reduced,
+        file = "cache/LH_SIP_data")
+
+saveRDS(peaks_mapped_with_threes_analytes_reduced,
+        file = "cache/LH_SIP_data_3d_onwards")
+
+saveRDS(F_L_2F,
+        file = "cache/heavy_label_data")
+```

### 2022-03-24 02_LH-SIP_Quantification.Rmd
rename

--- 2022-03-23 00_LH-SIP_Data_Reduction.Rmd
@@
 ---
-title: "00_LH-SIP_Data_Reduction"
+title: "01_LH-SIP_Quantification"
 author: "Tristan Caro"
-date: "`r Sys.Date()`"
-output:
-    html_document:
-    code_folding: show
-    df_print: paged
-    number_sections: yes
-    toc: yes
-    toc_depth: 3
-    toc_float: yes
-editor_options:
-  chunk_output_type: console
+date: "3/23/2022"
+output: html_document
 ---
@@
 
-# Load data
-
-## Load F_L 2F Data
+## Read RDS from cache
 
 ```{r}
-F_L_2F <- read_csv("data/Label_2H_Data/dD_cleaned.csv") %>% 
-  group_by(soil) %>% 
-  summarize(F_label_ppm_mn = mean(F_label_ppm),
-            F_label_ppm_se = sd(F_label_ppm)) %>% 
-  mutate(F_label_mn = F_label_ppm_mn / 10000,
-         F_label_se = F_label_ppm_se / 10000) %>% 
-  mutate(terrain = case_when(
-    soil == "Conifer" ~ "Gordon Gulch Conifer Forest",
-    soil == "Tundra" ~ "Niwot Ridge Tundra",
-    soil == "Grassland" ~ "Marshall Mesa Grassland"
-  ))
+LH_SIP_data <- readRDS(file = "cache/LH_SIP_data")
+
+LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
 ```
 
-## Load Compound nC and nH Data sheet
+# Calculate Turnover
 
 ```{r}
-compound_nC_nH <- read_xlsx("data/compound_nC_nH.xlsx")
-```
+turnover <- LH_SIP_data %>% 
+  # Combine 0d --> and 3d --> datasets
+  bind_rows(LH_SIP_data_3d_onwards) %>% 
+  # Evaluate each row individually
+  ungroup() %>%
+  mutate(
 
-## Load Phthalic Acid IRMS Data
+    # Explicitly define incubation parameters:
+    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
+    a = 0.6, # assimilation efficiency
+    # start time
+    t0 = case_when(
+      time_course == "0d -->" ~ 0,
+      time_course == "3d -->" ~ 3),
+    d_t = inc_time_d - t0, # change in time
+    f_start = case_when(
+      time_course == "0d -->" ~at2H_mn_zero,
+      time_course == "3d -->" ~ at2H_mn_three),
+    f_t = `2F_alk`, # use PAME-corrected 2F value
 
-```{r}
-# Load PAME Iso Files
-PAME_data_path <- file.path("data", "IRMS", "PAME_data")
-ref_ratio <- get_standard("2H") %>% as.numeric()
+    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
+    u_d = calculate_turnover(
+      a = a, # Assimilation efficiency
+      FT = f_t, # 2F at time t (at%)
+      F0 = f_start, # 2F at t0 (at%)
+      FL = f_label, # 2F of label (at%)
+      t = d_t # change in time
+      ),
+    # "negative" turnovers are artifacts of noise and should be zero
+    u_d = if_else(u_d < 0, 0, u_d),
+    # calculate generation time, converting negatives to zero
+    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
 
-# read files
-PAME_iso_files_raw <- 
-  # path to data files
-  PAME_data_path %>% 
-  # read data files in parallel for fast read
-  iso_read_continuous_flow() %>%
-  # filter out files with read errors (e.g. from aborted analysis)
-  iso_filter_files_with_problems()
-
-# Load Peak Map
-
-PAME_peak_map <- 
-  # initial peak map:
-  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
-  # corrected peak map
-  readxl::read_excel(file.path("data", "IRMS", "PAME_peak_map.xlsx"))
-PAME_peak_map
-
-# process file information
-PAME_iso_files <- PAME_iso_files_raw %>% 
-  # rename key file info columns
-  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
-  # parse text info into numbers
-  iso_parse_file_info(number = analysis) %>% 
-  # process other file information that is specific to the naming conventions
-  # of this particular sequence
-  iso_mutate_file_info(
-    # what is the type of each analysis?
-    type = case_when(
-      str_detect(id1, "[Zz]ero")      ~ "on_off",
-      str_detect(id1, "H3")           ~ "H3_factor",
-      str_detect(id1, "F8")           ~ "F8_std",
-      str_detect(id1, "F9")           ~ "F9_std",
-      TRUE                            ~ "sample"
-    ),
-    # what was the concentration? (assuming Preparation = concentration or volume)
-    concentration = 
-      ifelse(type == "std",  
-             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
-               parse_number() %>% iso_double_with_units("ng/uL"),
-             NA),
-    # what folder are the data files in? (assuming folder = sequence)
-    folder = basename(dirname(file_path))
-  ) %>% 
-  # focus only on the relevant file info, discarding the rest
-  iso_select_file_info(
-    folder, analysis, file_datetime, id1, type, concentration
+    # Calculate uncertainty in turnover rate
+    su_d = calculate_sigma_mu(
+      # Mean values:
+      a = a,
+      F_L = f_label,
+      F_T = f_t,
+      F_0 = f_start,
+      t = d_t,
+      # Uncertainties:
+      sF_0 = F_0_at2H_se,
+      sF_L = F_label_se,
+      sF_T = 0,
+      sa = 0
     )
 
-# Peak Mapping
-# set peak table from vendor data table with default isodat template
-PAME_iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(PAME_iso_files) %>% 
-  # convert units from mV to V for amplitudes and area
-  iso_convert_peak_table_units(V = mV, Vs = mVs)
-
-# Create Peak Table and filter out non-PAME samples
-PAME_peak_table <- PAME_iso_files %>%
-  iso_filter_files(str_detect(id1, "PAME")) %>% 
-  # Choose only runs that worked
-  iso_filter_files(str_detect(file_id, "success")) %>% 
-  iso_set_peak_table_from_isodat_vendor_data_table() %>%
-  iso_get_peak_table() %>% 
-  mutate(Analysis = substr(file_id, 1, 7),
-         sample_id = substr(file_id, 10,14))
-
-PAME_peak_mapped <- PAME_peak_table %>%
-  iso_map_peaks(PAME_peak_map, map_id = Analysis) %>%
-  filter(!is.na(compound))
-
-# Summarize the mean and standard error
-PAME_summarized <- PAME_peak_mapped %>%
-  summarize(at2H_mn = mean(at2H),
-            at2H_se = sd(at2H)) %>% 
-  mutate(at2H_mn_ppm = at2H_mn * 10000,
-         at2H_se_ppm = at2H_se * 10000)
-```
-
-## Load IRMS Data
-
-### Load Metadata and Problematic Run Data
-
-```{r}
-mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
-sample_names <- mtda$id1
-
-problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
-problematic_analyses <- problematic_runs$Analysis
-problematic_analyses_num <- parse_number(problematic_analyses)
-```
-
-### Load Peak Map
-
-```{r}
-# this information is often maintained in a csv or Excel file
-peak_map <- 
-  # initial peak map:
-  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
-  # corrected peak map
-  readxl::read_excel(file.path("data", "IRMS", "peak_maps_resolved.xlsx"))
-```
-
-### Read raw IRMS data files
-
-```{r, warning=FALSE}
-# Set file path(s) to data files, folders or rds collections 
-# can be multiple folders or mix of folders and files
-# Isoverse will iteratively search subfolders. Huzzah! ^_^
-data_path <- file.path("data", "IRMS", "raw_data")
-ref_ratio <- get_standard("2H") %>% as.numeric()
-
-# read files
-iso_files_raw <- 
-  # path to data files
-  data_path %>% 
-  # read data files in parallel for fast read
-  iso_read_continuous_flow() %>%
-  # filter out files with read errors (e.g. from aborted analysis)
-  iso_filter_files_with_problems()
-```
-
-### Process file info & peak table
-
-```{r}
-# process IRMS file information
-iso_files <- iso_files_raw %>% 
-  # rename key file info columns
-  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
-  # parse text info into numbers
-  iso_parse_file_info(number = analysis) %>% 
-  # process other file information that is specific to the naming conventions
-  # of this particular sequence
-  iso_mutate_file_info(
-    # what is the type of each analysis?
-    type = case_when(
-      str_detect(id1, "[Zz]ero")      ~ "on_off",
-      str_detect(id1, "H3")           ~ "H3_factor",
-      str_detect(id1, "F8")           ~ "F8_std",
-      str_detect(id1, "F9")           ~ "F9_std",
-      TRUE                            ~ "sample"
-    ),
-    # what was the concentration? (assuming Preparation = concentration or volume)
-    concentration = 
-      ifelse(type == "std",  
-             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
-               parse_number() %>% iso_double_with_units("ng/uL"),
-             NA),
-    # what folder are the data files in? (assuming folder = sequence)
-    folder = basename(dirname(file_path))
-  ) %>% 
-  # focus only on the relevant file info, discarding the rest
-  iso_select_file_info(
-    folder, analysis, file_datetime, id1, type, concentration
-  ) %>% 
-  # add in additional sample metadata (could be any info)
-  # note: this would typically be stored in / read from a csv or excel file
-  iso_add_file_info(
-    read_csv(file.path("data", "sample_metadata_2021.csv")),
-    join_by = "id1"
-  )
-
-# set peak table from vendor data table with default isodat template
-iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
-  # convert units from mV to V for amplitudes and area
-  iso_convert_peak_table_units(V = mV, Vs = mVs)
-
-# focus on sample files
-sample_files <- iso_filter_files(iso_files, type == "sample")
-
-# Include only sample files
-sample_files <- iso_filter_files(sample_files, id1 %in% sample_names)
-
-# EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
-sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))
-
-sample_files <- iso_filter_files(sample_files, str_detect(id1, "cr0", negate = TRUE))
-
-# EXCLUDE RUN WE'VE DEEMED PROBLEMATIC
-sample_files <- iso_filter_files(sample_files, analysis %nin% problematic_analyses_num)
-
-```
-
-### Show file information
-
-```{r}
-# display file information
-iso_files %>% 
-  iso_get_file_info() %>% select(-file_id, -folder) %>% 
-  iso_make_units_explicit() %>% knitr::kable()
-```
-
-### Example chromatogram
-
-```{r "example_chromatograms", fig.width=8, fig.height=8}
-# plot an example chromatogram
-
-# sample_files[10] %>% # choosing arbitrary file to plot
-# iso_plot_continuous_flow_data(
-#   # select data and aesthetics
-#   data = c(2), color = id1, panel = id1,
-#   # zoom in on time interval
-#   time_interval = c(750, 4000),
-#   # peak labels for all peaks > 2V
-#   peak_bounds = TRUE,
-#   peak_marker = FALSE,
-#   peak_label = iso_format(rt),
-#   #peak_label_size = 3,
-#   peak_label_filter = analysis == 5685 & amp2 > 1
-# ) + scale_color_npg() + 
-#   theme_classic() +
-#   theme(strip.background = element_blank())
-```
-
-## Load GC-FID Data
-
-```{r}
-root <- file.path("data", "gc_fid_data_2021")
-file_list = list.files(path = root)
-file_list <- file_list %>% 
-  str_subset("blank", negate = TRUE) %>% 
-  str_subset("Blank", negate = TRUE) %>% 
-  str_subset("GCMS-STD", negate = TRUE) %>% 
-  str_subset("BLK", negate = TRUE) # remove procedural blanks
-sample_names <- file_list %>% 
-  str_replace("FID.....", "") %>% 
-  str_replace("_100ul-nhex.xls", "") %>% 
-  str_replace("_100ul.xls", "")
-
-FID_all_data <-
-  tibble(
-    sample = sample_names,
-    file = file_list,
-    data = map(file.path(root, file), read_chromeleon_export),
-    injection_details = map(data, "injection_details"),
-    integration_results = map(data, "integration_results")
-  ) %>% select(-data)
-```
-
-### Unnest FID integration details and clean
-
-```{r}
-FID_results <- FID_all_data %>% 
-  select(-injection_details) %>% 
-  unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0) %>% 
-  # Specify chain length
-  mutate(
-    chain = `Peak Name` %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs() %>% 
-      {paste0("C", .)} %>% 
-      factor()
-      ) %>% 
-  # Rename these columns so we can join the IRMS and FID data
-  # Important to specify what data comes from FID!
-  rename(
-    "sample_id" = sample,
-    "compound" = `Peak Name`,
-    "rt_FID" = `Retention Time`,
-    "area_FID" = `Area`,
-    "height_FID" = `Height`,
-    "rel_area_FID" = `Relative Area`,
-    "rel_height_FID" = `Relative Height`,
-    "amount_FID" = `Amount`
-         ) %>% 
-  # Make FID notation match IRMS notation
-  mutate(
-    compound = 
-      case_when(
-        str_detect(compound, "18:2 trans 9, 12") ~ "18:2 9, 12",
-        str_detect(compound, "18:2 trans 9,12") ~ "18:2 9, 12",
-        str_detect(compound, "18:2 9,12") ~ "18:2 9, 12",
-        str_detect(compound, "16:1 cis-9") ~ "16:1 cis 9",
-        str_detect(compound, "16:1 trans-9") ~ "16:1 trans 9",
-        str_detect(compound, "18:1 cis-9") ~ "18:1 cis 9",
-        str_detect(compound, "18:1 trans-9") ~ "18:1 trans 9",
-        str_detect(compound, "21:0") ~ "21:0 (STD)",
-        str_detect(compound, "23:0") ~ "23:0 (STD)",
-        TRUE ~ compound
-      )
   )
@@
 
-# Compound abundance
-
-```{r compound_abundance}
-# Compute the instrument response for each run:
-# Response = µg per unit area using 10µg of PAIBE as quantification STD
-
-FID_results_PAIBE_ug <- FID_results %>% 
-  select(
-    sample_id, 
-    file,
-    compound,
-    area_FID, 
-    rel_area_FID) %>% 
-  filter(compound == "PAIBE") %>% 
-  mutate(
-    PAIBE_area = area_FID,
-    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
-    # Find instrument response as PAIBE mass per FID area
-    ug_per_area = PAIBE_ug_inj / PAIBE_area,
-    # Check that the inferred mass is the same as known mass
-    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
-  ) %>%
-  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
-
+# Export
+```{r}
+turnover %>% saveRDS(file = "cache/turnover_rates")
 ```
-
-## Calculate mass of analyte injected into GC-FID
-
-```{r response}
-# Put the response info back into the abundance data frame:
-FID_results_abundance <- 
-  left_join(
-    FID_results, 
-    FID_results_PAIBE_ug, 
-    by = "file"
-    ) %>%
-  # Calculate the quantity of analyte injected based off of area and 
-  # instrument response
-  mutate(
-    compound_ug_inj = area_FID * ug_per_area,
-    inj_vol_ul = 1, # GC-FID injection volume µL
-    susp_vol_ul = 100, # suspension volume µL
-    # The mass of analyte in vial is the concentration of analyte (mass 
-    # seen per unit volume injected) times the suspension volume.
-    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
-  )
-
-```
-
-## Calculate fractional derivatization efficiency (21-PC)
-```{r 21_PC}
-FID_results_abundance_21 <- FID_results_abundance %>% 
-  filter(compound == "21:0 (STD)") %>% 
-  # Derivatization efficiency is the amount of standard observed divided by 
-  # the amount of standard added (21:0 PC = 10µg)
-  mutate(
-    STD21_ug = 10,
-    deriv_efficiency = compound_ug_vial / STD21_ug
-  ) %>% 
-  select(file, STD21_ug, deriv_efficiency)
-
-# Add deriv efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance, 
-    FID_results_abundance_21, 
-    by = "file"
-  ) %>% 
-  # Calculate mass of fatty acids in extraction mixture as
-  # compounds present as FAMEs multiplied by derivatization efficiency
-  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
-```
-
-## Calculate extraction efficiency (23-PC)
-
-```{r 23_PC}
-FID_results_abundance_23 <- FID_results_abundance %>% 
-  filter(compound == "23:0 (STD)") %>% 
-  # Lipid Recovery Efficiency is the amount of initial standard 
-  # observed divided by the amount of standard added (23:0 PC = 100ug)
-  mutate(
-    STD23_ug = 100,
-    extr_efficiency = compound_ug_vial / STD23_ug
-  ) %>% 
-  select(file, STD23_ug, extr_efficiency)
-
-# Add extr efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance,
-    FID_results_abundance_23,
-    by = "file"
-  ) %>% 
-  mutate(
-    # Calculate amount of analyte in soil sample
-    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
-    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
-    soil_mass_g = 10, # 10 g of each soil were used for this study
-    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
-  )
-```
-
-## Remove standards from soil abundances
-
-```{r}
-# Remove standards from soil abundances
-
-FID_results_abundance_no_stds <- FID_results_abundance %>% 
-  filter(
-    compound %nin% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
-    str_detect(sample_id, "FAME", negate = TRUE),
-    str_detect(sample_id, "BAME", negate = TRUE)
-  )
-```
-
-# IRMS Peak Mapping
-
-```{r}
-sample_peak_table <- sample_files %>%
-  iso_set_peak_table_from_isodat_vendor_data_table() %>%
-  iso_get_peak_table() %>% 
-  mutate(Analysis = substr(file_id, 1, 7),
-         sample_id = substr(file_id, 10,14))
-```
-
-## Generate Isoverse Peak Map
-```{r}
-# Generate an isoverse peak map
-peaks_mapped <- sample_peak_table %>%
-  iso_map_peaks(peak_map, map_id = Analysis) %>%
-  filter(!is.na(compound))
-```
-
-## Remove readychecks, blanks, etc. from analysis
-```{r}
-# Filter based on what is in the sample_names metadata
-peaks_mapped <- peaks_mapped %>% 
-  filter(sample_id %in% sample_names)
-
-# Filter out runs that are on our problematic_runs list
-peaks_mapped <- peaks_mapped %>% 
-  filter(Analysis %nin% problematic_runs)
-```
-
-## Check problematic peak assignments
-```{r}
-problem_peaks <- iso_get_problematic_peak_mappings(peaks_mapped)
-```
-
-## Export summary of unresolved peaks
-```{r}
-# Spit out peaks that need to be resolved
-peaks_mapped %>%
-  ungroup() %>%
-  select(Analysis, compound, rt) %>%
-  mutate(rt = round(rt, digits=0)) %>%
-  pivot_wider(
-    names_from = Analysis, 
-    names_prefix = "rt:",
-    values_from = rt, 
-    id_cols = compound, 
-    values_fn = function(x) paste(x, collapse = "; ")
-  ) %>%
-  openxlsx::write.xlsx(file.path("data", "IRMS", "peak_maps_resolve.xlsx"))
-```
-
-## Assign incubation params
-```{r}
-# Add Some Parameters
-peaks_mapped <- peaks_mapped %>% 
-  group_by(sample_id) %>% 
-  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
-         inc_time_d_str = paste(inc_time_d, "Days"),
-         f_label = 0.005,
-         t_series_id = paste0(substr(sample_id, 1,1), 
-                              substr(sample_id, 5,5)),
-         soil_id = substr(t_series_id, 1,1),
-         replicate_id = substr(t_series_id, 2,2),
-         terrain = case_when(
-           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
-           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
-           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
-           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))
-# 
-# inc_time_zero <- peaks_mapped %>% 
-#   filter(inc_time_d == 0) %>% 
-#   select(sample_id, compound, at2H, t_series_id) %>% 
-#   mutate(f_start = at2H) %>% 
-#   select(-at2H)
-# 
-#
-
-```
-
-## Extract zero timepoint values
-```{r}
-zero_peaks <- peaks_mapped %>%
-  filter(inc_time_d_str == "0 Days") %>%
-  group_by(t_series_id, compound) %>%
-  mutate(n_analyical_reps = n()) %>%
-  ungroup() %>%
-  # exclude ambiguous peaks
-  filter(!is_ambiguous)
-
-zero_peaks_averaged <- zero_peaks %>% 
-  group_by(soil_id, compound) %>% 
-  summarise(at2H_mn_zero = mean(at2H),
-            d2H_mn_zero = mean(d2H),
-            area2_mn_zero = mean(area2))
-
-zero_peaks_averaged %>% 
-  openxlsx::write.xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"),
-                       overwrite = TRUE)
-
-# zero_peaks_averaged <- read_xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"))
-
-# This is the dataset we will use for generation time calculations
-peaks_mapped_with_zeros <- 
-  peaks_mapped %>%
-  left_join(
-    zero_peaks_averaged,
-    by = c("soil_id", "compound")
-  )
-stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))
-
-# no zero samples
-# peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
-
-peaks_mapped_with_zeros <- peaks_mapped_with_zeros %>% 
-  mutate(
-    sample_id = substr(file_id, 10,14)
-    )
-```
-
-## Extract 3 day timepoint values
-
-```{r}
-three_day_peaks <- peaks_mapped %>%
-  filter(inc_time_d_str == "3 Days") %>%
-  group_by(t_series_id, compound) %>%
-  mutate(n_analyical_reps = n()) %>%
-  ungroup() %>%
-  # exclude ambiguous peaks
-  filter(!is_ambiguous)
-
-three_day_peaks_averaged <- three_day_peaks %>% 
-  group_by(soil_id, compound) %>% 
-  summarise(at2H_mn_three = mean(at2H),
-            d2H_mn_three = mean(d2H),
-            area2_mn_three = mean(area2))
-
-peaks_mapped_with_threes <- 
-  peaks_mapped %>%
-  left_join(
-    three_day_peaks_averaged,
-    by = c("soil_id", "compound")
-  )
-stopifnot(nrow(peaks_mapped_with_threes) == nrow(peaks_mapped))
-
-peaks_mapped_with_threes <- peaks_mapped_with_threes %>% 
-  mutate(
-    sample_id = substr(file_id, 10,14)
-    )
-```
-
-## Join IRMS and GC-FID Data
-
-```{r}
-# peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
-#   left_join(FID_results, by = c("sample_id", "compound"))
-
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>%
-  left_join(
-    FID_results_abundance_no_stds, 
-    by = c("sample_id", "compound")
-  )
-
-peaks_mapped_with_threes_FID <- peaks_mapped_with_threes %>% 
-    left_join(
-    FID_results_abundance_no_stds, 
-    by = c("sample_id", "compound")
-  )
-```
-
-## Correct for PAME
-
-```{r}
-
-# For 0 -3, 0-7 timepoints
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros_FID %>% 
-  left_join(compound_nC_nH, by = "compound") %>% 
-  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
-
-# for 3-7 timepoints
-peaks_mapped_with_threes_FID <- peaks_mapped_with_threes_FID %>% 
-  left_join(compound_nC_nH, by = "compound") %>% 
-  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
-```
-
-## Separate analytes and standards, calculate F_0 se
-
-```{r}
-# For 0-3,0-7 timepoints
-# Analytes
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
-  # Don't want our standard compounds to be used for generation time calculations! x_x
-  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
-  # Also don't want our yeast-extract stimulated condition in our analyte pool
-  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
-  left_join(F_L_2F, by = "terrain")
-
-# Standards
-peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID %>% 
-  filter(str_detect(compound, "STD"))
-
-# 23:0 and 21:0 PC standard errors at inc time zero
-# Determines our standard error in FAME measurements at F_0
-sF_0 <- peaks_mapped_with_zeros_standards %>% 
-  # Select only 21 and 23 PC standards at initial time point
-  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
-         inc_time_d == 0) %>%
-  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
-  ungroup() %>% 
-  summarize(F_0_at2H_mn = mean(at2H),
-            F_0_at2H_se = sd(at2H))
-
-# Add sF_0 to analyte data
-
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
-
-# For 3 -7 timepoints
-# Analytes
-peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID %>% 
-  # Don't want our standard compounds to be used for generation time calculations! x_x
-  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
-  # Also don't want our yeast-extract stimulated condition in our analyte pool
-  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
-  left_join(F_L_2F, by = "terrain")
-
-# Standards
-peaks_mapped_with_threes_standards<- peaks_mapped_with_threes_FID %>% 
-  filter(str_detect(compound, "STD"))
-
-# 23:0 and 21:0 PC standard errors at inc time zero
-# Determines our standard error in FAME measurements at F_0
-sF_0 <- peaks_mapped_with_threes_standards %>% 
-  # Select only 21 and 23 PC standards at initial time point
-  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
-         inc_time_d == 0) %>%
-  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
-  ungroup() %>% 
-  summarize(F_0_at2H_mn = mean(at2H),
-            F_0_at2H_se = sd(at2H))
-
-# Add sF_0 to analyte data
-
-peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
-
-```

### 2022-03-24 archive/isotope_data_reduction.rmd
move to archive folder

--- 2020-12-10 isotope_data_reduction.rmd
@@
 a = 0.5 # incorporation efficiency of 50%
-FT = 0.02 # resultant isotopic enrichment
+FT = 0.02 # resulting isotopic enrichment
 F0 = 0.0124 # beginning isotopic enrichment

### 2022-03-24 archive/modified_silver_ion_chroma.Rmd
move to archive folder

--- 2020-12-16 modified_silver_ion_chroma.Rmd
@@
 
-5.  Elute **F1** with 4mL hexane.
-    *F1 should rule out solvent carry-through.*
+5.  Elute **F1** with 4mL hexane. *F1 should rule out solvent carry-through.*
 
@@
 
-2.  Divide in half:
-    Use 100µL as a **standard**.
-    Use 100µL as a **sample.**
-    *The column sees 100µL \* 10ng/µL = 1000ng (1µg) per compound).*
+2.  Divide in half: Use 100µL as a **standard**. Use 100µL as a **sample.** *The column sees 100µL \* 10ng/µL = 1000ng (1µg) per compound).*
 
@@
 
+plot_results <- plot_results %>% 
+  mutate(fraction_eluent = case_when(
+    sample == "tcbames3" ~ "NA",
+    sample == "BAME_modagion_F1" ~ "F1 Hexane",
+    sample == "BAME_modagion_F2" ~ "F2 99:1 Hex:ac",
+    sample == "BAME_modagion_F3" ~ "F3 96:4 Hex:ac",
+    sample == "BAME_modagion_F4" ~ "F4 90:10 Hex:ac",
+    sample == "BAME_modagion_F5" ~ "F5 Acetone"
+     )
+  )
+
+factored_eluents <- c('NA', 'F1 Hexane','F2 99:1 Hex:ac','F3 96:4 Hex:ac','F4 90:10 Hex:ac', 'F5 Acetone')
+plot_results$fraction_eluent_f = factor(plot_results$fraction_eluent, levels=factored_eluents)
+
 p_tc_bames2 <- plot_results %>%
@@
   geom_bar(stat = 'identity', width = 0.1)+
-  facet_wrap(~sample_f, ncol = 1, scales = "free_y") +
-  ggtitle("BAMES Standard 10µg/µL") +
+  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
+  ggtitle("BAMES Standard 10ng/µL") +
   theme_bw()
+
+ggsave(filename = "fig_output/p_tc_bames2.png", plot = p_tc_bames2, height = 10, width = 7)
 
@@
 
-```{results <- results %>%}
+    results <- results %>%
       group_by(sample) %>% 
@@
 
-```
-
 ###

### 2022-03-24 archive/modified_silver_ion_chroma_2.Rmd
move to archive folder

--- 2021-01-21 modified_silver_ion_chroma_2.Rmd
@@
 
-Most compounds derivatized from the free fatty acid fraction (F4) of Jamie's Boulder soil sample are saturated FAMEs or not readily identifiable by mass spec.
-For clarity, sterols, alkanes, and ethers were excluded from the chromeleon data export.
-FAMEs are saturated unless noted otherwise.
-
-```{r, fig.width=8, fig.height=10, warning=FALSE}
+```{r, fig.width=8, fig.height=13, warning=FALSE}
 # Any necessary limitations to plotted results would go here
@@
   ggplot() +
-  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
-  geom_bar(stat = 'identity', width = 0.1)+
+  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`, label = saturation) +
+  geom_bar(stat = 'identity', width = 0.1) +
   facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
   ggtitle("Boulder Soil Free FA as FAMES") +
-  theme_bw()
+  geom_label_repel(data = subset(plot_results, saturation %in% c("n1 cis", "n1 trans")),
+                   aes(vjust =-7, box.padding = 0.5),
+                   show.legend = FALSE,
+                   size = 2,
+                   segment.alpha = 0.5) +
+  theme_bw() +
+  theme(legend.position = "bottom")
 
+p_sfames
 p_sfames %>% ggplotly(dynamicTicks = TRUE, tooltip = c("key", "x", "y"))

### 2022-03-24 archive/sk_isotope_data_analysis.Rmd
move to archive folder

---
title: "Isotope data reduction"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# global knitting options for code rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Load packages

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # devtools::install_github("isoverse/isotopia")
library(readxl)
source(file.path("scripts", "plotting_functions.R"))
```

This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.

All code chunks that contain a critical step towards the final data (i.e. do more than visualization or a data summary) are marked with `(*)` in the header to make it easier to follow all key steps during interactive use.

# Load data

## Read raw data files (*)

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files, using example data set here
# (this is a reduced data set of mostly standards with just a few example samples)
data_path <- file.path("data", "201911_isotope_data.cf.rds")

# read files
iso_files_raw <- 
  # path to data files
  data_path %>% 
  # read data files in parallel for fast read
  iso_read_continuous_flow() %>%
  # filter out files with read errors (e.g. from aborted analysis)
  iso_filter_files_with_problems()
```

## Process file info & peak table (*)

```{r}
# process file information
iso_files <- iso_files_raw %>% 
  # rename key file info columns
  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
  # parse text info into numbers
  iso_parse_file_info(number = analysis) %>% 
  # process other file information that is specific to the naming conventions
  # of this particular sequence
  iso_mutate_file_info(
    # what is the type of each analysis?
    type = case_when(
      str_detect(id2, "blank")        ~ "blank",
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "H3")           ~ "H3_factor",
      str_detect(id1, "F[89]")        ~ "std",
      TRUE                            ~ "sample"
    ),
    # what was the concentration? (assuming Preparation = concentration or volume)
    concentration = 
      ifelse(type == "std",  
             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
               parse_number() %>% iso_double_with_units("ng/uL"),
             NA),
    # what folder are the data files in? (assuming folder = sequence)
    folder = basename(dirname(file_path))
  ) %>% 
  # focus only on the relevant file info, discarding the rest
  iso_select_file_info(
    folder, analysis, file_datetime, id1, type, concentration, gc_method = `GC Method`
  ) %>% 
  # add in additional sample metadata (could be any info)
  # note: this would typically be stored in / read from a csv or excel file
  iso_add_file_info(
    readxl::read_excel(file.path("data", "isotopes_metadata.xlsx")),
    join_by = "id1"
  )

# set peak table from vendor data table with default isodat template
iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)

# focus on sample files
sample_files <- iso_filter_files(iso_files, type == "sample" & analysis > 5651) %>% 
  iso_mutate_file_info(
    id1 = str_replace(id1, "^.*[mM]([^wWxX]+[wWxX]).*$", "m\\1") %>% 
      str_replace("6", "G") %>% str_replace("V", "N") %>% str_replace("X", "x") %>% str_replace("W", "w")
  )
```

## Standards chromatograms

Somehow the entire chromatograms shifted massively around for reasons that I don't understand at all - about a 900s shift.

```{r "standard_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # all sample files
  iso_filter_files(iso_files, analysis %in% c(5645, 5695, 6212, 6225)),
  # select data and aesthetics
  data = c(2), color = folder, panel = analysis,
  linetype = gc_method,
  # zoom in on time interval
  time_interval = c(1050, 2100),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = TRUE,
  peak_label = iso_format(rt),
  #peak_label_size = 3,
  peak_label_filter = analysis == 5685 & amp2 > 1
) +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  scale_x_continuous(breaks = (0:30) * 100)
#ggsave(file.path("fig_output", "chromatograms_standards.pdf"), width = 12, height = 10)
```

## Show file information

```{r}
# display file information
iso_files %>% 
  iso_get_file_info() %>% select(-file_id, -folder) %>% 
  iso_make_units_explicit() %>% knitr::kable()
```

## Example chromatograms

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # all sample files
  iso_filter_files(sample_files, analysis < 6000 | id1 == "mAw"),
  # select data and aesthetics
  data = c(2), color = id1, panel = analysis,
  linetype = gc_method,
  # zoom in on time interval
  time_interval = c(1200, 1800),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = TRUE,
  peak_label = iso_format(rt),
  #peak_label_size = 3,
  peak_label_filter = analysis == 5685 & amp2 > 1
) +
  theme(legend.position = "bottom", legend.direction = "vertical")
#ggsave(file.path("fig_output", "chromatograms_example.pdf"), width = 12, height = 10)
```

# Peak Mapping

```{r}
# this information is often maintained in a csv or Excel file instead
# but generated here from scratch for demonstration purposes
peak_maps <- 
  readxl::read_excel(file.path("data","isotopes_peak_maps.xlsx"))
peak_maps %>% knitr::kable(digits = 0)

# identify peaks
sample_files_w_ids <- sample_files  %>% 
  # filter (focus on initial analytical run since later runs the GC was shit)
  iso_filter_files(analysis < 6000) %>% 
  # map peaks
  iso_map_peaks(peak_maps, map_id = type)
```

## Chromatograms

```{r "sample_chromatograms", fig.width=8, fig.height=8}
# plot the chromatograms
iso_plot_continuous_flow_data(
  # all sample files
  sample_files_w_ids,
  # select data and aesthetics
  data = c(2), color = id1, panel = analysis,
  # zoom in on time interval
  time_interval = c(1000, 3000),
  # peak labels for all peaks > 2V
  peak_bounds = TRUE,
  peak_marker = FALSE,
  peak_label = iso_format(compound, d2H),
  #peak_label_size = 3,
  peak_label_filter = compound != "unknown"
) 
```

# Process Data

## Equations

$$
\Delta F(t_2 - t_1) = \left(1 - e^{-\mu \cdot (t_2 - t_1)} \right) \left(a \cdot F_L - F (t_1)\right) 
$$

$$
\rightarrow \mu = -\frac{1}{t_2 - t_1} \ln{\left(\frac{a \cdot F_L - F(t_2)}{a \cdot F_L  - F(t_1)}\right)}
$$

## Calculations

### Enrichment data

```{r}
enrichment_data <-
  sample_files_w_ids %>% 
  # get peak table
  iso_get_peak_table(include_file_info = everything()) %>% 
  # focus on analyte compounds
  filter(compound != "H2") %>%
  # calculate relative amounts ignoring internal standard
  group_by(file_id) %>% 
  mutate(rel_amount = area2 / sum(area2[compound != "IS"])) %>% 
  ungroup() %>% 
  # diregard unknown compounds for now
  filter(compound != "unknown") %>% 
  # generate an easy to use sample label
  mutate(sample_label = sprintf("%.0fhrs%s%s", inc_time, ifelse(with_glu, " (with glu)", ""), ifelse(control, " - CTRL", ""))) %>% 
  # use the kill control as 0 time point (0 time point was not in the first analytical run and is useless in the 2nd)
  mutate(inc_time = ifelse(control == TRUE, 0, inc_time)) %>% 
  # test with just a few columns (expand here if more are needed)
  select(sample_label, compound, rt, id1, inc_time, with_glu, rel_amount, d2H) %>% 
  # convert dD to fractional abundance
  mutate(
    F2H.ppm = 
      delta(d2H, ref_ratio = get_standard("2H")) %>% 
      to_ratio() %>% to_abundance() %>% 
      as.numeric %>% { .*1e6 }
  )
```

### Labeling times

```{r}
FL.ppm = 0.5/100 * 1e6 # tracer strength = 0.5%
a = 0.5 # incorporation efficiency of 50%

# calculates all permutations of enrichment calculations
labeling_rates <- 
  full_join(
    enrichment_data,
    select(enrichment_data, compound, with_glu, start_inc_time = inc_time, 
           start_d2H = d2H, start_F2H.ppm = F2H.ppm),
    by = c("compound", "with_glu")
  ) %>% 
  filter(inc_time > start_inc_time | start_inc_time == 0) %>% 
  # calculate differences
  mutate(
    inc_time_label = sprintf("%.0f to %.0f hrs", start_inc_time, inc_time),
    Dd2H = d2H - start_d2H,
    DF2H.ppm = F2H.ppm - start_F2H.ppm
  ) %>% 
  select(-start_d2H) %>% 
  arrange(with_glu, compound, inc_time, start_inc_time) %>% 
  # calculate labeling time
  mutate(
    mu.1_hr = case_when(
      inc_time - start_inc_time == 0 ~ NA_real_,
      TRUE ~ - (1/(inc_time - start_inc_time))*(log((a*FL.ppm - F2H.ppm)/(a*FL.ppm - start_F2H.ppm)))
    ),
    mu.1_d = mu.1_hr * 24,
    gen.d = log(2) / (mu.1_d)
  )

labeling_rates
```

# Analyze Data

## Delta data overview

```{r "data_overview_figure_permil", fig.width=12, fig.height=10}
# all data in delta space
labeling_rates %>% 
  filter(start_inc_time == 0) %>% 
  gather("var", "val", d2H, Dd2H) %>% 
  iso_plot_data(
    x = inc_time, y = val, color = compound, shape = with_glu, size = rel_amount,
    points = TRUE,
    lines = TRUE,
    panel = with_glu ~ var
    #panel_scales = "fixed"
  )
```

## Abundace [ppm]

```{r "data_overview_figure_ppm", fig.width=12, fig.height=10}
# all data in abundace space
labeling_rates %>% 
  filter(start_inc_time == 0) %>% 
  gather("var", "val", DF2H.ppm) %>% 
  iso_plot_data(
    x = inc_time, y = val, color = compound, shape = with_glu, size = rel_amount,
    points = TRUE,
    lines = TRUE,
    panel = with_glu ~ var
  )
```

## Generation times / Growth rates

```{r "all_generation_times"}
labeling_rates %>% 
  mutate(glu = ifelse(with_glu, "+glucose", "no glucose")) %>% 
  filter(gen.d > 0) %>% 
  filter(inc_time_label %in% c("0 to 1 hrs", "1 to 6 hrs", "0 to 6 hrs", "6 to 50 hrs")) %>% 
  ggplot() +
  aes(compound, mu.1_d, fill = inc_time_label) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_figure(axis_x_rotate = 90) +
  facet_wrap(~glu, scales = "free_y", ncol = 1)
```

# Time course

```{r}
make_time_course_plot <- function(df) {

  # calculate weighted mean of multiple lipids
  calculate_DF2H_weighted_mean <- function(df) {
    df %>% 
      group_by(inc_time, inc_time_label) %>% 
      summarize(
        DF2H.ppm = sum(DF2H.ppm * rel_amount) / sum(rel_amount),
        name = "weighted\nmean"
      )
  }

  quant_limit <- tibble(
    inc_time = 5, DF2H.ppm = c(0.8 * max(df$DF2H.ppm), 0.8 * max(df$DF2H.ppm) + 15), 
    name = as.character(expression(atop(Delta*D==15*'ppm',Delta*delta*D%~~%100*'‰')))
  )

  df %>% 
    dplyr::filter(start_inc_time == 0) %>%
    ggplot() +
    aes(x = inc_time, y = DF2H.ppm, label = name, group = name) + #, color = name) +
    #geom_smooth(method = "lm", formula = y ~ x + 0, se = FALSE) +
    geom_line(size = 0.5, color = "gray") +
    geom_line(data = calculate_DF2H_weighted_mean, size = 1.5, color = "black") +
    geom_point(mapping = aes(size = rel_amount), color = "gray") +
    geom_point(data = calculate_DF2H_weighted_mean, size = 6, shape = 25, color = "black", fill = "black") +
    ggrepel::geom_label_repel(
      data = function(df) {
        df <- filter(df, inc_time == 50)
        vctrs::vec_rbind(df, calculate_DF2H_weighted_mean(df))
      },
      min.segment.length = 0, seed = 7,
      nudge_x = 5, force = 3
    ) +
    geom_line(data = quant_limit, size = 2) +
    ggrepel::geom_label_repel(
      data = filter(quant_limit, DF2H.ppm == max(DF2H.ppm)),
      min.segment.length = 0, seed = 7,
      nudge_x = 10, nudge_y = 10,
      parse = TRUE
    ) +
    #facet_wrap(~compound, scales = "free_y") + 
    theme_figure(legend = FALSE) +
    scale_x_continuous(breaks = c(0:6) * 10) +
    expand_limits(x = 60) +
    labs(x = "incubation time [hrs]", y = expression(Delta*D~"[ppm]"))

}
```

## No glucose time course

```{r "time_course_no_glucose", warning=FALSE}
peaks_of_interest <- readxl::read_excel(file.path("data", "peaks_of_interest.xlsx"))

noglu_enrichment_data <- 
  labeling_rates %>% 
  right_join(peaks_of_interest, by = c("compound" = "mapping_name")) %>% 
  # include 1 hour time point? yes, important part of the trend
  #filter(inc_time != 1) %>% 
  filter(!with_glu)

p_noglu_time_course <- make_time_course_plot(noglu_enrichment_data)
p_noglu_time_course
```

## Glucose time course

```{r "time_course_glucose", fig.width=8, fig.height=6, warning=FALSE}
peaks_of_interest <- readxl::read_excel(file.path("data", "peaks_of_interest.xlsx"))

glu_enrichment_data <- 
  labeling_rates %>% 
  right_join(peaks_of_interest, by = c("compound" = "mapping_name")) %>% 
  # include 1 hr tp? --> makes it more confusing than one might think
  filter(inc_time != 1) %>% 
  filter(with_glu)

p_glu_time_course <- make_time_course_plot(glu_enrichment_data)
p_glu_time_course
```

# Growth rates

```{r}
make_growth_rate_plot <- function(df, mu_breaks, ylim, tps = c("0 to 6 hrs", "6 to 50 hrs")) {

  calculate_mu_weighted_mean <- function(df) {
    df %>% 
      summarize(
        mu.1_d = sum(mu.1_d * rel_amount) / sum(rel_amount),
        mu_min.1_d = sum(mu_min.1_d * rel_amount) / sum(rel_amount),
        mu_max.1_d = sum(mu_max.1_d * rel_amount) / sum(rel_amount),
        name = "weighted\nmean"
      )
  }

  df %>% 
    filter(gen.d > 0) %>% 
    filter(inc_time_label %in% tps) %>% 
    group_by(name) %>% 
    filter(length(mu.1_d) == length(tps)) %>% 
    summarize(
      n_estimates = n(),
      # these end up being very assymetric activities
      mu_min.1_d = min(mu.1_d),
      mu_max.1_d = max(mu.1_d),
      # weighted mean (by time interval length)
      mu.1_d = sum((inc_time - start_inc_time) * mu.1_d) / sum(inc_time - start_inc_time),
      rel_amount = mean(rel_amount)
    ) %>% 
    { bind_rows(., calculate_mu_weighted_mean(.)) } %>% 
    # sort by abundance
    arrange(mu.1_d) %>% 
    mutate(name = factor(name) %>% fct_inorder()) %>% 
    ggplot() +
    aes(name, mu.1_d) +
    geom_bar(data = function(df) filter(df, name != "weighted\nmean"), stat = "identity", fill = "gray") +
    geom_bar(data = function(df) filter(df, name == "weighted\nmean"), stat = "identity", fill = "gray30") +
    # geom_errorbar(
    #   data = function(df) filter(df, !is.na(mu_min.1_d)),
    #   mapping = aes(ymin = mu_min.1_d, ymax = mu_max.1_d),
    #   width = 0
    # ) +
    scale_x_discrete(drop=FALSE) +
    scale_y_continuous(
      breaks = mu_breaks,
      labels = function(x) {
        days <- round(log(2)/x)
        days <- ifelse(days > 30, paste(round(days/30, 1), "months"), paste(round(days), "days"))
        paste0(x, "/day\n~", days)
      },
      expand = c(0, 0)
    ) +
    expand_limits(y = ylim) +
    theme_figure(axis_x_rotate = 90) +
    theme() +
    labs(x = NULL, y = "apparent growth rate / generation time") +
    coord_flip()
}
```

## No glucose growth rates

```{r "growth_rates)noglucose", fig.width=8, fig.height=6, warning=FALSE}
p_noglu_rates <- make_growth_rate_plot(noglu_enrichment_data, ylim = 0.018, mu_breaks = c(0.001, 0.005, 0.01, 0.015))
p_noglu_rates
```

## Glucose growth rates

```{r "growth_rates_glucose", fig.width=8, fig.height=6, warning=FALSE}
p_glu_rates <- make_growth_rate_plot(glu_enrichment_data, ylim = 0.085, mu_breaks = c(0.0023, 0.015, 0.031, 0.05, 0.071))
p_glu_rates
```

# Combined plot

## No glucose

```{r "labeling_plot_noglu", fig.width=12, fig.height=7, warning=FALSE}
library(cowplot)
plot_grid(
  p_noglu_time_course,
  p_noglu_rates,
  labels = "AUTO", 
  rel_widths = c(1, 1),
  align = "h"
)
```

## Glucose

```{r "labeling_plot_glu", fig.width=12, fig.height=7, warning=FALSE}
library(cowplot)
plot_grid(
  p_glu_time_course,
  p_glu_rates,
  labels = "AUTO", 
  rel_widths = c(1, 1),
  align = "h"
)
```

# Abundances

```{r "peak_abundances"}
# what do the abundances look like?
# NOTE: make sure that peak intregrations are all correct, they migt be off by quite a bit
vctrs::vec_rbind(
  glu_enrichment_data,
  noglu_enrichment_data,
) %>% 
  arrange(inc_time) %>% 
  mutate(
    x = paste(inc_time, "hrs") %>% factor() %>% fct_inorder(),
    glu = ifelse(with_glu, "+glucose", "no glucose")
  ) %>% 
  group_by(with_glu, inc_time) %>% 
  mutate(rel_amount = rel_amount / sum(rel_amount)) %>% 
  ggplot()+
  aes(paste(inc_time, "hrs"), rel_amount, fill = name) +
  geom_bar(stat = "identity") +
  labs(x = "sample") +
  facet_wrap(~glu)
```

# ===== OLD CODE =====

# all growth data

```{r, eval=FALSE}
calc_data %>% 
  filter(
    !is.na(u.1_hr), 
    u.1_hr > 0
  ) %>% 
  mutate(
    `var µ [1/day]` = u.1_d,
    `var T [days]` = gen.d,
    `var Amt [%]` = 100 * rel_amount_present
  ) %>% 
  gather(key = "variable", value = "value", starts_with("var")) %>% 
  mutate(variable = str_remove(variable, "^var ") %>% factor() %>% fct_inorder()) %>% 
  ggplot() +
    aes(compound, y = value, fill = factor(inc_time)) +
    geom_bar(stat = "identity", position = "dodge") +
    facet_grid(variable ~ panel, scales = "free_y", switch = "y") +
    labs(x = NULL, y = NULL) + 
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
#  coord_cartesian(y = c(0, 1000))
```

```{r, eval=FALSE}
calc_data %>% 
  filter(
    !is.na(u.1_hr), 
    u.1_hr > 0
  ) %>% 
  mutate(
    `var µ [1/day]` = u.1_d
  ) %>% 
  gather(key = "variable", value = "value", starts_with("var")) %>% 
  mutate(variable = str_remove(variable, "^var ") %>% factor() %>% fct_inorder()) %>% 
  ggplot() +
  aes(compound, y = value, fill = factor(inc_time)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(variable ~ panel, scales = "free_y", switch = "y") +
  labs(x = NULL, y = NULL) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
#  coord_cartesian(y = c(0, 1000))
```

# weighted growth data

```{r, eval=FALSE}
spread_data <- calc_data %>% 
  filter(!control) %>%  
  {
    full_join(
      filter(., with_glu) %>% select(inc_time, compound, with_glu_rel_amount = rel_amount_present, with_glu_u.1_mon = u.1_mon),
      filter(., !with_glu) %>% select(inc_time, compound, no_glu_rel_amount = rel_amount_present, no_glu_u.1_mon = u.1_mon),
      by = c("inc_time", "compound")
    ) %>% 
      mutate(mean_rel_amount = 0.5 * with_glu_rel_amount + 0.5 * no_glu_rel_amount)
  }
spread_data_sum <- spread_data %>% 
  group_by(inc_time) %>% 
  summarise(
    with_glu_u.1_mon = sum(with_glu_rel_amount * with_glu_u.1_mon) / sum(with_glu_rel_amount),
    no_glu_u.1_mon = sum(no_glu_rel_amount * no_glu_u.1_mon) / sum(no_glu_rel_amount),
    mean_rel_amount = 1
    # what is a good weighted measure of the mu distribution spread??
  ) 
spread_data_sum
```

```{r, eval=FALSE}
ggplot() +
  aes(no_glu_u.1_mon, with_glu_u.1_mon, shape = paste(inc_time, "hours")) +
  geom_abline(slope = 1, intercept = 0, color = 'orange') +
  xlab('Cell Turnover per Month: No Glucose') +
  ylab('Cell Turnover per Month: With Glucose') +
  # individual compounds
  #geom_path(data = spread_data, mapping = aes(color = compound, shape = NULL), alpha = 0.5) +
  #geom_point(data = spread_data, mapping = aes(color = compound, size = 100 * mean_rel_amount), alpha = 0.5) +
  # weighted means
  geom_path(data = spread_data_sum, mapping = aes(shape = NULL)) +
  geom_point(data = spread_data_sum, mapping = aes(size = 100 * mean_rel_amount)) +
  #coord_fixed(x = c(0, 15), y = c(0, 15))
  coord_fixed(x = c(0, 4), y = c(0, 4))

```

```{r, eval=FALSE}

mean_u <- read_csv(file.path("data", "weighted_mean_u.csv"))
mean_u %>%
ggplot() +
  aes(x = factor(inc_time), y = u.1_mon, fill = with_glu) +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme_bw() +
  xlab('Incuation Time') +
  ylab('Generations per Month')
ggsave(file.path("figures", "weighted_mean_u_bar.png"), width = 8, height = 8)
```

# control - look good

```{r, eval=FALSE}
calc_data %>% 
  filter(control) %>% 
  ggplot() +
  aes(compound, d2H, color = panel) +
  geom_point() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# FOR PROCESSING ONLY

# Export data

```{r, eval=FALSE}
irms_example_data <- 
  sample_files_w_ids %>%
  iso_filter_files(analysis == 5689) %>% 
  iso_get_peak_table() %>% 
  filter(compound != "H2") %>% 
  select(rt, rt_start, rt_end, amp2, area2) %>% 
  mutate(rel_height = amp2/sum(amp2) * 100) %>% 
  filter(rel_height > 1)

irms_example_data %>% 
  openxlsx::write.xlsx(file.path("tables", "gc_irms_single_sample_peak_table.xlsx"))
```

# Peak Mapping help

```{r, eval=FALSE}
tsq_example_data <- read_excel(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
```

```{r, eval=FALSE}
bind_rows(
  irms_example_data %>% mutate(type = "irms") %>% iso_strip_units(),
  tsq_example_data %>% mutate(type = "tsq")
) %>% 
  ggplot() +
  aes(rt, rel_height, label = paste0(`Peak Name`, "\n", round(rt))) +
  geom_bar(stat = "identity")+
  ggrepel::geom_text_repel(color = "red", alpha = 0.5, min.segment.length = 0)+
  facet_grid(type ~ .)
ggsave(file.path("figures", "irms_tsq_comparison2.pdf"), width = 12, height = 8)
```

### 2022-03-24 archive/template.Rmd
move to archive folder

---
title: "Analysis: NAME"
subtitle: "SUBTITLE"
author: "AUTHORS"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    css: stylesheet.css
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console
---

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(latex2exp)

# source functions
source(file.path("libs", "functions.R"))

# set global chunk options for figure output
figure_prefix <- "PREFIX-"
knitr::opts_chunk$set(
  dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path=file.path("figures", figure_prefix))
```

# Header A

```{r}
cars
```

# Header B

## Subheader C

```{r "cars", fig.width = 8, fig.height = 6}
cars %>% ggplot() + aes(speed, dist) + geom_point()
```

## Subheader D

```{r "latex", warning=FALSE}
iris %>% 
  mutate(
    latex_species = as_factor(Species) %>% 
      fct_recode(
        "$\\left(\\frac{\\textbf{setsoa}}{\\beta^2}\\right)$" = "setosa",
        "$\\int_{\\infinity}\\sqrt[2]_{\\textbf{versicolor}}$" = "versicolor")
  ) %>% 
  ggplot() + 
  aes(Sepal.Length, Sepal.Width, color = latex_species) + 
  geom_point() +
  scale_color_discrete(labels = latex_labeller) +
  facet_wrap(~latex_species, labeller = latex_labeller) +
  labs(x = TeX("my x axis $\\delta^{42}X\\,\\[\U2030\\]$")) + 
  theme_figure(text_size = 16)
```

### 2022-03-24 03_data_viz.Rmd
reconnecting to quantification script

---
title: "Paper Figures"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r, echo = FALSE, warning = FALSE, message=FALSE}
library(tidyverse)    # CRAN v1.3.1    
library(forcats)      # CRAN v0.5.1      
library(isoreader)    # CRAN v1.3.0    
library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
library(readxl)       # CRAN v1.3.1       
library(ggsci)        # CRAN v2.9        
library(ggborderline) # [github::wurli/ggborderline] v0.1.0 
library(ggrepel)      # CRAN v0.9.1      
library(latex2exp)    # CRAN v0.5.0    
library(ggdist)       # CRAN v3.0.0       
library(ggsignif)     # CRAN v0.6.2     
library(ggridges)     # CRAN v0.5.3     
library(ggalluvial)   # CRAN v0.12.3   
library(cowplot)      # CRAN v1.1.1      
library(scales)       # CRAN v1.1.1
```

# Load sourced functions

```{r}
# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromeleon.R"))
source(file.path("libs", "error_prop.R"))
source(file.path("libs", "calculate_turnover.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

# Setup

## Read RDS from cache

```{r workspace images}
# Turnover data
turnover <- readRDS("cache/turnover_rates")

# Weighted turnover data
turnover_weighted <- readRDS("cache/turnover_weighted")

# LH-SIP data
LH_SIP_data <- readRDS(file = "cache/LH_SIP_data")

# LH-SIP data but with 3d as the starting timepoint
LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
```

### Lit search data

```{r lit search data}
lit_turnover_w_ours <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
```

## Set color swatches

```{r color swatches}
tundra_color <- "#4ebad5"

grassland_color <- "#01a088"

conifer_color <- "#e64a35"

terrain_color_swatch <- c(conifer_color, grassland_color, tundra_color)
terrain_fill_swatch <- c(conifer_color, grassland_color, tundra_color)
```

# Plots

## Figure: Microbial turnover rate across soil types

```{r turnover_across_soil}
p_turnover_distributions <- turnover %>% 
  filter(inc_time_d == 7) %>%
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  mutate(terrain = forcats::fct_reorder(terrain, -u_d)) %>% 
  ggplot(
  aes(x = u_d, 
      y = terrain,
      color = terrain,
      fill = terrain)) +
  stat_slab(height = 0.5, 
            alpha = 0.7,
            color = "black") +
  stat_pointinterval(color = "black",
                     height = 0.2) +
  geom_point(
    color = "black",
    shape = 124,
    size = 5,
    alpha = 0.5,
    position = position_nudge(y = -.15)) +
  scale_x_log10(
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))
  ) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  theme_classic() +
  labs(y = "Soil Type",
       x = TeX("Turnover rate ($d^{-1}$)")) +
  theme(axis.text.y = element_text(hjust = 1),
        legend.position = "none")
p_turnover_distributions
```

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  group_by(terrain, inc_time_d) %>% 
  summarize(terrain = terrain,
            gen_d_weighted = gen_d_weighted) %>% 
  unique() %>% 
  ggplot(aes(x = terrain,
             y = gen_d_weighted,
             fill = terrain)) +
  geom_col(width = 0.5) +
  scale_fill_manual(values = terrain_fill_swatch) +
  labs(x = "Soil Type",
       y = "Community Generation Time (d)",
       caption = "Generation time weighted by compound relative abundance") +
  theme_classic() +
  theme(legend.position = "none")
p_gen_time_mean
```

```{r cowplot mooooo}
p_community_turnover_cow <- cowplot::plot_grid(
  p_turnover_distributions,
  p_gen_time_mean,
  labels = "AUTO",
  rel_widths = c(1,1),
  align = "h",
  nrow = 1
)

# 
# save_plot(filename = "fig_output/p_community_turnover_cow.png",
#           plot = p_community_turnover_cow,
#           base_height = 5,
#           base_width = 10
#           )

```

## Figure: Phyla FA profiles

```{r}
p_tax_FA <- fatty_acids_wide_with_tax %>% 
  select(-ID) %>% 
  # Remove Fungi from this plot
  filter(phylum != "Fungi") %>% 
  pivot_longer(cols = -phylum, 
               names_to = "FA",
               values_to = "rel_abund") %>%
  ggplot(aes(x = FA, 
             y = rel_abund,
             color = phylum)) +
  #stat_pointinterval(point_interval = "mean_qi") +
  geom_boxplot(
    outlier.shape = NA,
    alpha = 0.1
    ) +
  facet_wrap(vars(phylum), nrow = 1) +
  scale_color_futurama() +
  labs(y = "Relative Abundance",
       x = "",
       color = "Phylum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        legend.position = "NA",
        strip.text = element_text(size = 16)
        # legend.background = element_rect(
        #                           size=0.5, 
        #                           linetype="solid", 
        #                           colour ="black")
        )

p_tax_FA

# cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
#           plot = p_tax_FA,
#           base_height = 8,
#           base_width = 14
#           )
```

## Figure: Weighted turnover time

```{r 2H_plots}

peaks_mapped_summarized_wppm <- peaks_mapped_summarized %>% 
    mutate(at2H_ppm = at2H * 10000,
         at2H_mn_zero_ppm = at2H_mn_zero * 10000,
         at2H_weighted_ppm = at2H_weighted * 10000)

p_conifer_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Gordon Gulch Conifer Forest") %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = conifer_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = conifer_color,
             size = 3,
             alpha = 0.5) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Conifer Forest") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_conifer_2H

p_grassland_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Marshall Mesa Grassland") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                      y = at2H_weighted_ppm),
                      color = grassland_color,
                  size = 1.5) +
  geom_point(aes(x = inc_time_d,
                 y = at2H_weighted_ppm), 
                 color = grassland_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Grassland") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_grassland_2H

p_tundra_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Niwot Ridge Tundra") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = tundra_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = tundra_color,
                fill = tundra_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Tundra") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_tundra_2H
```

```{r}

p_tundra_2H_3d <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Niwot Ridge Tundra") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = tundra_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = tundra_color,
                fill = tundra_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Tundra") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_tundra_2H
```

```{r turnover_plots}
add_weighted_mean <- function(df) {
  df %>% 
    ungroup() %>% 
    mutate(type = "sample") %>% 
    add_row(compound = "Weighted Mean",
            u_d_weighted = df$u_d_weighted[1],
            terrain = df$terrain[1],
            u_d = df$u_d_weighted[1],
            type = "Weighted Mean")
}

# Add weighted generation time

summarized_weighted_gen_d <- gen_calc_data_summarized_weighted %>% 
  filter(inc_time_d == 7) %>% 
  select(terrain, gen_d_weighted) %>% 
  unique()

p_conifer_u_d <- gen_calc_data_summarized_weighted %>%
  filter(terrain == "Gordon Gulch Conifer Forest",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>%
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound,
               y = u_d, 
               fill = type)) +
  scale_fill_manual(values = c("#000000", conifer_color)) +
  # Secondary axis option:
  # scale_y_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
  #                                        breaks = c(7, 14, 30, 90, 365),
  #                                        name = "Generation time (d)")) +
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Conifer Forest") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))
p_conifer_u_d

p_grassland_u_d <- gen_calc_data_summarized_weighted %>% 
  filter(terrain == "Marshall Mesa Grassland",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound, y = u_d, fill = type)) +
  scale_fill_manual(values = c("#000000", grassland_color)) +
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Grassland") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))

p_tundra_u_d <- gen_calc_data_summarized_weighted %>% 
  filter(terrain == "Niwot Ridge Tundra",
         inc_time_d == 7) %>% 
  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
  add_weighted_mean() %>% 
  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
  # PLOT IT
  ggplot() +
  geom_col(aes(x = compound, y = u_d, fill = type)) +
  scale_fill_manual(values = c("#000000", tundra_color)) +
  # Add weighted generation time label
  coord_flip(ylim = c(0, 0.09), clip = "off") +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Tundra") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5))
p_tundra_u_d
```

```{r moo}
# HORIZONTAL
p_turnover_enrichment_cow_h <- cowplot::plot_grid(
  p_conifer_2H,
  p_grassland_2H,
  p_tundra_2H,
  p_conifer_u_d,
  p_grassland_u_d,
  p_tundra_u_d,
  labels = "AUTO",
  rel_widths = c(1,1),
  align = "h",
  nrow = 2
)

p_turnover_enrichment_cow_h
# 
# cowplot::save_plot(filename = "fig_output/p_turnover_enrichment_cow_horiz.pdf",
#           plot = p_turnover_enrichment_cow,
#           base_height = 8,
#           base_width = 12
#           )

# VERTICAL
p_turnover_enrichment_cow_v <- cowplot::plot_grid(
  p_conifer_2H,
  p_conifer_u_d,
  p_grassland_2H,
  p_grassland_u_d,
  p_tundra_2H,
  p_tundra_u_d,
  labels = "AUTO",
  rel_widths = c(1,1),
  align = "h",
  nrow = 3
)

p_turnover_enrichment_cow_v
# 
# cowplot::save_plot(filename = "fig_output/p_turnover_enrichment_cow_vertical.pdf",
#           plot = p_turnover_enrichment_cow_v,
#           base_height = 12,
#           base_width = 8
#           )
```

## Figure: Compound abundance vs. turnover

```{r}
gen_calc_data %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(x = rel_area_FID,
             y = u_d)) +
  geom_point(aes(color = chain_fctr)) +
  scale_color_viridis_d(option = "plasma") +
  facet_wrap(~terrain) +
  labs(x = "Relative Area (GC-FID)",
       y = TeX("$Turnover (d^{-1})$"),
       color = "Compound class") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        strip.background = element_blank())
```

## Meta analysis of turnover rates reported in literature

Generation time is related to the turnover rate as below:
$$
g = \frac{ln(2)}{\mu}
$$

```{r}
# Import lit search data
lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))
lit_turnover <- lit_turnover %>% 
  # Arrange by turnover time
  arrange(u_d_mn) %>% 
  # Reassign n values
  mutate(n = seq(from = 1, to = nrow(lit_turnover)))

# Our summarized data
gen_calc_mini <- gen_calc_data_summarized %>% 
  # Calculate mean per terrain per inc time
  group_by(inc_time_d, terrain) %>% 
  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
            u_d_max = max(u_d),
            u_d_min = min(u_d)) %>%
  # Calculate mean of means (combine inc_times)
  group_by(terrain) %>% 
  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
            u_d_max = max(u_d_mn, na.rm = TRUE),
            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
  # Rename to match `lit_turnover` tibble
  arrange(u_d_mn) %>% 
  mutate(method = "2H Lipid SIP",
         method_type = "2H-Lipid-SIP",
         n = c(17, 18, 19),
    soil_type = case_when(
      terrain == "Niwot Ridge Tundra" ~ "tundra",
      terrain == "Gordon Gulch Conifer Forest" ~ "conifer forest",
      terrain == "Marshall Mesa Grassland" ~ "grassland")
  )
# Add in our data! ^_^
lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)

lit_turnover_w_ours <- lit_turnover_w_ours %>% 
  mutate(
    source = case_when(
      method == "2H Lipid SIP" ~ "This study",
      TRUE ~ "Literature values"
  )) %>% 
  # Add in generation times of u_d mean value
  left_join(summarized_weighted_gen_d, by = "terrain") %>% 
  mutate(gen_d_weighted = case_when(
    is.na(gen_d_weighted) ~ log(2)/u_d_mn,
    TRUE ~ gen_d_weighted
    )
  )
```

## Literature Rates of Cell Turnover by Method

```{r lit rates}
literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7", "#ffb1ad")

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(
    aes(x = n,
        y = u_d_mn,
        fill = method_type
        )
    ) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = literature_values_swatch) +
  labs(y = TeX("Turnover (d$^{-1}$)")) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5))

# cowplot::save_plot(filename = "fig_output/p_lit_turnover_w_ours.pdf",
#                    plot = p_lit_turnover_w_ours,
#                    base_height = 8,
#                    base_width = 10)
```

```{r}
# By terrain  
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(label = "This study",
            x = 18,
            y = 0.13,
            color = "black") +
  geom_label(label = "Literature values",
            x = 9,
            y = 0.6,
            color = "black") +
  #scale_y_log10() +
  #annotation_logticks(sides = "l") +
  coord_cartesian(
    xlim = c(0, 20),
    ylim = c(0, 0.80), 
    expand = FALSE) +
  labs(y = "Mean Turnover Time (d^-1)",
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
## With log scale
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(label = "This study",
            x = 18,
            y = 0.10,
            color = "black") +
  geom_label(label = "Literature values",
            x = 9,
            y = 0.35,
            color = "black") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(y = "Mean Turnover Time (d^-1)",
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
```

```{r}
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(aes(
    x = 9,
    y = 0.4),
            label = "Literature values",
            color = "black") +
  geom_label(aes(
    x = 18,
    y = .1),
             label = "This study",
             color = "black") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(y = TeX("Mean turnover rate ($d^{-1}$)"),
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
```

## Meta analysis of turnover rates in literature, grouped by method

```{r}
p_lit_turnover_across_method <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(y = n, 
             x = u_d_mn,
             color = source)) +
  geom_segment(aes(x = 0, xend = u_d_mn, yend = n),
               color = "black") +
  geom_point(size = 3) +
  geom_text_repel(aes(label = method),
                  color = "black",
                  size = 3.5,
                  segment.color = NA,
                  nudge_x = 1,
                  segment.curvature = -0.1,
                  segment.angle = -20,
                  segment.ncp = 3,
                  segment.size = 0.1) +
  scale_color_manual(values = c("#000000", "#1986bd")) +
  #scale_x_log10(breaks = c(0.01, 0.05, 0.1, 0.5)) +
  #annotation_logticks(sides = "b") +
  scale_x_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
                                         breaks = c(1, 3, 5, 7, 14, 30, 365),
                                         labels = c("1 Day", "3 Days", "5 Days", "1 Week", "2 Weeks", "1 Month", "1 Year"),
                                         name = "Generation time")) +
  coord_cartesian(xlim = c(0, 0.8), ylim = c(0, 20), expand = FALSE) +
  labs(x = TeX("Mean turnover rate ($d^{-1}$)"),
       color = "Source") +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom",
        axis.text.x.top = element_text(angle = 30, hjust = 0)
        )

p_lit_turnover_across_method
```

```{r}
cowplot::save_plot(filename = "fig_output/p_lit_turnover_across_method.png",
          plot = p_lit_turnover_across_method,
          base_height = 6,
          base_width = 8)
```

## Compare extraction efficiency

```{r extr_eff}
FID_results_abundance_reported_long <- FID_results_abundance_no_stds %>% 
  select(
    sample_id, 
    compound, 
    deriv_efficiency, 
    extr_efficiency
  ) %>% 
  pivot_longer(
    !c(sample_id, compound),
    names_to = "stage", 
    values_to = "efficiency"
  ) %>% 
  mutate(
    stage = case_when(
      str_detect(stage, "deriv") ~ "Derivatization Efficiency",
      str_detect(stage, "extr") ~ "Extraction Efficiency"
    )
  )

FID_results_abundance_reported_long %>% 
  ggplot(aes(x = stage, y = efficiency)) +
  geom_boxplot(
    outlier.shape = NA,
    width = 0.3
    ) +
  coord_cartesian(ylim = c(0, 1.1)) +
  labs(x = "",
       y = "Efficiency") +
  theme_classic()
```

## Turnover versus abundance

```{r}
p_turnover_vs_abundance <- gen_calc_data %>% 
  ggplot(
    aes(x = u_d,
        y = compound_ug_ext,
        color = terrain
    )
  ) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = terrain_color_swatch) +
  facet_wrap(vars(terrain)) +
  labs(
    x = TeX("Turnover rate ($d^{-1}$)"),
    y = "Extracted compound mass (µg)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

save_plot(
  filename = "fig_output/p_turnover_vs_abundance.pdf", 
  plot = p_turnover_vs_abundance,
  base_height = 3,
  base_width = 7
  )
```

## Example chromatogram
```{r}
# plot an example chromatogram

sample_files[10] %>% # choosing arbitrary file to plot
  iso_plot_continuous_flow_data(
# select data and aesthetics
data = c(2), color = id1, panel = id1,
# zoom in on time interval
time_interval = c(750, 4000),
# peak labels for all peaks > 2V
peak_bounds = TRUE,
peak_marker = FALSE,
peak_label = iso_format(rt),
#peak_label_size = 3,
peak_label_filter = analysis == 5685 & amp2 > 1
+ scale_color_npg() +
theme_classic() +
theme(strip.background = element_blank()))
```

## Assimilation efficiency error propagation

```{r}
p_gen_calc_errorprop <- gen_calc_errorprop %>%
  mutate(u_d = case_when(
    is.na(u_d) ~ 0,
    TRUE ~ u_d
  )) %>% filter(inc_time_d_str != "0 Days") %>% 
  ggplot(aes(x = a,
             y = u_d,
             color = compound,
             group = compound)) +
    geom_smooth(method = "lm",
                formula = "y~x") +
  facet_wrap(vars(terrain, inc_time_d_str),
             ncol = 2) +
  labs(x = "Assimilation efficiency (a)",
       y = TeX("Turnover rate ($d^{-1}$)"),
       color = "Compound"
       ) +
  theme_bw()

p_gen_calc_errorprop
```

```{r cowplot moo}
save_plot(filename = "fig_output/p_gen_calc_error_prop.pdf",
          plot = p_gen_calc_errorprop,
          base_height = 12,
          base_width = 8
          )
```

### 2022-03-24 01_LH-SIP_Data_Reduction.Rmd
add weighted

--- 2022-03-23 00_LH-SIP_Data_Reduction.Rmd
@@
 ```
+
+# Export
+```{r}
+# Reduce the 0d --> 3d --> 7d incubation data
+peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
+  mutate(time_course = "0d -->") %>%
+  # Column reduction
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         rel_area_FID,
+         area_FID,
+         d2H_mn_zero,
+         d2H,
+         at2H_mn_zero,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_zero,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Turn all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+
+peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
+  # Filter out 0d data points from this dataset
+  filter(inc_time_d != 0) %>% 
+  # Add a time course tag
+  mutate(time_course = "3d -->") %>% 
+  # Column reduction
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         rel_area_FID,
+         area_FID,
+         d2H_mn_three,
+         d2H,
+         at2H_mn_three,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_three,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Convert all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+
+# Export as RDS
+saveRDS(peaks_mapped_with_zeros_analytes_reduced,
+        file = "cache/LH_SIP_data")
+
+saveRDS(peaks_mapped_with_threes_analytes_reduced,
+        file = "cache/LH_SIP_data_3d_onwards")
+
+saveRDS(F_L_2F,
+        file = "cache/heavy_label_data")
+```

### 2022-03-24 02_LH-SIP_Quantification.Rmd
add weighted dF

@@
     # Explicitly define incubation parameters:
-    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
-    a = 0.6, # assimilation efficiency
+    # label is adjusted for the actual isotopic composition of the label within a specific terrain
+    f_label = F_label_mn,
+     # assimilation efficiency
+    a = 0.6,
     # start time
@@
       time_course == "3d -->" ~ at2H_mn_three),
-    f_t = `2F_alk`, # use PAME-corrected 2F value
-
+    # use PAME-corrected 2F value
+    f_t = `2F_alk`,
+    # delta 2F: change in 2F enrichment over time t
+    dF = case_when(
+      f_t - f_start >= 0 ~ f_t - f_start,
+      f_t - f_start < 0 ~ 0),
     # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
@@
 
+# Create weighted turnover
+
+```{r}
+# Create a summarized dataframe grouped by experimental replicates
+turnover_summarized <- turnover %>% 
+  group_by(
+    time_course,
+    terrain, 
+    inc_time_d, 
+    compound
+  ) %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
+  summarize_if(
+    is.numeric, 
+    mean, 
+    na.rm = TRUE
+  )
+
+# Weight
+weighted_time_course <- turnover_summarized %>% 
+  group_by(
+    terrain, 
+    inc_time_d
+  ) %>%
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
+  summarize(
+    at2H_weighted = 
+      sum(at2H * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE)
+  )
+
+turnover_summarized_weighted <- 
+  left_join(turnover_summarized, 
+            weighted_time_course,
+            by = c("terrain", "inc_time_d")
+  ) %>% 
+  group_by(
+    terrain, 
+    inc_time_d
+  ) %>%
+  summarize(
+    u_d_weighted = 
+      sum(u_d * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    gen_d_weighted = 
+      sum(gen_d * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    dF_weighted = 
+      sum(dF * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE)
+    )
+
+```
+
 # Export
@@
 turnover %>% saveRDS(file = "cache/turnover_rates")
+
+turnover_summarized_weighted %>% saveRDS(file = "cache/turnover_weighted")
 ```

### 2022-03-25 libs/turnover_to_gen.R
Create turnover_to_gen.R

@@ -1,0 +1,13 @@
+#' Turnover rate to generation time
+#' @param mu a rate of turnover in units turnover per unit time
+#' @return generation time/doubling time in units of t
+#' 
+
+turnover_to_gen <- function(mu) {
+  return(
+    case_when(
+      mu < 0 ~ 0,
+      mu >= 0 ~ log(2) / mu
+    )
+  )
+}

### 2022-03-25 03_data_viz.Rmd
add cache import

@@
 LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
+
+# BacDive Data
+bacdive_FA <- readRDS(file = "cache/bacdive_FA")
+bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")
 ```

### 2022-03-25 02_LH-SIP_Quantification.Rmd
weighted turnover calculations

--- 2022-03-24 02_LH-SIP_Quantification.Rmd
@@
 source(file.path("libs", "error_prop.R"))                 # Error Propagation
-source(file.path("libs", "calculate_turnover.R"))         # Turnover Calculator
+source(file.path("libs", "calculate_turnover.R"))         # Calculate turnover rate
+source(file.path("libs", "turnover_to_gen.R"))            # Turnover rate to generation time
 `%nin%` = Negate(`%in%`)                                  # "Not In" function
@@
       ),
-    # "negative" turnovers are artifacts of noise and should be zero
-    u_d = if_else(u_d < 0, 0, u_d),
     # calculate generation time, converting negatives to zero
-    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
+    gen_d = turnover_to_gen(u_d),
 
@@
 
+# Create weighted turnover
+
+```{r}
+# Create a summarized dataframe grouped by experimental replicates
+turnover_summarized <- turnover %>% 
+  group_by(
+    time_course,
+    terrain, 
+    inc_time_d, 
+    compound
+  ) %>% 
+  summarize_if(
+    is.numeric, 
+    mean, 
+    na.rm = TRUE
+  )
+
+# Summarize by combining experimental replicates
+
+LH_SIP_data_summarized <- LH_SIP_data %>% 
+  group_by(
+    terrain, 
+    inc_time_d, 
+    compound
+  ) %>% 
+  # FILTER OUT NON BACTERIAL COMPOUNDS
+  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
+  summarize_if(
+    is.numeric, 
+    mean, 
+    na.rm = TRUE
+  )
+
+weighted_time_course <- LH_SIP_data_summarized %>%
+  group_by(
+    terrain, 
+    inc_time_d
+  ) %>% 
+  dplyr::summarize(
+    # Weight at2H
+    at2H_weighted = 
+      sum(at2H * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    # Weight `2F_alk`
+    `2F_alk_weighted` = 
+      sum(`2F_alk` * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    # Keep these:
+    f_label = mean(F_label_mn, na.rm = TRUE),
+    a = 0.6,
+    t0 = 0,
+    d_t = inc_time_d - t0, # change in time
+    f_start = mean(at2H_mn_zero, na.rm = TRUE),
+    f_t = `2F_alk_weighted`,
+    dF = `2F_alk_weighted` - f_start
+  ) %>%
+  dplyr::summarize_if(
+    is.numeric,
+    mean,
+    na.rm = TRUE
+  ) %>%
+  mutate(
+    u_d_weighted = calculate_turnover(
+      a = a,
+      FT = f_t,
+      F0 = f_start,
+      FL = f_label,
+      t = d_t
+    ),
+    gen_d_weighted = turnover_to_gen(u_d_weighted)
+  )
+```
+
 # Export
@@
 turnover %>% saveRDS(file = "cache/turnover_rates")
+
+weighted_time_course %>% saveRDS(file = "cache/turnover_weighted")
 ```

### 2022-03-25 02_bacdive_taxonomy.Rmd
rename
took out plotting --> dataviz

--- 2021-10-27 qSIP_taxonomy.Rmd
@@
 
-# Plot Averages
+# Export
 
 ```{r}
-fatty_acids_wide_with_tax %>% 
-  group_by(phylum) %>% 
-  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
-  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
-  ggplot(aes(x = FA, 
-             y = `Relative Abundance`,
-             color = phylum,
-             fill = phylum)) +
-  geom_col() +
-  facet_wrap(vars(phylum)) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1),
-        legend.position = "none")
-```
+fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide")
 
-## Acidobacteria
-
-```{r}
-fatty_acids_wide_with_tax %>% 
-  group_by(phylum) %>% 
-  summarize_if(is.numeric, mean, na.rm = TRUE) %>% 
-  pivot_longer(cols = -phylum, values_to = "Relative Abundance", names_to = "FA") %>% 
-  filter(phylum == "Acidobacteria") %>% 
-  ggplot(aes(x = FA, 
-             y = `Relative Abundance`,
-             color = phylum,
-             fill = phylum)) +
-  geom_col() +
-  facet_wrap(vars(phylum)) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1),
-        legend.position = "none")
-```
-
-## Proteobacteria
-
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Proteobacteria") %>% 
-  ggplot(aes(y = u_d, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Proteobacteria") +
-  theme_bw()
-```
-
-## Actinobacteria
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Actinobacteria") %>% 
-  ggplot(aes(y = u_d, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Actinobacteria") +
-  theme_bw()
-```
-
-## Acidobacteria
-
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Acidobacteria") %>% 
-  ggplot(aes(y = u_d, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Acidobacteria") +
-  theme_bw()
-```
-
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Firmicutes") %>% 
-  ggplot(aes(y = u_d, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Firmicutes") +
-  theme_bw()
-```
-
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Bacteroidetes") %>% 
-  ggplot(aes(y = u_d, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Bacteroidetes") +
-  theme_bw()
+fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA")
 
 ```
-
-```{r}
-FA_w_turnover %>% 
-  filter(phylum == "Actinobacteria") %>% 
-  ggplot(aes(y = rel_area_FID, 
-             x = `Relative Abundance`,
-             fill = u_d,
-             color = u_d)) +
-  geom_point() +
-  geom_smooth(se = FALSE,
-              method = "lm",
-              size = 0.5) +
-  geom_label_repel(aes(label = FA),
-                   color = "black",
-                   fill = "white") +
-  labs(title = "Actinobacteria") +
-  theme_bw()
-```

### 2022-03-29 02_LH-SIP_Quantification.Rmd
added weighting

@@
 ---
-title: "01_LH-SIP_Quantification"
+title: "02_LH-SIP_Quantification"
 author: "Tristan Caro"
@@
   ) %>% 
-  summarize_if(
+  dplyr::summarize_if(
     is.numeric, 
@@
     f_t = `2F_alk_weighted`,
-    dF = `2F_alk_weighted` - f_start
+    dF_weighted = case_when(
+      f_t - f_start >= 0 ~ f_t - f_start,
+      f_t - f_start < 0 ~ 0),
   ) %>%
@@
 
+turnover_summarized %>% saveRDS(file = "cache/turnover_summarized")
+
 weighted_time_course %>% saveRDS(file = "cache/turnover_weighted")

### 2022-03-29 03_data_viz.Rmd
added weighting

@@
 ---
-title: "Paper Figures"
+title: "03 Data Vizualization"
 author: "Tristan Caro"
@@
 
+# Summarized turnover
+
+turnover_summarized <- readRDS("cache/turnover_summarized")
+
 # Weighted turnover data
@@
 
-## Figure: Microbial turnover rate across soil types
+## Microbial turnover rate across soil types
 
@@
 
-## Figure: Phyla FA profiles
+## Phyla FA profiles
 
@@
 
-## Figure: Weighted turnover time
+## dF
+
+```{r}
+p_dF <- turnover_summarized %>% 
+  filter(time_course == "0d -->") %>% 
+  ungroup() %>% 
+  select(terrain, inc_time_d, compound, dF) %>%
+  left_join(
+    turnover_weighted %>% 
+      select(terrain, inc_time_d, dF_weighted), 
+    by = c("terrain", "inc_time_d")) %>% 
+  group_by(
+    terrain,
+    inc_time_d
+  ) %>% 
+  pivot_longer(
+    cols = c(dF, dF_weighted),
+    values_to = "dF", 
+    names_to = "type"
+  ) %>% view()
+
+  ggplot(
+    aes(
+      x = inc_time_d,
+      y = dF
+    )
+  ) +
+  # Weighted data here:
+  geom_line(aes(
+    x = inc_time_d,
+    y = dF_weighted,
+    color = terrain),
+    size = 1.5,
+    alpha = 0.5
+    ) +
+  geom_point(
+    aes(
+      x = inc_time_d,
+      y = dF_weighted,
+      color = terrain,
+      fill = terrain),
+    size = 2,
+    alpha = 0.5
+    ) +
+  # Unweighted data here:
+  geom_borderline(
+    data = turnover_summarized,
+    aes(group = compound),
+    color = "gray"
+) +
+  geom_point(
+    data = turnover_summarized,
+    size = 2,
+    alpha = 0.5
+    ) +
+  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
+  coord_cartesian(
+    xlim = c(0, 8),
+    clip = "off"
+    ) +
+  facet_wrap(vars(terrain),
+             nrow = 1) +
+  labs(x = "Incubation Time (Days)",
+       y = TeX("$ \\Delta ^2H$ (at%)"),
+       ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  theme_classic() +
+  theme(legend.position = "none",
+        strip.background = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        axis.title.x = element_text(size = 10))
+
+p_dF
+```
 
@@
 
-## Figure: Compound abundance vs. turnover
+## Compound abundance vs. turnover
 

### 2022-03-29 01_LH-SIP_Data_Reduction.Rmd
added assim efficiency calculations

--- 2022-03-23 00_LH-SIP_Data_Reduction.Rmd
@@
 ---
-title: "00_LH-SIP_Data_Reduction"
+title: "01_LH-SIP_Data_Reduction"
 author: "Tristan Caro"
@@
 # Load data
+
+## Load lipid d2H assimilation efficiency data
+
+```{r}
+d2H_assim <- read_xlsx("data/d2H_data_isotope_measurements.xlsx", sheet = 'lipids')
+```
 
@@
 ```
+
+## Reduce columns
+
+```{r}
+# Reduce the 0d --> 3d --> 7d incubation data
+peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>% 
+  mutate(time_course = "0d -->") %>%
+  # Column reduction
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         rel_area_FID,
+         area_FID,
+         d2H_mn_zero,
+         d2H,
+         at2H_mn_zero,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_zero,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Turn all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+
+peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
+  # Filter out 0d data points from this dataset
+  filter(inc_time_d != 0) %>% 
+  # Add a time course tag
+  mutate(time_course = "3d -->") %>% 
+  # Column reduction
+  select(file_id,
+         sample_id,
+         terrain,
+         soil,
+         inc_time_d,
+         inc_time_d_str,
+         compound,
+         rel_area_FID,
+         area_FID,
+         d2H_mn_three,
+         d2H,
+         at2H_mn_three,
+         F_0_at2H_se,
+         at2H,
+         area2_mn_three,
+         area2,
+         area_FID,
+         compound_ug_per_g_soil,
+         `2F_Me`,
+         `2F_FAME`,
+         `2F_alk`,
+         F_label_mn,
+         F_label_se,
+         time_course
+  ) %>% 
+  # Convert all unit dbls into unitless
+  mutate(
+    across(
+      where(is.numeric),
+      as.numeric
+    )
+  )
+```
+
+# Assimilation efficiency
+
+## Reduce data and get linear model
+
+```{r}
+d2H_assim_lm <- d2H_assim %>% 
+  # Select columns of interest
+  select(
+    org_id,
+    exp_id,
+    Analyte,
+    `Water dD`,
+    `Lipid dD`
+  ) %>% 
+  drop_na() %>% 
+  # Group by organism, experiment, analyte
+  group_by(
+    org_id,
+    exp_id,
+    Analyte
+  ) %>% 
+  # Filter out samples with three or fewer observations
+  # (so that we can do a linear model)
+  filter(n() > 3) %>% 
+  tidyr::nest(
+    data = c(`Water dD`, `Lipid dD`)
+  ) %>% 
+  mutate(
+    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
+    estimates = purrr::map(fit, broom::tidy),
+    summary = purrr::map(fit, broom::glance)
+  ) %>% tidyr::unnest(estimates)
+
+# Simplify by only looking at the slopes
+d2H_assim_lm_summary <- d2H_assim_lm %>% 
+  filter(term == "`Water dD`")
+```
+
+# Export
+```{r}
+# Export as RDS
+saveRDS(peaks_mapped_with_zeros_analytes_reduced,
+        file = "cache/LH_SIP_data")
+
+saveRDS(peaks_mapped_with_threes_analytes_reduced,
+        file = "cache/LH_SIP_data_3d_onwards")
+
+saveRDS(F_L_2F,
+        file = "cache/heavy_label_data")
+
+saveRDS(d2H_assim_lm_summary,
+        file = "cache/d2H_assimilation")
+```

### 2022-03-29 03_data_viz.Rmd
Update 03_data_viz.Rmd

@@
 
-## Microbial turnover rate across soil types
+## Turnover distributions
 
@@
     names_to = "type"
-  ) %>% view()
+  ) %>%
 
@@
 
-peaks_mapped_summarized_wppm <- peaks_mapped_summarized %>% 
+peaks_mapped_summarized_wppm <- turnover_summarized %>% 
     mutate(at2H_ppm = at2H * 10000,

### 2022-03-29 02_LH-SIP_Quantification.Rmd
updated assimilation efficiency to use calculated values of a and sa

@@
     f_label = F_label_mn,
-     # assimilation efficiency
-    a = 0.6,
     # start time
@@
     u_d = calculate_turnover(
-      a = a, # Assimilation efficiency
+      a = a, # Assimilation efficiency defined in data reduction step
       FT = f_t, # 2F at time t (at%)
@@
       sF_T = 0,
-      sa = 0
+      sa = sa
     )

### 2022-03-29 01_LH-SIP_Data_Reduction.Rmd
moved assimilation efficiency chunk up

@@
   )
+```
+
+# Assimilation efficiency
+
+## Reduce data and get linear model
+
+```{r}
+# Find Fatty acid analytes manually
+
+fas_in_d2H_assim <- d2H_assim %>% 
+  filter(str_detect(Analyte, "acid") |
+           str_detect(Analyte, "ate")) %>% 
+  pull(Analyte) %>% 
+  unique()
+
+d2H_assim_lm <- d2H_assim %>% 
+  # Select columns of interest
+  select(
+    org_id,
+    exp_id,
+    Analyte,
+    `Water dD`,
+    `Lipid dD`
+  ) %>% 
+  # Filter to only look at FAs
+  filter(Analyte %in% fas_in_d2H_assim) %>% 
+  drop_na() %>% 
+  # Group by organism, experiment, analyte
+  group_by(
+    org_id,
+    exp_id,
+    Analyte
+  ) %>% 
+  # Filter out samples with three or fewer observations
+  # (so that we can do a linear model)
+  filter(n() > 3) %>% 
+  tidyr::nest(
+    data = c(`Water dD`, `Lipid dD`)
+  ) %>% 
+  mutate(
+    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
+    estimates = purrr::map(fit, broom::tidy),
+    summary = purrr::map(fit, broom::glance)
+  ) %>% tidyr::unnest(estimates)
+
+# Simplify by only looking at the slopes
+# This is what gets added to the peaks_mapped dataframes!
+d2H_assim_lm_summary <- d2H_assim_lm %>% 
+  ungroup() %>% 
+  filter(term == "`Water dD`") %>% 
+  summarize(sa = sd(estimate, na.rm = TRUE),
+            a_mn = mean(estimate, na.rm = TRUE))
 ```
@@
     )
+  ) %>% 
+  # Add assimilation efficiency data
+  mutate(
+    a = d2H_assim_lm_summary$a_mn,
+    sa = d2H_assim_lm_summary$sa
   )
@@
     )
+  ) %>% 
+  # Add assimilation efficiency data
+  mutate(
+    a = d2H_assim_lm_summary$a_mn,
+    sa = d2H_assim_lm_summary$sa
   )
-```
 
-# Assimilation efficiency
-
-## Reduce data and get linear model
-
-```{r}
-d2H_assim_lm <- d2H_assim %>% 
-  # Select columns of interest
-  select(
-    org_id,
-    exp_id,
-    Analyte,
-    `Water dD`,
-    `Lipid dD`
-  ) %>% 
-  drop_na() %>% 
-  # Group by organism, experiment, analyte
-  group_by(
-    org_id,
-    exp_id,
-    Analyte
-  ) %>% 
-  # Filter out samples with three or fewer observations
-  # (so that we can do a linear model)
-  filter(n() > 3) %>% 
-  tidyr::nest(
-    data = c(`Water dD`, `Lipid dD`)
-  ) %>% 
-  mutate(
-    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
-    estimates = purrr::map(fit, broom::tidy),
-    summary = purrr::map(fit, broom::glance)
-  ) %>% tidyr::unnest(estimates)
-
-# Simplify by only looking at the slopes
-d2H_assim_lm_summary <- d2H_assim_lm %>% 
-  filter(term == "`Water dD`")
 ```

### 2022-04-06 03_data_viz.Rmd
updated literature turnover plot

@@
 ```{r lit search data}
-lit_turnover_w_ours <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
+lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
+turnover_means <- turnover_weighted %>% 
+  filter(inc_time_d == 7) %>%
+  select(terrain, u_d_weighted) %>% 
+  rename(u_d_mn = u_d_weighted) %>% 
+  mutate(comment = terrain) %>% 
+  mutate(n = case_when(
+    terrain == "Niwot Ridge Tundra" ~ 3,
+    terrain == "Gordon Gulch Conifer Forest" ~ 1,
+    terrain == "Marshall Mesa Grassland" ~ 2
+  )) %>% 
+  mutate(method = "LH-SIP",
+         method_type = "LH-SIP")
+
+lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means)
 ```
@@
 
-Generation time is related to the turnover rate as below:
-$$
-g = \frac{ln(2)}{\mu}
-$$
-
 ```{r}
@@
   ggplot(
-    aes(x = n,
+    aes(x = -n,
         y = u_d_mn,
@@
   geom_col() +
-  coord_flip() +
+  coord_flip(ylim = c(0, 0.5)) +
   scale_fill_manual(values = literature_values_swatch) +
-  labs(y = TeX("Turnover (d$^{-1}$)")) +
+  labs(y = TeX("Turnover (d$^{-1}$)"),
+       fill = "Method") +
   theme_classic() +
   theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 0, hjust = 0.5),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
         axis.ticks.y = element_blank(),
         axis.text.y = element_blank(),
-        legend.position = "bottom",
-        plot.title = element_text(hjust = 0.5))
+        axis.title.x = element_text(size = 18),
+        #legend.position = "bottom",
+        plot.title = element_text(hjust = 0.5),
+        legend.position = c(0.85, 0.1),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank())
+p_lit_turnover_w_ours
 
-# cowplot::save_plot(filename = "fig_output/p_lit_turnover_w_ours.pdf",
-#                    plot = p_lit_turnover_w_ours,
-#                    base_height = 8,
-#                    base_width = 10)
+cowplot::save_plot(filename = "fig_output/literature_values.pdf",
+                   plot = p_lit_turnover_w_ours,
+                   base_height = 8,
+                   base_width = 10)
 ```
@@
 ```
-
-## Meta analysis of turnover rates in literature, grouped by method
 

### 2022-04-06 03_data_viz.Rmd
Update 03_data_viz.Rmd

@@
 source(file.path("libs", "calculate_turnover.R"))
+source(file.path("libs", "turnover_to_gen.R"))
 `%nin%` = Negate(`%in%`) # "Not In" function
@@
 
-lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means)
+lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means) %>% 
+  # Convert to generation time:
+  mutate(gen_d = turnover_to_gen(u_d_mn))
 ```
@@
   facet_wrap(vars(phylum), nrow = 1) +
-  scale_color_futurama() +
+  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
   labs(y = "Relative Abundance",
@@
 
-## Compound abundance vs. turnover
-
-```{r}
-gen_calc_data %>% 
-  filter(inc_time_d != 0) %>% 
-  ggplot(aes(x = rel_area_FID,
-             y = u_d)) +
-  geom_point(aes(color = chain_fctr)) +
-  scale_color_viridis_d(option = "plasma") +
-  facet_wrap(~terrain) +
-  labs(x = "Relative Area (GC-FID)",
-       y = TeX("$Turnover (d^{-1})$"),
-       color = "Compound class") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        strip.background = element_blank())
-```
-
-## Meta analysis of turnover rates reported in literature
-
-```{r}
-# Import lit search data
-lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))
-lit_turnover <- lit_turnover %>% 
-  # Arrange by turnover time
-  arrange(u_d_mn) %>% 
-  # Reassign n values
-  mutate(n = seq(from = 1, to = nrow(lit_turnover)))
-
-# Our summarized data
-gen_calc_mini <- gen_calc_data_summarized %>% 
-  # Calculate mean per terrain per inc time
-  group_by(inc_time_d, terrain) %>% 
-  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
-            u_d_max = max(u_d),
-            u_d_min = min(u_d)) %>%
-  # Calculate mean of means (combine inc_times)
-  group_by(terrain) %>% 
-  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
-            u_d_max = max(u_d_mn, na.rm = TRUE),
-            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
-  # Rename to match `lit_turnover` tibble
-  arrange(u_d_mn) %>% 
-  mutate(method = "2H Lipid SIP",
-         method_type = "2H-Lipid-SIP",
-         n = c(17, 18, 19),
-    soil_type = case_when(
-      terrain == "Niwot Ridge Tundra" ~ "tundra",
-      terrain == "Gordon Gulch Conifer Forest" ~ "conifer forest",
-      terrain == "Marshall Mesa Grassland" ~ "grassland")
-  )
-# Add in our data! ^_^
-lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)
-
-lit_turnover_w_ours <- lit_turnover_w_ours %>% 
-  mutate(
-    source = case_when(
-      method == "2H Lipid SIP" ~ "This study",
-      TRUE ~ "Literature values"
-  )) %>% 
-  # Add in generation times of u_d mean value
-  left_join(summarized_weighted_gen_d, by = "terrain") %>% 
-  mutate(gen_d_weighted = case_when(
-    is.na(gen_d_weighted) ~ log(2)/u_d_mn,
-    TRUE ~ gen_d_weighted
-    )
-  )
-```
-
 ## Literature Rates of Cell Turnover by Method
@@
 ```{r lit rates}
-literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7", "#ffb1ad")
+literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7")
+literature_values_swatch_2 <- c("#26AFE1", "#6269EB", "#E0187B")
 
 p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
+  filter(method_type != "Microscopy") %>% 
   # order by mean turnover rate
@@
         y = u_d_mn,
-        fill = method_type
+        fill = method_type,
+        label = round(gen_d, 1)
         )
@@
   geom_col() +
+  geom_text(nudge_y = 0.05, size = 2) +
   coord_flip(ylim = c(0, 0.5)) +
-  scale_fill_manual(values = literature_values_swatch) +
+  scale_fill_manual(values = literature_values_swatch_2) +
   labs(y = TeX("Turnover (d$^{-1}$)"),
@@
         legend.text = element_text(size = 15),
-        legend.title = element_blank())
+        legend.title = element_blank(),
+        plot.margin = margin(1,1,1.5,1.2, "in"))
 p_lit_turnover_w_ours
@@
                    base_width = 10)
-```
-
-```{r}
-# By terrain  
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = soil_type)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  scale_color_npg() +
-  geom_label(label = "This study",
-            x = 18,
-            y = 0.13,
-            color = "black") +
-  geom_label(label = "Literature values",
-            x = 9,
-            y = 0.6,
-            color = "black") +
-  #scale_y_log10() +
-  #annotation_logticks(sides = "l") +
-  coord_cartesian(
-    xlim = c(0, 20),
-    ylim = c(0, 0.80), 
-    expand = FALSE) +
-  labs(y = "Mean Turnover Time (d^-1)",
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        legend.position = "bottom")
-## With log scale
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = soil_type)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  scale_color_npg() +
-  geom_label(label = "This study",
-            x = 18,
-            y = 0.10,
-            color = "black") +
-  geom_label(label = "Literature values",
-            x = 9,
-            y = 0.35,
-            color = "black") +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  labs(y = "Mean Turnover Time (d^-1)",
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        legend.position = "bottom")
-```
-
-```{r}
-lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(x = n, 
-             y = u_d_mn,
-             color = soil_type)) +
-  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  scale_color_npg() +
-  geom_label(aes(
-    x = 9,
-    y = 0.4),
-            label = "Literature values",
-            color = "black") +
-  geom_label(aes(
-    x = 18,
-    y = .1),
-             label = "This study",
-             color = "black") +
-  scale_y_log10() +
-  annotation_logticks(sides = "l") +
-  labs(y = TeX("Mean turnover rate ($d^{-1}$)"),
-       color = "Soil Source") +
-  theme_classic() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.title.x = element_blank(),
-        legend.position = "bottom")
-```
-
-```{r}
-p_lit_turnover_across_method <- lit_turnover_w_ours %>%
-  # order by mean turnover rate
-  ggplot(aes(y = n, 
-             x = u_d_mn,
-             color = source)) +
-  geom_segment(aes(x = 0, xend = u_d_mn, yend = n),
-               color = "black") +
-  geom_point(size = 3) +
-  geom_text_repel(aes(label = method),
-                  color = "black",
-                  size = 3.5,
-                  segment.color = NA,
-                  nudge_x = 1,
-                  segment.curvature = -0.1,
-                  segment.angle = -20,
-                  segment.ncp = 3,
-                  segment.size = 0.1) +
-  scale_color_manual(values = c("#000000", "#1986bd")) +
-  #scale_x_log10(breaks = c(0.01, 0.05, 0.1, 0.5)) +
-  #annotation_logticks(sides = "b") +
-  scale_x_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
-                                         breaks = c(1, 3, 5, 7, 14, 30, 365),
-                                         labels = c("1 Day", "3 Days", "5 Days", "1 Week", "2 Weeks", "1 Month", "1 Year"),
-                                         name = "Generation time")) +
-  coord_cartesian(xlim = c(0, 0.8), ylim = c(0, 20), expand = FALSE) +
-  labs(x = TeX("Mean turnover rate ($d^{-1}$)"),
-       color = "Source") +
-  theme_classic() +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        axis.title.y = element_blank(),
-        legend.position = "bottom",
-        axis.text.x.top = element_text(angle = 30, hjust = 0)
-        )
-
-p_lit_turnover_across_method
-```
-
-```{r}
-cowplot::save_plot(filename = "fig_output/p_lit_turnover_across_method.png",
-          plot = p_lit_turnover_across_method,
-          base_height = 6,
-          base_width = 8)
 ```
@@
 
-## Turnover versus abundance
-
-```{r}
-p_turnover_vs_abundance <- gen_calc_data %>% 
-  ggplot(
-    aes(x = u_d,
-        y = compound_ug_ext,
-        color = terrain
-    )
-  ) +
-  geom_point(alpha = 0.5) +
-  scale_color_manual(values = terrain_color_swatch) +
-  facet_wrap(vars(terrain)) +
-  labs(
-    x = TeX("Turnover rate ($d^{-1}$)"),
-    y = "Extracted compound mass (µg)"
-  ) +
-  theme_bw() +
-  theme(
-    legend.position = "none",
-    strip.background = element_blank(),
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank()
-  )
-
-save_plot(
-  filename = "fig_output/p_turnover_vs_abundance.pdf", 
-  plot = p_turnover_vs_abundance,
-  base_height = 3,
-  base_width = 7
-  )
-```
-
 ## Example chromatogram
@@
 ```
-
-## Assimilation efficiency error propagation
-
-```{r}
-p_gen_calc_errorprop <- gen_calc_errorprop %>%
-  mutate(u_d = case_when(
-    is.na(u_d) ~ 0,
-    TRUE ~ u_d
-  )) %>% filter(inc_time_d_str != "0 Days") %>% 
-  ggplot(aes(x = a,
-             y = u_d,
-             color = compound,
-             group = compound)) +
-    geom_smooth(method = "lm",
-                formula = "y~x") +
-  facet_wrap(vars(terrain, inc_time_d_str),
-             ncol = 2) +
-  labs(x = "Assimilation efficiency (a)",
-       y = TeX("Turnover rate ($d^{-1}$)"),
-       color = "Compound"
-       ) +
-  theme_bw()
-
-p_gen_calc_errorprop
-```
-
-```{r cowplot moo}
-save_plot(filename = "fig_output/p_gen_calc_error_prop.pdf",
-          plot = p_gen_calc_errorprop,
-          base_height = 12,
-          base_width = 8
-          )
-```

### 2022-04-06 03_data_viz.Rmd
re-did bacdive FA plots

@@
 
-```
-
-## Phyla FA profiles
-
-```{r}
-p_tax_FA <- fatty_acids_wide_with_tax %>% 
-  select(-ID) %>% 
-  # Remove Fungi from this plot
-  filter(phylum != "Fungi") %>% 
-  pivot_longer(cols = -phylum, 
-               names_to = "FA",
-               values_to = "rel_abund") %>%
-  ggplot(aes(x = FA, 
-             y = rel_abund,
-             color = phylum)) +
-  #stat_pointinterval(point_interval = "mean_qi") +
-  geom_boxplot(
-    outlier.shape = NA,
-    alpha = 0.1
-    ) +
-  facet_wrap(vars(phylum), nrow = 1) +
-  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
-  labs(y = "Relative Abundance",
-       x = "",
-       color = "Phylum") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 90,
-                                   hjust = 1),
-        panel.grid = element_blank(),
-        strip.background = element_blank(),
-        legend.position = "NA",
-        strip.text = element_text(size = 16)
-        # legend.background = element_rect(
-        #                           size=0.5, 
-        #                           linetype="solid", 
-        #                           colour ="black")
-        )
-
-p_tax_FA
-
-# cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
-#           plot = p_tax_FA,
-#           base_height = 8,
-#           base_width = 14
-#           )
 ```
@@
 
+## BacDive FA profiles
+
+```{r}
+p_tax_FA <- bacdive_FA_wide %>% 
+  select(-ID) %>% 
+  pivot_longer(cols = -phylum, 
+               names_to = "FA",
+               values_to = "rel_abund") %>%
+  ggplot(aes(x = FA, 
+             y = rel_abund)) +
+  geom_jitter(aes(color = phylum),
+              size = 0.25,
+              alpha = 0.3) +
+  stat_pointinterval(point_interval = "median_qi",
+                     alpha = 0.65) +
+  facet_wrap(vars(phylum), nrow = 3) +
+  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
+  labs(y = "Relative Abundance (%)",
+       x = "",
+       color = "Phylum") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90,
+                                   hjust = 1),
+        panel.grid = element_blank(),
+        strip.background = element_blank(),
+        legend.position = "NA",
+        strip.text = element_text(size = 16)
+        )
+
+p_tax_FA
+
+cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
+          plot = p_tax_FA,
+          base_height = 11,
+          base_width = 9
+          )
+```
+
 ## Compare extraction efficiency

### 2022-04-06 03_data_viz.Rmd
add chromatogram and abund v turnover update

@@
 bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")
+
+# IRMS chromatogram data
+sample_files <- readRDS(file = "cache/sample_files")
 ```
@@
 # Plots
-
-## Turnover distributions
-
-```{r turnover_across_soil}
-p_turnover_distributions <- turnover %>% 
-  filter(inc_time_d == 7) %>%
-  mutate(terrain = case_when(
-    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
-    terrain == "Marshall Mesa Grassland" ~ "Grassland",
-    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
-  mutate(terrain = forcats::fct_reorder(terrain, -u_d)) %>% 
-  ggplot(
-  aes(x = u_d, 
-      y = terrain,
-      color = terrain,
-      fill = terrain)) +
-  stat_slab(height = 0.5, 
-            alpha = 0.7,
-            color = "black") +
-  stat_pointinterval(color = "black",
-                     height = 0.2) +
-  geom_point(
-    color = "black",
-    shape = 124,
-    size = 5,
-    alpha = 0.5,
-    position = position_nudge(y = -.15)) +
-  scale_x_log10(
-    breaks = trans_breaks("log10", function(x) 10^x),
-    labels = trans_format("log10", math_format(10^.x))
-  ) +
-  annotation_logticks(sides = "b") +
-  scale_color_manual(values = terrain_color_swatch) +
-  scale_fill_manual(values = terrain_fill_swatch) +
-  theme_classic() +
-  labs(y = "Soil Type",
-       x = TeX("Turnover rate ($d^{-1}$)")) +
-  theme(axis.text.y = element_text(hjust = 1),
-        legend.position = "none")
-p_turnover_distributions
-```
 
@@
 
-## dF
+## dF and turnover plot
 
@@
 
+## Abundance versus turnover
+
+```{r}
+p_abundance_v_turnover <- turnover %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(aes(
+    x = compound_ug_per_g_soil,
+    y = u_d,
+    color = dF*10000
+  )) +
+  facet_wrap(vars(inc_time_d, soil), ncol = 3) +
+  geom_point(alpha = 0.6) +
+  scale_color_viridis_c() +
+  theme_bw() +
+  labs(x = "µg analyte per g soil",
+       y = TeX("Turnover (d$^{-1}$)"),
+       color = TeX("$ \\Delta ^2H$ (ppm)")
+  ) +
+  guides(color = guide_colorbar(barwidth = 0.5)) +
+  theme(
+    strip.background = element_blank(),
+    panel.grid = element_blank(),
+  )
+p_abundance_v_turnover
+```
+
 ## Literature Rates of Cell Turnover by Method
@@
     peak_marker = FALSE,
-peak_label = iso_format(rt),
-#peak_label_size = 3,
-peak_label_filter = analysis == 5685 & amp2 > 1
-+ scale_color_npg() +
+    #peak_label_size = 3
+    ) +
+    scale_color_npg() +
     theme_classic() +
-theme(strip.background = element_blank()))
+    theme(strip.background = element_blank())
+
 ```
+
+## Turnover distributions
+
+```{r turnover_across_soil}
+p_turnover_distributions <- turnover %>% 
+  filter(inc_time_d == 7) %>%
+  mutate(terrain = case_when(
+    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+    terrain == "Marshall Mesa Grassland" ~ "Grassland",
+    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
+  mutate(terrain = forcats::fct_reorder(terrain, -u_d)) %>% 
+  ggplot(
+  aes(x = u_d, 
+      y = terrain,
+      color = terrain,
+      fill = terrain)) +
+  stat_slab(height = 0.5, 
+            alpha = 0.7,
+            color = "black") +
+  stat_pointinterval(color = "black",
+                     height = 0.2) +
+  geom_point(
+    color = "black",
+    shape = 124,
+    size = 5,
+    alpha = 0.5,
+    position = position_nudge(y = -.15)) +
+  scale_x_log10(
+    breaks = trans_breaks("log10", function(x) 10^x),
+    labels = trans_format("log10", math_format(10^.x))
+  ) +
+  annotation_logticks(sides = "b") +
+  scale_color_manual(values = terrain_color_swatch) +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  theme_classic() +
+  labs(y = "Soil Type",
+       x = TeX("Turnover rate ($d^{-1}$)")) +
+  theme(axis.text.y = element_text(hjust = 1),
+        legend.position = "none")
+p_turnover_distributions
+```

### 2022-04-06 03_data_viz.Rmd
added save

@@
     strip.background = element_blank(),
+
     panel.grid = element_blank(),
@@
 p_abundance_v_turnover
+
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
+                   plot = p_abundance_v_turnover,
+                   base_height = 6,
+                   base_width = 8)
 ```

### 2022-05-11 01_LH-SIP_Data_Reduction.Rmd
save sample_files as cache
began memory effect correction

@@
 
-# Setup
+# '######## SETUP ########'
 
@@
 library(cowplot)      # CRAN v1.1.1
+library(isotopia)
 ```
@@
 source(file.path("libs", "calculate_turnover.R"))         # Turnover Calculator
+source(file.path("libs", "d2H_to_2F.R"))                  # Convert delta to frac abund
 `%nin%` = Negate(`%in%`)                                  # "Not In" function
@@
 
+# Cache the sample files for plotting
+saveRDS(sample_files, file = "cache/sample_files")
+
 ```
 
-### Show file information
+Show file information
 
@@
 ```
+
+## Load memory-corrected IRMS data
+
+```{r}
+LH_SIP_memcorr <- readxl::read_excel("data/samples_data_memory_corrected.xlsx") %>% 
+# Trim it down
+  select(-c(standard, is_std_peak, folder, file_datetime, id2, individual, injection_volume,
+            gc_method, map_id, gc_ramp, group, peak_type, ref_nr, calib_peak, peak_nr,
+            is_ref, rt_start, rt, rt_end, n_overlapping, n_matches, use_in_calib, d2H_in_calib, d2H_resid, 
+            d2H_calib_points)) %>% 
+  filter(id1 %nin% c("cr0f0x", "cr0f0y", "cr0f0z",
+                     "cr0f3x", "cr0f3y", "cr0f3z",
+                     "cr0f7x", "cr0f7y", "cr0f7z",
+                     "cri0", "cri3", "cri7")) %>% 
+  rename(sample_id = id1)
+```
+
+# '########## DATA REDUCTION #############
 
@@
 
+## Correct for memory effect
+
+This uses memory-effect corrected data. See SI.
+
+```{r}
+LH_SIP_memcorr <- LH_SIP_memcorr %>% 
+  select(sample_id, compound, area2, area3, note, 
+          calibrated_d2H_without_memory, 
+          calibrated_d2H_without_memory_se,
+          calibrated_d2H_with_memory_correction, 
+          calibrated_d2H_with_memory_correction_se) %>% 
+  mutate(
+    calibrated_at2H_without_memory = d2H_to_2F(calibrated_d2H_without_memory),
+    calibrated_at2H_without_memory_se = d2H_to_2F(calibrated_d2H_without_memory_se),
+    calibrated_at2H_with_memory_correction = d2H_to_2F(calibrated_d2H_with_memory_correction), 
+    calibrated_at2H_with_memory_correction_se = d2H_to_2F(calibrated_d2H_with_memory_correction_se)
+  )
+
+```
+
 ## Correct for PAME
+
+Correcting for the isotopic composition of the derivatization agent by measuring phthalic acid methyl ester (PAME).
 
@@
         file = "cache/d2H_assimilation")
+
+saveRDS(LH_SIP_memcorr,
+        file = "cache/LH_SIP_memcorr")
 ```

### 2022-05-11 02_LH-SIP_Quantification.Rmd
began memory effect correction

@@
 LH_SIP_data <- readRDS(file = "cache/LH_SIP_data")
-
 LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
+LH_SIP_memcorr <- readRDS(file = "cache/LH_SIP_memcorr")
 ```

### 2022-05-11 libs/d2H_to_2F.R

@@ -1,0 +1,19 @@
+#' Delta 2H to 2F
+#' @param d2H deuterium isotopic enrichment in delta notation relative to VSMOW
+#' @return fractional abundance of deuterium in atom percent
+#' 
+
+d2H_to_2F <- function(d2H) {
+  # Define VSMOW in ratio space
+  R_VSMOW = 0.0001557643
+  
+  # Convert delta to ratio
+  R_sample = (d2H + 1) * R_VSMOW
+  
+  # Convert ratio to fractional abundance
+  F_sample = R_sample/(1 + R_sample)
+  
+  # Return fractional abundance in atom percent (*100)
+  # We do this because our IRMS reports fractional abundance in atom percent!
+  return(F_sample*100)
+}

### 2022-05-13 01_LH-SIP_Data_Reduction.Rmd
memory effect data added into exported df

@@
 ---
-
-# '######## SETUP ########'
 
@@
                      "cri0", "cri3", "cri7")) %>% 
-  rename(sample_id = id1)
+  rename(sample_id = id1,
+         Analysis = analysis)
 ```
 
-# '########## DATA REDUCTION #############
+# `
 
@@
 LH_SIP_memcorr <- LH_SIP_memcorr %>% 
-  select(sample_id, compound, area2, area3, note, 
+  select(Analysis, sample_id, compound, area2, area3, note, 
           calibrated_d2H_without_memory, 
@@
           calibrated_d2H_with_memory_correction_se) %>% 
+  mutate(Analysis = as.numeric(Analysis)) %>% 
   mutate(
@@
 
+## Join raw and mem-corrected (mc) datasets
+
+```{r}
+peaks_mapped_with_zeros_FID_mc <- peaks_mapped_with_zeros_FID %>% 
+  # Need to remove "BF" from Analysis number
+  mutate(Analysis = parse_number(Analysis)) %>%
+  # Join
+  left_join(
+    LH_SIP_memcorr, 
+    by = c("Analysis", "sample_id", "compound"))
+
+peaks_mapped_with_threes_FID_mc <- peaks_mapped_with_threes_FID %>% 
+  # Need to remove "BF" from Analysis number
+  mutate(Analysis = parse_number(Analysis)) %>%
+  # Join
+  left_join(
+    LH_SIP_memcorr, 
+    by = c("Analysis", "sample_id", "compound"))
+```
+
 ## Correct for PAME
@@
 # For 0 -3, 0-7 timepoints
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros_FID %>% 
+peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID_mc %>% 
   left_join(compound_nC_nH, by = "compound") %>% 
   mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+         # define calibrated 2F
+         `2F_FAME` = calibrated_at2H_without_memory,
+         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
+         # define calibrated 2F mc
+         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
+         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
 
 # for 3-7 timepoints
-peaks_mapped_with_threes_FID <- peaks_mapped_with_threes_FID %>% 
+peaks_mapped_with_threes_FID_mc_pame <- peaks_mapped_with_threes_FID_mc %>% 
   left_join(compound_nC_nH, by = "compound") %>% 
   mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+         # define calibrated 2F
+         `2F_FAME` = calibrated_at2H_without_memory,
+         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
+         # define calibrated 2F mc
+         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
+         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
 ```
@@
 # Analytes
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
+peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID_mc_pame %>% 
   # Don't want our standard compounds to be used for generation time calculations! x_x
@@
   filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
+  # Add in label strengths
   left_join(F_L_2F, by = "terrain")
@@
 # Standards
-peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID %>% 
+peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID_mc_pame %>% 
   filter(str_detect(compound, "STD"))
@@
 peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
+  mutate(F_0_at2H_se = sF_0 %>% pull(F_0_at2H_se))
 
@@
 # Analytes
-peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID %>% 
+peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID_mc_pame %>% 
   # Don't want our standard compounds to be used for generation time calculations! x_x
@@
 peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
+  mutate(F_0_at2H_se = sF_0 %>% pull(F_0_at2H_se))
 
@@
 
-## Reduce columns
+## Eliminate extraneous columns
 
@@
          at2H,
+         calibrated_at2H_without_memory,
+         calibrated_at2H_with_memory_correction,
+         calibrated_at2H_without_memory_se,
+         calibrated_at2H_with_memory_correction_se,
          area2_mn_zero,
-         area2,
+         area2.x,
          area_FID,
@@
          `2F_FAME`,
-         `2F_alk`,
+         `2F_FAME_mc`, # Memory corrected value
+         `2F_alk`, # Memory corrected value
+         `2F_alk_mc`,
          F_label_mn,
@@
          at2H,
+         calibrated_at2H_without_memory,
+         calibrated_at2H_with_memory_correction,
+         calibrated_at2H_without_memory_se,
+         calibrated_at2H_with_memory_correction_se,
          area2_mn_three,
-         area2,
+         area2.x,
          area_FID,

### 2022-05-13 02_LH-SIP_Quantification.Rmd
memory effect data propagated into turnover calculations

@@
 
+# Clear the environment
+
+```{r}
+rm(list=ls())
+```
+
 # Setup
@@
 ```{r setup, include = FALSE}
+
 # global knitting options for code rendering
@@
 ## Load packages
-
+Tidyverse required. Isoverse packages available at `isoverse.org`.
 ```{r, message=FALSE, warning=FALSE}
@@
 ## Read RDS from cache
-
+Cache is located in `cache/` directory.
 ```{r}
@@
   mutate(
+    # Explicitly define incubation parameters:
 
-    # Explicitly define incubation parameters:
     # label is adjusted for the actual isotopic composition of the label within a specific terrain
@@
     f_t = `2F_alk`,
+    f_t_mc = `2F_alk_mc`, # memory corrected value
     # delta 2F: change in 2F enrichment over time t
@@
       ),
+
+    # And a memory-corrected turnover:
+    u_d_mc = calculate_turnover(
+      a = a, # Assimilation efficiency defined in data reduction step
+      FT = f_t_mc, # 2F at time t (at%) (memory corrected)
+      F0 = f_start, # 2F at t0 (at%)
+      FL = f_label, # 2F of label (at%)
+      t = d_t # change in time
+      ),
+
     # calculate generation time, converting negatives to zero
     gen_d = turnover_to_gen(u_d),
+
+    # And a memory corrected gen time:
+    gen_d_mc = turnover_to_gen(u_d_mc),
 
@@
       sF_L = F_label_se,
-      sF_T = 0,
+      sF_T = calibrated_at2H_without_memory_se,
+      sa = sa
+    ),
+
+    # Same for memory corrected data
+    su_d_mc = calculate_sigma_mu(
+      # Mean values:
+      a = a,
+      F_L = f_label,
+      F_T = f_t_mc,
+      F_0 = f_start,
+      t = d_t,
+      # Uncertainties:
+      sF_0 = F_0_at2H_se,
+      sF_L = F_label_se,
+      sF_T = calibrated_at2H_with_memory_correction_se,
       sa = sa
@@
 
-# Create weighted turnover
+# Calculate abundance-weighted turnover
 
@@
     at2H_weighted = 
-      sum(at2H * rel_area_FID, na.rm = TRUE) / 
+      sum(calibrated_at2H_without_memory * rel_area_FID, na.rm = TRUE) / 
       sum(rel_area_FID, na.rm = TRUE),
@@
       sum(rel_area_FID, na.rm = TRUE),
+
+    # Do the same for memory-corrected data:
+    at2H_weighted_mc = 
+      sum(calibrated_at2H_with_memory_correction * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+    `2F_alk_mc_weighted` = 
+      sum(`2F_alk_mc` * rel_area_FID, na.rm = TRUE) / 
+      sum(rel_area_FID, na.rm = TRUE),
+
     # Keep these:
@@
     f_t = `2F_alk_weighted`,
+    f_t_mc = `2F_alk_mc_weighted`,
     dF_weighted = case_when(
@@
     ),
-    gen_d_weighted = turnover_to_gen(u_d_weighted)
+    gen_d_weighted = turnover_to_gen(u_d_weighted),
+    # Do the same for memory corrected data
+    u_d_mc_weighted = calculate_turnover(
+      a = a,
+      FT = f_t_mc,
+      F0 = f_start,
+      FL = f_label,
+      t = d_t
+    ),
+    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
   )

### 2022-05-13 03_data_viz.Rmd
tidying

@@
 ---
+
+# Clear the environment
+
+```{r}
+rm(list=ls())
+```
 
@@
 
-### Lit search data
+### Read lit analysis data
 
-```{r lit search data}
+```{r lit analysis data}
 lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))

### 2022-05-13 libs/d2H_to_2F.R
d2H/1000!!!!!

@@ -7,8 +7,9 @@ d2H_to_2F <- function(d2H) {
   # Define VSMOW in ratio space
   R_VSMOW = 0.0001557643
   
-  # Convert delta to ratio
-  R_sample = (d2H + 1) * R_VSMOW
+
+  # Convert delta to ratio, remove permil units from d2H
+  R_sample = ((d2H/1000) + 1) * R_VSMOW
   
   # Convert ratio to fractional abundance
   F_sample = R_sample/(1 + R_sample)

### 2022-05-13 03_data_viz.Rmd
added weighted dF with mem effect

@@
 lit_turnover <- readxl::read_excel(file.path("data", "literature_turnover_rates.xlsx"))
+
 turnover_means <- turnover_weighted %>% 
@@
 
-```{r cowplot mooooo}
-p_community_turnover_cow <- cowplot::plot_grid(
-  p_turnover_distributions,
-  p_gen_time_mean,
-  labels = "AUTO",
-  rel_widths = c(1,1),
-  align = "h",
-  nrow = 1
-)
-
-# 
-# save_plot(filename = "fig_output/p_community_turnover_cow.png",
-#           plot = p_community_turnover_cow,
-#           base_height = 5,
-#           base_width = 10
-#           )
-
-```
-
 ## dF and turnover plot
@@
     names_to = "type"
-  ) %>%
+  ) %>% view()
 
@@
     x = inc_time_d,
-    y = dF_weighted,
+    y = dF,
     color = terrain),
@@
       x = inc_time_d,
-      y = dF_weighted,
+      y = dF,
       color = terrain,
@@
 peaks_mapped_summarized_wppm <- turnover_summarized %>% 
-    mutate(at2H_ppm = at2H * 10000,
+    mutate(
+      at2H_ppm = calibrated_at2H_without_memory * 10000,
+      at2H_ppm_mc = calibrated_at2H_with_memory_correction * 10000,
       at2H_mn_zero_ppm = at2H_mn_zero * 10000,

### 2022-05-13 02_LH-SIP_Quantification.Rmd
weighted dF with mem effect

@@
       ),
+
+    dF_mc = case_when(
+      f_t_mc - f_start >= 0 ~ f_t_mc - f_start,
+      f_t_mc - f_start < 0 ~ 0),
 
@@
     f_t_mc = `2F_alk_mc_weighted`,
+
     dF_weighted = case_when(
@@
       f_t - f_start < 0 ~ 0),
+    #Do the same for memory-corrected data:
+    dF_weighted_mc = case_when(
+      f_t_mc - f_start >= 0 ~ f_t_mc - f_start,
+      f_t_mc - f_start < 0 ~ 0),
+
   ) %>%

### 2022-05-13 03_data_viz.Rmd
dF plot now PASSING

@@
 
+# Setup
 ```{r setup, include=FALSE}
@@
 
-# Load libraries
+## Load libraries
 
@@
 
-# Load sourced functions
+## Load sourced functions
 
@@
 ```
-
-# Setup
 
@@
 
+## (PASSING) Memory effect on gen_d
+
 ```{r mean_generation_time}
 p_gen_time_mean <- turnover_weighted %>% 
+  select(c(terrain, inc_time_d, gen_d_weighted, gen_d_mc_weighted)) %>% 
+  pivot_longer(cols = c(gen_d_weighted, gen_d_mc_weighted),
+               values_to = "gen_d",
+               names_to = "type") %>% 
   filter(inc_time_d == 7) %>% 
@@
     terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
-  group_by(terrain, inc_time_d) %>% 
-  summarize(terrain = terrain,
-            gen_d_weighted = gen_d_weighted) %>% 
-  unique() %>% 
+  # group_by(terrain, inc_time_d) %>% 
+  # summarize(terrain = terrain,
+  #           gen_d_weighted = gen_d_weighted) %>% 
+  # unique() %>% 
+  # Plot it
   ggplot(aes(x = terrain,
-             y = gen_d_weighted,
-             fill = terrain)) +
-  geom_col(width = 0.5) +
-  scale_fill_manual(values = terrain_fill_swatch) +
+             y = gen_d,
+             fill = type)) +
+  geom_col(width = 0.5,
+           position = "dodge") +
+  scale_fill_tron() +
   labs(x = "Soil Type",
-       y = "Community Generation Time (d)",
-       caption = "Generation time weighted by compound relative abundance") +
+       y = "Weighted Mean Generation Time (d)") +
   theme_classic() +
-  theme(legend.position = "none")
+  theme()
 p_gen_time_mean
@@
 
-## dF and turnover plot
+## (PASSING) dF plot
+Using memory-corrected values
 
@@
 p_dF <- turnover_summarized %>% 
-  filter(time_course == "0d -->") %>% 
+  filter(
+    time_course == "0d -->",
+    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
   ungroup() %>% 
-  select(terrain, inc_time_d, compound, dF) %>%
+  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
   left_join(
     turnover_weighted %>% 
-      select(terrain, inc_time_d, dF_weighted), 
+      select(terrain, inc_time_d, dF_weighted_mc), 
     by = c("terrain", "inc_time_d")) %>% 
@@
   pivot_longer(
-    cols = c(dF, dF_weighted),
+    cols = c(dF_mc, dF_weighted_mc),
     values_to = "dF", 
     names_to = "type"
-  ) %>% view()
+  ) %>% 
+  mutate(compound = case_when(
+    type == "dF_weighted_mc" ~ "Weighted Mean",
+    TRUE ~ compound
+  )) %>%
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
+  )) %>%
 
@@
       x = inc_time_d,
-      y = dF
+      y = dF * 10000, # convert from at% to ppm
+      group = compound,
+      color = terrain,
+      fill = terrain,
+      alpha = type,
+      size = type
     )
   ) +
-  # Weighted data here:
-  geom_line(aes(
-    x = inc_time_d,
-    y = dF,
-    color = terrain),
-    size = 1.5,
-    alpha = 0.5
-    ) +
-  geom_point(
-    aes(
-      x = inc_time_d,
-      y = dF,
-      color = terrain,
-      fill = terrain),
-    size = 2,
-    alpha = 0.5
-    ) +
-  # Unweighted data here:
-  geom_borderline(
-    data = turnover_summarized,
-    aes(group = compound),
-    color = "gray"
-) +
-  geom_point(
-    data = turnover_summarized,
-    size = 2,
-    alpha = 0.5
-    ) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  coord_cartesian(
-    xlim = c(0, 8),
-    clip = "off"
-    ) +
-  facet_wrap(vars(terrain),
-             nrow = 1) +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("$ \\Delta ^2H$ (at%)"),
-       ) +
+  geom_point() +
+  geom_line() +
+  facet_wrap(vars(terrain)) +
   scale_color_manual(values = terrain_color_swatch) +
   scale_fill_manual(values = terrain_fill_swatch) +
+  scale_alpha_discrete(range = c(0.2, 1)) +
+  scale_size_discrete(range = c(0.75, 1.25)) +
   theme_classic() +
+  labs(
+    x = "Time elapsed (d)",
+    y = TeX("$ \\Delta ^2H$ (ppm)")
+  ) +
   theme(legend.position = "none",
@@
         axis.title.x = element_text(size = 10))
+p_dF
 
-p_dF
 ```
 
-```{r 2H_plots}
-
-peaks_mapped_summarized_wppm <- turnover_summarized %>% 
-    mutate(
-      at2H_ppm = calibrated_at2H_without_memory * 10000,
-      at2H_ppm_mc = calibrated_at2H_with_memory_correction * 10000,
-      at2H_mn_zero_ppm = at2H_mn_zero * 10000,
-      at2H_weighted_ppm = at2H_weighted * 10000)
-
-p_conifer_2H <- peaks_mapped_summarized_wppm %>% 
-  filter(terrain == "Gordon Gulch Conifer Forest") %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H_ppm,
-             group = compound)) +
-  geom_borderline(color = "gray") +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  geom_borderline(aes(x = inc_time_d,
-                y = at2H_weighted_ppm),
-                color = conifer_color,
-            size = 1.5) +
-  geom_point(aes(x = inc_time_d,
-                y = at2H_weighted_ppm), 
-                color = conifer_color,
-             size = 3,
-             alpha = 0.5) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("$^2H$ (ppm)"),
-       title = "Conifer Forest") +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10))
-p_conifer_2H
-
-p_grassland_2H <- peaks_mapped_summarized_wppm %>% 
-  filter(terrain == "Marshall Mesa Grassland") %>% 
-  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H_ppm,
-             group = compound)) +
-  geom_borderline(color = "gray") +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  geom_borderline(aes(x = inc_time_d,
-                      y = at2H_weighted_ppm),
-                      color = grassland_color,
-                  size = 1.5) +
-  geom_point(aes(x = inc_time_d,
-                 y = at2H_weighted_ppm), 
-                 color = grassland_color,
-             size = 3) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("$^2H$ (ppm)"),
-       title = "Grassland") +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10))
-p_grassland_2H
-
-p_tundra_2H <- peaks_mapped_summarized_wppm %>% 
-  filter(terrain == "Niwot Ridge Tundra") %>% 
-  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H_ppm,
-             group = compound)) +
-  geom_borderline(color = "gray") +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  geom_borderline(aes(x = inc_time_d,
-                y = at2H_weighted_ppm),
-                color = tundra_color,
-            size = 1.5) +
-  geom_point(aes(x = inc_time_d,
-                y = at2H_weighted_ppm), 
-                color = tundra_color,
-                fill = tundra_color,
-             size = 3) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("$^2H$ (ppm)"),
-       title = "Tundra") +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10))
-p_tundra_2H
-```
-
-```{r}
-
-p_tundra_2H_3d <- peaks_mapped_summarized_wppm %>% 
-  filter(terrain == "Niwot Ridge Tundra") %>% 
-  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
-  ggplot(aes(x = inc_time_d,
-             y = at2H_ppm,
-             group = compound)) +
-  geom_borderline(color = "gray") +
-  geom_point(size = 2,
-             alpha = 0.5) +
-  geom_borderline(aes(x = inc_time_d,
-                y = at2H_weighted_ppm),
-                color = tundra_color,
-            size = 1.5) +
-  geom_point(aes(x = inc_time_d,
-                y = at2H_weighted_ppm), 
-                color = tundra_color,
-                fill = tundra_color,
-             size = 3) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
-  labs(x = "Incubation Time (Days)",
-       y = TeX("$^2H$ (ppm)"),
-       title = "Tundra") +
-  theme_classic() +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10))
-p_tundra_2H
-```
+## Turnover plot
 

### 2022-05-15 03_data_viz.Rmd
dF and turnover plots now use memory-corrected data

@@
   filter(inc_time_d == 7) %>%
-  select(terrain, u_d_weighted) %>% 
-  rename(u_d_mn = u_d_weighted) %>% 
+  select(terrain, u_d_mc_weighted) %>% 
+  rename(u_d_mn = u_d_mc_weighted) %>% 
   mutate(comment = terrain) %>% 
@@
 
+# cowplot::save_plot(
+#   filename = "fig_output/p_dF.pdf",
+#   plot = p_dF,
+#   base_width = 7,
+#   base_height = 4
+#   )
+
 ```
 
-## Turnover plot
+## (PASSING) Turnover plot
+
+```{r turnover plot}
+# Clean up weighted turnover data
+turnover_weighted_cleaned <- turnover_weighted %>% 
+  filter(inc_time_d == 7) %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  mutate(
+    compound = "Weighted Mean",
+    type = "Weighted"
+  ) %>% 
+  rename(
+    "u_d_mc" = u_d_mc_weighted,
+    "u_d" = u_d_weighted,
+    "gen_d" = gen_d_weighted,
+    "gen_d_mc" = gen_d_mc_weighted
+  ) %>%
+  select(terrain, compound, u_d_mc, u_d, gen_d, gen_d_mc, type)
+
+# Define a function for turnover plots
+plot_turnover <- function(df, terrain_choice, color_choice) {
+  df %>% 
+  # Data organization and cleanup
+  ungroup() %>% 
+  filter(
+    time_course == "0d -->",
+    inc_time_d == "7",
+    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
+  mutate(type = "unweighted") %>% 
+  bind_rows(
+    turnover_weighted_cleaned) %>%
+  group_by(terrain) %>%
+
+  # Choose terrain
+  filter(terrain == terrain_choice) %>% 
+  mutate(compound = forcats::fct_reorder(compound, u_d_mc)) %>%
+
+  # Plot it
+  ggplot(
+    aes(
+      x = u_d_mc,
+      y = compound,
+      color = type,
+      fill = type
+      )
+  ) +
+  geom_col() +
+  geom_errorbar(aes(
+    xmin = u_d_mc - (0.5 * su_d_mc),
+    xmax = u_d_mc + (0.5 * su_d_mc)),
+    color = "black",
+    width = 0.25
+    ) +
+  coord_cartesian(xlim = c(0, 0.175)) +
+  scale_fill_manual(values = c("black", color_choice)) +
+  scale_color_manual(values = c("black", color_choice)) +
+  theme_classic() +
+  labs(x = TeX("Turnover ($d^{-1}$)"),
+       title = terrain_choice) +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.ticks.y = element_blank(),
+    strip.background = element_blank(),
+    legend.position = "none",
+    plot.title = element_text(hjust = 0.5),
+  )
+
+  }
+
+p_tundra_turnover <- plot_turnover(
+  turnover_summarized, 
+  terrain_choice = "Tundra", 
+  color_choice = tundra_color)
+
+p_grassland_turnover <- plot_turnover(
+  turnover_summarized,
+  terrain_choice = "Grassland",
+  color_choice = grassland_color
+)
+
+p_conifer_forest_turnover <- plot_turnover(
+  turnover_summarized,
+  terrain_choice = "Conifer Forest",
+  color_choice = conifer_color
+)
+
+p_turnover <- cowplot::plot_grid(
+  p_conifer_forest_turnover,
+  p_grassland_turnover,
+  p_tundra_turnover,
+  nrow = 1
+)
+
+p_turnover
+
+# cowplot::save_plot(
+#   filename = "fig_output/p_turnover.pdf",
+#   plot = p_turnover,
+#   base_width = 11,
+#   base_height = 4
+#   )
+
+```
+
+```{r}
+
+turnover_summarized %>% 
+  # Data organization and cleanup
+  ungroup() %>% 
+  filter(
+    time_course == "0d -->",
+    inc_time_d == "7",
+    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
+  bind_rows(
+    turnover_weighted_cleaned) %>%
+  group_by(terrain) %>%
+
+  # Choose terrain
+  filter(terrain == "Tundra") %>% 
+  mutate(compound = forcats::fct_reorder(compound, u_d_mc)) %>% view()
+
+  # Plot it
+  ggplot(
+    aes(
+      x = u_d_mc,
+      y = compound,
+      color = terrain,
+      fill = terrain
+      )
+  ) +
+  geom_col(
+    fill = "black",
+    color = "black"
+  ) +
+  geom_errorbar(aes(
+    xmin = u_d_mc - (0.5 * su_d_mc),
+    xmax = u_d_mc + (0.5 * su_d_mc)),
+    color = "black",
+    width = 0.25
+    ) +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  scale_color_manual(values = terrain_color_swatch) +
+  theme_classic() +
+  labs(x = TeX("Turnover ($d^{-1}$)"),
+       title = "Tundra") +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.ticks.y = element_blank(),
+    strip.background = element_blank(),
+    legend.position = "none",
+    plot.title = element_text(hjust = 0.5),
+  )
+
+```
+
+## (PASSING) Abundance versus turnover
+
+```{r}
+p_abundance_v_turnover <- turnover %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(aes(
+    x = compound_ug_per_g_soil,
+    y = u_d_mc,
+    color = terrain #dF*10000
+  )) +
+  geom_point(aes(size = dF*10000),
+    alpha = 0.6,
+    ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  theme_bw() +
+  labs(x = "µg analyte per g soil",
+       y = TeX("Turnover (d$^{-1}$)"),
+       size = TeX("$ \\Delta ^2H$ (ppm)"),
+       color = " "
+  ) +
+  #guides(color = guide_colorbar(barwidth = 0.5)) +
+  theme(
+    strip.background = element_blank(),
+
+    panel.grid = element_blank(),
+  )
+p_abundance_v_turnover
+
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
+                   plot = p_abundance_v_turnover,
+                   base_height = 6,
+                   base_width = 8)
+```
+
+## (PASSING) Literature Rates of Cell Turnover by Method
+
+```{r lit rates}
+literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7")
+literature_values_swatch_2 <- c("#26AFE1", "#6269EB", "#E0187B")
+
+p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
+  filter(method_type != "Microscopy") %>% 
+  # order by mean turnover rate
+  ggplot(
+    aes(x = -n,
+        y = u_d_mn,
+        fill = method_type,
+        label = round(gen_d, 1)
+        )
+    ) +
+  geom_col() +
+  geom_text(nudge_y = 0.05, size = 2) +
+  coord_flip(ylim = c(0, 0.5)) +
+  scale_fill_manual(values = literature_values_swatch_2) +
+  labs(y = TeX("Turnover (d$^{-1}$)"),
+       fill = "Method") +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
+        axis.ticks.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.x = element_text(size = 18),
+        #legend.position = "bottom",
+        plot.title = element_text(hjust = 0.5),
+        legend.position = c(0.85, 0.1),
+        legend.text = element_text(size = 15),
+        legend.title = element_blank(),
+        plot.margin = margin(1,1,1.5,1.2, "in"))
+p_lit_turnover_w_ours
+
+# cowplot::save_plot(filename = "fig_output/literature_values.pdf",
+#                    plot = p_lit_turnover_w_ours,
+#                    base_height = 8,
+#                    base_width = 10)
+```
+
+## (PASSING) BacDive FA profiles
+
+```{r}
+p_tax_FA <- bacdive_FA_wide %>% 
+  select(-ID) %>% 
+  pivot_longer(cols = -phylum, 
+               names_to = "FA",
+               values_to = "rel_abund") %>%
+  ggplot(aes(x = FA, 
+             y = rel_abund)) +
+  geom_jitter(aes(color = phylum),
+              size = 0.25,
+              alpha = 0.3) +
+  stat_pointinterval(point_interval = "median_qi",
+                     alpha = 0.65) +
+  facet_wrap(vars(phylum), nrow = 3) +
+  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
+  labs(y = "Relative Abundance (%)",
+       x = "",
+       color = "Phylum") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90,
+                                   hjust = 1),
+        panel.grid = element_blank(),
+        strip.background = element_blank(),
+        legend.position = "NA",
+        strip.text = element_text(size = 16)
+        )
+p_tax_FA
+
+# cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
+#           plot = p_tax_FA,
+#           base_height = 11,
+#           base_width = 9
+#           )
+```
+
+## (FAILING) Compare extraction efficiency
+
+```{r extr_eff}
+FID_results_abundance_reported_long <- FID_results_abundance_no_stds %>% 
+  select(
+    sample_id, 
+    compound, 
+    deriv_efficiency, 
+    extr_efficiency
+  ) %>% 
+  pivot_longer(
+    !c(sample_id, compound),
+    names_to = "stage", 
+    values_to = "efficiency"
+  ) %>% 
+  mutate(
+    stage = case_when(
+      str_detect(stage, "deriv") ~ "Derivatization Efficiency",
+      str_detect(stage, "extr") ~ "Extraction Efficiency"
+    )
+  )
+
+FID_results_abundance_reported_long %>% 
+  ggplot(aes(x = stage, y = efficiency)) +
+  geom_boxplot(
+    outlier.shape = NA,
+    width = 0.3
+    ) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  labs(x = "",
+       y = "Efficiency") +
+  theme_classic()
+```
+
+## (PASSING) Example chromatogram
+```{r}
+# plot an example chromatogram
+
+sample_files[10] %>% # choosing arbitrary file to plot
+  iso_plot_continuous_flow_data(
+    # select data and aesthetics
+    data = c(2), color = id1, panel = id1,
+    # zoom in on time interval
+    time_interval = c(750, 4000),
+    # peak labels for all peaks > 2V
+    peak_bounds = TRUE,
+    peak_marker = FALSE,
+    #peak_label_size = 3
+    ) +
+    scale_color_npg() +
+    theme_classic() +
+    theme(strip.background = element_blank())
+
+```
+
+## (PASSING) Turnover distributions
+
+```{r turnover_across_soil}
+p_turnover_distributions <- turnover %>% 
+  filter(inc_time_d == 7) %>%
+  mutate(terrain = case_when(
+    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+    terrain == "Marshall Mesa Grassland" ~ "Grassland",
+    terrain == "Niwot Ridge Tundra" ~ "Tundra" )) %>% 
+  mutate(terrain = forcats::fct_reorder(terrain, -u_d)) %>% 
+  ggplot(
+  aes(x = u_d, 
+      y = terrain,
+      color = terrain,
+      fill = terrain)) +
+  stat_slab(height = 0.5, 
+            alpha = 0.7,
+            color = "black") +
+  stat_pointinterval(color = "black",
+                     height = 0.2) +
+  geom_point(
+    color = "black",
+    shape = 124,
+    size = 5,
+    alpha = 0.5,
+    position = position_nudge(y = -.15)) +
+  scale_x_log10(
+    breaks = trans_breaks("log10", function(x) 10^x),
+    labels = trans_format("log10", math_format(10^.x))
+  ) +
+  annotation_logticks(sides = "b") +
+  scale_color_manual(values = terrain_color_swatch) +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  theme_classic() +
+  labs(y = "Soil Type",
+       x = TeX("Turnover rate ($d^{-1}$)")) +
+  theme(axis.text.y = element_text(hjust = 1),
+        legend.position = "none")
+p_turnover_distributions
+```
+
+## (Deprecated) Turnover plot
 
@@
 ```
-
-## Abundance versus turnover
-
-```{r}
-p_abundance_v_turnover <- turnover %>% 
-  filter(inc_time_d != 0) %>% 
-  ggplot(aes(
-    x = compound_ug_per_g_soil,
-    y = u_d,
-    color = dF*10000
-  )) +
-  facet_wrap(vars(inc_time_d, soil), ncol = 3) +
-  geom_point(alpha = 0.6) +
-  scale_color_viridis_c() +
-  theme_bw() +
-  labs(x = "µg analyte per g soil",
-       y = TeX("Turnover (d$^{-1}$)"),
-       color = TeX("$ \\Delta ^2H$ (ppm)")
-  ) +
-  guides(color = guide_colorbar(barwidth = 0.5)) +
-  theme(
-    strip.background = element_blank(),
-
-    panel.grid = element_blank(),
-  )
-p_abundance_v_turnover
-
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
-                   plot = p_abundance_v_turnover,
-                   base_height = 6,
-                   base_width = 8)
-```
-
-## Literature Rates of Cell Turnover by Method
-
-```{r lit rates}
-literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7")
-literature_values_swatch_2 <- c("#26AFE1", "#6269EB", "#E0187B")
-
-p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
-  filter(method_type != "Microscopy") %>% 
-  # order by mean turnover rate
-  ggplot(
-    aes(x = -n,
-        y = u_d_mn,
-        fill = method_type,
-        label = round(gen_d, 1)
-        )
-    ) +
-  geom_col() +
-  geom_text(nudge_y = 0.05, size = 2) +
-  coord_flip(ylim = c(0, 0.5)) +
-  scale_fill_manual(values = literature_values_swatch_2) +
-  labs(y = TeX("Turnover (d$^{-1}$)"),
-       fill = "Method") +
-  theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
-        axis.ticks.y = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.x = element_text(size = 18),
-        #legend.position = "bottom",
-        plot.title = element_text(hjust = 0.5),
-        legend.position = c(0.85, 0.1),
-        legend.text = element_text(size = 15),
-        legend.title = element_blank(),
-        plot.margin = margin(1,1,1.5,1.2, "in"))
-p_lit_turnover_w_ours
-
-cowplot::save_plot(filename = "fig_output/literature_values.pdf",
-                   plot = p_lit_turnover_w_ours,
-                   base_height = 8,
-                   base_width = 10)
-```
-
-## BacDive FA profiles
-
-```{r}
-p_tax_FA <- bacdive_FA_wide %>% 
-  select(-ID) %>% 
-  pivot_longer(cols = -phylum, 
-               names_to = "FA",
-               values_to = "rel_abund") %>%
-  ggplot(aes(x = FA, 
-             y = rel_abund)) +
-  geom_jitter(aes(color = phylum),
-              size = 0.25,
-              alpha = 0.3) +
-  stat_pointinterval(point_interval = "median_qi",
-                     alpha = 0.65) +
-  facet_wrap(vars(phylum), nrow = 3) +
-  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
-  labs(y = "Relative Abundance (%)",
-       x = "",
-       color = "Phylum") +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 90,
-                                   hjust = 1),
-        panel.grid = element_blank(),
-        strip.background = element_blank(),
-        legend.position = "NA",
-        strip.text = element_text(size = 16)
-        )
-
-p_tax_FA
-
-cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
-          plot = p_tax_FA,
-          base_height = 11,
-          base_width = 9
-          )
-```
-
-## Compare extraction efficiency
-
-```{r extr_eff}
-FID_results_abundance_reported_long <- FID_results_abundance_no_stds %>% 
-  select(
-    sample_id, 
-    compound, 
-    deriv_efficiency, 
-    extr_efficiency
-  ) %>% 
-  pivot_longer(
-    !c(sample_id, compound),
-    names_to = "stage", 
-    values_to = "efficiency"
-  ) %>% 
-  mutate(
-    stage = case_when(
-      str_detect(stage, "deriv") ~ "Derivatization Efficiency",
-      str_detect(stage, "extr") ~ "Extraction Efficiency"
-    )
-  )
-
-FID_results_abundance_reported_long %>% 
-  ggplot(aes(x = stage, y = efficiency)) +
-  geom_boxplot(
-    outlier.shape = NA,
-    width = 0.3
-    ) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  labs(x = "",
-       y = "Efficiency") +
-  theme_classic()
-```
-
-## Example chromatogram
-```{r}
-# plot an example chromatogram
-
-sample_files[10] %>% # choosing arbitrary file to plot
-  iso_plot_continuous_flow_data(
-    # select data and aesthetics
-    data = c(2), color = id1, panel = id1,
-    # zoom in on time interval
-    time_interval = c(750, 4000),
-    # peak labels for all peaks > 2V
-    peak_bounds = TRUE,
-    peak_marker = FALSE,
-    #peak_label_size = 3
-    ) +
-    scale_color_npg() +
-    theme_classic() +
-    theme(strip.background = element_blank())
-
-```
-
-## Turnover distributions
-
-```{r turnover_across_soil}
-p_turnover_distributions <- turnover %>% 
-  filter(inc_time_d == 7) %>%
-  mutate(terrain = case_when(
-    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
-    terrain == "Marshall Mesa Grassland" ~ "Grassland",
-    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
-  mutate(terrain = forcats::fct_reorder(terrain, -u_d)) %>% 
-  ggplot(
-  aes(x = u_d, 
-      y = terrain,
-      color = terrain,
-      fill = terrain)) +
-  stat_slab(height = 0.5, 
-            alpha = 0.7,
-            color = "black") +
-  stat_pointinterval(color = "black",
-                     height = 0.2) +
-  geom_point(
-    color = "black",
-    shape = 124,
-    size = 5,
-    alpha = 0.5,
-    position = position_nudge(y = -.15)) +
-  scale_x_log10(
-    breaks = trans_breaks("log10", function(x) 10^x),
-    labels = trans_format("log10", math_format(10^.x))
-  ) +
-  annotation_logticks(sides = "b") +
-  scale_color_manual(values = terrain_color_swatch) +
-  scale_fill_manual(values = terrain_fill_swatch) +
-  theme_classic() +
-  labs(y = "Soil Type",
-       x = TeX("Turnover rate ($d^{-1}$)")) +
-  theme(axis.text.y = element_text(hjust = 1),
-        legend.position = "none")
-p_turnover_distributions
-```

### 2022-05-15 02_LH-SIP_Quantification.Rmd
Update 02_LH-SIP_Quantification.Rmd

@@
     # Explicitly define incubation parameters:
-
     # label is adjusted for the actual isotopic composition of the label within a specific terrain

### 2022-05-23 01_LH-SIP_Data_Reduction.Rmd
memory-corrected zero timepoints

--- 2022-05-11 01_LH-SIP_Data_Reduction.Rmd
@@
                      "cri0", "cri3", "cri7")) %>% 
-  rename(sample_id = id1)
+  rename(sample_id = id1,
+         Analysis = analysis) %>% 
+  select(Analysis, sample_id, compound, area2, area3, note, 
+          calibrated_d2H_without_memory, 
+          calibrated_d2H_without_memory_se,
+          calibrated_d2H_with_memory_correction, 
+          calibrated_d2H_with_memory_correction_se) %>% 
+  mutate(Analysis = as.numeric(Analysis)) %>% 
+  mutate(
+    calibrated_at2H_without_memory =
+      d2H_to_2F(calibrated_d2H_without_memory),
+    calibrated_at2H_without_memory_se =
+      d2H_to_2F(calibrated_d2H_without_memory_se),
+    calibrated_at2H_with_memory_correction =
+      d2H_to_2F(calibrated_d2H_with_memory_correction), 
+    calibrated_at2H_with_memory_correction_se =
+      d2H_to_2F(calibrated_d2H_with_memory_correction_se)
+  )
 ```
 
-# '########## DATA REDUCTION #############
+# `
 
-# Assimilation efficiency
+# Assimilation efficiency calcs
 
-## Reduce data and get linear model
+### Reduce data and get linear model
 
@@
 
-# Compound abundance
+# FID Data
 
@@
 
-## Calculate mass of analyte injected into GC-FID
+### Calculate mass of analyte injected into GC-FID
 
@@
 
-## Calculate fractional derivatization efficiency (21-PC)
+### Calculate fractional derivatization efficiency (21-PC)
 ```{r 21_PC}
@@
 
-## Calculate extraction efficiency (23-PC)
+### Calculate extraction efficiency (23-PC)
 
@@
 
-## Remove standards from soil abundances
+### Remove standards from soil abundances
 
@@
 
-## Generate Isoverse Peak Map
+### Generate Isoverse peak map
 ```{r}
@@
 
-## Remove readychecks, blanks, etc. from analysis
+### Remove readychecks, blanks, etc. from analysis
 ```{r}
@@
 
-## Check problematic peak assignments
+### Check problematic peak assignments
 ```{r}
@@
 
-## Export summary of unresolved peaks
+### Export summary of unresolved peaks
 ```{r}
@@
 
-## Assign incubation params
+# Metadata and cleanup
+
+### Assign incubation params
 ```{r}
@@
 
-## Extract zero timepoint values
+### Join memory-corrected data
+
 ```{r}
-zero_peaks <- peaks_mapped %>%
+peaks_mapped_mc <- peaks_mapped %>% 
+# Need to remove "BF" from Analysis number
+  mutate(Analysis = parse_number(Analysis)) %>%
+  select(-c(area2, area3)) %>% 
+  # Join
+  left_join(
+    LH_SIP_memcorr, 
+    by = c("Analysis", "sample_id", "compound"))
+```
+
+### Extract zero timepoint values
+These SIP measurements compare an enriched isotopic value to a starting isotopic composition. To have a time `t = 0` value, we need to define the starting point of our incubation.
+
+```{r}
+zero_peaks <- peaks_mapped_mc %>%
   filter(inc_time_d_str == "0 Days") %>%
@@
   group_by(soil_id, compound) %>% 
-  summarise(at2H_mn_zero = mean(at2H),
-            d2H_mn_zero = mean(d2H),
-            area2_mn_zero = mean(area2))
+  summarise(
+    # at2H at zero (no mc)
+    at2H_mn_zero = mean(calibrated_at2H_without_memory,
+                        na.rm = TRUE),
+    # Memory corrected value
+    at2H_mn_zero_mc = mean(calibrated_at2H_with_memory_correction, 
+                           na.rm = TRUE),
+    # d2H at zero (no mc)
+    d2H_mn_zero = mean(calibrated_d2H_without_memory, 
+                       na.rm = TRUE),
+    # Memory corrected value
+    d2H_mn_zero_mc = mean(calibrated_d2H_with_memory_correction, 
+                          na.rm = TRUE))
 
+# Cache the zero-timepoint dataframe
 zero_peaks_averaged %>% 
-  openxlsx::write.xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"),
+  openxlsx::write.xlsx(
+    file.path("cache", 
+              "IRMS", 
+              "zero_peaks_averaged.xlsx"),
     overwrite = TRUE)
-
-# zero_peaks_averaged <- read_xlsx(file.path("data", "IRMS", "zero_peaks_averaged.xlsx"))
 
@@
 peaks_mapped_with_zeros <- 
-  peaks_mapped %>%
+  peaks_mapped_mc %>%
   left_join(
@@
 
-# no zero samples
-# peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
-
 peaks_mapped_with_zeros <- peaks_mapped_with_zeros %>% 
-  mutate(
-    sample_id = substr(file_id, 10,14)
-    )
-```
-
-## Extract 3 day timepoint values
-
-```{r}
-three_day_peaks <- peaks_mapped %>%
-  filter(inc_time_d_str == "3 Days") %>%
-  group_by(t_series_id, compound) %>%
-  mutate(n_analyical_reps = n()) %>%
-  ungroup() %>%
-  # exclude ambiguous peaks
-  filter(!is_ambiguous)
-
-three_day_peaks_averaged <- three_day_peaks %>% 
-  group_by(soil_id, compound) %>% 
-  summarise(at2H_mn_three = mean(at2H),
-            d2H_mn_three = mean(d2H),
-            area2_mn_three = mean(area2))
-
-peaks_mapped_with_threes <- 
-  peaks_mapped %>%
-  left_join(
-    three_day_peaks_averaged,
-    by = c("soil_id", "compound")
-  )
-stopifnot(nrow(peaks_mapped_with_threes) == nrow(peaks_mapped))
-
-peaks_mapped_with_threes <- peaks_mapped_with_threes %>% 
-  mutate(
-    sample_id = substr(file_id, 10,14)
-    )
+  mutate(sample_id = substr(file_id, 10,14))
 ```
@@
   )
-
-peaks_mapped_with_threes_FID <- peaks_mapped_with_threes %>% 
-    left_join(
-    FID_results_abundance_no_stds, 
-    by = c("sample_id", "compound")
-  )
 ```
 
-## Correct for memory effect
+# Apply corrections
 
-This uses memory-effect corrected data. See SI.
+### Join raw and memory-corrected (mc) datasets
 
 ```{r}
-LH_SIP_memcorr <- LH_SIP_memcorr %>% 
-  select(sample_id, compound, area2, area3, note, 
-          calibrated_d2H_without_memory, 
-          calibrated_d2H_without_memory_se,
-          calibrated_d2H_with_memory_correction, 
-          calibrated_d2H_with_memory_correction_se) %>% 
-  mutate(
-    calibrated_at2H_without_memory = d2H_to_2F(calibrated_d2H_without_memory),
-    calibrated_at2H_without_memory_se = d2H_to_2F(calibrated_d2H_without_memory_se),
-    calibrated_at2H_with_memory_correction = d2H_to_2F(calibrated_d2H_with_memory_correction), 
-    calibrated_at2H_with_memory_correction_se = d2H_to_2F(calibrated_d2H_with_memory_correction_se)
-  )
-
+# peaks_mapped_with_zeros_FID_mc <- peaks_mapped_with_zeros_FID %>% 
+#   # Need to remove "BF" from Analysis number
+#   mutate(Analysis = parse_number(Analysis)) %>%
+#   # Join
+#   left_join(
+#     LH_SIP_memcorr, 
+#     by = c("Analysis", "sample_id", "compound"))
+# 
+# peaks_mapped_with_threes_FID_mc <- peaks_mapped_with_threes_FID %>% 
+#   # Need to remove "BF" from Analysis number
+#   mutate(Analysis = parse_number(Analysis)) %>%
+#   # Join
+#   left_join(
+#     LH_SIP_memcorr, 
+#     by = c("Analysis", "sample_id", "compound"))
 ```
 
-## Correct for PAME
+### Correct for PAME
 
@@
 # For 0 -3, 0-7 timepoints
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros_FID %>% 
+peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
   left_join(compound_nC_nH, by = "compound") %>% 
   mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
-
-# for 3-7 timepoints
-peaks_mapped_with_threes_FID <- peaks_mapped_with_threes_FID %>% 
-  left_join(compound_nC_nH, by = "compound") %>% 
-  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         `2F_FAME` = at2H,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk)
+         # define calibrated 2F
+         `2F_FAME` = calibrated_at2H_without_memory,
+         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
+         # define calibrated 2F mc
+         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
+         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
 ```
 
-## Separate analytes and standards, calculate F_0 se
+### Separate analytes and standards, calculate F_0 standard error
 
@@
 peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
-
-# For 3 -7 timepoints
-# Analytes
-peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_FID %>% 
-  # Don't want our standard compounds to be used for generation time calculations! x_x
-  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
-  # Also don't want our yeast-extract stimulated condition in our analyte pool
-  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
-  left_join(F_L_2F, by = "terrain")
-
-# Standards
-peaks_mapped_with_threes_standards<- peaks_mapped_with_threes_FID %>% 
-  filter(str_detect(compound, "STD"))
-
-# 23:0 and 21:0 PC standard errors at inc time zero
-# Determines our standard error in FAME measurements at F_0
-sF_0 <- peaks_mapped_with_threes_standards %>% 
-  # Select only 21 and 23 PC standards at initial time point
-  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
-         inc_time_d == 0) %>%
-  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
-  ungroup() %>% 
-  summarize(F_0_at2H_mn = mean(at2H),
-            F_0_at2H_se = sd(at2H))
-
-# Add sF_0 to analyte data
-
-peaks_mapped_with_threes_analytes <- peaks_mapped_with_threes_analytes %>% 
-  mutate(F_0_at2H_se = 
-           sF_0 %>% pull(F_0_at2H_se)
-         )
+  mutate(F_0_at2H_se = sF_0 %>% pull(F_0_at2H_se))
 
@@
 
-## Reduce columns
+### Eliminate extraneous columns
 
@@
 peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>%
-  mutate(time_course = "0d -->") %>%
+  # Add assimilation efficiency data
+  mutate(
+    a = d2H_assim_lm_summary$a_mn,
+    sa = d2H_assim_lm_summary$sa
+  ) %>% 
   # Column reduction
-  select(file_id,
+  select(Analysis,
          sample_id,
@@
          compound,
-         rel_area_FID,
          area_FID,
@@
          at2H_mn_zero,
-         F_0_at2H_se,
-         at2H,
+         at2H_mn_zero_mc, # MC
+         at2H, # not-corrected value
+         calibrated_at2H_without_memory,
+         calibrated_at2H_with_memory_correction, # MC
          area2_mn_zero,
@@
          compound_ug_per_g_soil,
+         a, # assimilation efficiency
          `2F_Me`,
          `2F_FAME`,
+         `2F_FAME_mc`, # MC
          `2F_alk`,
+         `2F_alk_mc`,  # MC
          F_label_mn,
-         F_label_se,
-         time_course
+         # Uncertainty terms:
+         F_label_se, # error in the label strength (pipetting error)
+         F_0_at2H_se, # error in the initial F_0 (instrument error)
+         calibrated_at2H_without_memory_se, # error in F_T
+         calibrated_at2H_with_memory_correction_se, # error in F_T, MC
+         sa, # error in assimilation efficiency (se of literature values)
   ) %>% 
@@
     )
-  ) %>% 
-  # Add assimilation efficiency data
-  mutate(
-    a = d2H_assim_lm_summary$a_mn,
-    sa = d2H_assim_lm_summary$sa
-  )
-
-peaks_mapped_with_threes_analytes_reduced <- peaks_mapped_with_threes_analytes %>% 
-  # Filter out 0d data points from this dataset
-  filter(inc_time_d != 0) %>% 
-  # Add a time course tag
-  mutate(time_course = "3d -->") %>% 
-  # Column reduction
-  select(file_id,
-         sample_id,
-         terrain,
-         soil,
-         inc_time_d,
-         inc_time_d_str,
-         compound,
-         rel_area_FID,
-         area_FID,
-         d2H_mn_three,
-         d2H,
-         at2H_mn_three,
-         F_0_at2H_se,
-         at2H,
-         area2_mn_three,
-         area2,
-         area_FID,
-         compound_ug_per_g_soil,
-         `2F_Me`,
-         `2F_FAME`,
-         `2F_alk`,
-         F_label_mn,
-         F_label_se,
-         time_course
-  ) %>% 
-  # Convert all unit dbls into unitless
-  mutate(
-    across(
-      where(is.numeric),
-      as.numeric
-    )
-  ) %>% 
-  # Add assimilation efficiency data
-  mutate(
-    a = d2H_assim_lm_summary$a_mn,
-    sa = d2H_assim_lm_summary$sa
   )

### 2022-05-23 01_LH-SIP_Data_Reduction.Rmd
added .RDS file extension to cached dfs

@@
 ---
+
+# Setup
+
+## Clear the environment
+
+```{r}
+rm(list=ls())
+```
 
@@
 
-# `
+# Data Reduction
 
-# Assimilation efficiency calcs
+## Assimilation efficiency calcs
 
@@
 
-# FID Data
+## FID Data
 
@@
 
-# IRMS Peak Mapping
+## IRMS Peak Mapping
 
@@
 
-# Metadata and cleanup
+## Metadata and cleanup
 
@@
 
-# Apply corrections
-
-### Join raw and memory-corrected (mc) datasets
-
-```{r}
-# peaks_mapped_with_zeros_FID_mc <- peaks_mapped_with_zeros_FID %>% 
-#   # Need to remove "BF" from Analysis number
-#   mutate(Analysis = parse_number(Analysis)) %>%
-#   # Join
-#   left_join(
-#     LH_SIP_memcorr, 
-#     by = c("Analysis", "sample_id", "compound"))
-# 
-# peaks_mapped_with_threes_FID_mc <- peaks_mapped_with_threes_FID %>% 
-#   # Need to remove "BF" from Analysis number
-#   mutate(Analysis = parse_number(Analysis)) %>%
-#   # Join
-#   left_join(
-#     LH_SIP_memcorr, 
-#     by = c("Analysis", "sample_id", "compound"))
-```
+## Apply corrections
 

### 2022-05-23 02_LH-SIP_Quantification.Rmd
added .RDS file extension to cached dfs

--- 2022-05-13 02_LH-SIP_Quantification.Rmd
@@
 
-## Load packages
+### Load packages
 Tidyverse required. Isoverse packages available at `isoverse.org`.
@@
 
-## Load sourced functions
+### Load sourced functions
 These functions are found in the `libs/` directory.
@@
 
-## Read RDS from cache
+### Read RDS from cache
 Cache is located in `cache/` directory.
 ```{r}
-LH_SIP_data <- readRDS(file = "cache/LH_SIP_data")
-LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
-LH_SIP_memcorr <- readRDS(file = "cache/LH_SIP_memcorr")
+LH_SIP_data <- readRDS(file = "cache/LH_SIP_data.RDS")
+LH_SIP_memcorr <- readRDS(file = "cache/LH_SIP_memcorr.RDS")
 ```
@@
     # Explicitly define incubation parameters:
-
-    # label is adjusted for the actual isotopic composition of the label within a specific terrain
-    f_label = F_label_mn,
-    # start time
-    t0 = case_when(
-      time_course == "0d -->" ~ 0,
-      time_course == "3d -->" ~ 3),
+    f_label = F_label_mn, # actual measured F_L
+    t0 = 0, # incubation start = 0
     d_t = inc_time_d - t0, # change in time
-    f_start = case_when(
-      time_course == "0d -->" ~at2H_mn_zero,
-      time_course == "3d -->" ~ at2H_mn_three),
+    f_start = at2H_mn_zero,
+    f_start_mc = at2H_mn_zero_mc,
     # use PAME-corrected 2F value

### 2022-05-24 02_LH-SIP_Quantification.Rmd
added RDS extension and memcorr turnover

@@
   # Combine 0d --> and 3d --> datasets
-  bind_rows(LH_SIP_data_3d_onwards) %>% 
   # Evaluate each row individually
@@
       FT = f_t_mc, # 2F at time t (at%) (memory corrected)
-      F0 = f_start, # 2F at t0 (at%)
+      F0 = f_start_mc, # 2F at t0 (at%)
       FL = f_label, # 2F of label (at%)
@@
 
+## Summarize turnover by experimental replicates
+
 ```{r}
-# Create a summarized dataframe grouped by experimental replicates
 turnover_summarized <- turnover %>% 
   group_by(
-    time_course,
     terrain, 
@@
 
-# Summarize by combining experimental replicates
+```
+
+## Summarize 2F by experimental replicates
+
+```{r}
 
@@
   ) %>% 
-  # FILTER OUT NON BACTERIAL COMPOUNDS
+  # Filter out long-chain compounds
   filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
@@
   )
+
+```
+
+## Weight values by abundance (rel_area_FID)
+
+```{r}
 
@@
     f_start = mean(at2H_mn_zero, na.rm = TRUE),
+    f_start_mc = mean(at2H_weighted_mc, na.rm = TRUE),
     f_t = `2F_alk_weighted`,
@@
       f_t - f_start < 0 ~ 0),
+
     #Do the same for memory-corrected data:
     dF_weighted_mc = case_when(
-      f_t_mc - f_start >= 0 ~ f_t_mc - f_start,
-      f_t_mc - f_start < 0 ~ 0),
+      f_t_mc - f_start_mc >= 0 ~ f_t_mc - f_start_mc,
+      f_t_mc - f_start_mc < 0 ~ 0),
 
@@
       FT = f_t_mc,
-      F0 = f_start,
+      F0 = f_start_mc,
       FL = f_label,
@@
 ```{r}
-turnover %>% saveRDS(file = "cache/turnover_rates")
+turnover %>% saveRDS(file = "cache/turnover_rates.RDS")
 
-turnover_summarized %>% saveRDS(file = "cache/turnover_summarized")
+turnover_summarized %>% saveRDS(file = "cache/turnover_summarized.RDS")
 
-weighted_time_course %>% saveRDS(file = "cache/turnover_weighted")
+weighted_time_course %>% saveRDS(file = "cache/turnover_weighted.RDS")
 ```

### 2022-05-24 03_data_viz.Rmd
added .RDS extensions

@@
 # Turnover data
-turnover <- readRDS("cache/turnover_rates")
+turnover <- readRDS("cache/turnover_rates.RDS")
 
@@
 
-turnover_summarized <- readRDS("cache/turnover_summarized")
+turnover_summarized <- readRDS("cache/turnover_summarized.RDS")
 
 # Weighted turnover data
-turnover_weighted <- readRDS("cache/turnover_weighted")
+turnover_weighted <- readRDS("cache/turnover_weighted.RDS")
 
 # LH-SIP data
-LH_SIP_data <- readRDS(file = "cache/LH_SIP_data")
-
-# LH-SIP data but with 3d as the starting timepoint
-LH_SIP_data_3d_onwards <- readRDS(file = "cache/LH_SIP_data_3d_onwards")
+LH_SIP_data <- readRDS(file = "cache/LH_SIP_data.RDS")
 
@@
 bacdive_FA <- readRDS(file = "cache/bacdive_FA")
-bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide")
+bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide.RDS")
 
 # IRMS chromatogram data
-sample_files <- readRDS(file = "cache/sample_files")
+sample_files <- readRDS(file = "cache/sample_files.RDS")
 ```
@@
   filter(
-    time_course == "0d -->",
     compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 

### 2022-05-24 01_LH-SIP_Data_Reduction.Rmd
added .rds extensions

@@
 sample_files <- iso_filter_files(sample_files, analysis %nin% problematic_analyses_num)
-
-# Cache the sample files for plotting
-saveRDS(sample_files, file = "cache/sample_files")
 
@@
          area_FID,
+         rel_area_FID,
          d2H_mn_zero,
@@
          calibrated_at2H_with_memory_correction, # MC
-         area2_mn_zero,
          area2,
@@
 saveRDS(peaks_mapped_with_zeros_analytes_reduced,
-        file = "cache/LH_SIP_data")
+        file = "cache/LH_SIP_data.RDS")
 
 saveRDS(peaks_mapped_with_threes_analytes_reduced,
-        file = "cache/LH_SIP_data_3d_onwards")
+        file = "cache/LH_SIP_data_3d_onwards.RDS")
 
 saveRDS(F_L_2F,
-        file = "cache/heavy_label_data")
+        file = "cache/heavy_label_data.RDS")
 
 saveRDS(d2H_assim_lm_summary,
-        file = "cache/d2H_assimilation")
+        file = "cache/d2H_assimilation.RDS")
 
 saveRDS(LH_SIP_memcorr,
-        file = "cache/LH_SIP_memcorr")
+        file = "cache/LH_SIP_memcorr.RDS")
+
+saveRDS(sample_files, 
+        file = "cache/sample_files.RDS")
 ```

### 2022-05-24 01_LH-SIP_Data_Reduction.Rmd
removed deprecated export fn

@@
 
+```{r}
+
+```
+
 ### Reduce data and get linear model
@@
     area_FID, 
-    rel_area_FID) %>% 
+    rel_area_FID
+  ) %>% 
   filter(compound == "PAIBE") %>% 
@@
 
-# For 0 -3, 0-7 timepoints
 peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
@@
 
-saveRDS(peaks_mapped_with_threes_analytes_reduced,
-        file = "cache/LH_SIP_data_3d_onwards.RDS")
-
 saveRDS(F_L_2F,

### 2022-05-24 03_data_viz.Rmd
removed timecourse option

@@
 # BacDive Data
-bacdive_FA <- readRDS(file = "cache/bacdive_FA")
+bacdive_FA <- readRDS(file = "cache/bacdive_FA.RDS")
 bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide.RDS")
@@
   filter(
-    time_course == "0d -->",
     inc_time_d == "7",

### 2022-05-24 02_LH-SIP_Quantification.Rmd
corrected weighted turnover for mc data

@@
     f_start = mean(at2H_mn_zero, na.rm = TRUE),
-    f_start_mc = mean(at2H_weighted_mc, na.rm = TRUE),
+    f_start_mc = mean(at2H_mn_zero_mc, na.rm = TRUE),
     f_t = `2F_alk_weighted`,
@@
 
+    # Calculate change in 2F:
     dF_weighted = case_when(
@@
 
-    #Do the same for memory-corrected data:
+    # Calculate change in 2F (MC):
     dF_weighted_mc = case_when(
@@
   ) %>%
+  # Summarize:
   dplyr::summarize_if(
@@
   ) %>%
+
+  # Calculate turnover:
   mutate(
@@
     gen_d_weighted = turnover_to_gen(u_d_weighted),
-    # Do the same for memory corrected data
+
+    # Memory-corrected turnover:
     u_d_mc_weighted = calculate_turnover(

### 2022-05-24 03_data_viz.Rmd
added hull around geom_points()

@@
 library(scales)       # CRAN v1.1.1
+library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
 ```
@@
 ```{r}
+hull_data <- 
+  turnover %>% 
+  drop_na() %>% 
+  group_by(terrain) %>% 
+  slice(chull(compound_ug_per_g_soil, u_d_mc)) %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  ))
+
 p_abundance_v_turnover <- turnover %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
   filter(inc_time_d != 0) %>% 
@@
     y = u_d_mc,
-    color = terrain #dF*10000
+    color = terrain
   )) +
-  geom_point(aes(size = dF*10000),
+  geom_point(
+    aes(size = dF_mc*10000),
     alpha = 0.6,
     ) +
+  geom_polygon(data = hull_data,
+               aes(fill = terrain),
+               show.legend = FALSE,
+               alpha = 0.05,
+               size = 0.15) +
   scale_color_manual(values = terrain_color_swatch) +
   theme_bw() +
-  labs(x = "µg analyte per g soil",
-       y = TeX("Turnover (d$^{-1}$)"),
+  labs(x = "µg analyte (/g soil)",
+       y = TeX("Turnover rate (d$^{-1}$)"),
        size = TeX("$ \\Delta ^2H$ (ppm)"),
@@
 
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
-                   plot = p_abundance_v_turnover,
-                   base_height = 6,
-                   base_width = 8)
+# 
+# cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
+#                    plot = p_abundance_v_turnover,
+#                    base_height = 6,
+#                    base_width = 8)
 ```

### 2022-06-07 03_data_viz.Rmd
FA abundances and changed F1 to dots

@@
 
+### Read detection limit data
+
+```{r}
+dl_df <- readxl::read_excel("data/detection_limit_calcs.xlsx")
+```
+
 ## Set color swatches
@@
 p_gen_time_mean
+
+cowplot::save_plot(
+  plot = p_gen_time_mean,
+  filename = "fig_output/generation_time_mean_mc.pdf",
+  base_height = 4,
+  base_width = 7
+)
 ```
@@
   ) +
-  geom_col() +
+  geom_point(size = 2) +
   geom_errorbar(aes(
@@
     xmax = u_d_mc + (0.5 * su_d_mc)),
-    color = "black",
-    width = 0.25
+    width = 0,
+    size = 1.1
     ) +
@@
   theme_classic() +
-  labs(x = TeX("Turnover ($d^{-1}$)"),
+  labs(x = TeX("Turnover ($day^{-1}$)"),
        title = terrain_choice) +
@@
   geom_point(
-    aes(size = dF_mc*10000),
+    #aes(size = dF_mc*10000),
     alpha = 0.6,
@@
                show.legend = FALSE,
-               alpha = 0.05,
+               alpha = 0.15,
                size = 0.15) +
@@
   theme_bw() +
-  labs(x = "µg analyte (/g soil)",
-       y = TeX("Turnover rate (d$^{-1}$)"),
+  labs(x = "µg analyte (per g soil)",
+       y = TeX("Turnover rate (day$^{-1}$)"),
        size = TeX("$ \\Delta ^2H$ (ppm)"),
@@
     strip.background = element_blank(),
-
+    legend.position = c(0.9, 0.87),
     panel.grid = element_blank(),
@@
 
-# 
-# cowplot::save_plot(filename = "fig_output/abundance_v_turnover.pdf",
-#                    plot = p_abundance_v_turnover,
-#                    base_height = 6,
-#                    base_width = 8)
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover_1p.pdf",
+                   plot = p_abundance_v_turnover,
+                   base_height = 6,
+                   base_width = 8)
 ```
@@
 
-## (Deprecated) Turnover plot
+## (DEPRECATED) Turnover plot
 
@@
 ```
+
+## (PASSING) Detection limit
+
+```{r}
+p_dl <- dl_df %>% 
+  ggplot(
+    aes(x = extraction_deriv_efficiency_frac*100,
+        y = detection_limit_cells,
+        fill = as.factor(extraction_deriv_efficiency_frac))) +
+  geom_col() +
+  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100)) +
+  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
+              labels = trans_format("log10", math_format(10^.x))) +
+  coord_cartesian(xlim = c(10, 110), ylim = c(1e4, 1e10)) +
+  scale_fill_grey(start = 0.4, end = 0.1) +
+  annotation_logticks(sides = "l") +
+  labs(
+    x = "Combined extraction and derivatization efficiency (%)",
+    y = TeX("$^2 H$ detection limit (cells)")
+  ) +
+  theme_bw() +
+  theme(
+    legend.position = "NA",
+    panel.grid.minor = element_blank(),
+    panel.grid.major.x = element_blank(),
+    axis.ticks = element_blank(),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 8)
+  )
+p_dl
+
+cowplot::save_plot(
+  plot = p_dl,
+  filename = "fig_output/detection_limit_cells.pdf",
+  base_height = 4,
+  base_width = 4
+)
+
+```
+
+## (FAILING) Fatty Acid Abundances
+
+```{r}
+turnover_summarized %>% 
+  filter(compound != "H2") %>% 
+  filter(compound != "i-16:0") %>% 
+  mutate(compound_edit = str_remove(compound, "-")) %>% 
+  mutate(C_num = parse_number(compound_edit)) %>% 
+  mutate(C_num = as.numeric(C_num)) %>% 
+  mutate(compound = forcats::fct_reorder(compound, C_num)) %>% 
+  ggplot(aes(x = compound,
+             y = area_FID,
+             fill = terrain,
+             color = terrain)) +
+  geom_col() +
+  facet_wrap(vars(terrain, inc_time_d),
+             scales = "free_y") +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  scale_color_manual(values = terrain_color_swatch) +
+  theme_bw() +
+  labs(x = "Analyte",
+       y = TeX("Peak Area ($pA \\cdot s$)"),
+       fill = "Terrain",
+       color = "Terrain") +
+  theme(
+    axis.text.x = element_text(angle = 90)
+  )
+```

### 2022-06-07 01_LH-SIP_Data_Reduction.Rmd
rename FAs with omega notation

@@
 source(file.path("libs", "d2H_to_2F.R"))                  # Convert delta to frac abund
-`%nin%` = Negate(`%in%`)                                  # "Not In" function
+source(file.path("libs", "rename_FAs.R"))                 # Rename FAs to correctly ID'd FAs
+`%nin%` = Negate(`%in%`)                                  # Nifty "Not In" function
 var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
@@
     )
-  )
+  ) %>% 
+  # Rename FAs to match correctly ID'd analytes
+  rename_FAs()
 
+```
+
+```{r}
+LH_SIP_memcorr <- LH_SIP_memcorr %>% rename_FAs()
 ```

### 2022-06-07 03_data_viz.Rmd
updated FA profile and det lim

@@
   scale_color_manual(values = c("black", color_choice)) +
+  scale_x_discrete(labels =)
   theme_classic() +
@@
     plot.title = element_text(hjust = 0.5),
+    panel.grid.major.x = element_line(linetype = "dotted")
   )
@@
 
-# cowplot::save_plot(
-#   filename = "fig_output/p_turnover.pdf",
-#   plot = p_turnover,
-#   base_width = 11,
-#   base_height = 4
-#   )
+cowplot::save_plot(
+  filename = "fig_output/turnover_plot.pdf",
+  plot = p_turnover,
+  base_width = 11,
+  base_height = 4
+  )
 
@@
   geom_col() +
+  geom_hline(yintercept = 1e10,
+             linetype = "dotted",
+             color = "red") +
+  geom_hline(yintercept = 1e9,
+             linetype = "dotted",
+             color = "blue") +
   scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100)) +
@@
 
-cowplot::save_plot(
-  plot = p_dl,
-  filename = "fig_output/detection_limit_cells.pdf",
-  base_height = 4,
-  base_width = 4
-)
+# cowplot::save_plot(
+#   plot = p_dl,
+#   filename = "fig_output/detection_limit_cells.pdf",
+#   base_height = 4,
+#   base_width = 4
+# )
 
@@
 
-## (FAILING) Fatty Acid Abundances
+## (PASSING) Fatty Acid Abundances
 
@@
   filter(compound != "i-16:0") %>% 
+  filter(compound != "16:1:ω5c") %>% 
   mutate(compound_edit = str_remove(compound, "-")) %>% 
@@
   scale_color_manual(values = terrain_color_swatch) +
-  theme_bw() +
+  theme_classic() +
   labs(x = "Analyte",
@@
   theme(
-    axis.text.x = element_text(angle = 90)
+    axis.text.x = element_text(angle = 90),
+    legend.position = "NA"
   )

### 2022-06-07 libs/rename_FAs.R
script for renaming FA in dfs

@@ -1,0 +1,17 @@
+#' Rename fatty acids 
+#' @param df a data frame containing a "compound" column containing FA names
+#' @return data frame with renamed FAs
+
+rename_FAs <- function(df) {
+  return(
+    df %>% 
+      mutate(compound = case_when(
+        compound == "16:1 cis 9" ~ "16:1ω7c",
+        compound == "16:1 trans 9" ~ "16:1:ω5c",
+        compound == "18:2 9,12" ~ "18:2",
+        compound == "18:1 cis 9" ~ "18:1ω9",
+        compound == "18:1 trans 9" ~ "18:1ω7",
+        TRUE ~ compound
+      ))
+  )
+}

### 2022-06-08 03_data_viz.Rmd
updated save output

@@
       terrain == "Marshall Mesa Grassland" ~ "Grassland",
-      terrain == "Niwot Ridge Tundra" ~ "Tundra"
-  )) %>% 
+      terrain == "Niwot Ridge Tundra" ~ "Tundra")
+    ) %>% 
+  # mutate(
+  #   compound = str_replace(
+  #     string = compound, 
+  #     pattern = "ω", 
+  #     replacement = "$\omega$")
+  # ) %>% 
   select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
@@
       x = u_d_mc,
-      y = compound,
+      y = TeX(compound),
       color = type,
-      fill = type
+      fill = type,
+      label = round(gen_d_mc, 1)
       )
@@
       ) +
+    # Uncomment to show generation times
+    # geom_text(
+    #   nudge_x = 0.05
+    # ) +
     coord_cartesian(xlim = c(0, 0.175)) +
@@
     scale_color_manual(values = c("black", color_choice)) +
-  scale_x_discrete(labels =)
     theme_classic() +
@@
 
-cowplot::save_plot(
-  filename = "fig_output/turnover_plot.pdf",
-  plot = p_turnover,
-  base_width = 11,
-  base_height = 4
-  )
+# ggsave(
+#   plot = p_turnover,
+#   filename = "fig_output/turnover_plot.pdf",
+#   device = cairo_pdf, # Need this for greek symbols to render correctly
+#   width = 11,
+#   height = 4
+#   )
 

### 2022-06-09 02_bacdive_taxonomy.Rmd
added .RDS extension
output data for supplemental dataset

@@
 ```{r}
-fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide")
+fatty_acids_wide_with_tax %>% saveRDS(file = "cache/bacdive_FA_wide.RDS")
+write_csv(fatty_acids_wide_with_tax, file = "data_output/bacdive_FAs.csv")
 
-fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA")
+fatty_acids_with_tax %>% saveRDS(file = "cache/bacdive_FA.RDS")
 

### 2022-06-09 03_data_viz.Rmd
ggsave pdf compatible

@@
   scale_alpha_discrete(range = c(0.2, 1)) +
-  scale_size_discrete(range = c(0.75, 1.25)) +
+  scale_size_discrete(range = c(1.5, 2)) +
+  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
   theme_classic() +
   labs(
-    x = "Time elapsed (d)",
+    x = "Time elapsed (days)",
     y = TeX("$ \\Delta ^2H$ (ppm)")
@@
         plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10))
+        axis.title.x = element_text(size = 10),
+        panel.grid.major.y = element_line(linetype = "dotted"))
 p_dF
 
-# cowplot::save_plot(
-#   filename = "fig_output/p_dF.pdf",
-#   plot = p_dF,
-#   base_width = 7,
-#   base_height = 4
-#   )
+cowplot::save_plot(
+  filename = "fig_output/p_dF.pdf",
+  plot = p_dF,
+  base_width = 11,
+  base_height = 4
+  )
 
@@
       x = u_d_mc,
-      y = TeX(compound),
+      y = compound,
       color = type,
       fill = type,
-      label = round(gen_d_mc, 1)
+      label = round(u_d_mc, 2)
       )
   ) +
-    geom_point(size = 2) +
+    geom_point(size = 3) +
     geom_errorbar(aes(
@@
       ) +
-    # Uncomment to show generation times
-    # geom_text(
-    #   nudge_x = 0.05
-    # ) +
+    #Uncomment to show generation times
+    geom_text(
+      nudge_x = 0.05
+    ) +
     coord_cartesian(xlim = c(0, 0.175)) +
@@
 #           )
+
+ggsave(p_tax_FA,
+       filename = "fig_output/p_tax_FA.png",
+       height = 11,
+       width = 9)
 ```
@@
 ```{r}
-p_dl <- dl_df %>% 
+dl_df_abbreviated <- dl_df %>% 
+  select(extraction_deriv_efficiency_frac, 
+         detection_limit_cells,
+         type) %>% 
+  pivot_wider(names_from = type,
+              values_from = detection_limit_cells)
+
+p_dl <- dl_df_abbreviated %>% 
   ggplot(
     aes(x = extraction_deriv_efficiency_frac*100,
-        y = detection_limit_cells,
-        fill = as.factor(extraction_deriv_efficiency_frac))) +
-  geom_col() +
+        y = average,
+        color = as.factor(extraction_deriv_efficiency_frac))) +
+  #geom_point(size = 1) +
+  geom_errorbar(aes(
+    ymin = lower, 
+    ymax = upper),
+    width = 0,
+    size = 4) +
   geom_hline(yintercept = 1e10,
@@
   coord_cartesian(xlim = c(10, 110), ylim = c(1e4, 1e10)) +
-  scale_fill_grey(start = 0.4, end = 0.1) +
+  scale_color_grey(start = 0.4, end = 0.1) +
   annotation_logticks(sides = "l") +
@@
 
-# cowplot::save_plot(
-#   plot = p_dl,
-#   filename = "fig_output/detection_limit_cells.pdf",
-#   base_height = 4,
-#   base_width = 4
-# )
+cowplot::save_plot(
+  plot = p_dl,
+  filename = "fig_output/detection_limit_cells.pdf",
+  base_height = 4,
+  base_width = 4
+)
 
@@
 ```{r}
-turnover_summarized %>% 
+p_FA <- turnover_summarized %>% 
   filter(compound != "H2") %>% 
@@
   )
+
+# ggsave(plot = p_FA,
+#        filename = "fig_output/FA_profiles.pdf",
+#        device = cairo_pdf,
+#        height = 7,
+#        width = 7)
+
+ggsave(plot = p_FA,
+       filename = "fig_output/FA_profiles.png",
+       height = 7,
+       width = 7)
 ```

### 2022-06-09 archive/qSIP_calculations_CRC.Rmd
archived scripts

---
title: "CRC Analysis"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
# global knitting options for code rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

# Load packages

```{r, message=FALSE, warning=FALSE}
# Libraries
library(tidyverse) # general data wrangling and plotting
library(forcats) # handling factors
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel) # nice looking ggplot labels
library(latex2exp) # latex parsing
library(ggdist) # ggplot distribution geoms
library(ggsignif) # ggplot significance markers
library(ggridges) # ggplot ridgeline geoms

# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
`%nin%` = Negate(`%in%`)
```

This analysis was run using [isoreader](http://isoreader.kopflab.org) version `r packageVersion("isoreader")` and [isoprocessor](http://isoprocessor.kopflab.org/) version `r packageVersion("isoprocessor")`.

# Turnover Calculation Function

```{r}
# Define a function to calculate turnover and generation time
# ARGUMENTS:
# FL = 0.005 # tracer strength = 0.5%
# a = 0.5 # incorporation efficiency of 50%
# FT = numeric # resulting isotopic enrichment
# F0 = numeric # beginning isotopic enrichment

gencalc <- function(a, FT, F0, FL, t) {
  case_when(
    t == 0 ~ NA_real_,
    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
  )
}

```

# Load data

## Load IRMS Data

### Load Metadata and Problematic Run Data

```{r}
mtda <- read_csv(file.path("data", "sample_metadata_2021.csv"))
sample_names <- mtda$id1

problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
problematic_analyses <- problematic_runs$Analysis
problematic_analyses_num <- parse_number(problematic_analyses)
```

### Load Peak Map

```{r}
# this information is often maintained in a csv or Excel file
peak_map <- 
  # initial peak map:
  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
  # corrected peak map:
  readxl::read_excel(file.path("data", "IRMS", "peak_maps_resolved.xlsx"))
peak_map
```

### Read raw IRMS data files

```{r, warning=FALSE}
# Set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files
# Isoverse will iteratively search subfolders. Huzzah! ^_^
data_path <- file.path("data", "IRMS", "raw_data")
ref_ratio <- get_standard("2H") %>% as.numeric()

# read files
iso_files_raw <- 
  # path to data files
  data_path %>% 
  # read data files in parallel for fast read
  iso_read_continuous_flow() %>%
  # filter out files with read errors (e.g. from aborted analysis)
  iso_filter_files_with_problems()
```

### Process file info & peak table

```{r}
# process file information
iso_files <- iso_files_raw %>% 
  # rename key file info columns
  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
  # parse text info into numbers
  iso_parse_file_info(number = analysis) %>% 
  # process other file information that is specific to the naming conventions
  # of this particular sequence
  iso_mutate_file_info(
    # what is the type of each analysis?
    type = case_when(
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "H3")           ~ "H3_factor",
      str_detect(id1, "F8")           ~ "F8_std",
      str_detect(id1, "F9")           ~ "F9_std",
      TRUE                            ~ "sample"
    ),
    # what was the concentration? (assuming Preparation = concentration or volume)
    concentration = 
      ifelse(type == "std",  
             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
               parse_number() %>% iso_double_with_units("ng/uL"),
             NA),
    # what folder are the data files in? (assuming folder = sequence)
    folder = basename(dirname(file_path))
  ) %>% 
  # focus only on the relevant file info, discarding the rest
  iso_select_file_info(
    folder, analysis, file_datetime, id1, type, concentration
  ) %>% 
  # add in additional sample metadata (could be any info)
  # note: this would typically be stored in / read from a csv or excel file
  iso_add_file_info(
    read_csv(file.path("data", "sample_metadata_2021.csv")),
    join_by = "id1"
  )

# set peak table from vendor data table with default isodat template
iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)

# focus on sample files
sample_files <- iso_filter_files(iso_files, type == "sample")

# EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
CRC_samples <- c("cri0", "cri3", "cri5", "cri7", "cr0f0x", "cr0f0y", "cr0f0z",
                 "cr0f3x", "cr0f3y", "cr0f3z", "cr0f7x", "cr0f7y", "cr0f7z")

biocrust_light_samples <- c("cri0", "cri3", "cri5", "cri7")

biocrust_dark_samples <- c("cr0f0x", "cr0f0y", "cr0f0z",
                           "cr0f3x", "cr0f3y", "cr0f3z", 
                           "cr0f7x", "cr0f7y", "cr0f7z")

sample_files <- iso_filter_files(sample_files, id1 %in% CRC_samples)

# EXCLUDE RUN WE'VE DEEMED PROBLEMATIC
# Should be okay, no CRC samples were problematic! ^_^
sample_files <- iso_filter_files(sample_files, analysis %nin% problematic_analyses_num)

```

### Show file information

```{r}
# display file information
iso_files %>% 
  iso_get_file_info() %>% select(-file_id, -folder) %>% 
  iso_make_units_explicit() %>% knitr::kable()
```

### Example chromatograms

```{r "example_chromatograms", fig.width=8, fig.height=8}
# plot an example chromatogram
sample_files[1] %>% # choosing arbitrary file to plot
iso_plot_continuous_flow_data(
 # select data and aesthetics
 data = c(2), color = id1, panel = id1,
 # zoom in on time interval
 time_interval = c(750, 4000),
 # peak labels for all peaks > 2V
 peak_bounds = TRUE,
 peak_marker = FALSE,
 peak_label = iso_format(rt),
 #peak_label_size = 3,
 peak_label_filter = analysis == 5685 & amp2 > 1
) + scale_color_npg() +
 theme_classic() +
 theme(strip.background = element_blank())
```

## Import GC-FID Data
```{r}
root <- file.path("data", "gc_fid_data_2020")
file_list = list.files(path = root)
file_list <- file_list %>% 
  str_subset("blank", negate = TRUE) %>% 
  str_subset("Blank", negate = TRUE) %>% 
  str_subset("GCMS-STD", negate = TRUE) %>% 
  str_subset("BLK", negate = TRUE) # remove procedural blanks
sample_names <- file_list %>% 
  str_replace("FID.....", "") %>% 
  str_replace("_100ul-nhex.xls", "") %>% 
  str_replace("_100ul.xls", "")

FID_all_data <-
  tibble(
    sample = sample_names,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

### Unnest FID integration details

```{r}
FID_results <- FID_all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # Specify chain length
  mutate(
    chain = `Peak Name` %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  # Rename these columns so we can join the IRMS and FID data
  # Important to specify what data comes from FID!
  rename("sample_id" = sample,
         "compound" = `Peak Name`,
         "rt_FID" = `Retention Time`,
         "area_FID" = `Area`,
         "height_FID" = `Height`,
         "rel_area_FID" = `Relative Area`,
         "rel_height_FID" = `Relative Height`,
         "amount_FID" = `Amount`
         )

FID_results_CRC <- FID_results %>% 
  filter(sample_id %in% CRC_samples)
```

# Peak Mapping

```{r}
sample_peak_table <- sample_files %>%
  iso_set_peak_table_from_isodat_vendor_data_table() %>%
  iso_get_peak_table() %>% 
  mutate(Analysis = substr(file_id, 1, 7),
         sample_id = substr(file_id, 10,15),
         sample_id = str_remove(sample_id, "1"),
         sample_id = str_remove(sample_id, "_"))
```

## Generate Isoverse Peak Map
```{r}
# Generate an isoverse peak map
peaks_mapped <- sample_peak_table %>%
  iso_map_peaks(peak_map, map_id = Analysis) %>%
  filter(!is.na(compound)) %>% 
  # Filter out runs that are on our problematic_runs list
  filter(Analysis %nin% problematic_runs) %>% 
  # Add some metadata!
  group_by(sample_id) %>% 
  # remove the "1" that is added
  mutate(sample_id = str_remove(sample_id, "1")) %>% 
  mutate(inc_time_d = case_when(
    sample_id %in% biocrust_light_samples ~ parse_number(sample_id),
    str_detect(sample_id, "0x") ~ 0,
    str_detect(sample_id, "0y") ~ 0,
    str_detect(sample_id, "0z") ~ 0,
    str_detect(sample_id, "3x") ~ 0,
    str_detect(sample_id, "3y") ~ 3,
    str_detect(sample_id, "3z") ~ 3,
    str_detect(sample_id, "7x") ~ 7,
    str_detect(sample_id, "7y") ~ 7,
    str_detect(sample_id, "7z") ~ 7)
    ) %>%
  mutate(
         inc_time_d_str = paste(inc_time_d, "Days"),
         f_label = 0.005,
         t_series_id = case_when(
           sample_id %in% biocrust_light_samples ~ "cri",
           TRUE ~ "cr0"
         ),
         soil_id = substr(t_series_id, 1,2),
         replicate_id = substr(t_series_id, 2,2),
         terrain = case_when(
           sample_id %in% biocrust_light_samples ~ "Biocrust Light",
           sample_id %in% biocrust_dark_samples ~ "Biocrust Dark"
        )
      )
```

## Check for problematic peak assignments
```{r}
problem_peaks <- iso_get_problematic_peak_mappings(peaks_mapped)

# UNCOMMENT IF NEEDED
# # Spit out peaks that need to be resolved
# peaks_mapped %>%
#   ungroup() %>%
#   select(Analysis, compound, rt) %>%
#   mutate(rt = round(rt, digits=0)) %>%
#   pivot_wider(
#     names_from = Analysis, 
#     names_prefix = "rt:",
#     values_from = rt, 
#     id_cols = compound, 
#     values_fn = function(x) paste(x, collapse = "; ")
#   ) %>%
#   openxlsx::write.xlsx(file.path("data", "IRMS", "peak_maps_resolve_CRC.xlsx"))
```

## Extract zero timepoint values
```{r}
zero_peaks <- peaks_mapped %>%
  filter(inc_time_d_str == "0 Days") %>%
  group_by(t_series_id, compound) %>%
  mutate(n_analyical_reps = n()) %>%
  ungroup() %>%
  # exclude ambiguous peaks
  filter(!is_ambiguous)

zero_peaks_averaged <- zero_peaks %>% 
  group_by(soil_id, compound) %>% 
  summarise(at2H_mn_zero = mean(at2H),
            d2H_mn_zero = mean(d2H),
            area2_mn_zero = mean(area2))

zero_peaks_averaged %>% 
  openxlsx::write.xlsx(file.path("data", "IRMS", "zero_peaks_averaged_CRC.xlsx"),
                       overwrite = TRUE)

# Join the zero-timepoint data with the peak map:
# This is the dataset we will use for generation time calculations
peaks_mapped_with_zeros <- 
  peaks_mapped %>%
  left_join(
    zero_peaks_averaged,
    by = c("soil_id", "compound")
  )
stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))

# no zero samples
# peaks_mapped_with_zeros %>% filter(is.na(zero_sample_id)) %>% View()
```

## Join IRMS and GC-FID Data

```{r}
peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
  left_join(FID_results, by = c("sample_id", "compound"))
```

```{r}
# Combine triplicate samples into one
FID_results_trip <- FID_results_CRC %>% 
  # Remove standards and fractions
  filter(sample_id != "FAME37.1") %>% 
  filter(sample_id != "TCBAME-2") %>% 
  filter(!str_detect(sample_id, "F1")) %>% 
  filter(!str_detect(sample_id, "F2")) %>% 
  filter(!str_detect(sample_id, "F3")) %>% 
  mutate(sample_rep = str_remove(sample_id, "[xyz]")) %>% 
  group_by(sample_rep, compound) %>%
  # Generate summary stats
  summarize(rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
            rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
            rel_height_FID_max = max(rel_height_FID, na.rm=TRUE),
            rel_height_FID_min = min(rel_height_FID, na.rm=TRUE),
            rt_FID = mean(rt_FID, na.rm=TRUE),
            rel_area_FID = mean(rel_area_FID, na.rm=TRUE),
            rel_height_FID = mean(rel_height_FID, na.rm=TRUE)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = "CRC")
```

## Remove standards from gencalcs
```{r}
# Don't want our standard compounds to be used for generation time calculations! x_x
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

## Summarize Analytical and Experimental Replicates

```{r}
peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
  group_by(terrain, inc_time_d, compound) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)
```

## Calculate turnover time
Turnover is calculated as below:

$$
\mu = - \frac{1}{t} \cdot (ln (\frac{F_T - a \cdot F_L}{F_0 - a \cdot F_L})
$$

```
# R code:
gencalc <- function(a, FT, F0, FL, t) {
  case_when(
    t == 0 ~ NA_real_,
    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
  )
}

```

Generation time is related to the turnover rate as below:
$$
g = \frac{ln(2)}{\mu}
$$

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

```{r}

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

# gen_calc_data_summarized %>% openxlsx::write.xlsx(file.path("data", "gen_calc_data_summarized.xlsx"))

```

# Plots

## Compound enrichment over time

```{r}
gen_calc_data_summarized %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             color = compound)) +
  geom_borderline() +
  geom_point() +
  facet_wrap(vars(terrain)) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_viridis_d() +
  theme_bw() +
  labs(x = "Incubation Time (Days)",
       y = "Mean %D")

```

## Compound enrichment over time with label strength

```{r}
gen_calc_data_summarized %>% 
  filter(compound != "i-16:0") %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             color = compound)) +
  geom_point() +
  geom_borderline() +
  geom_hline(yintercept = 0.5,
             color = "red") +
  facet_wrap(vars(terrain)) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_viridis_d() +
  labs(x = "Incubation Time (Days)",
       y = "Mean %D") +
  theme_bw()
```

## Chromatogram scaled by 2F

```{r "shaded chromatogram", fig.width=8, fig.height=8}

peaks_mapped_with_zeros_analytes %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c(option = "magma") +
  facet_wrap(~sample_id, ncol = 1) +
  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = TeX("$^2F$"),
         x = "Retention Time (s)",
         y = "Amplitude (mV)") +
  theme(strip.background = element_blank())

```

## Turnover Time, Broken by Terrain

```{r}
gen_calc_data %>% 
  filter(inc_time_d != 0,
         chain_num < 19) %>% 
  ggplot(
  aes(y = u_d, 
      x = terrain,
      color = terrain,
      fill = terrain)) +
  stat_slab(width = 0.25, 
            alpha = 0.7,
            color = "black") +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.07)) +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = TeX("Turnover ($d^{-1}$)"),
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria in biocrust") +
  theme(axis.text.y = element_text(),
    axis.text.x = element_text(angle = 45, hjust = 1))

```

## Generation time by terrain

```{r}
gen_calc_data %>% 
  filter(inc_time_d != 0,
         chain_num < 19) %>% 
  ggplot(
  aes(y = gen_d, 
      x = terrain,
      color = terrain,
      fill = terrain)) +
  stat_slab(width = 0.25, 
            alpha = 0.7,
            color = "black") +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.07)) +
  scale_fill_npg() +
  scale_color_npg() +
  #scale_y_log10() +
  #annotation_logticks(side = "l") +
  theme_classic() +
  labs(y = TeX("Generation Time (d)"),
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria in biocrust") +
  theme(axis.text.y = element_text(),
    axis.text.x = element_text(angle = 45, hjust = 1))

```

## Turnover time by compound

```{r}
gen_calc_data_summarized %>% 
  filter(inc_time_d != 0) %>% 
  mutate(compound = fct_reorder(compound, u_d)) %>% 
  ggplot(aes(x = compound,
             y = u_d,
             fill = u_d)) +
  geom_col(position = position_dodge()) +
  facet_wrap(vars(terrain, inc_time_d)) +
  scale_fill_viridis_c(option = "plasma") +
  labs(x = "Compound",
       y = TeX("Mean Turnover time ($d^{-1}$)"),
       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90, 
                               hjust = 1)
  )
```

## Generation time by compound

```{r}
gen_calc_data_summarized %>% 
  filter(inc_time_d != 0,
         compound %nin% c("a-15:0", "i-15:0")) %>%
  mutate(compound = fct_reorder(compound, u_d)) %>% 
  ggplot(aes(x = compound,
             y = gen_d,
             fill = u_d)) +
  geom_col(position = position_dodge()) +
  facet_wrap(vars(terrain, inc_time_d)) +
  scale_fill_viridis_c(option = "plasma") +
  scale_y_log10() +
  geom_label_repel(aes(label = round(gen_d, 2)),
                  size = 3,
                  nudge_y = 2,
                  color = "black") +
  labs(x = "Compound",
       y = TeX("Mean Generation time (d)"),
       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90, 
                               hjust = 1)
  )
```

### 2022-06-16 03_data_viz.Rmd
time to visible colony plot

@@
 ```
+
+## (PASSING) Visible colony
+
+```{r}
+# Function Definitions
+col_volumer <- function(a,b,c) {
+  # Volume of a half-ellipsoid of axes a,b, and c
+  vol = (4/3)*pi*a*b*c
+  vol = vol/2
+  return(vol)
+}
+
+cell_volumer_rod <- function(a,b,c) {
+  vol = a*b*c
+  return(vol)
+}
+
+cell_volumer_cocci <- function(r) {
+  vol = (4/3)*pi*(r^3)
+  return(vol)
+}
+
+# Define parameters of colony needed to be visible:
+xax <-  1000 # x axis, y axis, z axis, in µm
+yax <-  1000
+zax <-  (1/6)*1000
+
+colony_vol = col_volumer(xax, yax, zax) # generate the volume of a half-ellipsoid, circular base, 1/6th as high as wide
+
+colony_data <- read_csv(file.path('data/bac_data.csv'))
+colony_data <- colony_data %>%
+  # Calculate cell volumes
+  mutate(cell_volume = 
+           case_when(shape == 'cocci' ~ cell_volumer_cocci(mjr_axis/2),
+                     shape == 'rod' ~ cell_volumer_rod(mjr_axis, mnr_axis, mnr_axis)
+                     )
+         ) %>%
+  # Calculate number of cells required for given volume
+  mutate(num_cells_reqd = colony_vol/cell_volume) %>%
+
+  # Calculate number of divisions required to reach visible colony
+  mutate(divis_reqd = log2(num_cells_reqd)) %>%
+
+  # Calculate hours required to reach that many divisions
+  mutate(time_reqd_hr = divis_reqd*gen_time_hr)
+
+# Get mean value for cells required in single colony
+cells_in_single_colony <- colony_data %>% 
+  pull(num_cells_reqd) %>% 
+  mean()
+
+colony_data_2 <- 
+  tibble(gen_time_hr = seq(1, 5000, by = 1),
+         num_cells_required = cells_in_single_colony,
+         divis_reqd = log2(num_cells_required),
+         time_reqd_hr = divis_reqd*gen_time_hr,
+         gen_time_d = gen_time_hr / 24,
+         time_reqd_d = time_reqd_hr / 24)
+```
+
+```{r}
+p_time_reqd_for_visible_colony <- colony_data_2 %>% 
+  ggplot(aes(x = gen_time_d,
+             y = time_reqd_d)) +
+  geom_line() +
+  geom_vline(xintercept = 60,
+             color = tundra_color,
+             linetype = "dotted") +
+    geom_vline(xintercept = 26,
+             color = grassland_color,
+             linetype = "dotted") +
+    geom_vline(xintercept = 19.4,
+             color = conifer_color,
+             linetype = "dotted") +
+  annotation_logticks(sides = "l") +
+  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x)
+              ) +
+  theme_classic() +
+  labs(
+    x = "Maximum potential generation time (days)",
+    y = "Time required for visible colony (days)")
+p_time_reqd_for_visible_colony
+
+cowplot::save_plot(
+  filename = "fig_output/time_for_visible_colony.pdf",
+  plot = p_time_reqd_for_visible_colony,
+  base_height = 4,
+  base_width = 4.5
+)
+```

### 2022-06-16 03_data_viz.Rmd
commented out geom_hline for p_dl

@@
     size = 4) +
-  geom_hline(yintercept = 1e10,
-             linetype = "dotted",
-             color = "red") +
-  geom_hline(yintercept = 1e9,
-             linetype = "dotted",
-             color = "blue") +
+  # geom_hline(yintercept = 1e10,
+  #            linetype = "dotted",
+  #            color = "red") +
+  # geom_hline(yintercept = 1e9,
+  #            linetype = "dotted",
+  #            color = "blue") +
   scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100)) +

### 2022-06-17 01_LH-SIP_Data_Reduction.Rmd
filter assim efficiencies 0<a<1

@@
   filter(term == "`Water dD`") %>% 
+  filter(estimate >= 0,
+         estimate <= 1) %>% 
   summarize(sa = sd(estimate, na.rm = TRUE),
@@
 # Export as RDS
+
+# Peak data
 saveRDS(peaks_mapped_with_zeros_analytes_reduced,
@@
 
+# Label 2F
 saveRDS(F_L_2F,
@@
 
+# Assimilation Efficiency Linear Model
 saveRDS(d2H_assim_lm_summary,
@@
 
+# Asssimilation Efficiency data
+saveRDS(d2H_assim_lm,
+        file = "cache/d2H_assimilation_lm.RDS")
+
+# Memory-corrected data
 saveRDS(LH_SIP_memcorr,
@@
 
+# Full dataset
 saveRDS(sample_files, 

### 2022-06-17 03_data_viz.Rmd
assimilation efficiency histogram

@@
   mutate(gen_d = turnover_to_gen(u_d_mn))
+```
+
+### Load d2H assimilation data
+
+```{r}
+d2H_assim <- read_xlsx("data/d2H_data_isotope_measurements.xlsx", sheet = 'lipids')
 ```
@@
       fill = type,
-      label = round(u_d_mc, 2)
+      label = round(u_d_mc, 4)
       )
@@
     #Uncomment to show generation times
-    geom_text(
-      nudge_x = 0.05
-    ) +
+    # geom_text(
+    #   nudge_x = 0.05
+    # ) +
     coord_cartesian(xlim = c(0, 0.175)) +
@@
 
-# ggsave(
-#   plot = p_turnover,
-#   filename = "fig_output/turnover_plot.pdf",
-#   device = cairo_pdf, # Need this for greek symbols to render correctly
-#   width = 11,
-#   height = 4
-#   )
+ggsave(
+  plot = p_turnover,
+  filename = "fig_output/turnover_plot.pdf",
+  device = cairo_pdf, # Need this for greek symbols to render correctly
+  width = 11,
+  height = 4
+  )
 
@@
 
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover_1p.pdf",
-                   plot = p_abundance_v_turnover,
-                   base_height = 6,
-                   base_width = 8)
+# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_1p.pdf",
+#                    plot = p_abundance_v_turnover,
+#                    base_height = 6,
+#                    base_width = 8)
 ```
@@
 ```
+
+## (PASSING) Assimilation efficiency histogram
+
+```{r}
+# Find Fatty acid analytes manually
+
+fas_in_d2H_assim <- d2H_assim %>% 
+  filter(str_detect(Analyte, "acid") |
+           str_detect(Analyte, "ate")) %>% 
+  pull(Analyte) %>% 
+  unique()
+
+d2H_assim_lm <- d2H_assim %>% 
+  # Select columns of interest
+  select(
+    org_id,
+    exp_id,
+    Analyte,
+    `Water dD`,
+    `Lipid dD`
+  ) %>% 
+  # Filter to only look at FAs
+  filter(Analyte %in% fas_in_d2H_assim) %>% 
+  drop_na() %>% 
+  # Group by organism, experiment, analyte
+  group_by(
+    org_id,
+    exp_id,
+    Analyte
+  ) %>% 
+  # Filter out samples with three or fewer observations
+  # (so that we can do a linear model)
+  filter(n() > 3) %>% 
+  tidyr::nest(
+    data = c(`Water dD`, `Lipid dD`)
+  ) %>% 
+  mutate(
+    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
+    estimates = purrr::map(fit, broom::tidy),
+    summary = purrr::map(fit, broom::glance)
+  ) %>% tidyr::unnest(estimates) %>%
+  filter(term == "`Water dD`") %>% 
+  filter(estimate >= 0,
+         estimate <= 1) %>% 
+  select(c(term, estimate))
+
+mean_assim <- d2H_assim_lm %>% pull(estimate) %>% mean(na.rm = TRUE)
+se_assim <- d2H_assim_lm %>% pull(estimate) %>% sd(na.rm = TRUE)
+
+```
+
+```{r}
+p_d2H_assim_lm <- d2H_assim_lm %>% 
+  ggplot(aes(x = estimate)) +
+  geom_histogram(binwidth = 0.1,
+                 color = tundra_color,
+                 fill = tundra_color) +
+  geom_vline(xintercept = mean_assim,
+             linetype = "dotted") +
+  geom_errorbar(
+    aes(
+      xmin = mean_assim - (0.5*se_assim),
+      xmax = mean_assim + (0.5*se_assim),
+      y = 16
+        )) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
+  coord_cartesian(ylim = c(0, 26),
+                  expand = FALSE) +
+  labs(x = "Assimilation Efficiency",
+       y = "Count") +
+  theme_classic()
+p_d2H_assim_lm
+
+# cowplot::save_plot(
+#   plot = p_d2H_assim_lm,
+#   filename = "fig_output/assim_efficiency.pdf",
+#   base_height = 4,
+#   base_width = 4
+# )
+```

### 2022-06-23 01_LH-SIP_Data_Reduction.Rmd
export label data

@@
   ))
+
+write_csv(F_L_2F, file = "data/Label_2H_Data/dD_summarized.csv")
 ```

### 2022-06-23 03_data_viz.Rmd
ggsaves

@@
 source(file.path("libs", "turnover_to_gen.R"))
+source(file.path("libs", "rename_FAs.R"))                
 `%nin%` = Negate(`%in%`) # "Not In" function
@@
 p_FA <- turnover_summarized %>% 
+  rename_FAs() %>% 
   filter(compound != "H2") %>% 
@@
   )
+p_FA
+
+ggsave(plot = p_FA,
+       filename = "fig_output/FA_profiles.pdf",
+       device = cairo_pdf,
+       height = 7,
+       width = 7)
 
 # ggsave(plot = p_FA,
-#        filename = "fig_output/FA_profiles.pdf",
-#        device = cairo_pdf,
+#        filename = "fig_output/FA_profiles.png",
 #        height = 7,
 #        width = 7)
-
-ggsave(plot = p_FA,
-       filename = "fig_output/FA_profiles.png",
-       height = 7,
-       width = 7)
 ```

### 2022-06-23 libs/rename_FAs.R
updated FA names

@@ -8,9 +8,10 @@ rename_FAs <- function(df) {
       mutate(compound = case_when(
         compound == "16:1 cis 9" ~ "16:1ω7c",
         compound == "16:1 trans 9" ~ "16:1:ω5c",
-        compound == "18:2 9,12" ~ "18:2",
-        compound == "18:1 cis 9" ~ "18:1ω9",
-        compound == "18:1 trans 9" ~ "18:1ω7",
+        compound == "18:2 9, 12" ~ "18:2",
+        compound == "18:1 cis 9" ~ "18:1ω9c",
+        compound == "18:1 trans 9" ~ "18:1ω7c",
+        compound == "17:0 cyclo" ~ "cyclo 17:0",
         TRUE ~ compound
       ))
   )

### 2022-07-07 01_LH-SIP_Data_Reduction.Rmd
export for SI

@@
          rel_area_FID,
+         rt,
          d2H_mn_zero,
@@
          area2,
+         area3,
          area_FID,
@@
         file = "cache/sample_files.RDS")
+
+# Export dataset for SI
+writexl::write_xlsx(
+  peaks_mapped_with_zeros_analytes_reduced %>% 
+    filter(compound != "H2"),
+  path = "cache/LH_SIP_data.xlsx"
+  )
 ```

### 2022-11-02 99_labeling_calculations.Rmd
required incubation times

--- 2019-12-28 labeling_calculations.Rmd
@@
 library(latex2exp)
-library(isotopia) # install.packages("devtools"); devtools::install_github("sebkopf/isotopia")
+library(isotopia) # install.packages("devtools"); devtools::install_github("isoverse/isotopia")
 
@@
 
+```{r}
+# plot
+inc_times %>% 
+  # spread the different F_t_type values
+  select(-F_t.percent, -inc_time.s) %>%  spread(F_t_type, inc_time.log10) %>% 
+  # color factor
+  mutate(label_strength = paste("F_L =", F_L.percent, "at%") %>% factor() %>% fct_inorder()) %>% 
+  # send to plot
+  ggplot() +
+  aes(
+    gen_time.log10, 
+    color = label_strength, 
+    fill = label_strength
+    ) + 
+  geom_ribbon(
+    mapping = aes(ymin = min, ymax = max), 
+    alpha = 0.1
+    ) +
+  geom_line(
+    mapping = aes(y = average), 
+    size = 2) +  
+  labs(title =
+         sprintf("Required incubation times to reach enrichment\nbetween %.0f\u2030 and %.0f\u2030 (thick line = %.0f\u2030)",
+                 dD_enrich_min, dD_enrich_max, dD_enrich_avg),
+       linetype = "target incubation times") +
+  scale_x_continuous(
+    "generation time", 
+    breaks = gen_times$gen_time.log10,
+    labels = function(x) gen_times$label,
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    "required incubation time",
+    breaks = y_breaks$inc_time.log10,
+    labels = function(x) y_breaks$label,
+    expand = c(0, 0)
+  ) +
+  scale_color_brewer("tracer strength", palette = "Set1") +
+  scale_fill_brewer("tracer strength", palette = "Set1") +
+  coord_cartesian(ylim = range(y_breaks$inc_time.log10)) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 12),
+        axis.text.y = element_text(size = 12),
+        axis.title = element_blank(),
+        panel.grid.minor = element_blank())
+```
+
 ## Enrichment curves by generation time
@@
 ```{r "enrichment_curves_zoomed2", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
-p1 + coord_cartesian(ylim = c(0.01, 0.025))
+p1 + coord_cartesian(ylim = c(0.01, 0.025), xlim = c(0, 300))
 ```

### 2022-11-02 02_LH-SIP_Quantification.Rmd
added abundance weighted mean def

@@
 
-    # calculate generation time, converting negatives to zero
-    gen_d = turnover_to_gen(u_d),
-
-    # And a memory corrected gen time:
-    gen_d_mc = turnover_to_gen(u_d_mc),
-
     # Calculate uncertainty in turnover rate
@@
     na.rm = TRUE
+  ) %>% 
+  # Calculate generation time based off of mean of replicates
+  mutate(
+    # calculate generation time, converting negatives to zero
+    gen_d = turnover_to_gen(u_d),
+
+    # And a memory corrected gen time:
+    gen_d_mc = turnover_to_gen(u_d_mc),
   )
@@
 ## Weight values by abundance (rel_area_FID)
+
+Abundance weighted mean is calculated by:
+
+$$
+weighted \space mean = 
+\frac{\displaystyle\sum_{i = 1} ^{N} x_{i}w_{i}}{\displaystyle\sum_{i=1} ^{N} x_{i}}
+$$
+
+Where $x_i$ is the fractional abundance of compound $i$ and $w_i$ is the relative abundance of compound $i$.
 

### 2022-11-02 03_data_viz.Rmd
updated growth/abundance plot

@@
 library(forcats)      # CRAN v0.5.1      
-library(isoreader)    # CRAN v1.3.0    
-library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
-library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
+#library(isoreader)    # CRAN v1.3.0    
+#library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7 
+#library(isotopia)     # [github::isoverse/isotopia] v0.5.8     
 library(readxl)       # CRAN v1.3.1       
@@
 library(ggridges)     # CRAN v0.5.3     
-library(ggalluvial)   # CRAN v0.12.3   
 library(cowplot)      # CRAN v1.1.1      
@@
       fill = type,
-      label = round(u_d_mc, 4)
+      label = round(gen_d_mc, 2)
       )
@@
     #Uncomment to show generation times
-    # geom_text(
-    #   nudge_x = 0.05
-    # ) +
+    geom_text(
+      nudge_x = 0.05
+    ) +
     coord_cartesian(xlim = c(0, 0.175)) +
@@
 p_turnover
-
-ggsave(
-  plot = p_turnover,
-  filename = "fig_output/turnover_plot.pdf",
-  device = cairo_pdf, # Need this for greek symbols to render correctly
-  width = 11,
-  height = 4
-  )
+# 
+# ggsave(
+#   plot = p_turnover,
+#   filename = "fig_output/turnover_plot.pdf",
+#   device = cairo_pdf, # Need this for greek symbols to render correctly
+#   width = 11,
+#   height = 4
+#   )
 
@@
 
-## (PASSING) Abundance versus turnover
+## Abundance versus turnover
 
@@
   geom_polygon(data = hull_data,
-               aes(fill = terrain),
+               aes(fill = terrain,
+                   color = terrain),
                show.legend = FALSE,
@@
 #                    base_width = 8)
+```
+
+### Draft 2
+```{r}
+# Compute hull data
+hull_data <- 
+  turnover %>% 
+  drop_na() %>% 
+  group_by(terrain) %>% 
+  slice(chull(compound_ug_per_g_soil, u_d_mc)) %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  ))
+
+# Determine fit data
+turnover_cleaned <- turnover %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>%
+  filter(inc_time_d != 0, compound != "H2")
+
+turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
+turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
+
+p_abundance_v_turnover2 <- turnover %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(aes(
+    x = compound_ug_per_g_soil,
+    y = u_d_mc
+  )) +
+  # Individual data points
+  geom_point(
+    aes(color = terrain),
+    alpha = 0.6,
+    ) +
+  geom_polygon(
+    data = hull_data,
+    aes(
+       fill = terrain,
+       color = terrain
+       ),
+     show.legend = FALSE,
+     alpha = 0.15,
+     size = 0.15
+    ) +
+  geom_smooth(
+    method = "lm",
+    formula = "y~x",
+    se = FALSE,
+    color = "gray",
+    size = 0.3,
+    linetype = "dotted"
+  ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  theme_bw() +
+  labs(
+    x = "µg analyte (per g soil)",
+    y = TeX("Turnover rate (day$^{-1}$)"),
+    size = TeX("$ \\Delta ^2H$ (ppm)"),
+    color = " "
+  ) +
+  theme(
+    strip.background = element_blank(),
+    legend.position = c(0.9, 0.87),
+    panel.grid = element_blank(),
+  )
+p_abundance_v_turnover2
+
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
+                   plot = p_abundance_v_turnover2,
+                   base_height = 6,
+                   base_width = 8)
+
 ```

### 2022-11-04 03_data_viz.Rmd
added inset plot to figure 2

@@
 
-## (PASSING) Memory effect on gen_d
+## Memory effect on gen_d
 
@@
 
-## (PASSING) dF plot
+## F1A: dF plot
 Using memory-corrected values
@@
 
-## (PASSING) Turnover plot
+## F1B: Turnover plot
 
@@
 
-## Abundance versus turnover
+## F2: Abundance versus turnover
 
@@
 turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
+writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
+writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")
 
@@
     x = "µg analyte (per g soil)",
-    y = TeX("Turnover rate (day$^{-1}$)"),
+    y = TeX("Compound-specific growth rate (day$^{-1}$)"),
     size = TeX("$ \\Delta ^2H$ (ppm)"),
@@
     strip.background = element_blank(),
-    legend.position = c(0.9, 0.87),
+    legend.position = c(0.9, 0.55),
+    legend.background = element_blank(),
     panel.grid = element_blank(),
@@
 
-## (PASSING) Literature Rates of Cell Turnover by Method
+### Inset Plot
+
+```{r}
+p_abundance_v_turnover_inset <- turnover %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(aes(
+    x = compound_ug_per_g_soil,
+    y = u_d_mc
+  )) +
+  # Individual data points
+  geom_point(
+    aes(color = terrain),
+    alpha = 0.6,
+    size = 2
+    ) +
+  coord_cartesian(xlim = c(0, 5), ylim = c(0, 0.01)) +
+  scale_color_manual(values = terrain_color_swatch) +
+  theme_bw() +
+  labs() +
+  theme(
+    strip.background = element_blank(),
+    legend.position = "NA",
+    legend.background = element_blank(),
+    panel.grid = element_blank(),
+    axis.title = element_blank(),
+    panel.background = element_blank()
+  )
+p_abundance_v_turnover_inset
+```
+
+### Draft 2 with inset plot!
+
+```{r}
+p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
+  draw_plot(
+    p_abundance_v_turnover_inset, 
+    x = 0.63, 
+    y = 0.63, 
+    width = 0.35, 
+    height = 0.35
+    )
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
+                   plot = p_abundance_v_turnover_w_inset,
+                   base_height = 6,
+                   base_width = 8)
+```
+
+## F3: Literature Rates of Cell Turnover by Method
 
@@
 
-## (PASSING) BacDive FA profiles
+## SF: BacDive FA profiles
 
@@
 
-## (FAILING) Compare extraction efficiency
+## Compare extraction efficiency
 
@@
 
-## (PASSING) Example chromatogram
+## Example chromatogram
 ```{r}
@@
 
-## (PASSING) Turnover distributions
+## Turnover distributions
 
@@
 
-## (PASSING) Detection limit
+## SF: Detection limit
 
@@
 
-## (PASSING) Fatty Acid Abundances
+## SF: Fatty Acid Abundances
 
@@
 
-## (PASSING) Visible colony
+## SF: Visible colony
 
@@
 
-## (PASSING) Assimilation efficiency histogram
+## SF: Assimilation efficiency histogram
 

### 2022-11-28 03_data_viz.Rmd
new figure draft

@@
 # Summarized turnover
-
 turnover_summarized <- readRDS("cache/turnover_summarized.RDS")
@@
 sample_files <- readRDS(file = "cache/sample_files.RDS")
+
+# IRMS Error Estimation
+sF_0 <- readRDS(file = "cache/sF_0.RDS")
+
 ```
@@
 
-lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means) %>% 
+lit_turnover_w_ours <- lit_turnover %>% 
+  bind_rows(turnover_means) %>% 
   # Convert to generation time:
@@
 
+### Draft 2
+
+```{r}
+p_dF2 <- turnover_summarized %>% 
+  filter(
+    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
+  ungroup() %>% 
+  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
+  left_join(
+    turnover_weighted %>% 
+      select(terrain, inc_time_d, dF_weighted_mc), 
+    by = c("terrain", "inc_time_d")) %>% 
+  group_by(
+    terrain,
+    inc_time_d
+  ) %>% 
+  pivot_longer(
+    cols = c(dF_mc, dF_weighted_mc),
+    values_to = "dF", 
+    names_to = "type"
+  ) %>% 
+  mutate(compound = case_when(
+    type == "dF_weighted_mc" ~ "Weighted Mean",
+    TRUE ~ compound
+  )) %>%
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
+  )) %>%
+
+  ggplot(
+    aes(
+      x = inc_time_d,
+      y = dF * 10000, # convert from at% to ppm
+      group = compound,
+      color = terrain,
+      fill = terrain,
+      alpha = type,
+      size = type
+    )
+  ) +
+  geom_borderline(
+    color = "gray",
+    alpha = 1,
+    size = 0.5
+    ) +
+  geom_point() +
+  facet_wrap(vars(terrain)) +
+  scale_color_manual(values = terrain_color_swatch) +
+  scale_fill_manual(values = terrain_fill_swatch) +
+  scale_alpha_discrete(range = c(0.2, 1)) +
+  scale_size_discrete(range = c(1.5, 2)) +
+  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
+  theme_classic() +
+  labs(
+    x = "Time elapsed (days)",
+    y = TeX("$ \\Delta ^2H$ (ppm)")
+  ) +
+  theme(legend.position = "none",
+        strip.background = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        axis.title.x = element_text(size = 10),
+        panel.grid.major.y = element_line(linetype = "dotted"))
+p_dF2
+
+```
+
 ## F1B: Turnover plot
@@
   geom_col() +
-  geom_text(nudge_y = 0.05, size = 2) +
+  #geom_text(nudge_y = 0.05, size = 2) +
   coord_flip(ylim = c(0, 0.5)) +
@@
 #                    base_width = 10)
+```
+
+### Draft 2
+
+```{r}
+
+# Colorblind friendly palette:
+lit_values_swatch_3 <- c(
+  "#20968d", # gray green
+  "#6269EB", # blue
+  "#E0187B", # pink
+  "#26AFE1" # light blue 
+  )
+p_lit_turnover_w_ours2 <- lit_turnover_w_ours %>%
+  filter(method_type != "Microscopy") %>% 
+  ggplot(
+  aes(
+    x = -n,
+    y = u_d_mn,
+    fill = method_type,
+    label = round(gen_d, 1)
+    )
+    ) +
+  geom_col() +
+  scale_fill_manual(
+    values = lit_values_swatch_3
+  ) +
+  # scale_fill_viridis_d(
+  #   begin = 0,
+  #   end = 0.8
+  # ) +
+  coord_flip(ylim = c(0, 0.5)) +
+  labs(
+    y = TeX("Turnover (d$^{-1}$)"),
+    fill = "Method"
+  ) +
+  theme_classic() +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.line.y = element_blank(),
+    legend.position = c(0.85, 0.8),
+    legend.background = element_rect(color = "black"),
+    legend.text = element_text(size = 15),
+    legend.title = element_blank(),
+  )
+p_lit_turnover_w_ours2
+# 
+# cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
+#                    plot = p_lit_turnover_w_ours2,
+#                    base_height = 8,
+#                    base_width = 10)
+
+```
+
+### Draft 2 Inset
+
+```{r}
+ p_lit_turnover_w_ours_inset <- lit_turnover_w_ours %>%
+  filter(method_type != "Microscopy") %>%
+  ggplot(
+    aes(
+      x = u_d_mn, 
+      y = method_type,
+      color = method_type
+      )
+  ) +
+  geom_boxplot(width = 0.2) +
+  coord_cartesian(xlim = c(0, 0.5)) +
+  #ggdist::stat_pointinterval() +
+  scale_color_manual(
+    values = lit_values_swatch_3
+  ) +
+  labs(
+    x = "",
+    y = "",
+    fill = "Method"
+  ) +
+  theme_classic() +
+  theme(
+    legend.position = "NA"
+  )
+p_lit_turnover_w_ours_inset
+```
+
+### Draw with inset
+
+```{r}
+p_literature2_w_inset <- ggdraw(p_lit_turnover_w_ours2) +
+  draw_plot(
+    p_lit_turnover_w_ours_inset, 
+    x = 0.63, 
+    y = 0.23, 
+    width = 0.35, 
+    height = 0.35
+    )
+p_literature2_w_inset
 ```
@@
 ```
+
+## SF: IRMS Error Assessment
+
+```{r}
+# Pull the IRMS standard error for this experiment from the error of measuring standards
+IRMS_standard_error <- sF_0 %>% select(F_0_at2H_se) %>% pull()
+paste0("The standard error of IRMS is +/- ", IRMS_standard_error, "% (", IRMS_standard_error*10000, " ppm)")
+
+test_standard_error_u <- tibble(
+  a = 1,
+  FT = IRMS_standard_error, # standard error in atom%
+  F0 = 0.00000000000000000001, # start at zero
+  t = seq(1, 100, by = 1), # time ranging between 0 and 100 days
+  FL = 100, # label strength in atom%
+  u = calculate_turnover(
+    a = a,
+    FT = FT,
+    F0 = F0,
+    t = t,
+    FL = FL
+  )
+)
+
+test_standard_error_u %>% 
+  ggplot(
+    aes(
+      x = t,
+      y = u
+    )
+  ) +
+    geom_line() +
+  labs(
+    x = "Incubation Time",
+    y = "Growth rate (day-1)",
+    caption = paste0("Growth estimate resulting from", round(IRMS_standard_error*10000,4), " ppm F2H error across incubation times" )
+  )
+```
+
+```{r}
+error_testing <- turnover %>% 
+  select(inc_time_d, dF, f_label, a, u_d_mc) %>% 
+  mutate(F0 = 0) %>% 
+  filter(
+    inc_time_d != 0,
+    !is.na(dF)) %>% 
+  mutate(FT_se = IRMS_standard_error) %>% 
+  mutate(
+    u_d_FT_se = calculate_turnover(
+      a = a, 
+      FT = FT_se,
+      F0 = F0,
+      FL = f_label,
+      t = inc_time_d
+      ),
+    turnover_ratio = u_d_FT_se / u_d_mc
+  )
+
+error_testing %>% 
+  ggplot(
+    aes(
+      x = u_d_FT_se,
+      fill = as.factor(inc_time_d),
+      #shape = as.factor(f_label)
+      )
+  ) +
+  geom_histogram() +
+  labs(
+    shape = "Label Strength (at%)",
+    fill = "Incubation Time (Days)"
+  )
+
+error_testing_summary <- error_testing %>% 
+  group_by(inc_time_d, f_label) %>% 
+  summarize(
+    u_d_FT_se_mn = mean(u_d_FT_se, na.rm = TRUE),
+    FT_se_mn = mean(FT_se, na.rm = TRUE)
+    ) %>% 
+  rename(
+    sensitivity_FT = FT_se_mn,
+    sensitivity_u_d = u_d_FT_se_mn
+    ) %>% 
+  mutate(
+    sensitivity_u_hr = sensitivity_u_d * 24,
+    sensitivity_u_min = sensitivity_u_hr * 60,
+    sensitivity_u_sec = sensitivity_u_min * 60
+  ) %>% 
+  select(inc_time_d, f_label, sensitivity_FT, sensitivity_u_d, sensitivity_u_hr, sensitivity_u_min, sensitivity_u_sec)
+
+```
+
+The resolution of LH-SIP is defined as the standard error of the IRMS instrument ($F_{SE}$) propagated through the turnover time calculation:
+
+$$
+\mu = - \frac{1}{t}ln(\frac{F_{SE} - a \cdot F_L}{F_0 - a \cdot F_L})
+$$
+
+Plugging in our standard error of:
+```{r}
+paste0("The standard error of IRMS is +/- ", IRMS_standard_error, "% (", IRMS_standard_error*10000, " ppm)")
+```
+
+```{r}
+knitr::kable(error_testing_summary)
+```

### 2022-11-28 02_LH-SIP_Quantification.Rmd
commented

@@
       # Uncertainties:
-      sF_0 = F_0_at2H_se,
-      sF_L = F_label_se,
-      sF_T = calibrated_at2H_without_memory_se,
-      sa = sa
+      sF_0 = F_0_at2H_se, # uncertainty in IRMS measurement
+      sF_L = F_label_se, # uncertainty in label strength
+      sF_T = calibrated_at2H_without_memory_se, # uncertainty in FT due to memory-effect calculation
+      sa = sa # uncertainty in assimilation efficiency
     ),

### 2022-11-28 01_LH-SIP_Data_Reduction.Rmd
added SE of IRMS at t = 0

@@
     file.path("cache", 
-              "IRMS", 
               "zero_peaks_averaged.xlsx"),
@@
   )
-stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped))
+stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped_mc))
 
@@
 
+# Standard Error of IRMS measurements at time zero
+saveRDS(sF_0,
+        file = "cache/sF_0.RDS")
+
 # Memory-corrected data

### 2022-12-17 03_data_viz.Rmd
supp figures

@@
 p_gen_time_mean
-
-cowplot::save_plot(
-  plot = p_gen_time_mean,
-  filename = "fig_output/generation_time_mean_mc.pdf",
-  base_height = 4,
-  base_width = 7
-)
-```
+# 
+# cowplot::save_plot(
+#   plot = p_gen_time_mean,
+#   filename = "fig_output/generation_time_mean_mc.pdf",
+#   base_height = 4,
+#   base_width = 7
+# )
+```
+## Memory effect on u_d
 
@@
 p_dF
-
-cowplot::save_plot(
-  filename = "fig_output/p_dF.pdf",
-  plot = p_dF,
-  base_width = 11,
-  base_height = 4
-  )
-
+# 
+# cowplot::save_plot(
+#   filename = "fig_output/p_dF.pdf",
+#   plot = p_dF,
+#   base_width = 11,
+#   base_height = 4
+#   )
+#   
 ```
@@
 
+# Calculate summary statistics and export them
 turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
 turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
+
+turnover_corr_test <- broom::tidy(
+  cor.test(
+    x = turnover_cleaned$compound_ug_per_g_soil,
+    y = turnover_cleaned$u_d_mc,
+    method = "pearson"
+  )
+  )
+
 writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
 writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")
-
+writexl::write_xlsx(turnover_corr_test, path = "data_output/turnover_corr_test.xlsx")
+
+# Plot it with the linear model!
 p_abundance_v_turnover2 <- turnover %>% 
@@
 
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
-                   plot = p_abundance_v_turnover2,
-                   base_height = 6,
-                   base_width = 8)
+# 
+# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
+#                    plot = p_abundance_v_turnover2,
+#                    base_height = 6,
+#                    base_width = 8)
 
@@
     )
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
-                   plot = p_abundance_v_turnover_w_inset,
-                   base_height = 6,
-                   base_width = 8)
+p_abundance_v_turnover_w_inset
+
+# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
+#                    plot = p_abundance_v_turnover_w_inset,
+#                    base_height = 6,
+#                    base_width = 8)
 ```
@@
 ```
+
+## SF: µ vs. 1/B
+
+### Compound-specific
+
+```{r}
+turnover_cleaned %>% 
+  ggplot(
+    aes(
+    x = 1/compound_ug_per_g_soil,
+    y = u_d_mc,
+    color = terrain
+    )
+  ) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(
+    method = "lm",
+    formula = "y~x",
+    se = FALSE
+  ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  labs(
+    x = "1/µg analyte per g soil",
+    y = "µ (days)"
+  ) +
+  theme_bw()
+```
+
+### Site-specific
+
+```{r}
+total_biomass <- turnover_cleaned %>% 
+  group_by(terrain) %>% 
+  summarize(
+    total_ug_per_g_soil = sum(compound_ug_per_g_soil, na.rm = TRUE)
+  )
+
+turnover_weighted_w_totals <- turnover_weighted %>% 
+  filter(inc_time_d == 7) %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  left_join(total_biomass, by = "terrain")
+
+p_turnover_totals <- turnover_weighted_w_totals %>% 
+  ggplot(
+    aes(
+      x = total_ug_per_g_soil,
+      y = u_d_mc_weighted
+    )
+  ) +
+  geom_point(aes(color = terrain),
+             size = 3) +
+  geom_smooth(
+    method = "lm",
+    formula = "y~x",
+    se = FALSE,
+    linetype = "dotted",
+    color = "gray",
+    size = 0.5
+  ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  labs(
+    x = "B (µg)",
+    y = TeX("µ $d^{-1}$"),
+    caption = "Where B is total biomass measured at a given site, µg per g soil",
+    color = ""
+  ) +
+  theme_bw() +
+  theme(
+    legend.position = "NA"
+  )
+p_turnover_totals
+```
+
+```{r}
+saveRDS(turnover_weighted_w_totals, file = "cache/turnover_weighted_w_totals.RDS")
+
+F2_draft3 <- cowplot::plot_grid(
+  p_abundance_v_turnover_w_inset,
+  p_turnover_totals,
+  rel_widths = c(2, 1),
+  rel_heights = c(2, 1),
+  labels = c("A", "B")
+)
+F2_draft3
+```
+
+## SF: Sensitivity Testing
+
+### at2H se
+
+```{r}
+LH_SIP_data %>% 
+  ggplot(
+    aes(
+      x = calibrated_at2H_without_memory_se,
+      y = calibrated_at2H_with_memory_correction_se,
+      color = inc_time_d_str
+    )
+  ) + 
+  geom_point(
+    alpha = 0.5
+  ) +
+  geom_abline(
+    slope = 1,
+    color = "red")
+```
+
+### IRMS instrument error
+
+```{r}
+instrument_error <- mean(LH_SIP_data$F_0_at2H_se)
+instrument_error_u_d <- calculate_turnover(
+  a = 0.7,
+  FL = 0.5,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error,
+  t = 7
+)
+
+instrument_error_test <- crossing(
+  t = seq(1, 30, by = 0.1),
+  FL = c(0.1, 0.25, 0.5, 1, 2.5, 5)
+) %>% mutate(
+  a = 0.7,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error,
+  u_d = calculate_turnover(
+    a = a,
+    FT = FT,
+    F0 = F0,
+    FL = FL,
+    t = t
+  )
+)
+
+instrument_error_test %>% 
+  ggplot(
+    aes(
+      x = t,
+      y = u_d,
+      color = as.factor(FL)
+    )
+  ) +
+  geom_line() +
+  geom_point(
+    y = instrument_error_u_d,
+    x = 7,
+    size = 2,
+    color = "black",
+    shape = 1
+    ) +
+  scale_color_viridis_d() +
+  theme_classic() +
+  labs(
+    x = "Incubation Time (days)",
+    y = TeX("Growth Rate Uncertainty (day $^{-1})"),
+    color = "Tracer Strength (%)"
+  )
+```
+
+### IRMS instrument "turnover"
+
+```{r}
+
+instrument_turnover <- turnover_summarized %>% 
+  mutate(
+    instrument_u_d = calculate_turnover(
+      a = a, # Assimilation efficiency defined in data reduction step
+      FT = F_0_at2H_se, # 2F instrument error (at%)
+      F0 = 0.0000000000000000000001, # 2F at t0 (at%)
+      FL = f_label, # 2F of label (at%)
+      t = d_t # change in time
+      ),
+    instrument_over_actual_u_d = instrument_u_d / u_d_mc
+  ) %>%
+  filter(inc_time_d == 7) %>% 
+  group_by(compound, terrain) %>% 
+  summarize(
+    instrument_u_d = instrument_u_d,
+    u_d_mc = u_d_mc,
+    instrument_over_actual_u_d_mn = mean(
+      instrument_over_actual_u_d, na.rm = TRUE
+      )
+    ) %>% 
+  filter(
+    !is.na(instrument_over_actual_u_d_mn),
+    is.finite(instrument_over_actual_u_d_mn)
+    ) %>% 
+  filter(!compound %in% c("20:0", "22:0", "24:0", "18:0", "cyclo 17:0"))
+
+instrument_frac_error <- mean(instrument_turnover$instrument_over_actual_u_d_mn)
+
+paste0("The accuracy of IRMS is such that we can accurately quantify deuterium incorporation corresponding to ", round(instrument_frac_error *100, 2), "% of an organism's growth rate.")
+
+```
+
+## Turnover MC effect
+
+```{r}
+turnover_summarized %>% 
+  ggplot(aes(
+    x = u_d,
+    y = u_d_mc,
+    color = as.factor(inc_time_d)
+  )) +
+  geom_point() +
+  geom_abline(linetype = "dashed") +
+  labs(
+    x = "Growth Rate (day^-1)",
+    y = "Memory Corrected Growth Rate (day^-1)"
+  )
+```
+
+```{r}
+turnover_summarized %>% 
+  filter(inc_time_d == 7) %>% 
+  pivot_longer(
+    cols = c(u_d, u_d_mc),
+    names_to = "corrected",
+    values_to = "u_d") %>% 
+  group_by(compound) %>%
+  mutate(y = paste(round(mean(rt), 0), compound)) %>% 
+  ungroup() %>% 
+  arrange(desc(y)) %>% 
+  ggplot(
+    aes(
+      x = u_d,
+      y = y,
+      color = corrected,
+      size = area2
+      )
+  ) +
+    geom_point() +
+  facet_wrap(vars(terrain))
+```

### 2022-12-17 02_LH-SIP_Quantification.Rmd
changed area columns to numeric

@@
 turnover_summarized <- turnover %>% 
+  mutate(
+    area2 = as.numeric(area2),
+    area3 = as.numeric(area3)
+  ) %>% 
   group_by(

### 2023-01-06 01_LH-SIP_Data_Reduction.Rmd
select relevant columns for export

@@
 source(file.path("libs", "rename_FAs.R"))                 # Rename FAs to correctly ID'd FAs
-`%nin%` = Negate(`%in%`)                                  # Nifty "Not In" function
 var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
@@
 # EXCLUDE RUN WE'VE DEEMED PROBLEMATIC
-sample_files <- iso_filter_files(sample_files, analysis %nin% problematic_analyses_num)
+sample_files <- iso_filter_files(sample_files, !analysis %in% problematic_analyses_num)
 
@@
 
-## Load memory-corrected IRMS data
+## Load memory-corrected IRMS data!
 
 ```{r}
-LH_SIP_memcorr <- readxl::read_excel("data/samples_data_memory_corrected.xlsx") %>% 
+LH_SIP_memcorr <- readxl::read_excel("data/samples_data_memory_corrected_20221228.xlsx") %>% 
 # Trim it down
-  select(-c(standard, is_std_peak, folder, file_datetime, id2, individual, injection_volume,
-            gc_method, map_id, gc_ramp, group, peak_type, ref_nr, calib_peak, peak_nr,
-            is_ref, rt_start, rt, rt_end, n_overlapping, n_matches, use_in_calib, d2H_in_calib, d2H_resid, 
-            d2H_calib_points)) %>% 
-  filter(id1 %nin% c("cr0f0x", "cr0f0y", "cr0f0z",
+  select(-c(type, # or `standard` if using original mc dataset 
+            #is_std_peak,
+            folder, 
+            file_datetime, 
+            id2, 
+            #individual,
+            #injection_volume,
+            #gc_method,
+            #map_id, 
+            gc_ramp, 
+            group, 
+            #peak_type,
+            #ref_nr,
+            #calib_peak, 
+            peak_nr,
+            #is_ref,
+            rt_start,
+            rt, 
+            rt_end, 
+            n_overlapping,
+            n_matches,
+            #use_in_calib,
+            #d2H_in_calib, 
+            #d2H_resid, 
+            d2H_calib_points
+            )
+         ) %>% 
+  filter(!id1 %in% c("cr0f0x", "cr0f0y", "cr0f0z",
                      "cr0f3x", "cr0f3y", "cr0f3z",
@@
   select(Analysis, sample_id, compound, area2, area3, note,
+          below_area_range, 
+          calibrated_d2H_without_area,
+          calibrated_d2H_without_area_se,
           calibrated_d2H_without_memory, 
@@
   mutate(Analysis = as.numeric(Analysis)) %>% 
+  # Convert Delta Values in Permil (vs. VSMOW) to fractional abundance (at%)
   mutate(
-    calibrated_at2H_without_memory =
-      d2H_to_2F(calibrated_d2H_without_memory),
-    calibrated_at2H_without_memory_se =
-      d2H_to_2F(calibrated_d2H_without_memory_se),
-    calibrated_at2H_with_memory_correction =
-      d2H_to_2F(calibrated_d2H_with_memory_correction), 
-    calibrated_at2H_with_memory_correction_se =
-      d2H_to_2F(calibrated_d2H_with_memory_correction_se)
+    # Without area correction:
+    calibrated_at2H_without_area = d2H_to_2F(calibrated_d2H_without_area),
+    calibrated_at2H_without_area_se = d2H_to_2F(calibrated_d2H_without_area_se),
+    # With Area, without memory correction:
+    calibrated_at2H_without_memory = d2H_to_2F(calibrated_d2H_without_memory),
+    calibrated_at2H_without_memory_se = d2H_to_2F(calibrated_d2H_without_memory_se),
+    # With memory correction:
+    calibrated_at2H_with_memory_correction = d2H_to_2F(calibrated_d2H_with_memory_correction), 
+    calibrated_at2H_with_memory_correction_se = d2H_to_2F(calibrated_d2H_with_memory_correction_se)
   )
@@
 # Data Reduction
-
-## Assimilation efficiency calcs
-
-```{r}
-
-```
 
@@
   filter(
-    compound %nin% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
+    !compound %in% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
     str_detect(sample_id, "FAME", negate = TRUE),
@@
 peaks_mapped <- peaks_mapped %>% 
-  filter(Analysis %nin% problematic_runs)
+  filter(!Analysis %in% problematic_runs)
 ```
@@
   ) %>% 
+  # REPAIR out-of-area t=0 datapoints:
+  mutate(
+    calibrated_at2H_with_memory_correction =
+      case_when(
+        below_area_range == TRUE & inc_time_d == 0 ~ at2H_mn_zero,
+        TRUE ~ calibrated_at2H_with_memory_correction
+        ),
+    below_area_range = 
+      case_when(
+        below_area_range == TRUE & inc_time_d == 0 ~ FALSE,
+        below_area_range == TRUE ~ TRUE,
+        below_area_range == FALSE ~ FALSE
+      )
+  ) %>% 
+  # REMOVE peaks that are outside area range of accurate correction!
+  filter(below_area_range == FALSE) %>% 
   # Column reduction
@@
          at2H, # not-corrected value
-         calibrated_at2H_without_memory,
-         calibrated_at2H_with_memory_correction, # MC
+         calibrated_at2H_without_area, # F_T, no area corr
+         calibrated_at2H_without_memory, # F_T, no memcorr
+         calibrated_at2H_with_memory_correction, # F_T, MC!
          area2,
@@
          F_0_at2H_se, # error in the initial F_0 (instrument error)
-         calibrated_at2H_without_memory_se, # error in F_T
-         calibrated_at2H_with_memory_correction_se, # error in F_T, MC
+         calibrated_at2H_without_area_se, # error in F_T, no area corr
+         calibrated_at2H_without_memory_se, # error in F_T, no memcorr
+         calibrated_at2H_with_memory_correction_se, # error in F_T, MC!
          sa, # error in assimilation efficiency (se of literature values)

### 2023-01-06 02_LH-SIP_Quantification.Rmd
create averaged growthrate dataset

@@
 output: html_document
+editor_options:
+  chunk_output_type: console
 ---
@@
 Tidyverse required. Isoverse packages available at `isoverse.org`.
+
 ```{r, message=FALSE, warning=FALSE}
@@
 source(file.path("libs", "turnover_to_gen.R"))            # Turnover rate to generation time
-`%nin%` = Negate(`%in%`)                                  # "Not In" function
 var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
@@
 
-# Calculate Turnover
+# Quantification
+
+## Calculate Turnover
 
@@
 turnover <- LH_SIP_data %>% 
-  # Combine 0d --> and 3d --> datasets
-  # Evaluate each row individually
-  ungroup() %>%
+  # CORRECT MC'd data so that it never is less than natural abundance at2H
   mutate(
-    # Explicitly define incubation parameters:
+    calibrated_at2H_with_memory_correction = 
+      case_when(
+        calibrated_at2H_with_memory_correction < at2H_mn_zero ~ at2H_mn_zero,
+        calibrated_at2H_with_memory_correction >= at2H_mn_zero ~ calibrated_at2H_with_memory_correction
+      )
+  ) %>% 
+  ungroup() %>%                             # Evaluate each row individually
+  mutate(
+
+    # Define incubation parameters:
     f_label = F_label_mn,                   # actual measured F_L
-    t0 = 0, # incubation start = 0
-    d_t = inc_time_d - t0, # change in time
-    f_start = at2H_mn_zero,
-    f_start_mc = at2H_mn_zero_mc,
-    # use PAME-corrected 2F value
-    f_t = `2F_alk`,
+    t0 = 0,                                 # incubation start t = 0 days:
+    d_t = inc_time_d - t0,                  # incubation start t = 0 days:
+    f_start_mc = at2H_mn_zero,              # use natabund values for t = 0
+    f_start = at2H_mn_zero,                 # use non-mc'd values for t = 0 samples
+    f_t = `2F_alk`,                         # use PAME-corrected 2F value
     f_t_mc = `2F_alk_mc`,                   # memory corrected value
-    # delta 2F: change in 2F enrichment over time t
+
+    # delta 2F: change in enrichment over time t
     dF = case_when(
       f_t - f_start >= 0 ~ f_t - f_start,
-      f_t - f_start < 0 ~ 0),
+      f_t - f_start < 0 ~ 0
+      ),
+
+    dF = case_when(
+      inc_time_d == 0 ~ 0,
+      TRUE ~ dF
+    ),
+
     # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
     u_d = calculate_turnover(
-      a = a, # Assimilation efficiency defined in data reduction step
+      a = a,                      # Assimilation efficiency
       FT = f_t,                   # 2F at time t (at%)
@@
       FL = f_label,               # 2F of label (at%)
-      t = d_t # change in time
+      t = d_t                     # change in time (days)
       ),
@@
       f_t_mc - f_start >= 0 ~ f_t_mc - f_start,
-      f_t_mc - f_start < 0 ~ 0),
+      f_t_mc - f_start < 0 ~ 0
+      ),
+
+    dF_mc = case_when(
+      inc_time_d == 0 ~ 0,
+      TRUE ~ dF_mc
+    ),
 
@@
     u_d_mc = calculate_turnover(
-      a = a, # Assimilation efficiency defined in data reduction step
-      FT = f_t_mc, # 2F at time t (at%) (memory corrected)
-      F0 = f_start_mc, # 2F at t0 (at%)
+      a = a,                     # Assimilation efficiency
+      FT = f_t_mc,               # 2F at time t (at%) (mc'd)
+      F0 = f_start_mc,           # 2F at t=0 (at%)
       FL = f_label,              # 2F of label (at%)
-      t = d_t # change in time
+      t = d_t                    # change in time (days)
       ),
@@
       sF_L = F_label_se,        # uncertainty in label strength
-      sF_T = calibrated_at2H_without_memory_se, # uncertainty in FT due to memory-effect calculation
+      sF_T =                    # uncertainty in FT due to memory-effect calculation
+        calibrated_at2H_without_memory_se, 
       sa = sa # uncertainty in assimilation efficiency
@@
   )
+
+turnover_avg <- turnover %>% 
+  # Average turnover across 3d and 7d incubations  
+  group_by(terrain, compound) %>%                  # do operation by terrain and compound
+  filter(inc_time_d != 0) %>%                      # remove 0 timepoint for averaging
+  # average the 3d and 7d timepoint values together
+  mutate(
+    u_d_mn = mean(u_d, na.rm = TRUE),
+    u_d_mc_mn = mean(u_d_mc, na.rm = TRUE),
+    gen_d_mn = turnover_to_gen(u_d_mn),
+    gen_d_mc_mn = turnover_to_gen(u_d_mc_mn)
+    ) %>% 
+  pivot_wider(
+    names_from = inc_time_d,
+    values_from = c(u_d, u_d_mc)
+  ) %>%
+  mutate(inc_time_d = as.numeric(parse_number(inc_time_d_str))) %>%
+  filter(inc_time_d == 7) %>% 
+  select(-c(u_d_3, u_d_7, u_d_mc_3, u_d_mc_7, inc_time_d, inc_time_d_str))
+  # select(
+  #   u_d_mn,
+  #   u_d_mc_mn,
+  #   gen_d_mn,
+  #   gen_d_mc_mn,
+  #   u_d_3,
+  #   u_d_7,
+  #   u_d_mc_3,
+  #   u_d_mc_7
+  # ) %>%
+
 ```
@@
 
+# For averaged 3d and 7d turnover
+turnover_summarized_avg <- turnover_avg %>% 
+  mutate(
+    area2 = as.numeric(area2),
+    area3 = as.numeric(area3)
+  ) %>% 
+  group_by(
+    terrain, 
+    compound
+  ) %>% 
+  dplyr::summarize_if(
+    is.numeric, 
+    mean, 
+    na.rm = TRUE
+  ) %>% 
+  # Calculate generation time based off of mean of replicates
+  mutate(
+    # calculate generation time, converting negatives to zero
+    gen_d = turnover_to_gen(u_d_mn),
+
+    # And a memory corrected gen time:
+    gen_d_mc = turnover_to_gen(u_d_mc_mn)
+  )
+
 ```
@@
   # Filter out long-chain compounds
-  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
+  filter(!compound %in% c("20:0", "22:0", "24:0")) %>% 
   summarize_if(
@@
     f_t_mc = `2F_alk_mc_weighted`,
+    F_0_at2H_se = F_0_at2H_se,
+    calibrated_at2H_with_memory_correction_se,
+    calibrated_at2H_without_memory_se,
+    F_label_se,
+    sa,
 
@@
       f_t - f_start >= 0 ~ f_t - f_start,
-      f_t - f_start < 0 ~ 0),
+      f_t - f_start < 0 ~ 0
+      ),
 
@@
       f_t_mc - f_start_mc >= 0 ~ f_t_mc - f_start_mc,
-      f_t_mc - f_start_mc < 0 ~ 0),
+      f_t_mc - f_start_mc < 0 ~ 0
+      ),
 
@@
     ),
-    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted),
+    gen_d_mc_weighted = turnover_to_gen(u_d_mc_weighted)
+  ) %>%
+
+  # Calculate error
+  mutate(
+    su_d_mc = calculate_sigma_mu(
+      # Mean values:
+      a = a,
+      F_L = f_label,
+      F_T = f_t_mc,
+      F_0 = f_start,
+      t = d_t,
+      # Uncertainties:
+      sF_0 = F_0_at2H_se,
+      sF_L = F_label_se,
+      sF_T = calibrated_at2H_with_memory_correction_se,
+      sa = sa
+    ),
+
+    su_d = calculate_sigma_mu(
+      # Mean values:
+      a = a,
+      F_L = f_label,
+      F_T = f_t,
+      F_0 = f_start,
+      t = d_t,
+      # Uncertainties:
+      sF_0 = F_0_at2H_se,       
+      sF_L = F_label_se,        
+      sF_T = calibrated_at2H_without_memory_se, 
+      sa = sa
+    )
+  )
+
+weighted_time_course_total <- weighted_time_course %>% 
+  group_by(terrain) %>%                  # do operation by terrain
+  filter(inc_time_d != 0) %>%            # remove 0 timepoint for averaging
+  # average the 3d and 7d timepoint values together
+  mutate(
+    u_d_weighted_mn = mean(u_d_weighted, na.rm = TRUE),
+    u_d_weighted_mc_mn = mean(u_d_mc_weighted, na.rm = TRUE),
+    gen_d_weighted_mn = turnover_to_gen(u_d_weighted_mn),
+    gen_d_weighted_mc_mn = turnover_to_gen(u_d_weighted_mc_mn)
+    ) %>% 
+  pivot_wider(
+    names_from = inc_time_d,
+    values_from = c(u_d_weighted, u_d_mc_weighted)
+  ) %>% 
+  select(
+    u_d_weighted_mn,
+    u_d_weighted_mc_mn,
+    gen_d_weighted_mn,
+    gen_d_weighted_mc_mn,
+    u_d_weighted_3,
+    u_d_weighted_7,
+    u_d_mc_weighted_3,
+    u_d_mc_weighted_7
+  ) %>% 
+  dplyr::summarize_if(
+    is.numeric,
+    mean,
+    na.rm = TRUE
   )
@@
 ```{r}
+# Turnover rates
 turnover %>% saveRDS(file = "cache/turnover_rates.RDS")
 
+# Turnover rates averaged across experimental replicates
 turnover_summarized %>% saveRDS(file = "cache/turnover_summarized.RDS")
 
+# Turnover rates averaged averaged between 3d and 7d estimates
+turnover_avg %>% saveRDS(file = "cache/turnover_avg.RDS")
+
+# Turnover rates averaged between 3d and 7d and experimental replicates
+turnover_summarized_avg %>% saveRDS(file = "cache/turnover_summarized_avg.RDS")
+
+# Abundance-weighted turnover rates
 weighted_time_course %>% saveRDS(file = "cache/turnover_weighted.RDS")
+
+# Abundance-weighted turnover rates averaged between 3d and 7d incubation time points
+weighted_time_course_total %>% saveRDS(file = "cache/turnover_weighted_avg")
 ```
+
+# Exploratory Plots
+```{r}
+turnover %>% 
+  pivot_longer(
+    cols = c(
+      calibrated_at2H_without_area, 
+      calibrated_at2H_without_memory,
+      calibrated_at2H_with_memory_correction
+      ),
+    values_to = "calibrated_at2H",
+    names_to = "correction_applied"
+  ) %>% 
+  ggplot(
+    aes(
+      x = inc_time_d,
+      y = calibrated_at2H,
+      color = correction_applied,
+      group = compound
+    )
+  ) +
+  geom_point() +
+  #geom_line() +
+    facet_wrap(vars(correction_applied)) +
+  theme(
+    legend.position = "NA"
+  )
+```

### 2023-01-06 03_data_viz.Rmd
SF sensitivity estimates

--- 2022-11-28 03_data_viz.Rmd
@@
 library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
+library(Cairo)
 ```
@@
 source(file.path("libs", "rename_FAs.R"))
+source(file.path("libs", "d2H_to_2F.R"))
 `%nin%` = Negate(`%in%`) # "Not In" function
@@
 ```{r workspace images}
-# Turnover data
+# Turnover rates
 turnover <- readRDS("cache/turnover_rates.RDS")
 
-# Summarized turnover
+# Turnover rates averaged across experimental replicates
 turnover_summarized <- readRDS("cache/turnover_summarized.RDS")
 
-# Weighted turnover data
+# Turnover rates averaged across 3d, 7d, experimental replicates
+turnover_summarized_avg <- readRDS("cache/turnover_summarized_avg.RDS")
+
+# Abundance-weighted turnover rates
 turnover_weighted <- readRDS("cache/turnover_weighted.RDS")
+
+# Abundance-weighted turnover rates averaged between 3d and 7d incubation time points
+turnover_weighted_avg <- readRDS("cache/turnover_weighted_avg")
 
@@
   # Convert to generation time:
-  mutate(gen_d = turnover_to_gen(u_d_mn))
+  mutate(gen_d = turnover_to_gen(u_d_mn)) %>% 
+  filter(method_type != "Microscopy")
 ```
@@
 
-## Memory effect on gen_d
-
-```{r mean_generation_time}
-p_gen_time_mean <- turnover_weighted %>% 
-  select(c(terrain, inc_time_d, gen_d_weighted, gen_d_mc_weighted)) %>% 
-  pivot_longer(cols = c(gen_d_weighted, gen_d_mc_weighted),
-               values_to = "gen_d",
-               names_to = "type") %>% 
-  filter(inc_time_d == 7) %>% 
-  mutate(terrain = case_when(
-    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
-    terrain == "Marshall Mesa Grassland" ~ "Grassland",
-    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
-  # group_by(terrain, inc_time_d) %>% 
-  # summarize(terrain = terrain,
-  #           gen_d_weighted = gen_d_weighted) %>% 
-  # unique() %>% 
-  # Plot it
-  ggplot(aes(x = terrain,
-             y = gen_d,
-             fill = type)) +
-  geom_col(width = 0.5,
-           position = "dodge") +
-  scale_fill_tron() +
-  labs(x = "Soil Type",
-       y = "Weighted Mean Generation Time (d)") +
-  theme_classic() +
-  theme()
-p_gen_time_mean
-
-cowplot::save_plot(
-  plot = p_gen_time_mean,
-  filename = "fig_output/generation_time_mean_mc.pdf",
-  base_height = 4,
-  base_width = 7
-)
-```
-
-## F1A: dF plot
+## F1: dF and growth rate Plot
+
+### 1A: dF plot
+
 Using memory-corrected values
@@
       terrain == "Marshall Mesa Grassland" ~ "Grassland",
-      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
   )) %>%
@@
   ) +
-  geom_point() +
+  geom_point(alpha = 1) +
   geom_line() +
-  facet_wrap(vars(terrain)) +
+  facet_wrap(vars(terrain), scales = "free_y") +
   scale_color_manual(values = terrain_color_swatch) +
   scale_fill_manual(values = terrain_fill_swatch) +
-  scale_alpha_discrete(range = c(0.2, 1)) +
-  scale_size_discrete(range = c(1.5, 2)) +
+  scale_alpha_discrete(range = c(1, 1)) +
+  scale_size_discrete(range = c(0.25, 2)) +
   scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
+  coord_cartesian(ylim = c(0, 2500)) +
   theme_classic() +
@@
   ) +
-  theme(legend.position = "none",
+  theme(
+    legend.position = "none",
     strip.background = element_blank(),
+    strip.text = element_text(size = 14),
     plot.title = element_text(hjust = 0.5),
     axis.title.x = element_text(size = 10),
-        panel.grid.major.y = element_line(linetype = "dotted"))
+    panel.grid.major.y = element_line(linetype = "dotted"),
+    panel.spacing = unit(1.75, "cm")
+  )
 p_dF
 
-cowplot::save_plot(
-  filename = "fig_output/p_dF.pdf",
-  plot = p_dF,
-  base_width = 11,
-  base_height = 4
-  )
-
-```
-
-### Draft 2
-
-```{r}
-p_dF2 <- turnover_summarized %>% 
-  filter(
-    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
-  ungroup() %>% 
-  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
-  left_join(
-    turnover_weighted %>% 
-      select(terrain, inc_time_d, dF_weighted_mc), 
-    by = c("terrain", "inc_time_d")) %>% 
-  group_by(
-    terrain,
-    inc_time_d
-  ) %>% 
-  pivot_longer(
-    cols = c(dF_mc, dF_weighted_mc),
-    values_to = "dF", 
-    names_to = "type"
-  ) %>% 
-  mutate(compound = case_when(
-    type == "dF_weighted_mc" ~ "Weighted Mean",
-    TRUE ~ compound
-  )) %>%
-  mutate(
-    terrain = case_when(
-      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
-      terrain == "Marshall Mesa Grassland" ~ "Grassland",
-      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
-  )) %>%
-
-  ggplot(
-    aes(
-      x = inc_time_d,
-      y = dF * 10000, # convert from at% to ppm
-      group = compound,
-      color = terrain,
-      fill = terrain,
-      alpha = type,
-      size = type
-    )
-  ) +
-  geom_borderline(
-    color = "gray",
-    alpha = 1,
-    size = 0.5
-    ) +
-  geom_point() +
-  facet_wrap(vars(terrain)) +
-  scale_color_manual(values = terrain_color_swatch) +
-  scale_fill_manual(values = terrain_fill_swatch) +
-  scale_alpha_discrete(range = c(0.2, 1)) +
-  scale_size_discrete(range = c(1.5, 2)) +
-  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
-  theme_classic() +
-  labs(
-    x = "Time elapsed (days)",
-    y = TeX("$ \\Delta ^2H$ (ppm)")
-  ) +
-  theme(legend.position = "none",
-        strip.background = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        axis.title.x = element_text(size = 10),
-        panel.grid.major.y = element_line(linetype = "dotted"))
-p_dF2
-
-```
-
-## F1B: Turnover plot
+#plotly::ggplotly()
+# 
+# cowplot::save_plot(
+#   filename = "fig_output/p_dF.pdf",
+#   plot = p_dF,
+#   base_width = 11,
+#   base_height = 4
+#   )
+#   
+```
+
+### 1B: Growth rate plot
 
@@
       ) +
-    #Uncomment to show generation times
-    geom_text(
-      nudge_x = 0.05
-    ) +
-    coord_cartesian(xlim = c(0, 0.175)) +
+    # #Uncomment to show generation times
+    # geom_text(
+    #   nudge_x = 0.05
+    # ) +
+    coord_cartesian(xlim = c(0, 0.25)) +
     scale_fill_manual(values = c("black", color_choice)) +
@@
     theme_classic() +
-    labs(x = TeX("Turnover ($day^{-1}$)"),
-         title = terrain_choice) +
+    labs(
+      x = TeX("Compound-specific growth rate (day$^{-1}$)"),
+      title = terrain_choice
+      ) +
     theme(
@@
 p_turnover
-# 
+
 # ggsave(
 #   plot = p_turnover,
-#   filename = "fig_output/turnover_plot.pdf",
+#   filename = "fig_output/p_turnover.pdf",
 #   device = cairo_pdf, # Need this for greek symbols to render correctly
@@
 #   )
+
+```
+
+### Cowplot
+
+```{r}
+p_dF_ud <- cowplot::plot_grid(
+  p_dF, p_turnover,
+  nrow = 2,
+  labels = "AUTO"
+)
+p_dF_ud
+
+ggsave(filename = "fig_output/p_dF_ud.pdf", 
+       plot = p_dF_ud,
+       device = cairo_pdf, # required for rendering unicode symbols
+       width = 11,
+       height = 8)
 
@@
 
+# Calculate summary statistics and export them
 turnover_fit_tidy <- broom::tidy(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
 turnover_fit_glance <- broom::glance(lm(data = turnover_cleaned, u_d_mc  ~ compound_ug_per_g_soil))
+
+turnover_corr_test <- broom::tidy(
+  cor.test(
+    x = turnover_cleaned$compound_ug_per_g_soil,
+    y = turnover_cleaned$u_d_mc,
+    method = "pearson"
+  )
+  )
+
 writexl::write_xlsx(turnover_fit_tidy, path = "data_output/turnover_fit_lm.xlsx")
 writexl::write_xlsx(turnover_fit_glance, path = "data_output/turnover_fit_lm_stats.xlsx")
-
+writexl::write_xlsx(turnover_corr_test, path = "data_output/turnover_corr_test.xlsx")
+```
+
+```{r}
+
+# Plot it with the linear model!
 p_abundance_v_turnover2 <- turnover %>% 
@@
   )) +
+  # stat_density_2d(
+  #   geom = "polygon", 
+  #   aes(
+  #     alpha = after_stat(level),
+  #     group = terrain,
+  #     fill = terrain
+  #     ),
+  #   bins = 10
+  #   ) +
   # Individual data points
@@
     ) +
+  # Using Hull Data:
   geom_polygon(
@@
     color = "gray",
-    size = 0.3,
+    linewidth = 0.3,
     linetype = "dotted"
@@
   scale_color_manual(values = terrain_color_swatch) +
+  #scale_fill_manual(values = terrain_color_swatch) +
+  #scale_x_log10() +
+  #scale_y_log10() +
+  #scale_alpha_continuous(range = c(0,0.5)) +
   theme_bw() +
   labs(
-    x = "µg analyte (per g soil)",
+    x = TeX("PLFA Concentration (µg $\\cdot g^{-1}$ soil)"),
     y = TeX("Compound-specific growth rate (day$^{-1}$)"),
@@
 
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
-                   plot = p_abundance_v_turnover2,
+# 
+# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_2p.pdf",
+#                    plot = p_abundance_v_turnover2,
+#                    base_height = 6,
+#                    base_width = 8)
+
+```
+
+### Inset: µ vs. 1/B
+
+```{r}
+total_biomass <- turnover_cleaned %>% 
+  group_by(terrain) %>% 
+  summarize(
+    total_ug_per_g_soil = sum(compound_ug_per_g_soil, na.rm = TRUE)
+  )
+
+turnover_weighted_w_totals <- turnover_weighted %>% 
+  filter(inc_time_d == 7) %>% 
+  mutate(
+    terrain = case_when(
+      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+      terrain == "Marshall Mesa Grassland" ~ "Grassland",
+      terrain == "Niwot Ridge Tundra" ~ "Tundra"
+  )) %>% 
+  left_join(total_biomass, by = "terrain")
+
+b_ud_fit <- broom::tidy(
+  lm(
+    data = turnover_weighted_w_totals, 
+    u_d_mc_weighted  ~ total_ug_per_g_soil
+    )
+  )
+b_ud_stats <- broom::glance(
+  lm(
+    data = turnover_weighted_w_totals, 
+    u_d_mc_weighted  ~ total_ug_per_g_soil
+    )
+)
+
+p_turnover_totals <- turnover_weighted_w_totals %>% 
+  ggplot(
+    aes(
+      x = total_ug_per_g_soil,
+      y = u_d_mc_weighted
+    )
+  ) +
+  geom_point(aes(color = terrain),
+             size = 5) +
+  # geom_smooth(
+  #   method = "lm",
+  #   formula = "y~x",
+  #   se = FALSE,
+  #   linetype = "dotted",
+  #   color = "gray",
+  #   size = 0.5
+  # ) +
+  scale_color_manual(values = terrain_color_swatch) +
+  coord_cartesian(xlim = c(0, 3000), ylim = c(0.01, 0.05)) +
+  labs(
+    x = TeX("B (µg $\\cdot g^{-1}$ soil)"),
+    y = TeX("Weighted mean \n growth rate (day$^{-1}$)"),
+    color = ""
+  ) +
+  theme_bw() +
+  theme(
+    legend.position = "NA",
+    axis.title = element_text(size = 10),
+    axis.text = element_text(size = 10),
+    axis.ticks.length = unit(-0.1, "cm"),
+    panel.grid = element_blank()
+  )
+p_turnover_totals
+```
+
+```{r}
+saveRDS(turnover_weighted_w_totals, file = "cache/turnover_weighted_w_totals.RDS")
+```
+
+### Draft 2 with inset plot!
+
+```{r}
+p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
+  draw_plot(
+    p_turnover_totals, 
+    x = 0.65, 
+    y = 0.63, 
+    width = 0.33, 
+    height = 0.35
+    )
+p_abundance_v_turnover_w_inset
+
+cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
+                   plot = p_abundance_v_turnover_w_inset,
                    base_height = 6,
                    base_width = 8)
-
-```
-
-### Inset Plot
+```
+
+### Inset: Zoom Plot (Deprecated)
 
@@
 p_abundance_v_turnover_inset
-```
-
-### Draft 2 with inset plot!
-
-```{r}
-p_abundance_v_turnover_w_inset <- ggdraw(p_abundance_v_turnover2) +
-  draw_plot(
-    p_abundance_v_turnover_inset, 
-    x = 0.63, 
-    y = 0.63, 
-    width = 0.35, 
-    height = 0.35
-    )
-cowplot::save_plot(filename = "fig_output/abundance_v_turnover_w_inset.pdf",
-                   plot = p_abundance_v_turnover_w_inset,
-                   base_height = 6,
-                   base_width = 8)
 ```
@@
 lit_values_swatch_3 <- c(
+  "#6269EB", # blue
   "#20968d", # gray green
-  "#6269EB", # blue
-  "#E0187B", # pink
-  "#26AFE1" # light blue 
-  )
+  "#26AFE1", # light blue 
+  "#E0187B" # pink
+  )
+
 p_lit_turnover_w_ours2 <- lit_turnover_w_ours %>% 
-  filter(method_type != "Microscopy") %>% 
+  mutate(
+    method_type = fct_relevel(method_type, c("LH-SIP", "DNA-SIP", "TdR/Leu", "Nutrient Budgeting"))) %>% 
+  arrange(method_type, desc(u_d_mn)) %>% 
+  mutate(
+    m = seq(1,nrow(lit_turnover_w_ours))
+  ) %>% 
   ggplot(
   aes(
-    x = -n,
+    x = -m,
     y = u_d_mn,
@@
   geom_col() +
-  scale_fill_manual(
-    values = lit_values_swatch_3
-  ) +
+  geom_text(aes(
+    label = format(round(gen_d, 1)),
+    color = method_type
+    ),
+    nudge_y = .01
+    )+
+  scale_fill_manual(values = lit_values_swatch_3) +
+  scale_color_manual(values = lit_values_swatch_3) +
   # scale_fill_viridis_d(
@@
   # ) +
-  coord_flip(ylim = c(0, 0.5)) +
+  coord_flip(ylim = c(0, 0.4)) +
   labs(
-    y = TeX("Turnover (d$^{-1}$)"),
+    y = TeX("Apparent Growth Rate (day$^{-1}$)"),
     fill = "Method"
@@
     axis.line.y = element_blank(),
-    legend.position = c(0.85, 0.8),
+    legend.position = c(0.85, 0.2),
     legend.background = element_rect(color = "black"),
@@
     legend.title = element_blank(),
+    panel.grid.major.x = element_line(linetype = "dotted")
+  ) +
+  guides(
+    color = "none"
   )
 p_lit_turnover_w_ours2
-# 
-# cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
-#                    plot = p_lit_turnover_w_ours2,
-#                    base_height = 8,
-#                    base_width = 10)
-
-```
-
-### Draft 2 Inset
-
-```{r}
- p_lit_turnover_w_ours_inset <- lit_turnover_w_ours %>%
-  filter(method_type != "Microscopy") %>%
-  ggplot(
-    aes(
-      x = u_d_mn, 
-      y = method_type,
-      color = method_type
-      )
-  ) +
-  geom_boxplot(width = 0.2) +
-  coord_cartesian(xlim = c(0, 0.5)) +
-  #ggdist::stat_pointinterval() +
-  scale_color_manual(
-    values = lit_values_swatch_3
-  ) +
-  labs(
-    x = "",
-    y = "",
-    fill = "Method"
-  ) +
-  theme_classic() +
-  theme(
-    legend.position = "NA"
-  )
-p_lit_turnover_w_ours_inset
-```
-
-### Draw with inset
-
-```{r}
-p_literature2_w_inset <- ggdraw(p_lit_turnover_w_ours2) +
-  draw_plot(
-    p_lit_turnover_w_ours_inset, 
-    x = 0.63, 
-    y = 0.23, 
-    width = 0.35, 
-    height = 0.35
-    )
-p_literature2_w_inset
+
+cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
+                   plot = p_lit_turnover_w_ours2,
+                   base_height = 8,
+                   base_width = 10)
+
+# Plot annotations
+lit_turnover_w_ours %>% 
+  group_by(method_type) %>% 
+  summarize(
+    gen_d_max = max(gen_d),
+    gen_d_min = min(gen_d),
+    gen_d_avg = mean(gen_d)
+  )
+
 ```
@@
 
-## (DEPRECATED) Turnover plot
-
-```{r turnover_plots}
-add_weighted_mean <- function(df) {
-  df %>% 
-    ungroup() %>% 
-    mutate(type = "sample") %>% 
-    add_row(compound = "Weighted Mean",
-            u_d_weighted = df$u_d_weighted[1],
-            terrain = df$terrain[1],
-            u_d = df$u_d_weighted[1],
-            type = "Weighted Mean")
-}
-
-# Add weighted generation time
-
-summarized_weighted_gen_d <- gen_calc_data_summarized_weighted %>% 
-  filter(inc_time_d == 7) %>% 
-  select(terrain, gen_d_weighted) %>% 
-  unique()
-
-p_conifer_u_d <- gen_calc_data_summarized_weighted %>%
-  filter(terrain == "Gordon Gulch Conifer Forest",
-         inc_time_d == 7) %>% 
-  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>%
-  add_weighted_mean() %>% 
-  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
-  # PLOT IT
-  ggplot() +
-  geom_col(aes(x = compound,
+## SF: Memory effect on gen_d and u_d
+
+```{r mean_generation_time}
+p_gen_time_mean <- turnover_weighted %>% 
+  pivot_longer(
+    cols = c(gen_d_weighted, gen_d_mc_weighted),
+    names_to = "Correction",
+    values_to = "gen_d"
+  ) %>% 
+  mutate(terrain = case_when(
+    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+    terrain == "Marshall Mesa Grassland" ~ "Grassland",
+    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
+  # group_by(terrain, inc_time_d) %>% 
+  # summarize(terrain = terrain,
+  #           gen_d_weighted = gen_d_weighted) %>% 
+  # unique() %>% 
+  # Plot it
+  ggplot(aes(x = terrain,
+             y = gen_d,
+             fill = Correction)) +
+  geom_col(width = 0.5,
+           position = "dodge") +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
+  labs(x = "Soil Type",
+       y = "Weighted Mean Generation Time (d)") +
+  theme_classic() +
+  theme(
+    legend.position = "NA",
+    axis.text = element_text(size = 6),
+    axis.title = element_text(size = 8)
+    )
+p_gen_time_mean
+
+p_ud_mean <- turnover_weighted %>% 
+  pivot_longer(
+    cols = c(u_d_weighted, u_d_mc_weighted),
+    names_to = "Correction",
+    values_to = "u_d"
+  ) %>% 
+  mutate(terrain = case_when(
+    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
+    terrain == "Marshall Mesa Grassland" ~ "Grassland",
+    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>%
+  # group_by(terrain, inc_time_d) %>% 
+  # summarize(terrain = terrain,
+  #           gen_d_weighted = gen_d_weighted) %>% 
+  # unique() %>% 
+  # Plot it
+  ggplot(aes(x = terrain,
              y = u_d,
-               fill = type)) +
-  scale_fill_manual(values = c("#000000", conifer_color)) +
-  # Secondary axis option:
-  # scale_y_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
-  #                                        breaks = c(7, 14, 30, 90, 365),
-  #                                        name = "Generation time (d)")) +
-  coord_flip(ylim = c(0, 0.09), clip = "off") +
-  labs(y = TeX("Turnover ($d^{-1}$)"),
-       title = "Conifer Forest") +
+             fill = Correction)) +
+  geom_col(width = 0.5,
+           position = "dodge") +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_fill_manual(values = c("#4690b0", "#3d3d3d")) +
+  labs(
+    x = "Soil Type",
+    y = TeX("Weighted Mean Growth Rate $(d^{-1})$")
+    ) +
   theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 90, hjust = 1),
-        legend.position = "none",
-        plot.title = element_text(hjust = 0.5))
-p_conifer_u_d
-
-p_grassland_u_d <- gen_calc_data_summarized_weighted %>% 
-  filter(terrain == "Marshall Mesa Grassland",
-         inc_time_d == 7) %>% 
-  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
-  add_weighted_mean() %>% 
-  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
-  # PLOT IT
-  ggplot() +
-  geom_col(aes(x = compound, y = u_d, fill = type)) +
-  scale_fill_manual(values = c("#000000", grassland_color)) +
-  coord_flip(ylim = c(0, 0.09), clip = "off") +
-  labs(y = TeX("Turnover ($d^{-1}$)"),
-       title = "Grassland") +
-  theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 90, hjust = 1),
-        legend.position = "none",
-        plot.title = element_text(hjust = 0.5))
-
-p_tundra_u_d <- gen_calc_data_summarized_weighted %>% 
-  filter(terrain == "Niwot Ridge Tundra",
-         inc_time_d == 7) %>% 
-  select(terrain, inc_time_d, compound, u_d, u_d_weighted) %>% 
-  add_weighted_mean() %>% 
-  mutate(compound = forcats::fct_reorder(compound, u_d)) %>%
-  # PLOT IT
-  ggplot() +
-  geom_col(aes(x = compound, y = u_d, fill = type)) +
-  scale_fill_manual(values = c("#000000", tundra_color)) +
-  # Add weighted generation time label
-  coord_flip(ylim = c(0, 0.09), clip = "off") +
-  labs(y = TeX("Turnover ($d^{-1}$)"),
-       title = "Tundra") +
-  theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 90, hjust = 1),
-        legend.position = "none",
-        plot.title = element_text(hjust = 0.5))
-p_tundra_u_d
-```
-
-```{r moo}
-# HORIZONTAL
-p_turnover_enrichment_cow_h <- cowplot::plot_grid(
-  p_conifer_2H,
-  p_grassland_2H,
-  p_tundra_2H,
-  p_conifer_u_d,
-  p_grassland_u_d,
-  p_tundra_u_d,
-  labels = "AUTO",
-  rel_widths = c(1,1),
-  align = "h",
-  nrow = 2
-)
-
-p_turnover_enrichment_cow_h
-# 
-# cowplot::save_plot(filename = "fig_output/p_turnover_enrichment_cow_horiz.pdf",
-#           plot = p_turnover_enrichment_cow,
-#           base_height = 8,
-#           base_width = 12
-#           )
-
-# VERTICAL
-p_turnover_enrichment_cow_v <- cowplot::plot_grid(
-  p_conifer_2H,
-  p_conifer_u_d,
-  p_grassland_2H,
-  p_grassland_u_d,
-  p_tundra_2H,
-  p_tundra_u_d,
-  labels = "AUTO",
-  rel_widths = c(1,1),
-  align = "h",
-  nrow = 3
-)
-
-p_turnover_enrichment_cow_v
-# 
-# cowplot::save_plot(filename = "fig_output/p_turnover_enrichment_cow_vertical.pdf",
-#           plot = p_turnover_enrichment_cow_v,
-#           base_height = 12,
-#           base_width = 8
-#           )
+  theme(
+    legend.position = "NA",
+    axis.text = element_text(size = 6),
+    axis.title = element_text(size = 8)
+    )
+p_ud_mean
+
+p_memcorr_effect <- cowplot::plot_grid(
+  p_gen_time_mean,
+  p_ud_mean,
+  nrow = 1
+)
+p_memcorr_effect
+
+cowplot::save_plot(
+  plot = p_memcorr_effect,
+  filename = "fig_output/memory_correction.pdf",
+  base_height = 2.5,
+  base_width = 6
+)
 ```
@@
   geom_line() +
-  geom_vline(xintercept = 60,
+  geom_vline(xintercept = 44.9,
              color = tundra_color,
              linetype = "dotted") +
-    geom_vline(xintercept = 26,
+    geom_vline(xintercept = 19.3,
              color = grassland_color,
              linetype = "dotted") +
-    geom_vline(xintercept = 19.4,
+    geom_vline(xintercept = 14.1,
              color = conifer_color,
@@
 ```
+
+## SF: Sensitivity Testing
+
+### at2H se
+
+```{r}
+LH_SIP_data %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(
+    aes(
+      x = calibrated_at2H_without_memory_se,
+      y = calibrated_at2H_with_memory_correction_se,
+      color = inc_time_d_str
+    )
+  ) +
+  geom_point(
+    alpha = 0.5
+  ) +
+  geom_smooth(
+    method = "lm",
+    formula = "y~x",
+    se = FALSE,
+    color = "red",
+    linewidth = 0.5
+  ) +
+  labs(
+    x = TeX("SE: Without Memory Correction ($^2$H %)"),
+    y = TeX("SE: With Memory Correction ($^2$H %)")
+  ) +
+  theme_classic()
+```
+
+### IRMS instrument error
+
+```{r}
+instrument_error <- as.numeric(isotopia::to_abundance(
+  isotopia::delta(
+    `2H` = 8.9, major = "1H",
+    ref = "VSMOW", notation = "permil")))
+instrument_error_u_d <- calculate_turnover(
+  a = 0.7,
+  FL = 0.5,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error,
+  t = 7
+)
+
+instrument_error_enriched <- as.numeric(isotopia::to_abundance(
+  isotopia::delta(
+    `2H` = 60, major = "1H",
+    ref = "VSMOW", notation = "permil")))
+
+instrument_error_enriched_u_d <- calculate_turnover(
+  a = 0.7,
+  FL = 0.5,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error_enriched,
+  t = 7
+)
+
+library(isotopia)
+tibble(
+  d2H_error_permil = c(8.9, 60),
+  at2H_error_percent = 100*as.numeric(
+    to_abundance(delta(
+    `2H` = d2H_error_permil, major = "1H",
+    ref = "VSMOW", notation = "permil"))
+    ),
+  at2H_error_ppm = 10000*at2H_error_percent,
+  growth_rate_error_d = calculate_turnover(
+    a = 0.7,
+    FL = 0.5,
+    F0 = 0,
+    FT = at2H_error_percent,
+    t = 7
+  )
+)
+
+instrument_error_test <- crossing(
+  t = seq(1, 30, by = 0.05),
+  FL = c(0.1, 0.25, 0.5, 1, 2.5, 5)
+) %>% mutate(
+  a = 0.7,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error,
+  u_d = calculate_turnover(
+    a = a,
+    FT = FT,
+    F0 = F0,
+    FL = FL,
+    t = t
+  )
+)
+
+instrument_error_test <- crossing(
+  t = seq(1, 30, by = 0.05),
+  FL = c(0.1, 0.25, 0.5, 1, 2.5, 5)
+) %>% mutate(
+  a = 0.7,
+  F0 = 0.00000000000000000000001,
+  FT = instrument_error,
+  u_d = calculate_turnover(
+    a = a,
+    FT = FT,
+    F0 = F0,
+    FL = FL,
+    t = t
+  )
+)
+
+p_IRMS_error_prop <- instrument_error_test %>% 
+  ggplot(
+    aes(
+      x = t,
+      y = u_d,
+      color = as.factor(FL),
+      fill = as.factor(FL)
+    )
+  ) +
+  geom_line() +
+  geom_area() +
+  geom_point(
+    y = instrument_error_u_d,
+    x = 7,
+    size = 2,
+    color = "black",
+    shape = 1,
+    fill = NA
+    ) +
+  scale_color_viridis_d() +
+  scale_fill_viridis_d() +
+  scale_y_continuous(expand=c(0,0)) +
+  scale_x_continuous(expand=c(0,0)) +
+  theme_classic() +
+  labs(
+    x = "Incubation Time (days)",
+    y = TeX("Growth Rate Uncertainty (day $^{-1})"),
+    color = "Tracer Strength (%)",
+    fill = "Tracer Strength (%)",
+  ) +
+  theme(
+    legend.position = c(0.75, 0.5)
+  )
+p_IRMS_error_prop
+
+cowplot::save_plot(
+  filename = "fig_output/p_IRMS_error_prop.pdf",
+  plot = p_IRMS_error_prop,
+  base_height = 5,
+  base_width = 6
+)
+```
+
+## SF: Turnover MC effect
+
+```{r}
+turnover_summarized %>% 
+  filter(inc_time_d != 0) %>% 
+  ggplot(aes(
+    x = u_d,
+    y = u_d_mc,
+    color = as.factor(inc_time_d)
+  )) +
+  geom_point() +
+  geom_abline(linetype = "dashed") +
+  labs(
+    x = TeX("Growth Rate (d$^{-1}$)"),
+    y = TeX("Memory Corrected (d$^{-1}$)")
+  ) +
+  theme_classic()
+```
+
+```{r}
+turnover_summarized %>% 
+  filter(inc_time_d == 7) %>% 
+  pivot_longer(
+    cols = c(u_d, u_d_mc),
+    names_to = "corrected",
+    values_to = "u_d") %>% 
+  group_by(compound) %>%
+  mutate(y = paste(round(mean(rt), 0), compound)) %>% 
+  ungroup() %>% 
+  arrange(desc(y)) %>% 
+  ggplot(
+    aes(
+      x = u_d,
+      y = y,
+      color = corrected,
+      size = area2
+      )
+  ) +
+    geom_point() +
+  facet_wrap(vars(terrain))
+```
+
+## SF: sµ / µ
+
+```{r}
+calculate_mu <- function(a, F2, F1, FL, t2, t1 = 0) {
+  return(- (1/(t2 - t1)) * (log((a * FL - F2)/(a*FL - F1))))
+}
+calculate_sigma_mu <- function(a, F2, F1, FL, t2, t1 = 0, sigma_a = 0, sigma_F2 = 0, sigma_F1 = 0, sigma_FL = 0) {
+  return(
+    sqrt(
+      ((a*FL - F2) * sigma_F1)^2 +
+
+      ((a*FL - F1) * sigma_F2)^2 +
+
+      (a * (F1 - F2) * sigma_FL)^2 +
+
+      (FL * (F1 - F2) * sigma_a)^2
+    ) / ( 
+      (t2-t1) * (a * FL - F1) * (a * FL - F2) 
+    )
+  )
+}
+
+# error matrix
+error_matrix <-
+  tribble(
+     ~use_a, ~use_FL, ~use_F1, ~use_F2, ~panel,
+     1,       1,      1,       1,       "all errors",
+     1,       0,      0,       0,       "a error only",
+     0,       1,      0,       0,       "FL error only",
+     0,       0,      1,       0,       "F0 error only",
+     0,       0,      0,       1,       "FT error only"
+  ) %>%
+  mutate(panel = as_factor(panel))
+
+# constants
+model_data <- 
+  tibble(
+  a = 0.7069045, # assimilation factor
+  t.days = 7, # days (doesn't actually matter, all cancels)
+  F1 = 0, # ppm
+  # errors
+  sigma_a = 0.1716424,
+  sigma_FL = 92, # ppm
+  sigma_F1 = 1.4, # ppm
+  sigma_F2 = 9.4 # ppm
+) %>%
+  # dynamics
+  crossing(
+    FL = c(5000, 10000, 25000, 50000), # ppm
+    F2_interval = seq(-10, 0, by = 0.1) %>% exp()
+  ) %>%
+  # mu calculations
+  mutate(
+    F2 = F1 + FL * F2_interval,
+    FL_factor = paste(FL/1e6 * 100, "at %") %>% as_factor(),
+    t_factor = paste(t.days, "days") %>% as_factor(),
+    mu.1_day = calculate_mu(a = a, F2 = F2, F1 = F1, FL = FL, t2 = t.days),
+    TD.days = log(2) / mu.1_day
+  ) %>%
+  # error calculations
+  crossing(error_matrix) %>%
+  mutate(
+    sigma_mu.1_day = calculate_sigma_mu(
+      a = a, F2 = F2, F1 = F1, FL = FL, t2 = t.days,
+      sigma_a = use_a * sigma_a,
+      sigma_F2 = use_F2 * sigma_F2, 
+      sigma_F1 = use_F1 * sigma_F1, sigma_FL = use_FL * sigma_FL
+    ),
+    rel_error = sigma_mu.1_day / mu.1_day
+  ) %>%
+  filter(!is.na(mu.1_day), !is.na(rel_error))
+
+# plot
+p_model_data <- model_data %>%
+  ggplot() + 
+  aes(x = TD.days / t.days, y = rel_error, color = FL_factor, linetype = t_factor) + 
+  geom_line() +
+  scale_x_log10(
+        breaks = trans_breaks("log10", function(x) 10^x),
+        labels = trans_format("log10", math_format(10^.x)),
+        sec.axis = dup_axis()) +
+  scale_y_continuous(labels = scales::percent) + 
+  coord_cartesian(ylim = c(0, 0.5), expand = FALSE) +
+  labs(
+    x = latex2exp::TeX("$\\frac{T_G}{\\Delta t}$"), 
+    y = latex2exp::TeX("$\\frac{\\sigma_{\\mu}}{\\mu}$"), 
+    color = "Tracer Strength (%)"
+  ) + 
+  facet_wrap(~panel) +
+  scale_color_viridis_d(option = "plasma", begin = 0, end = 0.6) +
+  theme_bw() +
+  theme(
+    legend.position = c(0.85, 0.2),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(1,1,1.5,1.2, "cm")
+  ) +
+  guides(
+    linetype = "none"
+  )
+p_model_data
+
+cowplot::save_plot(
+  plot = p_model_data,
+  filename = "fig_output/p_model_data.pdf",
+  base_height = 8,
+  base_width = 10
+)
+
+```
+
+# Supplementary Dataset Export
+
+```{r}
+# SDS1: Sent from Colorado State Lab
+# SDS2: Exported BacDive Data
+# SDS3: Manually-curated in Excel
+
+# SDS4:
+# SDS4.1: Summarized Growth Rates
+sds4_1 <- turnover_summarized %>% 
+  select(terrain, inc_time_d, compound, compound_ug_per_g_soil,
+         u_d_mc, su_d_mc, gen_d_mc)
+
+# SDS4.2: Assemblage-level growth rates
+sds4_2 <- turnover_weighted %>% 
+  filter(inc_time_d == 7) %>% 
+  select(terrain, f_label, dF_weighted_mc, 
+        u_d_mc_weighted, gen_d_mc_weighted)
+
+# SDS4.3: IRMS Data
+sds4_3 <- LH_SIP_data %>% 
+  select(-c(soil, inc_time_d_str, d2H_mn_zero, d2H, at2H, compound_ug_per_g_soil, 
+            `2F_Me`, `2F_FAME`, `2F_FAME_mc`, `2F_alk`, `2F_alk_mc`, `F_label_mn`,
+            `F_label_se`, `F_0_at2H_se`, sa, a))
+
+# SDS4.4: Uncertainty parameters
+sds4_4 <- turnover_summarized %>% 
+  filter(inc_time_d == 7) %>% 
+  select(terrain, compound, 
+         calibrated_at2H_with_memory_correction_se, F_label_se, 
+         F_0_at2H_se, sa, su_d_mc) %>% 
+  rename(
+    s_ft = calibrated_at2H_with_memory_correction_se,
+    s_fl = F_label_se,
+    s_f0 = F_0_at2H_se,
+    s_a = sa,
+    s_u_d_mc = su_d_mc
+    )
+
+writexl::write_xlsx(
+  sds4_1, 
+  path = "data_output/sds4_1.xlsx"
+  )
+
+writexl::write_xlsx(
+  sds4_2, 
+  path = "data_output/sds4_2.xlsx"
+  )
+
+writexl::write_xlsx(
+  sds4_3,
+  path = "data_output/sds4_3.xlsx"
+)
+
+writexl::write_xlsx(
+  sds4_4,
+  path = "data_output/sds4_4.xlsx"
+)
+
+writexl::write_xlsx(
+  s_u_d_mc_compound,
+  path = "data_output/sds4_5a.xlsx"
+)
+
+writexl::write_xlsx(
+  s_u_d_mc_terrain,
+  path = "data_output/sds4_5b.xlsx"
+)
+
+writexl::write_xlsx(
+  s_u_d_mc_total,
+  path = "data_output/sds4_5c.xlsx"
+)
+```

### 2023-01-06 Sequencing/tables and code/caro_16S.R
Delete Sequencing directory

@@ -1,337 +1,0 @@
-library(mctoolsr)
-
-tax_table_fp = 'seqtab_wTax_mctoolsr_16s_caro.txt'
-map_fp = 'caro_16s_mapping.txt' 
-input = load_taxa_table(tax_table_fp, map_fp)
-
-# Remove mitochondrial and chloroplast sequences, Remove reads assigned as eukaryotes
-input_filt <- filter_taxa_from_input(input, taxa_to_remove = c("Chloroplast","Mitochondria", "Eukaryota"))
-# Remove reads that are unassigned at domain level
-input_filt <- filter_taxa_from_input(input_filt, at_spec_level = 2, taxa_to_remove = "NA")
-
-# Normalize or rarefy your ASV table
-#input_filt <- single_rarefy(input = input_filt, depth = 5000) # CHANGE ME to desired depth.
-
-#### Now following Cliff's R Tutorial for Alpha & Beta Diversity and other Visualization Techniques
-library(plyr) # For hulls
-library(tidyverse) # For data manipulation and plotting
-library(RColorBrewer) # For color palettes
-library(vegan) # For alpha and beta diversity analyses
-library(indicspecies) # For indicator species
-library(car) # For Levene Test and anova
-library(PMCMR) # For Nemenyi posthoc test
-
-
-# We now have an object called input. It contains 3 files - a sequence table, a mapping file, and a taxonomic file.
-head(input$data_loaded) # Rows are OTUs, columns are samples
-head(input$taxonomy_loaded) # Rows are OTUs (now ASVs), columns are different taxonomic levels
-head(input$map_loaded) # Rows are samples, columns are variables
-
-# Initial data examination, rarefying, filtering
-# One of the first things we want to do is see how many sequences per sample there are
-# This is done by getting the column sums of the sequence table, and we'll sort it too.
-sort(colSums(input$data_loaded))
-# We could also save this as an object and plot it
-seqcounts <- as.data.frame(sort(colSums(input$data_loaded)))
-# This puts the sample names as row names and the sequence counts column is titled "sort(colSums(input$data_loaded)))
-# We'll use the pipeline %>% which is very useful for dataframe management with the dplyr package
-# We'll rename the column and make a new column all at once
-seqcounts <- as.data.frame(sort(colSums(input$data_loaded))) %>%
-  rename("seqs" = "sort(colSums(input$data_loaded))") %>%
-  rownames_to_column(var = "sampleID")
[…]

### 2023-01-06 01_LH-SIP_Data_Reduction.Rmd
moved PAME_data out of IRMS folder
moved data out of IRMS folder

@@
 # Load PAME Iso Files
-PAME_data_path <- file.path("data", "IRMS", "PAME_data")
+PAME_data_path <- file.path("data", "PAME_data")
 ref_ratio <- get_standard("2H") %>% as.numeric()
@@
 
-problematic_runs <- read_xlsx(file.path("data", "IRMS", "problematic_runs.xlsx"))
+problematic_runs <- read_xlsx(file.path("data", "problematic_runs.xlsx"))
 problematic_analyses <- problematic_runs$Analysis
@@
   # corrected peak map
-  readxl::read_excel(file.path("data", "IRMS", "peak_maps_resolved.xlsx"))
+  readxl::read_excel(file.path("data", "peak_maps_resolved.xlsx"))
 ```

### 2023-01-07 calibration_submodule/02_calibration.Rmd
calibration submodule commit

---
title: "Sample Data Analysis"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---

# Setup (*)

```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(rlang)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(purrr)
library(stringr)
library(readxl)
library(isoreader)
library(isoprocessor)

source("scripts/plotting_functions.R")
source("scripts/table_functions.R")
source("scripts/error_propagation.R")

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf", "postscript"),
  fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("plots", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

```{r}
message("using isoreader version ", packageVersion("isoprocessor"))
message("using isoprocessor version ", packageVersion("isoprocessor"))
```

# Load Data (*)

```{r}
sample_peak_table <-
  readxl::read_excel("data/peak_table_raw_data.xlsx") %>%
  iso_make_units_implicit()
```

# Analyte Peaks Overview

```{r "analytes_overview", fig.width=8, fig.height=8, warning=FALSE}
# generate overview
sample_peak_table %>%
  filter(!is.na(compound) & compound != "H2") %>%
  iso_plot_data(
    x = area2, y = d2H, 
    color = type,
    label = analysis,
    size = 3,
    points = TRUE
  ) +
  scale_color_brewer(palette = "Dark2") + 
  scale_x_log10(breaks = c(1, 2, 3, 6, 10, 25, 50, 100, 200, 400)) +
  theme(panel.grid.minor = element_blank()) +
  facet_grid(type~., scales = "free_y") 
```

# Memory Calculation (*)

```{r}
# alternative memory calculation not used in the end but included for completeness
sum_memory <- function(area, delta) {
  stopifnot(length(area) == length(delta))
  mem <- 0
  mem_area <- 0
  for (i in seq_along(area)) {
    if (area[i] > mem_area) {
      # new area bigger --> takes over entire memory
      mem <- delta[i]
      mem_area <- area[i]
    } else {
      # new area smaller --> partially replace memory
      mem = ((mem_area - area[i]) * mem + area[i] * delta[i])/(mem_area)
    }
  }
  return(mem)
}

# calculate memory effect
memory_effects <- 
  sample_peak_table %>%
  # focus on analyte peaks
  filter(is.na(compound) | compound != "H2") %>%
  select(file_id, peak_id, compound, rt, area2, d2H_vs_H2) %>%
  # cross join all peaks
  { left_join(
    ., 
    select(., file_id, compound_i = compound, rt_i = rt, area2_i = area2, d2H_vs_H2_i = d2H_vs_H2) %>%
      iso_strip_units(),
    by = "file_id"
    ) } %>%
  # use prior peaks for memory calculation
  group_by(file_id, peak_id, rt) %>%
  filter(rt_i <= rt) %>%
  ungroup() %>%
  # summarize for each file and peak
  group_by(file_id, peak_id) %>%
  summarize(
    mem_d2H = 
      if_else(
        n() == 1, 0, 
        sum(d2H_vs_H2_i[rt_i < rt] * area2_i[rt_i < rt]) / sum(area2_i[rt_i < rt])),
    mem_d2H_sum = sum_memory(area2_i, d2H_vs_H2_i),
    .groups = "drop"
  )

sample_peak_table_with_memory <-
  sample_peak_table %>%
  left_join(memory_effects, by = c("file_id", "peak_id"))
```

# Add Standards' Isotope Data (*)

```{r}
standards <-
  tibble(
    standard = readxl::excel_sheets("data/standards.xlsx"),
    data = map(standard, ~readxl::read_excel("data/standards.xlsx", sheet = .x))
  ) %>%
  unnest(data) %>%
  filter(!is.na(true_d2H)) %>%
  select(type = standard, compound, true_d2H)

standards %>% iso_make_units_explicit() %>% knitr::kable(digits=2)

sample_peak_table_with_stds <-
  sample_peak_table_with_memory %>%
  iso_add_standards(stds = standards, match_by = c("type", "compound"))
```

# Check individual F8 standards

Applying univariate linear regression:

$$
\begin{aligned}
\delta_{peak/H2} &= \beta_0 + \beta_1 \cdot \delta_{analyte/VSMOW}
\end{aligned}
$$

```{r}
F8_w_calibs <- sample_peak_table_with_stds %>%
  filter(type == "F8") %>%
  iso_remove_problematic_peak_mappings() %>%
  iso_prepare_for_calibration(group_by = file_id) %>%
  iso_generate_calibration(
    # simple direct calibration model
    model = lm(d2H_vs_H2 ~ true_d2H)
  )

F8_w_calibs %>% iso_get_problematic_calibrations() -> problematic.calibs

F8_w_calibs <- F8_w_calibs %>% iso_remove_problematic_calibrations()

F8_w_calibs %>%
   iso_get_calibration_parameters(
    select_from_coefs = c(term, estimate, SE = std.error, signif),
    select_from_summary = c(fit_R2 = adj.r.squared, fit_RSD = sigma, residual_df = df.residual)
    ) %>%
  arrange(term) %>%
  head() %>%
  knitr::kable(digits=4)
```

# Check derived parameters

Look at the derived parameters to check consistency:

$$
\begin{aligned}

\delta_{H2/VSMOW} &= -\frac{\delta_{VSMOW/H2}}{\delta_{VSMOW/H2} + 1} = 
  \frac{ (1 - \beta_1) \cdot \delta_{mem/H2} - \beta_0}{(1 + \delta_{mem/H2} ) \cdot \beta_1} 
  \approx \frac{-\beta_0}{\beta_1} \\

\frac{A_{mem}}{A_{peak}} &= \frac{1 + \beta_0 - \beta_1}{1 + \delta_{mem/H2}} \approx 1 + \beta_0 - \beta_1 \\
& \rightarrow A_{mem} = \overline{A_{peak}} \cdot \left(1 + \beta_0 - \beta_1 \right)
\end{aligned}
$$

```{r "standards_parameters", fig.width=10, fig.height=8, warning=FALSE}
calc_d2H_vs_VSMOW <- rlang::expr(-value_b0/value_b1)
calc_percent_mem <- rlang::expr(1 + value_b0/1000 - value_b1)
calc_A_mem <- rlang::expr(mean_area * (1 + value_b0/1000 - value_b1))

stds_w_derived_params <- 
  F8_w_calibs %>%
  iso_get_calibration_data(select = c(analysis, mean_area_identified, mean_area_identified_sd, 
                                      injection_volume, folder, group, type)) %>%
  iso_get_calibration_parameters(
    select_from_coefs = c(term, estimate, std.error),
    select_from_summary = c()
  ) %>%
  mutate(
    term = case_when(term == "(Intercept)" ~ "b0", term == "true_d2H" ~ "b1"),
    mean_area = as.numeric(mean_area_identified),
    mean_area_sd = as.numeric(mean_area_identified_sd)
  ) %>%
  rename(value = estimate, se = std.error) %>%
  pivot_wider(names_from = term, values_from = c(value, se)) %>%
  mutate(
    `d2H H2/VSMOW [permil]` = !!calc_d2H_vs_VSMOW,
    `d2H H2/VSMOW [permil] error` = propagate_error(!!calc_d2H_vs_VSMOW, dvalue_b0 = se_b0, dvalue_b1 = se_b1),
    `Amem / Apeak` = !!calc_percent_mem,
    `Amem / Apeak error` = propagate_error(!!calc_percent_mem, dvalue_b0 = se_b0, dvalue_b1 = se_b1),
    `Amem [Vs]` = !!calc_A_mem,
    `Amem [Vs] error` = propagate_error(!!calc_A_mem, dmean_area = mean_area_sd, dvalue_b0 = se_b0, dvalue_b1 = se_b1)
  )

stds_w_derived_params %>%
  pivot_longer( cols = c(`d2H H2/VSMOW [permil]`, `Amem / Apeak`, `Amem [Vs]`)) %>%
  left_join(
    stds_w_derived_params %>% 
      pivot_longer( cols = c(`d2H H2/VSMOW [permil] error`, `Amem / Apeak error`, `Amem [Vs] error`)) %>%
      mutate(name = str_remove(name, " error")) %>%
      select(file_id, name, error = value),
    by = c("file_id", "name")
  ) %>%
  filter(mean_area > 1) %>%
  mutate(name = as_factor(name)) %>%
  iso_plot_data(
    x=mean_area_identified, y=value, y_error = error, label = analysis,
    size=mean_area_identified, panel = name ~ ., color = group,
    shape = type,
    points = TRUE,
    # indicate means of d2H and Amem
    geom_smooth(
      data = ~filter(.x, !str_detect(name, fixed("Apeak"))),
      method = "lm", mapping = aes(color = NULL), formula = y ~ 1,
      color = "black", linetype = 2
    ),
    # indicate 1/A dependence of Amem/Apeak
    geom_smooth(
      data = ~filter(.x, str_detect(name, fixed("Apeak"))),
      method = "lm", mapping = aes(color = NULL), formula = y ~ I(1/x),
      color = "black", linetype = 2
    )
  ) + 
  scale_x_log10(breaks = c(1, 2, 3, 7, 15, 30, 60)) + 
  labs(y = NULL)
```

# Generate Global Galibration (*)

$$
\begin{aligned}
\delta_{peak/H2} 
  &= \beta_0 + \beta_1 \cdot \delta_{analyte/VSMOW} + \beta_2 \cdot \frac{1}{A_{peak}} + \beta_3 \cdot \frac{  \delta_{analyte/VSMOW}}{A_{peak}} + \beta_4 \cdot \frac{\delta_{mem/H2}}{A_{peak}}
\end{aligned}
$$

```{r}
# analytes
sample_peak_table_for_calibration <- 
  sample_peak_table_with_stds %>%
  filter(!is.na(compound), compound != "H2") %>%
  mutate(row_id = row_number())

# global calib
global_calib <- 
  bind_rows(
    # standards
    sample_peak_table_for_calibration %>%
      filter(
        !str_detect(type, "sample"), is_std_peak, 
        mean_area_identified > iso_double_with_units(3, "Vs")
      ) %>%
      mutate(use_in_calib = TRUE),
    # samples
    sample_peak_table_for_calibration %>%
      filter(str_detect(type, "sample")) %>%
      mutate(use_in_calib = FALSE)
  ) %>%
  iso_prepare_for_calibration() %>%
  iso_generate_calibration(
    calibration = "d2H",
    model=c(
      b0_b1_only = lm(d2H_vs_H2 ~ true_d2H),
      plus_area_b2_b3 = lm(d2H_vs_H2 ~ true_d2H * I(1/area2)),
      plus_area_b2_b3_mem = lm(d2H_vs_H2 ~ true_d2H * I(1/area2) + mem_d2H : I(1/area2))
    ),
    use_in_calib = use_in_calib
  ) %>%
  iso_remove_problematic_calibrations()

# global calib for t0 (natural abundance)
global_calib_t0 <- 
  bind_rows(
    # standards
    sample_peak_table_for_calibration %>%
      filter(
        !str_detect(type, "sample"), is_std_peak, 
        mean_area_identified > iso_double_with_units(3, "Vs"),
        type == "F8"
      ) %>%
      mutate(use_in_calib = TRUE),
    # samples
    sample_peak_table_for_calibration %>%
      filter(type == "unlabeled sample") %>%
      mutate(use_in_calib = FALSE)
  ) %>%
  iso_prepare_for_calibration() %>%
  iso_generate_calibration(
    calibration = "d2H",
    model=c(
      b0_b1_only = lm(d2H_vs_H2 ~ true_d2H),
      plus_area_b2_b3 = lm(d2H_vs_H2 ~ true_d2H * I(1/area2)),
      plus_area_b2_b3_log = lm(d2H_vs_H2 ~ true_d2H * log(area2)),
      plus_area_b2_log = lm(d2H_vs_H2 ~ true_d2H + log(area2))
    ),
    use_in_calib = use_in_calib
  ) %>%
  iso_remove_problematic_calibrations()
```

# Global Calibration Parameters

```{r "global_calib_parameters", fig.width=8, fig.height=12}
global_calib %>%
  iso_get_calibration_parameters(
    select_from_coefs = c(),
    select_from_summary = 
      c(fit_R2=adj.r.squared, fit_RSD=sigma, residual_df=df.residual)
  ) %>%
  knitr::kable(digits=4)

global_calib_t0 %>%
  iso_get_calibration_parameters(
    select_from_coefs = c(),
    select_from_summary = 
      c(fit_R2=adj.r.squared, fit_RSD=sigma, residual_df=df.residual)
  ) %>%
  knitr::kable(digits=4)

global_calib %>% iso_plot_calibration_parameters()
global_calib_t0 %>% iso_plot_calibration_parameters() 
```

# Check derived parameters

$$
\begin{aligned}
\delta_{H2/VSMOW} &= -\frac{\delta_{VSMOW/H2}}{\delta_{VSMOW/H2} + 1} = \frac{-\beta_0}{\beta_0 + 1} =  \frac{1-\beta_1}{\beta_1} = -\frac{\beta_2}{\beta_2 - \beta_4} = -\frac{\beta_3 + \beta_4}{\beta_3} \\
A_{mem} &= \beta_4 = -\frac{\beta_2}{\beta_0} = - \frac{\beta_3}{\beta_1} = \beta_2 - \beta_3
\end{aligned}
$$

```{r}
calc_d2H_b0 <- rlang::expr(-val_b0 / (val_b0/1000 + 1))
calc_d2H_b1 <- rlang::expr(1000 * (1 - val_b1) / val_b1)
calc_d2H_b2_b4 <- rlang::expr(-val_b2 / (val_b2/1000 - val_b4))
calc_d2H_b3_b4 <- rlang::expr(- 1000 * (val_b3 + val_b4) / val_b3)
calc_Amem_b0_b2 <- rlang::expr(-val_b2 / val_b0)
calc_Amem_b1_b3 <- rlang::expr(-val_b3 / val_b1)
calc_Amem_b2_b3 <- rlang::expr(val_b2/1000 - val_b3)

calib_params <- 
  global_calib %>%
  iso_get_calibration_parameters(
    select_from_coefs = c(term, val = estimate, se = std.error),
    select_from_summary = c()
  ) %>%
  mutate(
    term = as_factor(term) %>%
      fct_recode(
        b0 = "(Intercept)", b1 = "true_d2H",
        b2 = "I(1/area2)", b3 = "true_d2H:I(1/area2)", 
        b4 = "I(1/area2):mem_d2H"
      )
  ) %>% 
  pivot_wider(values_from = c(val, se), names_from = term) %>%
  mutate(
    val_dH2_b0 = !!calc_d2H_b0,
    se_dH2_b0 = propagate_error(!!calc_d2H_b0, dval_b0 = se_b0),
    val_dH2_b1 = !! calc_d2H_b1,
    se_dH2_b1 = propagate_error(!!calc_d2H_b1, dval_b1 = se_b1),
    val_dH2_b2_b4 = !!calc_d2H_b2_b4,
    se_dH2_b2_b4 = propagate_error(!!calc_d2H_b2_b4, dval_b2 = se_b2, dval_b4 = se_b4),
    val_dH2_b3_b4 = !!calc_d2H_b3_b4,
    se_dH2_b3_b4 = propagate_error(!!calc_d2H_b3_b4, dval_b3 = se_b3, dval_b4 = se_b4),
    val_Amem_b4 = val_b4,
    se_Amem_b4 = se_b4,
    val_Amem_b0_b2 = !!calc_Amem_b0_b2,
    se_Amem_b0_b2 = propagate_error(!!calc_Amem_b0_b2, dval_b2 = se_b2, dval_b0 = se_b0),
    val_Amem_b1_b3 = !!calc_Amem_b1_b3,
    se_Amem_b1_b3 = propagate_error(!!calc_Amem_b1_b3, dval_b3 = se_b3, dval_b1 = se_b1),
    val_Amem_b2_b3 = !!calc_Amem_b2_b3,
    se_Amem_b2_b3 = propagate_error(!!calc_Amem_b2_b3, dval_b3 = se_b3, dval_b2 = se_b2)
  )

calib_params_table <- 
  left_join(
  calib_params %>%
    select(d2H_calib, starts_with("val")) %>%
    pivot_longer(cols = -d2H_calib, names_to = "var", 
                 names_transform = ~str_remove(.x, "val_")),
  calib_params %>%
    select(d2H_calib, starts_with("se")) %>%
    pivot_longer(cols = -d2H_calib, names_to = "var", values_to = "se", 
                 names_transform = ~str_remove(.x, "se_")),
  by = c("d2H_calib", "var")
) %>%
  mutate(
    formatted = format_with_decimals(value, error = se, decimals = find_signif_decimals(se, 1), include_plus = FALSE)
  ) %>%
  pivot_wider(id_cols = var, names_from = d2H_calib, values_from = formatted)

# results
calib_params_table

```

# Residuals

## Labeled samples

```{r "residuals", fig.width=11, fig.height=6, warning=FALSE}
global_calib %>%
  mutate(
    d2H_calib = as_factor(d2H_calib) %>%
      fct_recode(
        "$\\delta_{peak/H2} = \\beta_0 + \\beta_1 \\cdot \\delta_{analyte/VSMOW}$" = "b0_b1_only",
        "$... + \\beta_2 \\cdot \\frac{1}{A_{peak}} + \\beta_3 \\cdot \\frac{\\delta_{analyte/VSMOW}}{A_{peak}}$" = "plus_area_b2_b3",
        "$... + \\beta_4 \\cdot \\frac{\\delta_{mem/H2}}{A_{peak}}$" = "plus_area_b2_b3_mem"
      )
  ) %>%
  # plot residuals
  iso_plot_residuals(
    x = area2, # vs. area
    points = TRUE, size = 2, alpha = 0.5,
    color = true_d2H,
    panel = NULL,
    # residual smoothing fit
    trendlines = FALSE,
    value_ranges = FALSE,
    smooth = geom_smooth(
      mapping = aes(color = NULL, shape = NULL), method = "loess", formula = y ~ x
    )
  ) +
  # put on log x scale
  scale_x_log10() +
  scale_color_continuous(labels = function(x) sprintf("%+.0f\U2030", x)) +
  theme_figure(grid = FALSE) +
  theme(legend.position = c(0.93, 0.23), legend.title.align = 0.5) +
  labs(
    x = "mass 2 area (A) in Vs",
    y = "standard residuals in \U2030",
    color = expression(delta^2*H)
  ) +
  facet_grid(.~d2H_calib, labeller = latex_labeller)
```

## Unlabeled samples

```{r "residuals_t0", fig.width=9, fig.height=6, warning=FALSE}
global_calib_t0 %>%
  # plot residuals
  iso_plot_residuals(
    x = area2, # vs. area
    points = TRUE, size = 2, alpha = 0.5,
    shape = type,
    # residual smoothing fit
    trendlines = FALSE,
    smooth = geom_smooth(
      mapping = aes(color = NULL, shape = NULL), method = "loess", formula = y ~ x
    )
  ) +
  # put on log x scale
  scale_x_log10() +
  theme(legend.position = "right")
```

# Apply Global Calibrations (*)

## Labeled samples

```{r, warning=FALSE, cache=TRUE}
# applying model (also include without memory to figure out how much of a difference it makes)
global_calibs_applied <-
  global_calib %>%
  iso_apply_calibration(
    predict = true_d2H,
    calculate_error = TRUE
  )

# ranges
global_calibs_w_ranges <-
  global_calibs_applied %>%
  iso_evaluate_calibration_range(area2, true_d2H_pred)

global_calibs_w_ranges %>%
  iso_get_calibration_range() %>%
  knitr::kable(d=2)

calib_range_area2 <- c(
  iso_get_calibration_range(global_calibs_w_ranges)  %>% filter(term == "area2") %>% pull(min),
  to = iso_get_calibration_range(global_calibs_w_ranges)  %>% filter(term == "area2") %>% pull(max)
)
```

## Unlabeled samples

```{r, warning=FALSE, cache=TRUE}
# applying model (also include without area to check differences)
global_calibs_applied_t0 <-
  global_calib_t0 %>%
  filter(d2H_calib %in% c("b0_b1_only", "plus_area_b2_b3_log")) %>%
  iso_apply_calibration(
    predict = true_d2H,
    calculate_error = TRUE
  )

# ranges
global_calibs_w_ranges_t0 <-
  global_calibs_applied_t0 %>%
  iso_evaluate_calibration_range(area2, true_d2H_pred)

global_calibs_w_ranges_t0 %>%
  iso_get_calibration_range() %>%
  knitr::kable(d=2)

calib_range_area2_t0 <- c(
  iso_get_calibration_range(global_calibs_w_ranges_t0)  %>% filter(term == "area2") %>% pull(min),
  to = iso_get_calibration_range(global_calibs_w_ranges_t0)  %>% filter(term == "area2") %>% pull(max)
)
```

# Calibrated Data Table (*)

```{r}
# calibrated table - combine all the information
peak_table_calibrated <- global_calibs_w_ranges %>%
  iso_get_calibration_data() %>%
  filter(!is.na(true_d2H_pred)) %>%
  mutate(
    below_area_range = str_detect(d2H_in_range, fixed("<'area2'")),
    above_area_range = str_detect(d2H_in_range, fixed(">'area2'")),
    outside_d2H_range = str_detect(d2H_in_range, "true_d2H")
  ) %>% 
  select(-d2H_calib_params) %>%
  { 
    x <- filter(., d2H_calib == "b0_b1_only") %>%
      rename(
        calibrated_d2H_without_area = true_d2H_pred, 
        calibrated_d2H_without_area_se = true_d2H_pred_se
      )
    y <- filter(., d2H_calib == "plus_area_b2_b3") %>%
      select(
        peak_id, 
        calibrated_d2H_without_memory = true_d2H_pred, 
        calibrated_d2H_without_memory_se = true_d2H_pred_se
      )
    z <- filter(., d2H_calib == "plus_area_b2_b3_mem") %>%
      select(
        peak_id, 
        calibrated_d2H_with_memory_correction = true_d2H_pred, 
        calibrated_d2H_with_memory_correction_se = true_d2H_pred_se
      )
    left_join(x, y, by = "peak_id") %>%
      left_join(z, by = "peak_id")
  } %>%
  {
    x <- global_calibs_w_ranges_t0 %>%
      filter(d2H_calib == "b0_b1_only") %>%
      iso_get_calibration_data() %>%
      select(
        peak_id, 
        calibrated_d2H_unlabeled_no_area = true_d2H_pred, 
        calibrated_d2H_unlabeled_no_area_se = true_d2H_pred_se
      )
    y <- global_calibs_w_ranges_t0 %>%
      filter(d2H_calib == "plus_area_b2_b3_log") %>%
      iso_get_calibration_data() %>%
      select(
        peak_id, 
        calibrated_d2H_unlabeled = true_d2H_pred, 
        calibrated_d2H_unlabeled_se = true_d2H_pred_se
      )
    left_join(., x, by = "peak_id") %>%
      left_join(y, by = "peak_id")
  }
```

# Calibration Standards

```{r}
calibration_std_peak_table <-
  peak_table_calibrated %>%
  filter(d2H_in_calib )

# residuals + errors of the inverted calibration
deg_freedom_calib <- global_calib %>%
  filter(d2H_calib == "plus_area_b2_b3") %>%
  iso_get_calibration_summary() %>% pull(df.residual)

deg_freedom_calib_t0 <- global_calib_t0 %>%
  filter(d2H_calib == "plus_area_b2_b3_log") %>%
  iso_get_calibration_summary() %>% pull(df.residual)

# by compound
calibration_std_peak_table %>%
  group_by(compound, type) %>%
  summarize(
    calibrated_d2H_without_memory_sd = sd(calibrated_d2H_without_memory),
    calibrated_d2H_with_memory_correction_sd = sd(calibrated_d2H_with_memory_correction),
    .groups = "drop"
  )

# over all rmse
calibration_std_peak_table %>%
  summarize(
    n = n(), 
    # residual standard deviation (sometimes called incorrectly residual standard error)
    RDS_unlabeled = sqrt(sum((calibrated_d2H_unlabeled - true_d2H)^2, na.rm = TRUE) /
                 (deg_freedom_calib_t0)) %>% round(2),
    RSD_no_area = sqrt(sum((calibrated_d2H_without_area - true_d2H)^2, na.rm = TRUE) /
                 (deg_freedom_calib)) %>% round(2),
    RSD_no_mem = sqrt(sum((calibrated_d2H_without_memory - true_d2H)^2, na.rm = TRUE) /
                 (deg_freedom_calib)) %>% round(2),
    RSD_w_mem = sqrt(sum((calibrated_d2H_with_memory_correction - true_d2H)^2, na.rm = TRUE) /
                 (deg_freedom_calib)) %>% round(2),
    # root mean square error / root mean square deviation
    RMSE_unlabeled = sqrt(mean((calibrated_d2H_unlabeled - true_d2H)^2, na.rm = TRUE)) %>%
      round(2),
    RMSE_no_area = sqrt(mean((calibrated_d2H_without_area - true_d2H)^2, na.rm = TRUE)) %>%
      round(2),
    RMSE_no_mem = sqrt(mean((calibrated_d2H_without_memory - true_d2H)^2, na.rm = TRUE)) %>%
      round(2),
    RMSE_w_mem = sqrt(mean((calibrated_d2H_with_memory_correction - true_d2H)^2, na.rm = TRUE)) %>%
      round(2),
    .groups = "drop"
  ) %>%
  knitr::kable()
```

# Extraction Standards

```{r}
extraction_std_peak_table <- 
  peak_table_calibrated %>%
  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"), !below_area_range)

extraction_std_peak_table %>%
  filter(!below_area_range, !above_area_range) %>%
  iso_plot_data(
    x = area2, y = c(calibrated_d2H_without_memory, calibrated_d2H_with_memory_correction), 
    color = compound,
    points = TRUE
  ) +
  scale_x_log10()

extraction_std_peak_table %>%
  filter(!below_area_range, !above_area_range) %>%
  group_by(compound) %>%
  summarize(
    calibrated_d2H_without_memory_sd = sd(calibrated_d2H_without_memory),
    calibrated_d2H_with_memory_correction_sd = sd(calibrated_d2H_with_memory_correction),
    .groups = "drop"
  )
```

# Sample Analytes

```{r}
# warning! 
# don't try to interpret peaks that are so small they are below the calibration area range,
# they are often overextrapolated
analytes_peak_table <-
  peak_table_calibrated %>%
  select(-use_in_calib, -is_std_peak, -individual, -injection_volume, -gc_method, -map_id, -peak_type, -ref_nr, -calib_peak, -is_ref, -d2H_in_calib, -d2H_calib, -true_d2H, -row_id, -d2H_resid) %>%
  filter(str_detect(type, "sample") & !str_detect(compound, "STD")) %>%
  mutate(
    calibrated_d2H_without_area = 
      ifelse(
        type == "unlabeled sample",
        calibrated_d2H_unlabeled_no_area,
        calibrated_d2H_without_area
      ),
    calibrated_d2H_without_area_se = 
      ifelse(
        type == "unlabeled sample",
        calibrated_d2H_unlabeled_no_area_se,
        calibrated_d2H_without_area_se
      ),
    calibrated_d2H_without_memory = 
      ifelse(
        type == "unlabeled sample",
        calibrated_d2H_unlabeled,
        calibrated_d2H_without_memory
      ),
    calibrated_d2H_without_memory_se = 
      ifelse(
        type == "unlabeled sample",
        calibrated_d2H_unlabeled_se,
        calibrated_d2H_without_memory_se
      ),
    note = ifelse(below_area_range, "careful interpreting these!", "")
  ) %>%
  select(
    -calibrated_d2H_unlabeled, -calibrated_d2H_unlabeled_se,
    -calibrated_d2H_unlabeled_no_area, calibrated_d2H_unlabeled_no_area_se
  ) %>%
  select(id1, type, everything()) %>%
  relocate(starts_with("calibrated_"), d2H_in_range, note, .after = last_col()) %>%
  iso_strip_units()

export_to_excel(analytes_peak_table, file = "output/samples_data.xlsx")
```

### 2023-01-07 calibration_submodule/scripts/error_propagation.R

@@ -1,0 +1,59 @@
+#' Propagate error by formula using formula: sigma = sqrt( (df/dx)^2 sx^2 + (df/dy)^2 sy^2 + ... ). 
+#' This only works for independent variables as there are no covariance terms!
+#' All errors must be supplied as named \code{...} parameters where the names all start with \code{d} and match the variable names in the \code{formula}.
+#' @param eq the equation for calculating a new quantity that should be used to propagate error
+#' @param ... the error terms for the variables in the formula. Must all start with \code{d} and match all variables in the code. Omit a term by setting its error to 0/
+#' @examples
+#' tibble::tibble(
+#'   x  = runif(5), 
+#'   y  = runif(5), 
+#'   x_err = runif(5)/10, 
+#'   y_err = runif(5)/10,
+#'   z = (x-y)/(x+y)^2,
+#'   z_err = propagate_error((x-y)/(x+y)^2, dx = x_err, dy = y_err)
+#' )
+propagate_error <- function(eq, ..., quiet = FALSE) {
+  require(rlang)
+  # expression, variables and error terms
+  eq_quo <- enquo(eq)
+  eq_expr <- quo_get_expr(eq_quo)
+  eq_env <- quo_get_env(eq_quo)
+  variables <- all.vars(eq_expr)
+  errors <- paste0("d", variables)
+  error_terms <- rlang::enexprs(...)
+  
+  # check error terms are provided
+  if (length(missing_terms <- setdiff(errors, names(error_terms))) > 0) {
+    sprintf(
+      "missing error term(s): '%s'. All terms must be defined but can be set to 0 to omit individual errors.",
+      paste(missing_terms, collapse = "', '")
+    ) %>%
+      stop(call. = FALSE)
+  } else if (length(extra_terms <- setdiff(names(error_terms), errors)) > 0) {
+    sprintf(
+      "extra error term(s): '%s'. These terms do not match the error terms expected for the formula.",
+      paste(extra_terms, collapse = "', '")
+    ) %>%
+      stop(call. = FALSE)
+  }
+  
+  # construct propagated error
+  derivatives <- map(variables, ~D(eq_expr, .x))
+  
+  # terms for each variables: (df/dx * err)^2
+  prop_error_terms <- map2(derivatives, error_terms[errors], ~rlang::expr(((!!.x) * (!!.y))^2))
+  
+  # sum
+  sum_expr <- prop_error_terms[[1]]
[…]

### 2023-01-07 calibration_submodule/scripts/plotting_functions.R

@@ -1,0 +1,242 @@
+# Plotting helper functions -------
+
+#' Figure Theme
+#' 
+#' Theme for figures with frequently used formatting instructions.
+#' @param legend whether to show the legend
+#' @param grid whether to show the grid
+#' @param plot_margin margins for c(top, right, bottom, left) in mm
+#' @param text_size font size for all text on plot 
+#' @param axis_text_size font size for the axes' text (define only if different from text_size)
+#' @param axis_x_rotated whether to rotate the x axis labels
+theme_figure <- function(legend = TRUE, grid = TRUE, plot_margin = c(1, 1, 1, 1), 
+                         text_size = 20, axis_text_size = NULL, axis_x_rotate = 0) {
+  the_theme <- theme_bw() + 
+    theme(text = element_text(size = text_size),
+          plot.background = element_blank(), panel.background = element_blank(),
+          panel.border = element_rect(color="black", size=1), 
+          strip.background = element_rect(color="black", linetype = 1),
+          plot.margin = unit(plot_margin, "mm")
+    )
+  # adjust grid
+  if(!grid)
+    the_theme <- the_theme + theme(panel.grid = element_blank())
+  else
+    the_theme <- the_theme + theme(panel.grid.minor = element_blank())
+  # adjust legend
+  if (!legend)
+    the_theme <- the_theme + theme(legend.position = "none")
+  # overwrite axis text size if provided
+  if (!is.null(axis_text_size))
+    the_theme <- the_theme + 
+      theme(axis.text = element_text(size = axis_text_size)) 
+  # axis rotation
+  if (axis_x_rotate != 0) {
+    the_theme <- the_theme + 
+      theme(axis.text.x = element_text(angle = axis_x_rotate, vjust = 0.5, hjust = 1))
+  }
+  return(the_theme)
+}
+
+#' Parse scientific notation formatter for plot axes
+#' @example 
+#' p + scale_y_continuous(labels = parsed_sci_format(signif = 3))
+parsed_sci_format <- function(signif = 2, include_plus = FALSE) {
+  require("latex2exp")
+  function(x) {
+    tex_labels <- format_with_signif(x, signif = signif, always_sci = TRUE, sci_as_latex = TRUE, include_plus = include_plus)
[…]

### 2023-01-07 calibration_submodule/scripts/table_functions.R

@@ -1,0 +1,202 @@
+#' Format number with decimals
+#' This is useful for including numbers on plots as text elements.
+#' 
+#' @param decimals number of decimals to display (vectorized)
+#' @param error +/- errors vector to include (if NULL no error included)
+#' @param error_sep separator for value and error, only relevant if errors provided
+#' @param include_plus whether to include plus sign for positive numbers (x>0)
+#' @param na_value what value to use for NA values
+#' @return textual representation of the number matching the parameter settings
+format_with_decimals <- function(x, decimals, error = NULL, error_sep = " \U00B1 ", include_plus = FALSE, na_value = NA_character_) {
+  # safety checks
+  if (missing(decimals)) stop("no number of decimals specified", call. = FALSE)
+  if (length(decimals) == 1) {
+    decimals <- rep(decimals, length(x))
+  } else if (length(decimals) != length(x)) {
+    stop("decimals vector needs to be the same length as x vector", call. = FALSE)
+  } else if (any(is.na(decimals[!is.na(x)]))) {
+    stop("decimals not provided for all non-na x values", call. = FALSE)
+  }
+  if (length(error) > 0 && length(error) != length(x)) {
+    stop("if provided, errors vector needs to be the same length as x vector", call. = FALSE)
+  } else if (length(error) > 0 && any(is.na(error[!is.na(x)]))) {
+    stop("errors not provided for all non-na x values", call. = FALSE)
+  }
+  # determine formatting
+  plus <- if(include_plus) "+" else ""
+  # generate output vector
+  out <- character(length(x))
+  out[is.na(x)] <- na_value
+  # formatting
+  if (length(error) > 0)
+    out[!is.na(x)] <- sprintf(
+      sprintf("%%%s.%0.ff%s%%.%0.ff", plus, decimals[!is.na(x)], error_sep, decimals[!is.na(x)]), 
+      x[!is.na(x)], error[!is.na(x)]
+    )
+  else
+    out[!is.na(x)] <- sprintf(sprintf("%%%s.%0.ff", plus, decimals[!is.na(x)]), x[!is.na(x)])
+  # finished
+  return(out)
+}
+
+#' Format number with significant digits
+#' This is useful for including numbers on plots as text elements.
+#' 
[…]

### 2023-02-16 03_data_viz.Rmd
fixed "Tunrda" typo, removed cairo library

@@
 library(ggforce)      # Accelerating 'ggplot2', CRAN v0.3.3
-library(Cairo)
+
 ```
@@
     terrain == "Marshall Mesa Grassland" ~ "Grassland",
-    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
+    terrain == "Niwot Ridge Tundra" ~ "Tundra" )) %>% 
   # group_by(terrain, inc_time_d) %>% 
@@
     terrain == "Marshall Mesa Grassland" ~ "Grassland",
-    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>%
+    terrain == "Niwot Ridge Tundra" ~ "Tundra" )) %>%
   # group_by(terrain, inc_time_d) %>% 

### 2024-02-20 00_methylation_correction.qmd
add methylation correction calculation

---
title: "Phthalic acid analysis"
date: "`r format(Sys.Date(), '%d %b %Y')`"
number-sections: true
number-offset: 0
toc: true
toc-depth: 3
df-print: tibble
embed-resources: true
output:
  html: 
    code-tools: true
    code-fold: show
    code-summary: "Show the code"
    toc-float: true
editor: source
editor_options: 
  chunk_output_type: console
---

Using `r R.version.string`, tidyverse version `r packageVersion("tidyverse")`, isoreader version `r packageVersion("isoreader")`, and isoprocessor version `r packageVersion("isoprocessor")`.

```{r}
#| label: setup
#| echo: true
#| message: false
#| warning: false

# load libraries
library(rlang)
library(tidyverse)
library(isoreader)
library(isoprocessor)

min_isoreader_version <- "1.3.9999"
min_isoprocesor_version <- "0.6.11"
if (packageVersion("isoreader") < min_isoreader_version) {
  sprintf(
    "min required isoreader version %s, install with devtools::install_github('isoverse/isoreader')", 
    min_isoreader_version) |> 
  stop(call. = FALSE)
}
if (packageVersion("isoprocessor") < min_isoprocesor_version) {
  sprintf(
    "min required isoprocessor version %s, install with devtools::install_github('isoverse/isoprocessor')", 
    min_isoprocesor_version) |> 
  stop(call. = FALSE)
}

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("plots", paste0(gsub("\\.[Rr](md|markdown)", "", knitr::current_input()), "_"))
)
```

# Calibration Prep

# Load data files

```{r}
# iso_files_raw <-
#   "data/PAME_data" |>
#   iso_read_continuous_flow(read_cache = TRUE, parallel = TRUE) |>
#   iso_save("data/PAME_data.cf.rds")

iso_files_raw <- 
  iso_read_continuous_flow("data/PAME_data.cf.rds") |>
  # remove files with read errors (usually aborted samples)
  iso_filter_files_with_problems() |>
  # process isodat peak table
  iso_set_peak_table_from_isodat_vendor_data_table() |>
  # convert units from mV to V for amplitudes and area
  iso_convert_peak_table_units(V = mV, Vs = mVs)
```

# Process File Information

```{r}
# parse file info
iso_files_w_file_info <- iso_files_raw |>
  # rename key file info columns
  iso_rename_file_info(id1 = `Identifier 1`, id2 = `Identifier 2`) |> 
  # process file information
  iso_mutate_file_info(
    # analysis as number
    analysis = as.integer(parse_number(Analysis)),
    # what is the type of each analysis?
    type = case_when(
      str_detect(id1, "[Zz]ero")      ~ "on_off",
      str_detect(id1, "H3")           ~ "H3_factor",
      str_detect(id1, "F8")           ~ "standard",
      str_detect(id1, "PAME")         ~ "pame",
      TRUE                            ~ "other"
    )
  ) |>
  # focus on the file info we want to use
  iso_select_file_info(analysis, file_datetime, id1, type)
```

# First look at chromatograms

```{r}
#| label: fig-chroms-first-look
#| warning: false
#| fig-width: 10
#| fig-height: 8
# look at specific files for peak mapping purposes

iso_files_w_file_info |> 
  iso_filter_files(analysis %in% c(12775, 12759)) |>
  iso_plot_continuous_flow_data(
    data = 2,
    #time_interval = c(1200, 1400),
    #time_interval = c(700, 1400),
    peak_label = iso_format(peak_nr, rt),
    panel = sprintf("%s (#%s)", id1, analysis),
    peak_label_options = list(size = 3)
  ) +
  theme(legend.position = "bottom")
```

# Peak Mapping

```{r}
# sample info and peak maps
peak_maps <- readxl::read_excel("data/PAME_peak_map.xlsx")

iso_files_w_mapped_peaks <- 
  iso_files_w_file_info |> 
  iso_filter_files(type %in% c("standard", "pame")) |>
  # map peaks
  iso_map_peaks(peak_maps, map_id = type)
iso_files <- iso_files_w_mapped_peaks
```

# Peak Table & Calculations

```{r}
#| label: all-peaks-calculations

# pull out the peak table and calculate the delta_peak vs. H2 ref
peak_table_all <- iso_files |>
  iso_get_peak_table(include_file_info = everything()) |>
  group_by(file_id) |>
  mutate(
    ref_ratio_at_rt = 
      lm(y ~ x, 
         data = tibble(
           x = rt[calib_peak == TRUE], 
           y = `r3/2`[calib_peak == TRUE])) |> 
      predict(newdata = tibble(x = rt)) |> 
      as.numeric(),
    d2H_vs_H2 = (`r3/2` / ref_ratio_at_rt - 1) * 1000
  ) |>
  ungroup()

# focus on analytes
peak_table <- peak_table_all |>
  filter(is.na(ref_nr)) |>
  iso_mutate_peak_table(
    group_by = file_id,
    rel_area = area2/sum(area2, na.rm=TRUE),
    mean_area = mean(area2, na.rm=TRUE),
    mean_area_identified = mean(area2[!is.na(compound)], na.rm=TRUE),
    sd_area_identified = sd(area2[!is.na(compound)], na.rm=TRUE),
    mean_amp_identified = mean(amp2[!is.na(compound)], na.rm=TRUE),
    contaminants = any(peak_type == "contaminant" & !is.na(d2H_vs_H2))
  )
```

# Add Standards' Isotope Data

```{r}
standards <- readxl::read_excel("data/standards.xlsx") |>
  mutate(
    type = "standard",
    true_d2H = iso_double_with_units(true_d2H, "permil")
  )

standards |> iso_make_units_explicit() |> knitr::kable(digits=2)

peak_table_with_stds <-
  peak_table |>
  iso_add_standards(stds = standards, match_by = c("type", "compound"))
```

# Generate Global Galibration

```{r}
# area_range
area_range <- c(10, 50)

global_calib_pame <- 
  peak_table_with_stds |>
  iso_remove_problematic_peak_mappings(remove_unidentified = FALSE, remove_ambiguous = FALSE) |>
  filter(type %in% c("standard", "pame")) |>
  iso_prepare_for_calibration() |>
  iso_generate_calibration(
    calibration = "d2H",
    model=c(calib = lm(d2H_vs_H2 ~ true_d2H)),
    # calibrate based on standards with all peaks
    use_in_calib = 
      type == "standard" & is_std_peak &
      # constrain area calibration range
      area2 >= iso_double_with_units(area_range[1], "Vs") &
      area2 <= iso_double_with_units(area_range[2], "Vs") 
  ) |>
  iso_remove_problematic_calibrations()
```

# Apply Calibration

For the narrow range where the pame peaks are, there's no point adding an area correction, instead just go with a linear correction.

```{r}
#| warning: false
global_calibs_pame_applied <-
  global_calib_pame |>
  iso_apply_calibration(
    predict = true_d2H,
    calculate_error = TRUE
  )

# ref tank (H2) isotope value estimate
beta_0 <- 
  global_calibs_pame_applied |> 
  iso_get_calibration_parameters(select_from_summary = c()) |> 
  filter(term == "(Intercept)")

d_H2_VSMOW.permil <- -beta_0$estimate/(1 + beta_0$estimate / 1000)
sprintf("Info: estimated d2H of the H2 ref tank (vs. VSMOW): %.1f permil", d_H2_VSMOW.permil)

# ranges
global_calibs_pame_w_ranges <-
  global_calibs_pame_applied |>
  iso_evaluate_calibration_range(area2, true_d2H_pred)

global_calibs_pame_w_ranges |>
  iso_get_calibration_range() |>
  knitr::kable(d=2)

# final peak table
peak_table_pame_final <- 
  global_calibs_pame_w_ranges |>
  iso_get_calibration_data() |>
  filter(!is.na(compound))
```

# Export

```{r "pame", fig.width=12, fig.height=9, warning = FALSE}
# phthala data
pame <- 
  peak_table_pame_final |>
  filter(peak_type == "analyte") |>
  iso_make_units_explicit(prefix = ".", suffix = "") |>
  rename(sample_id = id1) |>
  arrange(sample_id, compound, analysis)

pame_summary <- 
  pame |>
  summarize(
    pame_n = n(),
    pame_mean = mean(true_d2H_pred.permil),
    pame_sd = sd(true_d2H_pred.permil)
  )

# export
iso_export_data_to_excel(
  summary = pame_summary,
  data = pame, 
  filepath = "data/PAME_TAC_jan_2022.xlsx"
)
```

# Methanol Calculation

```{r}
pame_summary |>
  mutate(
    # known isotopic composition of the 4 non-exchangeable Hs of phthalic acid
    pa_d2H = -81.9,
    pa_d2H_err = 1.2,
    # mass balance calculation of methanol methyl group H d2H
    meoh_d2H = 10/6 * pame_mean - 4/6 * pa_d2H,
    meoh_d2H_err = sqrt((10/6 * pame_sd)^2 + (4/6 * pa_d2H_err)^2)
  ) |>
  knitr::kable(digits = 2)
```

### 2024-02-26 01C_Compare_PAME.qmd
comparison of non-corrected and corrected PAME data

---
title: "Compare PAME Correction Datasets"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

In this file, we compare the datasets which were generated with both un-corrected and corrected phthalic acid methyl ester (PAME) values.

```{r}
library(tidyverse)
```

## Import Datasets

```{r}
lipid_data_no_correction <- read_rds("cache/LH_SIP_data.RDS") |> 
  select(Analysis, sample_id, soil, inc_time_d, compound, area2, `2F_alk_mc`) |> 
  rename(`F2H_alk_not_corrected` = `2F_alk_mc`) |> 
  group_by(Analysis) |> 
  distinct(compound, .keep_all = TRUE)

lipid_data_corrected <- readxl::read_excel("data/LH_SIP_PAME_CORR.xlsx") |> 
  select(Analysis, sample_id, compound, `2F_alk_mc`) |> 
  rename(`F2H_alk_corrected` = `2F_alk_mc`) |> 
  group_by(Analysis) |> 
  distinct(compound, .keep_all = TRUE)
```

```{r}
lipid_data <- lipid_data_no_correction |> 
  left_join(lipid_data_corrected, by = c("Analysis", "sample_id", "compound")) |> 
  # filter non-negative F2H: some F2H are negative due to memory effect calculation
  # these negative F2H are filtered out in the growth rate script because
  # it is impossible to have negative growth
  filter(F2H_alk_not_corrected >= 0, F2H_alk_corrected >= 0) |> 
  mutate(diff_F2H = F2H_alk_not_corrected - F2H_alk_corrected) |> 
  mutate(F2H_alk_not_corrected_ppm = F2H_alk_not_corrected * 1e4,
         F2H_alk_corrected_ppm = F2H_alk_corrected * 1e4,
         diff_F2H_ppm = diff_F2H * 1e4)
```

# Compare

```{r}
p_line <- lipid_data |> 
  ggplot(
    aes(
      x = F2H_alk_not_corrected_ppm,
      y = F2H_alk_corrected_ppm
    )
  ) +
  geom_abline(color = "red") +
  stat_smooth(
    formula = "y~x", method = "lm", se = FALSE,
    color = "blue", linewidth = 0.5,
    fullrange = TRUE
  ) +
  #scale_x_continuous(limits = c(-3000, 3000)) +
  coord_cartesian(xlim = c(0, 2300), ylim = c(0, 2300)) +
  geom_point() +
  labs(
    x = "F2H (ppm) (before PAME correction)",
    y = "F2H (ppm) (after PAME correction)"
  ) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

```{r}
mean_offset = lipid_data |> pull(diff_F2H) |> abs() |> mean()

p_histogram <- lipid_data |> 
  ggplot(
    aes(x = abs(diff_F2H) * 1e4)
  ) +
  geom_histogram(binwidth = 0.5) +
  geom_vline(xintercept = mean_offset * 1e4,
             color = "red", linetype = "dashed") +
  labs(
    x = "F2H difference (ppm)",
    y = "Count"
  ) +
  theme_bw() +
  theme(aspect.ratio = 1)

paste("The average offset between the data that was and was not properly corrected for the isotopic composition of the derivatization agent is", 
      round(mean_offset, 3), 
      "atom %; or ", 
      round(mean_offset * 1e4, 3), 
      "parts per million."
      )
```

```{r}
combined <- cowplot::plot_grid(p_line, p_histogram, nrow = 2)

cowplot::save_plot(plot = combined, base_height = 8, base_width = 6, filename = "fig_output/PAME_correction.pdf")
```

### 2024-02-26 01B_LH-SIP_Data_Reduction_Correction.Rmd
Update 01B_LH-SIP_Data_Reduction_Correction.Rmd

--- 2023-01-06 01_LH-SIP_Data_Reduction.Rmd
@@
 
+> NOTE: For this analysis, we use the corrected PAME dataset: `data/PAME_TAC_jan_2022.xlsx`. The original script `01_LH-SIP_Data_Reduction.rmd` is retained for reference.
+
 ```{r}
-# Load PAME Iso Files
-PAME_data_path <- file.path("data", "PAME_data")
-ref_ratio <- get_standard("2H") %>% as.numeric()
-
-# read files
-PAME_iso_files_raw <- 
-  # path to data files
-  PAME_data_path %>% 
-  # read data files in parallel for fast read
-  iso_read_continuous_flow() %>%
-  # filter out files with read errors (e.g. from aborted analysis)
-  iso_filter_files_with_problems()
-
-# Load Peak Map
-
-PAME_peak_map <- 
-  # initial peak map:
-  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
-  # corrected peak map
-  readxl::read_excel(file.path("data", "IRMS", "PAME_peak_map.xlsx"))
-PAME_peak_map
-
-# process file information
-PAME_iso_files <- PAME_iso_files_raw %>% 
-  # rename key file info columns
-  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
-  # parse text info into numbers
-  iso_parse_file_info(number = analysis) %>% 
-  # process other file information that is specific to the naming conventions
-  # of this particular sequence
-  iso_mutate_file_info(
-    # what is the type of each analysis?
-    type = case_when(
-      str_detect(id1, "[Zz]ero")      ~ "on_off",
-      str_detect(id1, "H3")           ~ "H3_factor",
-      str_detect(id1, "F8")           ~ "F8_std",
-      str_detect(id1, "F9")           ~ "F9_std",
-      TRUE                            ~ "sample"
-    ),
-    # what was the concentration? (assuming Preparation = concentration or volume)
-    concentration = 
-      ifelse(type == "std",  
-             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
-               parse_number() %>% iso_double_with_units("ng/uL"),
-             NA),
-    # what folder are the data files in? (assuming folder = sequence)
-    folder = basename(dirname(file_path))
-  ) %>% 
-  # focus only on the relevant file info, discarding the rest
-  iso_select_file_info(
-    folder, analysis, file_datetime, id1, type, concentration
+PAME_summarized <- readxl::read_excel("data/PAME_TAC_jan_2022.xlsx") |> 
+  mutate(
+    # known isotopic composition of the 4 non-exchangeable Hs of phthalic acid
+    pa_d2H = -81.9,
+    pa_d2H_err = 1.2,
+    # mass balance calculation of methanol methyl group H d2H
+    meoh_d2H = 10/6 * pame_mean - 4/6 * pa_d2H,
+    meoh_d2H_err = sqrt((10/6 * pame_sd)^2 + (4/6 * pa_d2H_err)^2),
+    # convert delta d2H to atom percent at2H
+    at2H_mn = d2H_to_2F(meoh_d2H)
   )
 
-# Peak Mapping
-# set peak table from vendor data table with default isodat template
-PAME_iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(PAME_iso_files) %>% 
-  # convert units from mV to V for amplitudes and area
-  iso_convert_peak_table_units(V = mV, Vs = mVs)
-
-# Create Peak Table and filter out non-PAME samples
-PAME_peak_table <- PAME_iso_files %>%
-  iso_filter_files(str_detect(id1, "PAME")) %>% 
-  # Choose only runs that worked
-  iso_filter_files(str_detect(file_id, "success")) %>% 
-  iso_set_peak_table_from_isodat_vendor_data_table() %>%
-  iso_get_peak_table() %>% 
-  mutate(Analysis = substr(file_id, 1, 7),
-         sample_id = substr(file_id, 10,14))
-
-PAME_peak_mapped <- PAME_peak_table %>%
-  iso_map_peaks(PAME_peak_map, map_id = Analysis) %>%
-  filter(!is.na(compound))
-
-# Summarize the mean and standard error
-PAME_summarized <- PAME_peak_mapped %>%
-  summarize(at2H_mn = mean(at2H),
-            at2H_se = sd(at2H)) %>% 
-  mutate(at2H_mn_ppm = at2H_mn * 10000,
-         at2H_se_ppm = at2H_se * 10000)
+# uncomment this to write to drive:
+# writexl::write_xlsx(PAME_summarized, path = "data/PAME_TAC_jan_2022.xlsx")
+write_rds(PAME_summarized, file = "cache/PAME_summarized.rds")
 ```
@@
 
-## Load GC-FID Data
-
-```{r}
-root <- file.path("data", "gc_fid_data_2021")
-file_list = list.files(path = root)
-file_list <- file_list %>% 
-  str_subset("blank", negate = TRUE) %>% 
-  str_subset("Blank", negate = TRUE) %>% 
-  str_subset("GCMS-STD", negate = TRUE) %>% 
-  str_subset("BLK", negate = TRUE) # remove procedural blanks
-sample_names <- file_list %>% 
-  str_replace("FID.....", "") %>% 
-  str_replace("_100ul-nhex.xls", "") %>% 
-  str_replace("_100ul.xls", "")
-
-FID_all_data <-
-  tibble(
-    sample = sample_names,
-    file = file_list,
-    data = map(file.path(root, file), read_chromeleon_export),
-    injection_details = map(data, "injection_details"),
-    integration_results = map(data, "integration_results")
-  ) %>% select(-data)
-```
-
-### Unnest FID integration details and clean
-
-```{r}
-FID_results <- FID_all_data %>% 
-  select(-injection_details) %>% 
-  unnest(integration_results) %>% 
-  filter(nchar(`Peak Name`) > 0) %>% 
-  # Specify chain length
-  mutate(
-    chain = `Peak Name` %>% 
-      str_remove("\\d+-OH") %>% 
-      parse_number() %>% 
-      abs() %>% 
-      {paste0("C", .)} %>% 
-      factor()
-      ) %>% 
-  # Rename these columns so we can join the IRMS and FID data
-  # Important to specify what data comes from FID!
-  rename(
-    "sample_id" = sample,
-    "compound" = `Peak Name`,
-    "rt_FID" = `Retention Time`,
-    "area_FID" = `Area`,
-    "height_FID" = `Height`,
-    "rel_area_FID" = `Relative Area`,
-    "rel_height_FID" = `Relative Height`,
-    "amount_FID" = `Amount`
-         ) %>% 
-  # Make FID notation match IRMS notation
-  mutate(
-    compound = 
-      case_when(
-        str_detect(compound, "18:2 trans 9, 12") ~ "18:2 9, 12",
-        str_detect(compound, "18:2 trans 9,12") ~ "18:2 9, 12",
-        str_detect(compound, "18:2 9,12") ~ "18:2 9, 12",
-        str_detect(compound, "16:1 cis-9") ~ "16:1 cis 9",
-        str_detect(compound, "16:1 trans-9") ~ "16:1 trans 9",
-        str_detect(compound, "18:1 cis-9") ~ "18:1 cis 9",
-        str_detect(compound, "18:1 trans-9") ~ "18:1 trans 9",
-        str_detect(compound, "21:0") ~ "21:0 (STD)",
-        str_detect(compound, "23:0") ~ "23:0 (STD)",
-        TRUE ~ compound
-      )
-  )
-```
-
 ## Load memory-corrected IRMS data!
@@
             a_mn = mean(estimate, na.rm = TRUE))
-```
-
-## FID Data
-
-```{r compound_abundance}
-# Compute the instrument response for each run:
-# Response = µg per unit area using 10µg of PAIBE as quantification STD
-
-FID_results_PAIBE_ug <- FID_results %>% 
-  select(
-    sample_id, 
-    file,
-    compound,
-    area_FID, 
-    rel_area_FID
-  ) %>% 
-  filter(compound == "PAIBE") %>% 
-  mutate(
-    PAIBE_area = area_FID,
-    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
-    # Find instrument response as PAIBE mass per FID area
-    ug_per_area = PAIBE_ug_inj / PAIBE_area,
-    # Check that the inferred mass is the same as known mass
-    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
-  ) %>%
-  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
-
-```
-
-### Calculate mass of analyte injected into GC-FID
-
-```{r response}
-# Put the response info back into the abundance data frame:
-FID_results_abundance <- 
-  left_join(
-    FID_results, 
-    FID_results_PAIBE_ug, 
-    by = "file"
-    ) %>%
-  # Calculate the quantity of analyte injected based off of area and 
-  # instrument response
-  mutate(
-    compound_ug_inj = area_FID * ug_per_area,
-    inj_vol_ul = 1, # GC-FID injection volume µL
-    susp_vol_ul = 100, # suspension volume µL
-    # The mass of analyte in vial is the concentration of analyte (mass 
-    # seen per unit volume injected) times the suspension volume.
-    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
-  )
-
-```
-
-### Calculate fractional derivatization efficiency (21-PC)
-```{r 21_PC}
-FID_results_abundance_21 <- FID_results_abundance %>% 
-  filter(compound == "21:0 (STD)") %>% 
-  # Derivatization efficiency is the amount of standard observed divided by 
-  # the amount of standard added (21:0 PC = 10µg)
-  mutate(
-    STD21_ug = 10,
-    deriv_efficiency = compound_ug_vial / STD21_ug
-  ) %>% 
-  select(file, STD21_ug, deriv_efficiency)
-
-# Add deriv efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance, 
-    FID_results_abundance_21, 
-    by = "file"
-  ) %>% 
-  # Calculate mass of fatty acids in extraction mixture as
-  # compounds present as FAMEs multiplied by derivatization efficiency
-  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
-```
-
-### Calculate extraction efficiency (23-PC)
-
-```{r 23_PC}
-FID_results_abundance_23 <- FID_results_abundance %>% 
-  filter(compound == "23:0 (STD)") %>% 
-  # Lipid Recovery Efficiency is the amount of initial standard 
-  # observed divided by the amount of standard added (23:0 PC = 100ug)
-  mutate(
-    STD23_ug = 100,
-    extr_efficiency = compound_ug_vial / STD23_ug
-  ) %>% 
-  select(file, STD23_ug, extr_efficiency)
-
-# Add extr efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance,
-    FID_results_abundance_23,
-    by = "file"
-  ) %>% 
-  mutate(
-    # Calculate amount of analyte in soil sample
-    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
-    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
-    soil_mass_g = 10, # 10 g of each soil were used for this study
-    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
-  )
-```
-
-### Remove standards from soil abundances
-
-```{r}
-# Remove standards from soil abundances
-
-FID_results_abundance_no_stds <- FID_results_abundance %>% 
-  filter(
-    !compound %in% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
-    str_detect(sample_id, "FAME", negate = TRUE),
-    str_detect(sample_id, "BAME", negate = TRUE)
-  )
 ```
@@
 
-## Join IRMS and GC-FID Data
-
-```{r}
-# peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
-#   left_join(FID_results, by = c("sample_id", "compound"))
-
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>%
-  left_join(
-    FID_results_abundance_no_stds, 
-    by = c("sample_id", "compound")
-  )
-```
-
 ## Apply corrections
@@
 
-peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
+peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros %>% 
   left_join(compound_nC_nH, by = "compound") %>% 
@@
          compound,
-         area_FID,
-         rel_area_FID,
+         #area_FID,
+         #rel_area_FID,
          rt,
@@
          area3,
-         area_FID,
-         compound_ug_per_g_soil,
+         #area_FID,
+         #compound_ug_per_g_soil,
          a, # assimilation efficiency
@@
 ```{r}
-# Export as RDS
-
-# Peak data
-saveRDS(peaks_mapped_with_zeros_analytes_reduced,
-        file = "cache/LH_SIP_data.RDS")
-
-# Label 2F
-saveRDS(F_L_2F,
-        file = "cache/heavy_label_data.RDS")
-
-# Assimilation Efficiency Linear Model
-saveRDS(d2H_assim_lm_summary,
-        file = "cache/d2H_assimilation.RDS")
-
-# Asssimilation Efficiency data
-saveRDS(d2H_assim_lm,
-        file = "cache/d2H_assimilation_lm.RDS")
-
-# Standard Error of IRMS measurements at time zero
-saveRDS(sF_0,
-        file = "cache/sF_0.RDS")
-
-# Memory-corrected data
-saveRDS(LH_SIP_memcorr,
-        file = "cache/LH_SIP_memcorr.RDS")
-
-# Full dataset
-saveRDS(sample_files, 
-        file = "cache/sample_files.RDS")
-
-# Export dataset for SI
-writexl::write_xlsx(
-  peaks_mapped_with_zeros_analytes_reduced %>% 
-    filter(compound != "H2"),
-  path = "cache/LH_SIP_data.xlsx"
-  )
+peaks_mapped_with_zeros_analytes_reduced |> writexl::write_xlsx(path = "data/LH_SIP_PAME_CORR.xlsx")
 ```

### 2024-07-25 01_LH-SIP_Data_Reduction.Rmd
biocrust data analysis

@@
   # corrected peak map
-  readxl::read_excel(file.path("data", "IRMS", "PAME_peak_map.xlsx"))
+  readxl::read_excel(file.path("data", "PAME_peak_map.xlsx"))
 PAME_peak_map

### 2024-07-25 03_data_viz.Rmd
biocrust data analysis

@@
     ) %>% 
-  # mutate(
-  #   compound = str_replace(
-  #     string = compound, 
-  #     pattern = "ω", 
-  #     replacement = "$\omega$")
-  # ) %>% 
+  mutate(
+    compound = str_replace(
+      string = compound,
+      pattern = "ω",
+      replacement = "w")
+  ) %>%
   select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
@@
     # ) +
+    ggrepel::geom_text_repel(
+    data = function(df) df |> filter(compound == "Weighted Mean"),
+    aes(
+      label = paste(formatC(u_d, format = "e", digits = 1), 
+                    " = \n", round(gen_d_mc, 0), "days")
+      ),
+    nudge_x = 0.1,
+    nudge_y = -1,
+    color = "red",
+    size = 3,
+    segment.alpha = 0.5, segment.curvature = -1e-20
+
+  ) +
     coord_cartesian(xlim = c(0, 0.25)) +
@@
       plot.title = element_text(hjust = 0.5),
-      panel.grid.major.x = element_line(linetype = "dotted")
+      panel.grid.major.x = element_line(linetype = "dotted"),
+      aspect.ratio = 1
     )
@@
 
-# ggsave(
-#   plot = p_turnover,
-#   filename = "fig_output/p_turnover.pdf",
-#   device = cairo_pdf, # Need this for greek symbols to render correctly
-#   width = 11,
-#   height = 4
-#   )
+ggsave(
+  plot = p_turnover,
+  filename = "fig_output/p_turnover2.pdf",
+  #device = cairo_pdf, # Need this for greek symbols to render correctly
+  width = 11,
+  height = 4
+  )
 

### 2024-07-25 99_BioCrust_Analysis.qmd
biocrust data analysis

--- 2024-07-25 01_LH-SIP_Data_Reduction.Rmd
@@
 ---
-title: "01_LH-SIP_Data_Reduction"
-author: "Tristan Caro"
-date: "`r Sys.Date()`"
-output:
-    html_document:
-    code_folding: show
-    df_print: paged
-    number_sections: yes
-    toc: yes
-    toc_depth: 3
-    toc_float: yes
+title: "99: Biocrust Analysis"
+format: html
+editor: visual
 editor_options: 
@@
 
-## Load Phthalic Acid IRMS Data
-
-```{r}
-# Load PAME Iso Files
-PAME_data_path <- file.path("data", "PAME_data")
-ref_ratio <- get_standard("2H") %>% as.numeric()
-
-# read files
-PAME_iso_files_raw <- 
-  # path to data files
-  PAME_data_path %>% 
-  # read data files in parallel for fast read
-  iso_read_continuous_flow() %>%
-  # filter out files with read errors (e.g. from aborted analysis)
-  iso_filter_files_with_problems()
-
-# Load Peak Map
-
-PAME_peak_map <- 
-  # initial peak map:
-  # readxl::read_excel(file.path("data","IRMS", "peak_map_manual_general.xlsx"))
-  # corrected peak map
-  readxl::read_excel(file.path("data", "PAME_peak_map.xlsx"))
-PAME_peak_map
-
-# process file information
-PAME_iso_files <- PAME_iso_files_raw %>% 
-  # rename key file info columns
-  iso_rename_file_info(analysis = Analysis, id1 = `Identifier 1`, id2 = `Identifier 2`) %>% 
-  # parse text info into numbers
-  iso_parse_file_info(number = analysis) %>% 
-  # process other file information that is specific to the naming conventions
-  # of this particular sequence
-  iso_mutate_file_info(
-    # what is the type of each analysis?
-    type = case_when(
-      str_detect(id1, "[Zz]ero")      ~ "on_off",
-      str_detect(id1, "H3")           ~ "H3_factor",
-      str_detect(id1, "F8")           ~ "F8_std",
-      str_detect(id1, "F9")           ~ "F9_std",
-      TRUE                            ~ "sample"
-    ),
-    # what was the concentration? (assuming Preparation = concentration or volume)
-    concentration = 
-      ifelse(type == "std",  
-             str_extract(Preparation, "[0-9.]+ ?ng( per |/)uL") %>% 
-               parse_number() %>% iso_double_with_units("ng/uL"),
-             NA),
-    # what folder are the data files in? (assuming folder = sequence)
-    folder = basename(dirname(file_path))
-  ) %>% 
-  # focus only on the relevant file info, discarding the rest
-  iso_select_file_info(
-    folder, analysis, file_datetime, id1, type, concentration
-  )
-
-# Peak Mapping
-# set peak table from vendor data table with default isodat template
-PAME_iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(PAME_iso_files) %>% 
-  # convert units from mV to V for amplitudes and area
-  iso_convert_peak_table_units(V = mV, Vs = mVs)
-
-# Create Peak Table and filter out non-PAME samples
-PAME_peak_table <- PAME_iso_files %>%
-  iso_filter_files(str_detect(id1, "PAME")) %>% 
-  # Choose only runs that worked
-  iso_filter_files(str_detect(file_id, "success")) %>% 
-  iso_set_peak_table_from_isodat_vendor_data_table() %>%
-  iso_get_peak_table() %>% 
-  mutate(Analysis = substr(file_id, 1, 7),
-         sample_id = substr(file_id, 10,14))
-
-PAME_peak_mapped <- PAME_peak_table %>%
-  iso_map_peaks(PAME_peak_map, map_id = Analysis) %>%
-  filter(!is.na(compound))
-
-# Summarize the mean and standard error
-PAME_summarized <- PAME_peak_mapped %>%
-  summarize(at2H_mn = mean(at2H),
-            at2H_se = sd(at2H)) %>% 
-  mutate(at2H_mn_ppm = at2H_mn * 10000,
-         at2H_se_ppm = at2H_se * 10000)
-```
-
 ## Load IRMS Data
@@
   )
-
-# set peak table from vendor data table with default isodat template
-iso_files <- iso_set_peak_table_from_isodat_vendor_data_table(iso_files) %>% 
-  # convert units from mV to V for amplitudes and area
-  iso_convert_peak_table_units(V = mV, Vs = mVs)
-
-# focus on sample files
-sample_files <- iso_filter_files(iso_files, type == "sample")
-
-# Include only sample files
-sample_files <- iso_filter_files(sample_files, id1 %in% sample_names)
-
-# EXCLUDE CRC SAMPLES FROM THIS ANALYSIS
-sample_files <- iso_filter_files(sample_files, str_detect(id1, "cri", negate = TRUE))
-
-sample_files <- iso_filter_files(sample_files, str_detect(id1, "cr0", negate = TRUE))
-
-# EXCLUDE RUN WE'VE DEEMED PROBLEMATIC
-sample_files <- iso_filter_files(sample_files, !analysis %in% problematic_analyses_num)
-
 ```
 
-Show file information
+```{r}
+sample_files <- iso_filter_files(iso_files, type == "sample")
+sample_files <- iso_filter_files(sample_files, str_detect(id1, "cr"))
+```
+
+# Load GC-FID data
 
 ```{r}
-# display file information
-iso_files %>% 
-  iso_get_file_info() %>% select(-file_id, -folder) %>% 
-  iso_make_units_explicit() %>% knitr::kable()
-```
-
-### Example chromatogram
-
-```{r "example_chromatograms", fig.width=8, fig.height=8}
-# plot an example chromatogram
-
-# sample_files[10] %>% # choosing arbitrary file to plot
-# iso_plot_continuous_flow_data(
-#   # select data and aesthetics
-#   data = c(2), color = id1, panel = id1,
-#   # zoom in on time interval
-#   time_interval = c(750, 4000),
-#   # peak labels for all peaks > 2V
-#   peak_bounds = TRUE,
-#   peak_marker = FALSE,
-#   peak_label = iso_format(rt),
-#   #peak_label_size = 3,
-#   peak_label_filter = analysis == 5685 & amp2 > 1
-# ) + scale_color_npg() + 
-#   theme_classic() +
-#   theme(strip.background = element_blank())
-```
-
-## Load GC-FID Data
-
-```{r}
-root <- file.path("data", "gc_fid_data_2021")
+root <- file.path("data", "biocrust_FID_data", "2021-06-11_TAC_FAMEs_cr0f0x-m0f3zF3")
 file_list = list.files(path = root)
@@
     integration_results = map(data, "integration_results")
-  ) %>% select(-data)
-```
+  ) %>% select(-data) |> 
+  filter(str_detect(sample,))
 
-### Unnest FID integration details and clean
-
-```{r}
+# Unnest the data
 FID_results <- FID_all_data %>% 
@@
          ) %>% 
-  filter(!id1 %in% c("cr0f0x", "cr0f0y", "cr0f0z",
+  filter(id1 %in% c("cr0f0x", "cr0f0y", "cr0f0z",
                      "cr0f3x", "cr0f3y", "cr0f3z",
@@
 
-# Data Reduction
-
-### Reduce data and get linear model
+# Join FID and memory-corrected IRMS data
 
 ```{r}
-# Find Fatty acid analytes manually
-
-fas_in_d2H_assim <- d2H_assim %>% 
-  filter(str_detect(Analyte, "acid") |
-           str_detect(Analyte, "ate")) %>% 
-  pull(Analyte) %>% 
-  unique()
-
-d2H_assim_lm <- d2H_assim %>% 
-  # Select columns of interest
-  select(
-    org_id,
-    exp_id,
-    Analyte,
-    `Water dD`,
-    `Lipid dD`
-  ) %>% 
-  # Filter to only look at FAs
-  filter(Analyte %in% fas_in_d2H_assim) %>% 
-  drop_na() %>% 
-  # Group by organism, experiment, analyte
-  group_by(
-    org_id,
-    exp_id,
-    Analyte
-  ) %>% 
-  # Filter out samples with three or fewer observations
-  # (so that we can do a linear model)
-  filter(n() > 3) %>% 
-  tidyr::nest(
-    data = c(`Water dD`, `Lipid dD`)
-  ) %>% 
+joined <- LH_SIP_memcorr |> 
+  left_join(FID_results, join_by(sample_id, compound)) |> 
+  select(sample_id, compound, calibrated_at2H_with_memory_correction, calibrated_at2H_with_memory_correction_se, area2, area_FID) |> 
+  # add in incubation times
   mutate(
-    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
-    estimates = purrr::map(fit, broom::tidy),
-    summary = purrr::map(fit, broom::glance)
-  ) %>% tidyr::unnest(estimates)
-
-# Simplify by only looking at the slopes
-# This is what gets added to the peaks_mapped dataframes!
-d2H_assim_lm_summary <- d2H_assim_lm %>% 
-  ungroup() %>% 
-  filter(term == "`Water dD`") %>% 
-  filter(estimate >= 0,
-         estimate <= 1) %>% 
-  summarize(sa = sd(estimate, na.rm = TRUE),
-            a_mn = mean(estimate, na.rm = TRUE))
-```
-
-## FID Data
-
-```{r compound_abundance}
-# Compute the instrument response for each run:
-# Response = µg per unit area using 10µg of PAIBE as quantification STD
-
-FID_results_PAIBE_ug <- FID_results %>% 
-  select(
-    sample_id, 
-    file,
-    compound,
-    area_FID, 
-    rel_area_FID
-  ) %>% 
-  filter(compound == "PAIBE") %>% 
+    inc_time_d = case_when(
+      sample_id == "cri0" ~ 0,
+      sample_id == "cri3" ~ 3,
+      sample_id == "cri5" ~ 5,
+      sample_id == "cri7" ~ 7,
+      sample_id == "cr0f0x" ~ 0,
+      sample_id == "cr0f0y" ~ 0,
+      sample_id == "cr0f3x" ~ 3,
+      sample_id == "cr0f3y" ~ 3,
+      sample_id == "cr0f7x" ~ 7,
+      sample_id == "cr0f7y" ~ 7,
+      )
+  ) |> 
   mutate(
-    PAIBE_area = area_FID,
-    PAIBE_ug_inj = 0.1, # PAIBE injected = (10µg/100µL*1µL) = 0.1µg
-    # Find instrument response as PAIBE mass per FID area
-    ug_per_area = PAIBE_ug_inj / PAIBE_area,
-    # Check that the inferred mass is the same as known mass
-    PAIBE_ug_inj_inferred = ug_per_area * PAIBE_area
-  ) %>%
-  select(file, PAIBE_area, PAIBE_ug_inj, ug_per_area)
+    light_condition = case_when(
+      str_detect(sample_id, "cri") ~ "Sun",
+      str_detect(sample_id, "cr0") ~ "Dark"
+    )
+  ) |> 
+  # average out replicates
+  group_by(sample_id, compound, inc_time_d, light_condition) |> 
+  summarize(
+    calibrated_at2H_with_memory_correction = mean(calibrated_at2H_with_memory_correction),
+    calibrated_at2H_with_memory_correction_se = mean(calibrated_at2H_with_memory_correction_se),
+    area2 = mean(area2, na.rm = TRUE),
+    area_FID = mean(area_FID, na.rm = TRUE)
+  ) |> 
+  ungroup()
 
@@
 
-### Calculate mass of analyte injected into GC-FID
+Separate out the timepoint zero data, average it for an average t0 at2H value
+```{r}
+t0_data <- joined |> 
+  filter(inc_time_d == 0) |> 
+  summarize(t0_at2H = mean(calibrated_at2H_with_memory_correction),
+            t0_at2H_se = mean(calibrated_at2H_with_memory_correction_se))
+```
 
-```{r response}
-# Put the response info back into the abundance data frame:
-FID_results_abundance <- 
-  left_join(
-    FID_results, 
-    FID_results_PAIBE_ug, 
-    by = "file"
-    ) %>%
-  # Calculate the quantity of analyte injected based off of area and 
-  # instrument response
+Import our label strength data
+
+```{r}
+FL_data <- read_csv("data/Label_2H_Data/dD_summarized.csv") |> 
+  filter(soil == "Crust") |> 
+  select(F_label_mn, F_label_se)
+```
+
+Import assim dataset
+```{r}
+d2H_assim <- readRDS("cache/d2H_assimilation.RDS")
+```
+
+Combine the datasets, create the abundance-weighted mean dataset
+
+```{r}
+pre_calculation_df <- joined |> 
+  bind_cols(t0_data) |> 
+  bind_cols(FL_data) |> 
+  bind_cols(d2H_assim) |> 
+  # apply area filter: 3Vs or greater!
+  filter(area2 > 3)
+
+# create abundance-weighted mean
+weighted_df <- pre_calculation_df |> 
+  ungroup() |> 
+  group_by(sample_id, inc_time_d, light_condition) |> 
   mutate(
-    compound_ug_inj = area_FID * ug_per_area,
-    inj_vol_ul = 1, # GC-FID injection volume µL
-    susp_vol_ul = 100, # suspension volume µL
-    # The mass of analyte in vial is the concentration of analyte (mass 
-    # seen per unit volume injected) times the suspension volume.
-    compound_ug_vial = (compound_ug_inj * inj_vol_ul) * susp_vol_ul
+    relative_weight = area_FID / sum(area_FID, na.rm = TRUE)
+  ) |> 
+  summarize(
+    at2H_weighted = 
+      sum(calibrated_at2H_with_memory_correction * relative_weight, na.rm = TRUE) /
+      sum(relative_weight, na.rm = TRUE),
+    at2H_weighted_se = 
+      sum(calibrated_at2H_with_memory_correction_se * relative_weight, na.rm = TRUE) /
+      sum(relative_weight, na.rm = TRUE),
+    at2H_t0_weighted = 
+      sum(t0_at2H * relative_weight, na.rm = TRUE) /
+      sum(relative_weight, na.rm = TRUE)
+  ) |> 
+  ungroup() |> 
+  mutate(compound = "Weighted Mean")
+```
+
+Plot it:
+```{r}
+p_dF <- pre_calculation_df |> 
+  ggplot(
+    aes(
+      x = inc_time_d,
+      y = calibrated_at2H_with_memory_correction,
+      color = compound
+    )
+  ) +
+  geom_line(
+    data = weighted_df,
+    aes(y = at2H_weighted),
+    color = "black",
+    size = 1
+  ) +
+  geom_point(
+    data = weighted_df,
+    aes(y = at2H_weighted),
+    color = "black",
+    size = 3
+  ) +
+  geom_line(alpha = 0.5) +
+  geom_point(size = 2) +
+  scale_color_brewer(palette = "Set1") +
+  facet_wrap(vars(light_condition)) +
+  scale_x_continuous(breaks = c(0, 3, 7)) +
+  labs(
+    x = "Incubation Time (days)",
+    y = latex2exp::TeX("$^2F$")
+  ) +
+  theme_bw() +
+  theme(
+    panel.grid = element_blank(),
+    strip.background = element_blank()
   )
 
-```
+p_dF
 
-### Calculate fractional derivatization efficiency (21-PC)
-```{r 21_PC}
-FID_results_abundance_21 <- FID_results_abundance %>% 
-  filter(compound == "21:0 (STD)") %>% 
-  # Derivatization efficiency is the amount of standard observed divided by 
-  # the amount of standard added (21:0 PC = 10µg)
-  mutate(
-    STD21_ug = 10,
-    deriv_efficiency = compound_ug_vial / STD21_ug
-  ) %>% 
-  select(file, STD21_ug, deriv_efficiency)
-
-# Add deriv efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance, 
-    FID_results_abundance_21, 
-    by = "file"
-  ) %>% 
-  # Calculate mass of fatty acids in extraction mixture as
-  # compounds present as FAMEs multiplied by derivatization efficiency
-  mutate(compound_ug_ext = compound_ug_vial / deriv_efficiency)
-```
-
-### Calculate extraction efficiency (23-PC)
-
-```{r 23_PC}
-FID_results_abundance_23 <- FID_results_abundance %>% 
-  filter(compound == "23:0 (STD)") %>% 
-  # Lipid Recovery Efficiency is the amount of initial standard 
-  # observed divided by the amount of standard added (23:0 PC = 100ug)
-  mutate(
-    STD23_ug = 100,
-    extr_efficiency = compound_ug_vial / STD23_ug
-  ) %>% 
-  select(file, STD23_ug, extr_efficiency)
-
-# Add extr efficiency back into results data frame
-FID_results_abundance <- 
-  left_join(
-    FID_results_abundance,
-    FID_results_abundance_23,
-    by = "file"
-  ) %>% 
-  mutate(
-    # Calculate amount of analyte in soil sample
-    compound_ug_soil_sample = compound_ug_ext / extr_efficiency,
-    # Calculate amount of analyte per gram of soil (3g was used for each extraction)
-    soil_mass_g = 10, # 10 g of each soil were used for this study
-    compound_ug_per_g_soil = compound_ug_soil_sample / soil_mass_g
+cowplot::save_plot(
+  filename = "biocrust_figs/p_dF.pdf",
+  plot = p_dF, base_height = 4, base_width = 6
 )
@@
 
-### Remove standards from soil abundances
+# Calculate turnover
 
 ```{r}
-# Remove standards from soil abundances
 
-FID_results_abundance_no_stds <- FID_results_abundance %>% 
-  filter(
-    !compound %in% c("21:0 (STD)", "23:0 (STD)", "PAIBE"),
-    str_detect(sample_id, "FAME", negate = TRUE),
-    str_detect(sample_id, "BAME", negate = TRUE)
+turnover <- pre_calculation_df |> 
+  # CORRECT MC'd data so that it never is less than natural abundance at2H
+  ungroup() |>                           # Evaluate each row individually
+  mutate(
+    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
+    u_d = calculate_turnover(
+      a = a_mn,                      # Assimilation efficiency
+      FT = calibrated_at2H_with_memory_correction,                   # 2F at time t (at%)
+      F0 = t0_at2H,               # 2F at t0 (at%)
+      FL = F_label_mn,               # 2F of label (at%)
+      t = inc_time_d                     # change in time (days)
+      ),
+
+    # Calculate uncertainty in turnover rate
+    su_d = calculate_sigma_mu(
+      a = a_mn,                      # Assimilation efficiency
+      F_T = calibrated_at2H_with_memory_correction,                   # 2F at time t (at%)
+      F_0 = t0_at2H,               # 2F at t0 (at%)
+      F_L = F_label_mn,               # 2F of label (at%)
+      t = inc_time_d,                     # change in time (days)
+      # Uncertainties:
+      sF_0 = t0_at2H_se,       # uncertainty in IRMS measurement
+      sF_L = F_label_se,        # uncertainty in label strength
+      # uncertainty in FT due to memory-effect calculation:
+      sF_T = calibrated_at2H_with_memory_correction_se, 
+      sa = sa # uncertainty in assimilation efficiency
+    )
+  )
+
+weighted_turnover <- weighted_df |> 
+  ungroup() |> 
+  mutate(
+    u_d = calculate_turnover(
+      a = 0.7069045,                      # Assimilation efficiency
+      FT = at2H_weighted,                   # 2F at time t (at%)
+      F0 = at2H_t0_weighted,               # 2F at t0 (at%)
+      FL = 0.48385,               # 2F of label (at%)
+      t = inc_time_d                     # change in time (days)
+    ),
+    su_d = calculate_sigma_mu(
+      a = 0.7069045,                      # Assimilation efficiency
+      F_T = at2H_weighted,                   # 2F at time t (at%)
+      F_0 = at2H_t0_weighted,               # 2F at t0 (at%)
+      F_L = 0.48385,               # 2F of label (at%)
+      t = inc_time_d,                     # change in time (days)
+      # Uncertainties:
+      sF_0 = 0.01739246,       # uncertainty in IRMS measurement
+      sF_L = 0.007610569,        # uncertainty in label strength
+      # uncertainty in FT due to memory-effect calculation:
+      sF_T = at2H_weighted_se, 
+      sa = 0.1716424 # uncertainty in assimilation efficiency
+    )
+  )
+
+turnover_combined <- turnover |> 
+  bind_rows(weighted_turnover) |> 
+  mutate(
+    gen_d = log(2) / u_d
   )
@@
 
-## IRMS Peak Mapping
+Plot it:
+```{r}
+p_ud <- turnover_combined |> 
+  mutate(
+    is_wm = case_when(compound == "Weighted Mean" ~ TRUE)
+  ) |> 
+  filter(inc_time_d != 0) |> 
+  mutate(
+    compound = fct_reorder(compound, u_d)
+  ) |> 
+  ggplot(
+    aes(
+      y = compound,
+      x = u_d,
+      fill = is_wm
+    )
+  ) +
+  geom_text(
+    #data = function(df) df |> filter(is_wm),
+    aes(label = paste(round(gen_d, 0))),
+    x = 0.35,
+    size = 3
+  ) +
+  geom_pointrange(
+    aes(
+      xmin = u_d - su_d,
+      xmax = u_d + su_d
+    ),
+    shape = 21,
+    color = "black"
+  ) +
+  facet_wrap(vars(light_condition, inc_time_d), ncol = 1) +
+  coord_cartesian(xlim = c(0, 0.37)) +
+  scale_fill_manual(values = c("#f56042", "black")) +
+  labs(
+    x = latex2exp::TeX("Biomass growth rate $(day^{-1})$"),
+    y = ""
+  ) +
+  theme_classic() +
+  theme(
+    strip.background = element_blank(),
+    legend.position = "None"
+    )
+p_ud
 
-```{r}
-sample_peak_table <- sample_files %>%
-  iso_set_peak_table_from_isodat_vendor_data_table() %>%
-  iso_get_peak_table() %>% 
-  mutate(Analysis = substr(file_id, 1, 7),
-         sample_id = substr(file_id, 10,14))
-```
-
-### Generate Isoverse peak map
-```{r}
-# Generate an isoverse peak map
-peaks_mapped <- sample_peak_table %>%
-  iso_map_peaks(peak_map, map_id = Analysis) %>%
-  filter(!is.na(compound))
-```
-
-### Remove readychecks, blanks, etc. from analysis
-```{r}
-# Filter based on what is in the sample_names metadata
-peaks_mapped <- peaks_mapped %>% 
-  filter(sample_id %in% sample_names)
-
-# Filter out runs that are on our problematic_runs list
-peaks_mapped <- peaks_mapped %>% 
-  filter(!Analysis %in% problematic_runs)
-```
-
-### Check problematic peak assignments
-```{r}
-problem_peaks <- iso_get_problematic_peak_mappings(peaks_mapped)
-```
-
-### Export summary of unresolved peaks
-```{r}
-# Spit out peaks that need to be resolved
-peaks_mapped %>%
-  ungroup() %>%
-  select(Analysis, compound, rt) %>%
-  mutate(rt = round(rt, digits=0)) %>%
-  pivot_wider(
-    names_from = Analysis, 
-    names_prefix = "rt:",
-    values_from = rt, 
-    id_cols = compound, 
-    values_fn = function(x) paste(x, collapse = "; ")
-  ) %>%
-  openxlsx::write.xlsx(file.path("data", "IRMS", "peak_maps_resolve.xlsx"))
-```
-
-## Metadata and cleanup
-
-### Assign incubation params
-```{r}
-# Add Some Parameters
-peaks_mapped <- peaks_mapped %>% 
-  group_by(sample_id) %>% 
-  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
-         inc_time_d_str = paste(inc_time_d, "Days"),
-         f_label = 0.005,
-         t_series_id = paste0(substr(sample_id, 1,1), 
-                              substr(sample_id, 5,5)),
-         soil_id = substr(t_series_id, 1,1),
-         replicate_id = substr(t_series_id, 2,2),
-         terrain = case_when(
-           substr(sample_id, 1, 1) == "t" ~ "Niwot Ridge Tundra",
-           substr(sample_id, 1 ,1) == "c" ~ "Gordon Gulch Conifer Forest",
-           substr(sample_id, 1 ,1) == "m" ~ "Gordon Gulch Meadow",
-           substr(sample_id, 1 ,1) == "g" ~ "Marshall Mesa Grassland"))
-# 
-# inc_time_zero <- peaks_mapped %>% 
-#   filter(inc_time_d == 0) %>% 
-#   select(sample_id, compound, at2H, t_series_id) %>% 
-#   mutate(f_start = at2H) %>% 
-#   select(-at2H)
-# 
-#
-
-```
-
-### Join memory-corrected data
-
-```{r}
-peaks_mapped_mc <- peaks_mapped %>% 
-# Need to remove "BF" from Analysis number
-  mutate(Analysis = parse_number(Analysis)) %>%
-  select(-c(area2, area3)) %>% 
-  # Join
-  left_join(
-    LH_SIP_memcorr, 
-    by = c("Analysis", "sample_id", "compound"))
-```
-
-### Extract zero timepoint values
-These SIP measurements compare an enriched isotopic value to a starting isotopic composition. To have a time `t = 0` value, we need to define the starting point of our incubation.
-
-```{r}
-zero_peaks <- peaks_mapped_mc %>%
-  filter(inc_time_d_str == "0 Days") %>%
-  group_by(t_series_id, compound) %>%
-  mutate(n_analyical_reps = n()) %>%
-  ungroup() %>%
-  # exclude ambiguous peaks
-  filter(!is_ambiguous)
-
-zero_peaks_averaged <- zero_peaks %>% 
-  group_by(soil_id, compound) %>% 
-  summarise(
-    # at2H at zero (no mc)
-    at2H_mn_zero = mean(calibrated_at2H_without_memory,
-                        na.rm = TRUE),
-    # Memory corrected value
-    at2H_mn_zero_mc = mean(calibrated_at2H_with_memory_correction, 
-                           na.rm = TRUE),
-    # d2H at zero (no mc)
-    d2H_mn_zero = mean(calibrated_d2H_without_memory, 
-                       na.rm = TRUE),
-    # Memory corrected value
-    d2H_mn_zero_mc = mean(calibrated_d2H_with_memory_correction, 
-                          na.rm = TRUE))
-
-# Cache the zero-timepoint dataframe
-zero_peaks_averaged %>% 
-  openxlsx::write.xlsx(
-    file.path("cache", 
-              "zero_peaks_averaged.xlsx"),
-    overwrite = TRUE)
-
-# This is the dataset we will use for generation time calculations
-peaks_mapped_with_zeros <- 
-  peaks_mapped_mc %>%
-  left_join(
-    zero_peaks_averaged,
-    by = c("soil_id", "compound")
+cowplot::save_plot(
+  filename = "biocrust_figs/p_ud.pdf",
+  p_ud, base_height = 6, base_width = 6
 )
-stopifnot(nrow(peaks_mapped_with_zeros) == nrow(peaks_mapped_mc))
-
-peaks_mapped_with_zeros <- peaks_mapped_with_zeros %>% 
-  mutate(sample_id = substr(file_id, 10,14))
-```
-
-## Join IRMS and GC-FID Data
-
-```{r}
-# peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>% 
-#   left_join(FID_results, by = c("sample_id", "compound"))
-
-peaks_mapped_with_zeros_FID <- peaks_mapped_with_zeros %>%
-  left_join(
-    FID_results_abundance_no_stds, 
-    by = c("sample_id", "compound")
-  )
-```
-
-## Apply corrections
-
-### Correct for PAME
-
-Correcting for the isotopic composition of the derivatization agent by measuring phthalic acid methyl ester (PAME).
-
-```{r}
-
-peaks_mapped_with_zeros_FID_mc_pame <- peaks_mapped_with_zeros_FID %>% 
-  left_join(compound_nC_nH, by = "compound") %>% 
-  mutate(`2F_Me` = PAME_summarized %>% pull(at2H_mn),
-         # define calibrated 2F
-         `2F_FAME` = calibrated_at2H_without_memory,
-         `2F_alk` = (`2F_FAME` - `2F_Me`*x_me) / x_alk,
-         # define calibrated 2F mc
-         `2F_FAME_mc` = calibrated_at2H_with_memory_correction,
-         `2F_alk_mc` = (`2F_FAME_mc` - `2F_Me`*x_me) / x_alk)
-```
-
-### Separate analytes and standards, calculate F_0 standard error
-
-```{r}
-# For 0-3,0-7 timepoints
-# Analytes
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID_mc_pame %>% 
-  # Don't want our standard compounds to be used for generation time calculations! x_x
-  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
-  # Also don't want our yeast-extract stimulated condition in our analyte pool
-  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
-  # Add in label strengths
-  left_join(F_L_2F, by = "terrain")
-
-# Standards
-peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID_mc_pame %>% 
-  filter(str_detect(compound, "STD"))
-
-# 23:0 and 21:0 PC standard errors at inc time zero
-# Determines our standard error in FAME measurements at F_0
-sF_0 <- peaks_mapped_with_zeros_standards %>% 
-  # Select only 21 and 23 PC standards at initial time point
-  filter(compound %in% c("21:0 (STD)"),
-         inc_time_d == 0) %>%
-  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
-  ungroup() %>% 
-  summarize(F_0_at2H_mn = mean(at2H),
-            F_0_at2H_se = sd(at2H))
-
-# Add sF_0 to analyte data
-
-peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
-  mutate(F_0_at2H_se = sF_0 %>% pull(F_0_at2H_se))
-
-```
-
-### Eliminate extraneous columns
-
-```{r}
-# Reduce the 0d --> 3d --> 7d incubation data
-peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>%
-  # Add assimilation efficiency data
-  mutate(
-    a = d2H_assim_lm_summary$a_mn,
-    sa = d2H_assim_lm_summary$sa
-  ) %>% 
-  # REPAIR out-of-area t=0 datapoints:
-  mutate(
-    calibrated_at2H_with_memory_correction =
-      case_when(
-        below_area_range == TRUE & inc_time_d == 0 ~ at2H_mn_zero,
-        TRUE ~ calibrated_at2H_with_memory_correction
-        ),
-    below_area_range = 
-      case_when(
-        below_area_range == TRUE & inc_time_d == 0 ~ FALSE,
-        below_area_range == TRUE ~ TRUE,
-        below_area_range == FALSE ~ FALSE
-      )
-  ) %>% 
-  # REMOVE peaks that are outside area range of accurate correction!
-  filter(below_area_range == FALSE) %>% 
-  # Column reduction
-  select(Analysis,
-         sample_id,
-         terrain,
-         soil,
-         inc_time_d,
-         inc_time_d_str,
-         compound,
-         area_FID,
-         rel_area_FID,
-         rt,
-         d2H_mn_zero,
-         d2H,
-         at2H_mn_zero,
-         at2H_mn_zero_mc, # MC
-         at2H, # not-corrected value
-         calibrated_at2H_without_area, # F_T, no area corr
-         calibrated_at2H_without_memory, # F_T, no memcorr
-         calibrated_at2H_with_memory_correction, # F_T, MC!
-         area2,
-         area3,
-         area_FID,
-         compound_ug_per_g_soil,
-         a, # assimilation efficiency
-         `2F_Me`,
-         `2F_FAME`,
-         `2F_FAME_mc`, # MC
-         `2F_alk`,
-         `2F_alk_mc`,  # MC
-         F_label_mn,
-         # Uncertainty terms:
-         F_label_se, # error in the label strength (pipetting error)
-         F_0_at2H_se, # error in the initial F_0 (instrument error)
-         calibrated_at2H_without_area_se, # error in F_T, no area corr
-         calibrated_at2H_without_memory_se, # error in F_T, no memcorr
-         calibrated_at2H_with_memory_correction_se, # error in F_T, MC!
-         sa, # error in assimilation efficiency (se of literature values)
-  ) %>% 
-  # Turn all unit dbls into unitless
-  mutate(
-    across(
-      where(is.numeric),
-      as.numeric
-    )
-  ) %>% 
-  # Rename FAs to match correctly ID'd analytes
-  rename_FAs()
-
-```
-
-```{r}
-LH_SIP_memcorr <- LH_SIP_memcorr %>% rename_FAs()
 ```
@@
 ```{r}
-# Export as RDS
-
-# Peak data
-saveRDS(peaks_mapped_with_zeros_analytes_reduced,
-        file = "cache/LH_SIP_data.RDS")
-
-# Label 2F
-saveRDS(F_L_2F,
-        file = "cache/heavy_label_data.RDS")
-
-# Assimilation Efficiency Linear Model
-saveRDS(d2H_assim_lm_summary,
-        file = "cache/d2H_assimilation.RDS")
-
-# Asssimilation Efficiency data
-saveRDS(d2H_assim_lm,
-        file = "cache/d2H_assimilation_lm.RDS")
-
-# Standard Error of IRMS measurements at time zero
-saveRDS(sF_0,
-        file = "cache/sF_0.RDS")
-
-# Memory-corrected data
-saveRDS(LH_SIP_memcorr,
-        file = "cache/LH_SIP_memcorr.RDS")
-
-# Full dataset
-saveRDS(sample_files, 
-        file = "cache/sample_files.RDS")
-
-# Export dataset for SI
-writexl::write_xlsx(
-  peaks_mapped_with_zeros_analytes_reduced %>% 
-    filter(compound != "H2"),
-  path = "cache/LH_SIP_data.xlsx"
-  )
+writexl::write_xlsx(LH_SIP_memcorr, path = "biocrust_figs/biocrust_raw.xlsx")
+writexl::write_xlsx(turnover_combined, path = "biocrust_figs/biocrust_turnover_data.xlsx")
 ```
